### 2018-08-08 manuscript/figures_and_tables.tex
add figures and tables

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}

% Format
\usepackage{layout}

% Font
\usepackage{MinionPro}
\input glyphtounicode
\pdfgentounicode=1
\usepackage{microtype}
\usepackage[super]{nth}
\usepackage{tfrupee}

% Language
\usepackage[british]{babel}

% References
\usepackage[nosectionbib, tocbib, unnumberedbib]{apacite}

% Figures
\usepackage{graphicx}
\usepackage{caption}
\graphicspath{ {figures/} }

% Tables
\usepackage{booktabs}
\usepackage{tabularx}

% Commands
\newcommand{\pest}[4]{$ \text{Pr} (\text{``us''} | \text{#1}) = #2$, $[#3, #4]$}
\newcommand{\pdif}[4]{$ \Delta\text{Pr} (\text{``us''} | \text{#1}) = #2$, $[#3, #4]$}

\begin{document}

% Captions
\captionsetup[figure]{font={small},labelfont={it},labelformat={default}, labelsep=period}
\captionsetup[table]{font={small},labelfont={it},labelformat={default}, labelsep=period}

\section*{Figures}

\begin{figure}[h]
\centering
%\includegraphics[scale=1]{../figures/ch4-s4-2}
\caption[Estimated probabilities of participants' categorizing a target as ``us'' versus ``not us'']{Estimated probability of participants categorizing a target as ``us'' versus ``not us'' by targets' index (\#), nationality, religion, and caste (vertical), and participants' caste membership (horizontal). Dots (•) indicate the most likely \emph{estimate} for a given target's probability of inclusion (in Model~2, see Table~\ref{tab:ch4-s4-3}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most likely estimates of that probability. Pluses (+) indicate the \emph{observed} proportion of participants who included a target in their ingroup.}
\label{fig:f1}
\end{figure}

\section*{Tables}

\begin{table}[h]
\caption[Participants by gender, age, nationality, religion, and caste]{Participants by gender, age, nationality, religion, and caste. Categories in \textit{italics} were excluded from the final sample. N/A indicates missing responses.}
\centering
\figureversion{lining, tabular}
\small	
\begin{tabular}{llrr} \addlinespace \toprule
\multicolumn{2}{l}{Category} & $n$ & \% \\ \midrule \addlinespace 
Gender      & Woman      & 215 & 61 \\
            & Man & 121 & 34 \\
            & Other & 0 & 0 \\
            & N/A & 15 & 4 \\ \addlinespace \addlinespace
Age         & 18--20 & 1 & 0 \\
            & 21--23 & 254 & 72 \\
            & 24--26 &  77 & 22 \\
            & 27--29 &  10 &  3 \\
            & 30--32 &   1 &  0 \\
            & 36 or older & 1 & 0 \\ 
            & N/A & 7 & 2 \\ \addlinespace \addlinespace
Nationality & Indian & 339 & 97 \\
            & Other & 0 & 0 \\
            & N/A & 12 & 3 \\ \addlinespace \addlinespace
Religion    & Buddhism & 1 & 0 \\ 
            & Christianity & 11 & 3 \\ 
            & Hinduism & 297 & 85 \\ 
            & \textit{Islam} & \textit{27} & \textit{8} \\ 
            & Jainism & 8 & 2 \\ 
            & Other & 2 & 1 \\ 
            & N/A & 5 & 1 \\ \addlinespace \addlinespace
Caste       & General Caste & 104 & 30 \\ 
            & Other Backward Class & 143 & 41 \\ 
            & Scheduled Caste & 54 & 15 \\ 
            & Scheduled Tribe & 23 & 7 \\ 
            & \textit{Other / Not applicable} & \textit{20} & \textit{6} \\ 
            & \textit{N/A} & \textit{7} & \textit{2} \\ \addlinespace \midrule
Total       &   & 351 & 100 \\ \bottomrule
\end{tabular}
\label{tab:ch4-s4-1}
\end{table}

\end{document}

### 2018-08-08 data/impute_data.R

@@ -9,12 +9,6 @@ rm(list = ls())
   # Stan options
   options(mc.cores = parallel::detectCores())
   seed = 70475734
-  
-
-# Functions ---------------------------------------------------------------
-  # Standardise variables
-  x_scale   <- function(v, y = v) (v - mean(y, na.rm = TRUE)) / sd(y, na.rm = TRUE)
-  x_unscale <- function(v, y) v * sd(y, na.rm = TRUE) + mean(y, na.rm = TRUE)
 
 
 # Import ------------------------------------------------------------------
@@ -29,82 +23,72 @@ rm(list = ls())
     ig_scst = ifelse(ig_caste == "scst", 1L, 0L)
   ) %>% select(
     participant, ig_obc, ig_scst, q4:q23, q60_1:q60_8
-  ) %>% mutate_at(
-    vars(q4:q60_8), x_scale
+  ) %>% gather("item", "response", -participant)
+  
+  # Standardise variables
+  d_imp <- d_imp %>% left_join(
+    d_imp %>% 
+      group_by(item) %>% 
+      summarise_at(vars(response), funs(mean, sd), na.rm = TRUE), 
+    by = "item"
+  ) %>% mutate(
+    i = 1:n(),
+    x = (response - mean) / sd
   )
   
   # Compose data list
   data_list <- list(
-    # Matrix
-    X = d_imp %>% select(-participant) %>% data.matrix(),
     # Numbers
-    N_row = nrow(X),
-    N_col = ncol(X),
-    N_obs = length(X[!is.na(X)]),
-    N_mis = length(X[is.na(X)]),
+    N_row = n_distinct(d_imp$participant),
+    N_col = n_distinct(d_imp$item),
+    N_mis = sum(is.na(d_imp$x)),
+    N_obs = sum(!is.na(d_imp$x)),
     # Indices
-    ii_obs = matrix(1:length(X), nrow = nrow(X), ncol = ncol(X))[!is.na(X)],
-    ii_mis = matrix(1:length(X), nrow = nrow(X), ncol = ncol(X))[is.na(X)],
+    ii_mis = d_imp$i[is.na(d_imp$x)],
+    ii_obs = d_imp$i[!is.na(d_imp$x)],
     # Vectors
-    x_obs   = X[!is.na(X)],
[…]

### 2018-08-08 import_data.R

@@ -143,6 +143,9 @@ rm(list = ls())
   # Assign each participant an unambigious id
   d1 <- d1 %>% mutate(participant = paste(session, participant, sep = ""))
   d2 <- d2 %>% mutate(participant = paste(session, participant, sep = ""))
+  
+  # Rename target and index to make column names clearer.
+  d1 <- d1 %>% rename(order = target, target = index)
 
 
 # Export ------------------------------------------------------------------

### 2018-08-08 prepare_data.R

@@ -18,7 +18,7 @@ rm(list = ls())
 
   
 # Participants ------------------------------------------------------------
-  # Count religion, caste (before exclusion)
+  # Count religion, caste (after exclusion)
   d2 %>% count(q36)
   d2 %>% count(q37)
   
@@ -42,15 +42,15 @@ rm(list = ls())
   # Code target categories
   d1 <- d1 %>% mutate(
     category = case_when(
-      index <= 4 ~ 1L,
-      index <= 8 ~ 2L,
-      index <=12 ~ 3L,
-      index <=16 ~ 4L,
-      index <=20 ~ 5L,
-      index <=24 ~ 6L
+      target <= 4 ~ 1L,
+      target <= 8 ~ 2L,
+      target <=12 ~ 3L,
+      target <=16 ~ 4L,
+      target <=20 ~ 5L,
+      target <=24 ~ 6L
     )
   ) %>% left_join(d2 %>% select(participant, ig_caste)) %>% select(
-    session:index, category, lname:caste, ig_caste, everything()
+    session:target, category, lname:caste, ig_caste, everything()
   )
 
 

### 2018-08-13 manuscript/figures_and_tables.tex
method

@@
 \centering
-%\includegraphics[scale=1]{../figures/ch4-s4-2}
-\caption[Estimated probabilities of participants' categorizing a target as ``us'' versus ``not us'']{Estimated probability of participants categorizing a target as ``us'' versus ``not us'' by targets' index (\#), nationality, religion, and caste (vertical), and participants' caste membership (horizontal).
-Dots (•) indicate the most likely \emph{estimate} for a given target's probability of inclusion (in Model~2, see Table~\ref{tab:ch4-s4-3}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most likely estimates of that probability.
-Pluses (+) indicate the \emph{observed} proportion of participants who included a target in their ingroup.}
+\includegraphics[scale=1]{../figure-1}
+\caption{Examples of targets used in the triple crossed-categorization task.
+\ldots ($N = 26$) \ldots The targets' ages and silhouettes, as well as the order in which they were presented, varied across sessions.}
 \label{fig:f1}
 \end{figure}
+
+%\begin{figure}[h]
+%\centering
+%%\includegraphics[scale=1]{../figures/ch4-s4-2}
+%\caption{Estimated probability of participants categorizing a target as ``us'' versus ``not us'' by targets' index (\#), nationality, religion, and caste (vertical), and participants' caste membership (horizontal).
+Dots (•) indicate the most likely \emph{estimate} for a given target's probability of being included in participants' ingroup (in Model~2, Table~\ref{tab:2}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most likely estimates of that probability.
+Pluses (+) indicate the \emph{observed} proportion of participants who included a target in their ingroup.}
+%\label{fig:f2}
+%\end{figure}
 
@@
 Categories in \textit{italics} were excluded from the final sample.
-N/A indicates missing responses.}
+N/A marks missing responses.}
 \centering
@@
             & 30--32 &   1 &  0 \\
+            & 33--35 &   0 &  0 \\
             & 36 or older & 1 & 0 \\ 

### 2018-08-13 import_data.R

@@ -1,8 +1,11 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-  #  See materials/script.pdf (Appendix D) for items and answer options.
-  # Remove raw data .csv before publishing.
+  # See materials/script.pdf (Appendix D) for items and answer options.
+
+  # To protect participants, we do not provide the raw data (data/sessions/)
+  # with verbatim comments; this R script is thus not functional. Please import 
+  # data/d1_raw.rds and data/d2_raw.rds directly.
 
 
 # Library -----------------------------------------------------------------

### 2018-08-13 models_for_group_differences.R

@@ -1,0 +1,83 @@
+rm(list = ls())
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(tidybayes); library(rstan); library(loo)
+
+  # Stan options
+  options(mc.cores = parallel::detectCores())
+  rstan_options(auto_write = TRUE)
+  seed = 0892561437
+
+
+# Import ------------------------------------------------------------------
+  dl <- read_rds("data/d1.rds") %>%
+        filter(!is.na(q1))
+  
+  # Compose data list
+  data_list <- with(dl, list(
+    N = length(participant),
+    J = n_distinct(participant),
+    K = n_distinct(category),
+    jj = participant,
+    kk = category,
+    scst = ifelse(ig_caste == "scst", 1L, 0L),
+    obc = ifelse(ig_caste == "obc", 1L, 0L),
+    y = q1
+  ))
+
+
+# Models ------------------------------------------------------------------
+  # Model: Varying Intercept (Participant)
+  m0_stan <- stan("models/q1_m0.stan", data = data_list, seed = seed,
+                  iter = 2000, warmup = 1000, 
+                  pars = c("alpha"), include = FALSE)
+  
+  # Model: + Varying Intercept (Target: Category)
+  m1_stan <- stan("models/q1_m1.stan", data = data_list, seed = seed,
+                  iter = 2000, warmup = 1000, 
+                  pars = c("alpha"), include = FALSE)
+  
+  # Model: + Participant: SCST * Target: Category (4)
+  m2_stan <- stan("models/q1_m2.stan", data = data_list, seed = seed,
+                  iter = 2000, warmup = 1000, 
+                  pars = c("alpha"), include = FALSE)
+  
+  # Model: + Participant: OBC * Target: Category (4)
+  m3_stan <- stan("models/q1_m3.stan", data = data_list, seed = seed,
+                  iter = 2000, warmup = 1000, 
+                  pars = c("alpha"), include = FALSE)
+
+  # Export
+  mc_fit <- list(m0_stan, m1_stan, m2_stan, m3_stan)
+  write_rds(mc_fit, "models/mc_fit_group_differences.rds")
+
+# Compare -----------------------------------------------------------------
[…]

### 2018-08-13 prepare_data.R

@@ -53,7 +53,37 @@ rm(list = ls())
     session:target, category, lname:caste, ig_caste, everything()
   )
 
+  # Convert participant id to integer
+  d1 <- d1 %>% mutate(participant = as.integer(ordered(participant)))
+  d2 <- d2 %>% mutate(participant = as.integer(ordered(participant)))
+  
 
 # Export ------------------------------------------------------------------
   write_rds(d1, "data/d1.rds")
   write_rds(d2, "data/d2.rds")
+  
+  
+# Prepare -----------------------------------------------------------------
+  # Impute missing data (predictor variables)
+  # source("data/impute_data.R") 
+  # This takes a long time; import read_rds("data/d2_impute.rds") instead.
+  
+  # Prepare data for analyses
+  source("data/prepare_data_ic.R")
+  source("data/prepare_data_sdo.R")
+  source("data/prepare_data_it.R")
+  
+  # Compile data for analyses
+  # d1
+  # d1_pred
+  # d2_it
+  # d2_ps
+
+# Export ------------------------------------------------------------------
+  write_rds(d1, "data/d1_with_predictors.rds")
+  write_rds(d2_it, "data/d2_intergroup_threat.rds")
+  
+  # Export to other formats
+  # write_csv(d1, "data/export/d1.csv")
+  # write_csv(d1_pred, "data/export/d1_with_predictors.csv")
+  # write_csv(d2, "data/export/d2.csv")

### 2018-08-14 manuscript/figures_and_tables.tex
figure 2

@@
 \captionsetup[table]{font={small},labelfont={it},labelformat={default}, labelsep=period}
-
-\section*{Figures}
-
-\begin{figure}[h]
-\centering
-\includegraphics[scale=1]{../figure-1}
-\caption{Examples of targets used in the triple crossed-categorization task.
-\ldots ($N = 26$) \ldots The targets' ages and silhouettes, as well as the order in which they were presented, varied across sessions.}
-\label{fig:f1}
-\end{figure}
-
-%\begin{figure}[h]
-%\centering
-%%\includegraphics[scale=1]{../figures/ch4-s4-2}
-%\caption{Estimated probability of participants categorizing a target as ``us'' versus ``not us'' by targets' index (\#), nationality, religion, and caste (vertical), and participants' caste membership (horizontal).
-Dots (•) indicate the most likely \emph{estimate} for a given target's probability of being included in participants' ingroup (in Model~2, Table~\ref{tab:2}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most likely estimates of that probability.
-Pluses (+) indicate the \emph{observed} proportion of participants who included a target in their ingroup.}
-%\label{fig:f2}
-%\end{figure}
-
-\section*{Tables}
 
@@
 \end{tabular}
-\label{tab:ch4-s4-1}
+\label{tab:t1}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-1}
+\caption{Examples of targets used in the triple crossed-categorization task.
+Based on ratings in pilot study ($N = 26$), we selected the four most prototypical targets (out of fifty initial targets) for each of six plausible combinations of caste, religion, and nationality (for details, see Appendix~A).
+Each target showed a person's caste (GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe), religion (Hindu, Muslim), and nationality (Indian, Nepali, Sri Lankan, Bangladeshi).
+Each target also showed the person's first and last name, age (21--26 years), and a silhouette corresponding to the person's gender (adapted from Ma, Correll \& Wittenbrink, 2015).
+Each target's age and silhouette, as well as the order in which the targets were presented, varied across sessions.}
+\label{fig:f1}
+\end{figure}
+
+\begin{table}
+\caption{}
+\centering
+\figureversion{lining, tabular}
+\small	
+\begin{tabularx}{\linewidth}{r@{~}rXrrrrr} \toprule
+\# &  & Description & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
+0 &      & \ldots & -4262.5 & 33.0 & - & - & - \\
+1 & vs 0 & \ldots & -3156.0 & 46.7 & 1106.6 & 42.7 & 25.9 \\
+2 & vs 1 & \ldots & -3073.5 & 47.3 &   82.5 & 11.9 &  6.9 \\
+3 & vs 2 & \ldots & -3068.1 & 47.4 &    5.4 &  3.4 &  1.6 \\ \midrule
+4 & vs 2 & \ldots & . & . & . & . & . \\
+5 & vs 4 & \ldots & . & . & . & . & . \\
+6 & vs 5 & \ldots & . & . & . & . & . \\
+7 & vs 2 & \ldots & . & . & . & . & . \\
+\bottomrule
+\end{tabularx}
+\label{tab:t2}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-2}
+\caption{
+Estimated probability of participants categorizing a target as ``us'' versus ``not us'' by targets' nationality, religion, and caste (vertical), and participants' caste membership (horizontal).
+Dots (•) indicate the most likely \emph{estimate} for a given target's probability of being included in participants' ingroup (in Model~2, Table~\ref{tab:t2}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most likely estimates of that probability.
+Pluses (+) indicate the \emph{observed} proportion of participants who included a given target in their ingroup.
+% Add sentence about posterior predictive checking.
+}
+\label{fig:f2}
+\end{figure}
+
+\begin{figure}
+\centering
+%\includegraphics[scale=1]{../figures/figure-3}
+\caption{Estimated probability of participants categorising a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship (in Model~5, Table~\ref{tab:t2}).}
+\label{fig:f3}
+\end{figure}
+
+\begin{table}
+\caption{}
+\centering
+\figureversion{lining, tabular}
+\small	
+\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrr} \toprule
+\# &  & Description & $R^2_\text{Q2}$ & $R^2_\text{Q3}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
+0 &      & \ldots & . & . & . & . & . & . & . \\
+1 & vs 0 & \ldots & . & . & . & . & . & . & . \\
+2 & vs 1 & \ldots & . & . & . & . & . & . & . \\
+3 & vs 2 & \ldots & . & . & . & . & . & . & . \\ \midrule
+4 & vs 3 & \ldots & . & . & . & . & . & . & . \\
+5 & vs 4 & \ldots & . & . & . & . & . & . & . \\
+6 & vs 5 & \ldots & . & . & . & . & . & . & . \\
+\bottomrule
+\end{tabularx}
+\label{tab:t3}
 \end{table}

### 2018-08-14 figures/figure-2.R

@@ -1,0 +1,132 @@
+rm(list = ls())
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(tidybayes)
+
+
+# Import ------------------------------------------------------------------
+  # Observed proportions
+  dl   <- read_rds("data/d1.rds") %>% 
+          filter(!is.na(q1)) %>%
+          mutate(ig_caste = recode_factor(
+            ig_caste, "gm" = "GM", "obc" = "OBC", "scst" = "SC/ST", .ordered = TRUE
+          )) %>%
+          mutate(caste = recode_factor(
+            caste, "GM" = "GM", "OBC" = "OBC", "SCST" = "SC/ST", "N/A" = NA_character_, .ordered = TRUE
+          ))
+  
+  # Estimated probabilites
+  post <- read_rds("models/q1_post.rds") %>%
+          unnest(p_est) %>%
+          mutate(ig_caste = recode_factor(
+            ig_caste, "1" = "GM", "2" = "OBC", "3" = "SC/ST", .ordered = TRUE
+          ))
+  
+
+# Summarise ---------------------------------------------------------------
+  # Observed proportions
+  d_obs <- dl %>% 
+    group_by(target, category, lname, nation, religion, caste, ig_caste) %>%
+    summarise(p_obs = mean(q1))
+  
+  # Estimated probabilities
+  d_est <- post %>%
+    rename(p_est = p_k) %>%
+    group_by(model, category, ig_caste) %>%
+    median_hdi(.width = c(.67, .89, .97))
+
+
+# Plot --------------------------------------------------------------------
+  p1 <- d_est %>%
+    left_join(d_obs, ., by = c("category", "ig_caste")) %>%
+    filter(model == 2) %>%
+  ggplot(., aes(x = target, y = p_est, ymin = .lower, ymax = .upper)) +
+    geom_ribbon(aes(group = .width), fill = "white", colour = NA) +
+    geom_ribbon(aes(fill = ig_caste, group = 1-.width), colour = NA, alpha = 0.20) +
+    geom_path(aes(colour = ig_caste)) +
+    geom_point(aes(y = p_obs), shape = 3, colour = "grey60") +
+    geom_point(aes(colour = ig_caste)) +
+    geom_vline(xintercept = c(4.5, 8.5, 12.5, 16.5, 20.5), colour = "white", size = 2) +
+    geom_vline(xintercept = 0.5, colour = "black") +
[…]

### 2018-08-14 models_for_group_differences.R

@@ -1,83 +1,0 @@
-rm(list = ls())
-
-# Library -----------------------------------------------------------------
-  library(tidyverse); library(tidybayes); library(rstan); library(loo)
-
-  # Stan options
-  options(mc.cores = parallel::detectCores())
-  rstan_options(auto_write = TRUE)
-  seed = 0892561437
-
-
-# Import ------------------------------------------------------------------
-  dl <- read_rds("data/d1.rds") %>%
-        filter(!is.na(q1))
-  
-  # Compose data list
-  data_list <- with(dl, list(
-    N = length(participant),
-    J = n_distinct(participant),
-    K = n_distinct(category),
-    jj = participant,
-    kk = category,
-    scst = ifelse(ig_caste == "scst", 1L, 0L),
-    obc = ifelse(ig_caste == "obc", 1L, 0L),
-    y = q1
-  ))
-
-
-# Models ------------------------------------------------------------------
-  # Model: Varying Intercept (Participant)
-  m0_stan <- stan("models/q1_m0.stan", data = data_list, seed = seed,
-                  iter = 2000, warmup = 1000, 
-                  pars = c("alpha"), include = FALSE)
-  
-  # Model: + Varying Intercept (Target: Category)
-  m1_stan <- stan("models/q1_m1.stan", data = data_list, seed = seed,
-                  iter = 2000, warmup = 1000, 
-                  pars = c("alpha"), include = FALSE)
-  
-  # Model: + Participant: SCST * Target: Category (4)
-  m2_stan <- stan("models/q1_m2.stan", data = data_list, seed = seed,
-                  iter = 2000, warmup = 1000, 
-                  pars = c("alpha"), include = FALSE)
-  
-  # Model: + Participant: OBC * Target: Category (4)
-  m3_stan <- stan("models/q1_m3.stan", data = data_list, seed = seed,
-                  iter = 2000, warmup = 1000, 
-                  pars = c("alpha"), include = FALSE)
-
-  # Export
-  mc_fit <- list(m0_stan, m1_stan, m2_stan, m3_stan)
-  write_rds(mc_fit, "models/mc_fit_group_differences.rds")
-
-# Compare -----------------------------------------------------------------
[…]

### 2018-08-14 results_group_differences.R

@@ -1,0 +1,108 @@
+rm(list = ls())
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(tidybayes); library(rstan); library(loo)
+
+  # Stan options
+  options(mc.cores = parallel::detectCores())
+  rstan_options(auto_write = TRUE)
+  seed = 0892561437
+
+
+# Import ------------------------------------------------------------------
+  dl <- read_rds("data/d1.rds") %>%
+        filter(!is.na(q1))
+  
+  # Compose data list
+  data_list <- with(dl, list(
+    N = length(participant),
+    J = n_distinct(participant),
+    K = n_distinct(category),
+    jj = participant,
+    kk = category,
+    scst = ifelse(ig_caste == "scst", 1L, 0L),
+    obc = ifelse(ig_caste == "obc", 1L, 0L),
+    y = q1
+  ))
+
+
+# Models ------------------------------------------------------------------
+  # Model: Varying Intercept (Participant)
+  m0_stan <- stan("models/q1_m0.stan", data = data_list, seed = seed,
+                  iter = 2000, warmup = 1000, 
+                  pars = c("alpha"), include = FALSE)
+  
+  # Model: + Varying Intercept (Target: Category)
+  m1_stan <- stan("models/q1_m1.stan", data = data_list, seed = seed,
+                  iter = 2000, warmup = 1000, 
+                  pars = c("alpha"), include = FALSE)
+  
+  # Model: + Participant: SCST * Target: Category (4)
+  m2_stan <- stan("models/q1_m2.stan", data = data_list, seed = seed,
+                  iter = 2000, warmup = 1000, 
+                  pars = c("alpha"), include = FALSE)
+  
+  # Model: + Participant: OBC * Target: Category (4)
+  m3_stan <- stan("models/q1_m3.stan", data = data_list, seed = seed,
+                  iter = 2000, warmup = 1000, 
+                  pars = c("alpha"), include = FALSE)
+
+
+# Compare -----------------------------------------------------------------
+  # Compare models
[…]

### 2018-08-16 manuscript/figures_and_tables.tex
use imputed data

@@
 %\includegraphics[scale=1]{../figures/figure-3}
-\caption{Estimated probability of participants categorising a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship (in Model~5, Table~\ref{tab:t2}).}
+\caption{Estimated probability of participants categorising a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship with the relevant groups         (in Model~5, Table~\ref{tab:t2}).}
 \label{fig:f3}

### 2018-08-16 data/impute_data.R

@@ -1,94 +1,0 @@
-rm(list = ls())
-
-# Notes -------------------------------------------------------------------
-
-
-# Library -----------------------------------------------------------------
-  library(tidyverse); library(rstan); library(tidybayes)
-
-  # Stan options
-  options(mc.cores = parallel::detectCores())
-  seed = 70475734
-
-
-# Import ------------------------------------------------------------------
-  d2 <- read_rds("data/d2.rds")
-
-  
-# Prepare -----------------------------------------------------------------
-  # Prepare variables for imputation
-  d_imp <- d2 %>% mutate(
-    ig_gm   = ifelse(ig_caste ==   "gm", 1L, 0L),
-    ig_obc  = ifelse(ig_caste ==  "obc", 1L, 0L),
-    ig_scst = ifelse(ig_caste == "scst", 1L, 0L)
-  ) %>% select(
-    participant, ig_obc, ig_scst, q4:q23, q60_1:q60_8
-  ) %>% gather("item", "response", -participant)
-  
-  # Standardise variables
-  d_imp <- d_imp %>% left_join(
-    d_imp %>% 
-      group_by(item) %>% 
-      summarise_at(vars(response), funs(mean, sd), na.rm = TRUE), 
-    by = "item"
-  ) %>% mutate(
-    i = 1:n(),
-    x = (response - mean) / sd
-  )
-  
-  # Compose data list
-  data_list <- list(
-    # Numbers
-    N_row = n_distinct(d_imp$participant),
-    N_col = n_distinct(d_imp$item),
-    N_mis = sum(is.na(d_imp$x)),
-    N_obs = sum(!is.na(d_imp$x)),
-    # Indices
-    ii_mis = d_imp$i[is.na(d_imp$x)],
-    ii_obs = d_imp$i[!is.na(d_imp$x)],
-    # Vectors
-    x_obs   = d_imp$x[!is.na(d_imp$x)]
-  )
-  
-
-# Model -------------------------------------------------------------------
-  # Initial values
-  X <- d_imp %>% select(participant, item, x) %>% spread(item, x) %>% select(-participant) %>% data.matrix()
-  estimates <- function(X, N_mis, perturb = FALSE){
-    if(perturb) X <- X + rnorm(length(X), 0, 1)
-    x_mu    <- rep(0, 30)
-    x_sigma <- rep(1, 30)
-    x_mis   <- rnorm(N_mis, 0, 1)
-    Lcorr   <- t(chol(cor(X, use = "pairwise.complete")))
[…]

### 2018-08-16 data/prepare_data_intergroup_contact.R

@@ -1,0 +1,38 @@
+# Import Part 1 data (long)
+dl <- read_rds("data/d1.rds") %>%
+  filter(!is.na(q1)) %>%
+  mutate(og = case_when(
+    category == 1 & ig_caste == "gm" ~ 0L,
+    category == 2 & ig_caste == "obc" ~ 0L,
+    category == 3 & ig_caste == "scst" ~ 0L,
+    TRUE ~ 1L
+  )) %>%
+  arrange(participant, target)
+
+# Import Part 2 data (intergroup contact)
+d2_imp <- read_rds("data/d2_impute.rds") %>%
+  group_by(participant, category, item, missing) %>%
+  summarise(x_imp = mean(z_response), x_imp_sd = sd(z_response)) %>%
+  mutate(x_imp_sd = ifelse(missing, x_imp_sd, 0)) %>%
+  ungroup()
+
+# Merge Part 1 and Part 2 data (intergroup contact)
+dl <- d2_imp %>%
+  select(participant, category, item, x_imp) %>%
+  spread(item, x_imp) %>%
+  left_join(dl, ., by = c("participant", "category"))
+
+# Prepare imputed data (intergroup contact)
+dl_imp <- dl %>%
+  select(participant, target, category, cq:of) %>%
+  gather(item, x_imp, cq:of) %>%
+  mutate(
+    ii = 1:n(),
+    item = ordered(item, levels = c("cq", "pc", "nc", "of"))
+  ) %>% 
+  left_join(
+    d2_imp %>% select(-x_imp), 
+    by = c("participant", "category", "item")
+  ) %>% 
+  select(ii, participant:item, missing, x_imp, x_imp_sd) %>%
+  replace_na(list(x_imp = -99, missing = FALSE, x_imp_sd = 0))

### 2018-08-16 data/prepare_data_it.R

@@ -1,17 +1,0 @@
-# Notes -------------------------------------------------------------------
-  #  See materials/script.pdf (Appendix D) for items and answer options.
-
-
-# Library -----------------------------------------------------------------
-  library(tidyverse)
-
-
-# Functions ---------------------------------------------------------------
-
-
-  
-# Import ------------------------------------------------------------------
-
-
-
-# Export ------------------------------------------------------------------

### 2018-08-16 impute_data.R

@@ -1,0 +1,164 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+  # This script imputes missing responses (n = 66) to the intergroup contact
+  # variables, and returns a data frame with both observed responses and 
+  # draws from the posterior distribution for missing responses. 
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(rstan); library(tidybayes)
+
+  # Stan options
+  options(mc.cores = parallel::detectCores())
+  rstan_options(auto_write = TRUE)
+  seed = 70475734
+
+
+# Import ------------------------------------------------------------------
+  d2 <- read_rds("data/d2.rds") %>%
+        select(participant, ig_caste, q4:q23)
+  
+  # Prepare data (long format)
+  dl <- d2 %>%
+    gather("item", "response", q4:q23) %>%
+    mutate(item = str_extract(item, "[0-9]+") %>% as.integer()) %>% 
+    arrange(participant, item) %>%
+    mutate(ii = 1:n()) %>%
+    select(ii, participant, item, response)
+  
+  # Prepare data (wide format)
+  dw <- d2 %>%
+    mutate(
+      x_obc = ifelse(ig_caste == "obc", 1L, 0L),
+      x_scst = ifelse(ig_caste == "scst", 1L, 0L)
+    ) %>%
+    select(participant, x_obc, x_scst) %>%
+    arrange(participant)
+  
+  # Summarise
+  ds <- dl %>% 
+    group_by(item) %>% 
+    summarise_at(vars(response), funs(mean, sd), na.rm = TRUE)
+  
+  # Compose data list
+  data_list <- list(
+    # Numbers
+    N_row = n_distinct(dl$participant),
+    N_col = n_distinct(dl$item),
+    N_mis = sum(is.na(dl$response)),
+    N_obs = sum(!is.na(dl$response)),
+    # Indices
+    ii_mis  = dl$ii[is.na(dl$response)],
+    ii_obs  = dl$ii[!is.na(dl$response)],
+    ii_item = dl$item[!is.na(dl$response)] - 3,
+    # Vectors
+    x_obc = dw$x_obc,
+    x_scst = dw$x_scst,
+    x_mean = ds$mean,
+    x_sd = ds$sd,
+    x_obs = dl$response[!is.na(dl$response)]
+  )
+  
[…]

### 2018-08-16 prepare_data.R

@@ -64,26 +64,6 @@ rm(list = ls())
   
   
 # Prepare -----------------------------------------------------------------
-  # Impute missing data (predictor variables)
-  # source("data/impute_data.R") 
-  # This takes a long time; import read_rds("data/d2_impute.rds") instead.
-  
   # Prepare data for analyses
-  source("data/prepare_data_ic.R")
-  source("data/prepare_data_sdo.R")
-  source("data/prepare_data_it.R")
-  
-  # Compile data for analyses
-  # d1
-  # d1_pred
-  # d2_it
-  # d2_ps
-
-# Export ------------------------------------------------------------------
-  write_rds(d1, "data/d1_with_predictors.rds")
-  write_rds(d2_it, "data/d2_intergroup_threat.rds")
-  
-  # Export to other formats
-  # write_csv(d1, "data/export/d1.csv")
-  # write_csv(d1_pred, "data/export/d1_with_predictors.csv")
-  # write_csv(d2, "data/export/d2.csv")
+  # source("data/prepare_data_sdo.R")
+  # source("data/prepare_data_it.R")

### 2018-08-16 results_group_differences.R

@@ -20,8 +20,8 @@ rm(list = ls())
     K = n_distinct(category),
     jj = participant,
     kk = category,
-    scst = ifelse(ig_caste == "scst", 1L, 0L),
-    obc = ifelse(ig_caste == "obc", 1L, 0L),
+    x_scst = ifelse(ig_caste == "scst", 1L, 0L),
+    x_obc = ifelse(ig_caste == "obc", 1L, 0L),
     y = q1
   ))
 
@@ -95,14 +95,3 @@ rm(list = ls())
   
   # Export
   write_rds(post, "models/q1_post.rds")
-  
-  # post %>%
-  #   unnest(p_est) %>%
-  #   mutate(model = ordered(model)) %>%
-  #   group_by(model, category, ig_caste) %>%
-  #   # median_hdi(.width = .80) %>%
-  # ggplot(., aes(y = category, x = p_k)) +
-  #   geom_halfeyeh(aes(group = model, fill = model, colour = model)) +
-  #   scale_fill_viridis_d(alpha = 0.25) +
-  #   scale_y_reverse(breaks = 1:6) +
-  #   facet_grid(. ~ ig_caste)

### 2018-08-16 results_individual_differences.R

@@ -1,0 +1,90 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+  # Explain that you use single imputation (best guess) for intergroup contact
+  # because missingness is negligible (n = 66 out of ...) and explain how it doesn't make a difference.
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(tidybayes); library(rstan); library(loo)
+
+  # Stan options
+  options(mc.cores = parallel::detectCores())
+  rstan_options(auto_write = TRUE)
+  seed = 0892561437
+
+
+# Import ------------------------------------------------------------------
+  source("prepare_data_intergroup_contact.R")
+
+  # Compose data list
+  data_list <- list(
+    # Numbers
+    N_row = nrow(dl),
+    N_col = n_distinct(dl_imp$item),
+    N_mis = sum(dl_imp$missing),
+    N_obs = sum(!dl_imp$missing),
+    J = n_distinct(dl$participant),
+    K = n_distinct(dl$category),
+    # Indices
+    ii_mis  = dl_imp$ii[dl_imp$missing],
+    ii_obs  = dl_imp$ii[!dl_imp$missing],
+    jj = dl$participant,
+    kk = dl$category,
+    # Vectors
+    x_scst = ifelse(dl$ig_caste == "scst", 1L, 0L),
+    x_obc = ifelse(dl$ig_caste == "obc", 1L, 0L),
+    x_og = dl$og,
+    x_imp_m  = dl_imp$x_imp[dl_imp$missing],
+    x_imp_sd = dl_imp$x_imp_sd[dl_imp$missing], 
+    x_obs = dl_imp$x_imp[!dl_imp$missing],
+    y = dl$q1
+  )
+
+
+# Models ------------------------------------------------------------------
+  # Model: 
+  m4_stan <- stan("models/q1_m4.stan", data = data_list, seed = seed,
+                  iter = 2000, warmup = 1000,
+                  pars = c("alpha", "x", "X", "x_imp"), include = FALSE)
+  
+  # Model: 
+  m5_stan <- stan("models/q1_m5.stan", data = data_list, seed = seed,
+                  iter = 2000, warmup = 1000,
+                  pars = c("alpha", "x", "X", "x_imp"), include = FALSE)
+  
+  # Model: 
[…]

### 2018-09-13 manuscript/figures_and_tables.tex
update

--- 2018-08-14 manuscript/figures_and_tables.tex
@@
-\documentclass[12pt,a4paper]{article}
+\documentclass[12pt, a4paper]{article}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{layout}
+\setlength{\parindent}{0.5in}
+\setcounter{secnumdepth}{0}
+\usepackage{lineno}
 
@@
 \usepackage{graphicx}
-\usepackage{caption}    
-\graphicspath{ {figures/} }
+\usepackage[small, labelfont=it, labelsep=period]{caption}
 
@@
 
+% Frontmatter
+\title{Intergroup contact fosters\\more inclusive social identities}
+\date{August 23, 2018}
+
 \begin{document}
 
-% Captions
-\captionsetup[figure]{font={small},labelfont={it},labelformat={default}, labelsep=period}
-\captionsetup[table]{font={small},labelfont={it},labelformat={default}, labelsep=period}
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-1}
+\caption{
+Schematic representations of social identity structures, ordered by social identity inclusiveness.
+Shaded regions represent the groups which a participant has to categorize as ``us'' to be assigned that structure.
+An Indian Hindu, for example, may consider only people who share their nationality, religion, and caste as ingroup members (intersection).
+Someone else may consider all their fellow Indians, whatever their religion or caste, as ingroup members (dominance).
+Another person may consider anyone who shares their nationality or religion as ingroup members (merger).
+}
+\label{fig:f1}
+\end{figure}
 
-\begin{table}[h]
+\begin{table}    
 \caption[Participants by gender, age, nationality, religion, and caste]{Participants by gender, age, nationality, religion, and caste.
@@
 \centering
-\includegraphics[scale=1]{../figures/figure-1}
+\includegraphics[scale=1]{../figures/figure-2}
 \caption{Examples of targets used in the triple crossed-categorization task.
-Based on ratings in pilot study ($N = 26$), we selected the four most prototypical targets (out of fifty initial targets) for each of six plausible combinations of caste, religion, and nationality (for details, see Appendix~A).
+Based on ratings in a pilot study ($N = 26$), we selected the four most prototypical targets (out of fifty initial targets) for each of six plausible combinations of caste, religion, and nationality (for details, see Appendix~A).
 Each target showed a person's caste (GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe), religion (Hindu, Muslim), and nationality (Indian, Nepali, Sri Lankan, Bangladeshi).
@@
 Each target's age and silhouette, as well as the order in which the targets were presented, varied across sessions.}
-\label{fig:f1}
+\label{fig:f2}
 \end{figure}
@@
 \begin{table}
-\caption{}
+\caption{
+Comparison of models estimating the probability of participants categorising targets as ``us'' versus ``not us''.
+$\textit{ELPD}$ is the expected log predictive density, with higher numbers indicating that a model is expected to make more accurate out-of-sample predictions (Vehtari, Gelman, \& Gabry, 2017).
+$\Delta\textit{ELPD}$ is the difference in $\textit{ELPD}$ between the current and previous model, with positive values indicating that the current model is expected to make more accurate out-of-sample predictions.
+We selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.
+% Appendix~X describes all models in detail.
+}
 \centering
@@
 \# &  & Description & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
-0 &      & \ldots & -4262.5 & 33.0 & - & - & - \\
-1 & vs 0 & \ldots & -3156.0 & 46.7 & 1106.6 & 42.7 & 25.9 \\
-2 & vs 1 & \ldots & -3073.5 & 47.3 &   82.5 & 11.9 &  6.9 \\
-3 & vs 2 & \ldots & -3068.1 & 47.4 &    5.4 &  3.4 &  1.6 \\ \midrule
-4 & vs 2 & \ldots & . & . & . & . & . \\
-5 & vs 4 & \ldots & . & . & . & . & . \\
-6 & vs 5 & \ldots & . & . & . & . & . \\
-7 & vs 2 & \ldots & . & . & . & . & . \\
+0 &      & Varying intercept (Participant) & -4262.7 & 33.1 & - & - & - \\
+1 & vs 0 & Varying intercept (Category) & -3156.2 & 46.6 & 1106.5 & 42.7 & 25.9 \\
+2 & vs 1 & Group differences (SC/ST) & -3074.5 & 47.3 &   81.7 & 12.0 &  6.8 \\
+3 & vs 2 & Group differences (OBC) & -3069.2 & 47.4 &    5.3 &  3.4 &  1.7 \\ \midrule
+4 & vs 2 & Intergroup contact (4) & -3047.6 & 47.5 &   26.9 &  8.2 &  3.3 \\
+5 & vs 4 & Intergroup contact (2) & -3045.4 & 47.5 &    2.2 &  0.4 &  5.5 \\
+6 & vs 5 & Intergroup contact (OBC, SC/ST) & -3048.9 & 47.5 &   -3.4 &  2.5 & -1.4 \\
+7 & vs 2 & Social dominance orientation & -3076.0 & 47.5 &   -1.5 &  1.5 & -1.0 \\
 \bottomrule
@@
 \centering
-\includegraphics[scale=1]{../figures/figure-2}
+\includegraphics[scale=1]{../figures/figure-3}
 \caption{
 Estimated probability of participants categorizing a target as ``us'' versus ``not us'' by targets' nationality, religion, and caste (vertical), and participants' caste membership (horizontal).
-Dots (•) indicate the most likely \emph{estimate} for a given target's probability of being included in participants' ingroup (in Model~2, Table~\ref{tab:t2}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most likely estimates of that probability.
+Dots (•) indicate the most plausible \emph{estimate} for a given target's probability of being included in participants' ingroup (in Model~2, Table~\ref{tab:t2}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most plausible estimates of that probability.
 Pluses (+) indicate the \emph{observed} proportion of participants who included a given target in their ingroup.
-% Add sentence about posterior predictive checking.
+Comparing predicted and observed proportion shows that the model represents the data reasonably well.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
 }
-\label{fig:f2}
+\label{fig:f3}
 \end{figure}
@@
 \centering
-%\includegraphics[scale=1]{../figures/figure-3}
-\caption{Estimated probability of participants categorising a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship (in Model~5, Table~\ref{tab:t2}).}
-\label{fig:f3}
+\includegraphics[scale=1]{../figures/figure-4}
+\caption{Estimated probability of participants categorising a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship with the relevant groups (in Model~5, Table~\ref{tab:t2}).
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.}
+\label{fig:f4}
 \end{figure}
@@
 \begin{table}
-\caption{}
+\caption{Comparison of models estimating participants' social distance (SD) and feeling thermometer (FT) ratings for each target as a function of group differences and target categorizations.
+As in Table~\ref{tab:t2}, we selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.
+$R^2$ is a Bayesian analogue to $R^2$ in maximum likelihood estimation (Gelman, Goodrich, Gabry, \& Ali, 2017).}
 \centering
@@
 \begin{tabularx}{\linewidth}{r@{~}rXrrrrrrr} \toprule
-\# &  & Description & $R^2_\text{Q2}$ & $R^2_\text{Q3}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
-0 &      & \ldots & . & . & . & . & . & . & . \\
-1 & vs 0 & \ldots & . & . & . & . & . & . & . \\
-2 & vs 1 & \ldots & . & . & . & . & . & . & . \\
-3 & vs 2 & \ldots & . & . & . & . & . & . & . \\ \midrule
-4 & vs 3 & \ldots & . & . & . & . & . & . & . \\
-5 & vs 4 & \ldots & . & . & . & . & . & . & . \\
-6 & vs 5 & \ldots & . & . & . & . & . & . & . \\
+\# &  & Description & $R^2_\text{SD}$ & $R^2_\text{FT}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
+0 &      & \ldots~(Participant) & .23 & .26 & -15203.4 & 111.8 &     - &    - &    - \\
+1 & vs 0 & \ldots~(Category)    & .38 & .42 & -14300.1 & 117.9 & 903.3 & 39.6 & 22.8 \\
+2 & vs 1 & \ldots~(SC/ST)       & .38 & .43 & -14248.7 & 118.2 &  51.4 &  8.8 &  5.8 \\
+3 & vs 2 & \ldots~(OBC)         & .39 & .43 & -14222.2 & 118.4 &  26.5 &  7.2 &  3.7 \\ \midrule
+4 & vs 3 & Categorization       & .42 & .47 & -14004.5 & 120.6 & 217.7 & 22.7 &  9.6 \\
+5 & vs 4 & \ldots~(Category)    & .42 & .47 & -13986.9 & 120.9 &  17.6 &  7.7 &  2.3 \\
+6 & vs 5 & \ldots~(OBC, SC/ST)  & .42 & .47 & -13988.9 & 120.8 &  -2.0 &  3.6 & -0.6 \\
 \bottomrule    
@@
 
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-5}
+\caption{
+Posterior probabilities of social distance ratings as a function of target categorizations (in Model 5, Table~\ref{tab:t3}).
+Points are the estimated mean ratings for targets categorized as ``us''; triangles are the estimated mean ratings for targets categorized as ``not us''.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f5}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-6}
+\caption{
+Posterior probabilities of feeling thermometer ratings as a function of target categorizations (in Model 5, Table~\ref{tab:t3}).
+Points are the estimated mean ratings for targets categorized as ``us''; triangles are the estimated mean ratings for targets categorized as ``not us''.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f6}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-7}
+\caption{
+Posterior probabilities of perceived life difficulty ratings for different target groups (right) by participants' caste ingroup (left).
+Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f7}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-8}
+\caption{
+Posterior probabilities of policy support ratings for different target groups (right) by participants' caste ingroup (left).
+Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f8}
+\end{figure}
+
 \end{document}

### 2018-09-13 manuscript/manuscript.tex
update

--- 2018-09-13 manuscript/figures_and_tables.tex
@@
 
+\maketitle
+
+\begin{abstract}
+\noindent We examined how South Indian students construct their social identities from multiple group memberships---and whether contact with caste and religious outgroups fosters more inclusive social identities.
+Participants ($N = 351$) viewed 24 identity cards, each representing a person with whom participants shared none, one, two, or all three group memberships.
+Participants reported whether they considered each person as ``us'' or ``not us'', showing whom they included in their ingroup, and whom they excluded.
+Using this method, we found that participants tended to exclude caste and religious minorities, replicating persistent social divides.
+Bridging these divides, cross-group friendship was associated with more inclusive identities, while more inclusive identities were associated with more favourable outgroup attitudes.
+Negative contact---but not social dominance orientation---was associated with less inclusive identities, showing that past experiences shaped whom participants considered ``us'' and ``not us''.
+Contact and identity processes were unrelated to support for affirmative action.\\[1ex]
+%\noindent \emph{Keywords:} \ldots\\[1ex]
+\end{abstract}
+
+\linenumbers
+
+\noindent How we feel about and act toward other people depends on whom we consider ``us'' and ``them''---that is, whom we include in our ingroup, and whom we exclude (for a review, see Reimer, Schmid, Hewstone, \& Al Ramiah, in press).
+In some situations, it is clear who is in the ingroup and who is not.
+On a football pitch, for example, players tend to think of their own team as ``us'', and of the other team as ``them'', and try their best to make sure their own team wins.
+In many situations, this distinction is less clear because it rests on multiple category memberships.
+Often, the relevant categories are interrelated.
+Many Americans, for example, associate being American with being White American (Devos \& Banaji, 2005).
+This suggests that whom Americans consider ``us'' and ``them'' might depend on someone's race \emph{and} nationality (and perhaps other categories, such as religion or language).
+In this paper, we examine how people's group memberships shape whom they consider ``us'' and ``not us'', and test what the antecedents and consequences of more inclusive social identities are.
+
+Social psychological theories have argued for the importance of two (Berry, 1997; Crisp \& Hewstone, 2007; Dovidio, Gaertner \& Saguy, 2009) or more (Roccas \& Brewer, 2002) social categories for understanding intergroup relations.
+Broadly, these perspectives recognise that we are part of multiple overlapping groups; that we have a subjective sense of who is ``us'' and ``them'' that goes beyond the objective facts of group membership; and that this identification across multiple categories affects our attitudes toward people with whom we share some, but not all, group memberships.
+However, these perspectives have lacked a method for measuring social identification across multiple overlapping categories.
+
+Addressing this shortcoming, van Dommelen, Schmid, Hewstone, Gonsalkorale, and Brewer (2015) developed the triple crossed-categorization task to measure how individuals construct their social identities from multiple group memberships.
+In this task, participants view identity cards, each of which represents a fictitious person with whom participants share none, one, two, or all of three group memberships.
+Participants report whether they consider each person as ``us'' or ``not us'', showing whom they included in their ingroup, and whom they excluded.
+The researchers analysed participants' responses quantitatively, as social identity inclusiveness, and qualitatively, as social identity structure.
+They operationalised inclusiveness as the total number of targets a participant had categorized as ``us''.
+They coded response patterns according to structures proposed by Roccas and Brewer (2002).
+Figure~\ref{fig:f1} shows schematic representations of various plausible structures, ordered by their inclusiveness.
+
 \begin{figure}
@@
 Another person may consider anyone who shares their nationality or religion as ingroup members (merger).
+% This person has a more inclusive social identity than the other two people.
 }
@@
 \end{figure}
+
+In two studies, van Dommelen et al.
+(2015) studied social identification across ethnicity, religion, and nationality among Turkish-Belgian Muslims and Turkish-Australian Muslims.
+Participants categorized, on average, 59\% and 65\% of targets as ``us'', and endorsed a wide range of social identity structures.
+As the researchers recruited homogeneous samples, they studied individual differences, but not group differences, in social identity inclusiveness.
+Participants' group memberships, however, likely influence whom they consider ``us'' and ``not us''.
+For majority-group members, negotiating their ethnic and national identities likely means something different that for minority-group members (Dovidio et al., 2009).
+As group members share these experiences, we expect that group differences are as great as, if not greater than, individual differences in social identity construals---especially if groups differ in status and power.
+
+Shared experiences, however, make only part of an individual's day-to-day experiences.
+Of these, contact experiences could overcome group differences in social identity construals.
+First, encountering diverse others could initiate a process of cognitive differentiation (Schmid \& Hewstone, 2011) whereby interaction partners become aware of the complex interrelations of their cross-cutting group memberships.
+Second, intergroup interactions can motivate people to include the outgroup of an interaction partner in their self-concept (Page-Gould et al., 2010).
+As far as contact motivates people to include (partial) outgroups in the self, it should encourage social identities that include the inter-action partner's combination of group memberships.
+Together, these mechanisms suggest that intergroup contact could overcome group differences, and foster more inclusive social identities.
+
+Fostering more inclusive identities could reduce intergroup bias.
+Dividing others into “us'' and ``not us'' is a necessary and sufficient condition for in-group favouritism (Tajfel, 1981).
+Considering more people as ``us'' should ex-tend ingroup favouritism to a wider range of people, and thus reduce discrimination (Gaertner et al., 2016).
+Ingroup favouritism can turn into outgroup derogation when an outgroup threatens the ingroup (Brewer, 1999).
+Considering fewer people as ``not us'' should reduce the number of groups which are perceived to threaten the ingroup.
+Together, these mechanisms suggest that more inclusive identities could reduce intergroup bias.
+
+Beyond prejudice, researchers have debated whether fostering more inclusive identities helps or hinders social change.
+Changing attitudes and beliefs is often not enough to overcome structural inequalities.
+Instead, social change requires advantaged and disadvantaged groups to strive for redistributive policies.
+On the one hand, fostering more inclusive identities could break down the boundaries between the advantaged ingroup and the disadvantaged out-group---making injustice faced by ``them'' into ``our'' problem.
+This process could narrow the gap between advantaged-group members' support for the principle of equality and their opposition to its implementation in policies (Dixon, Durrheim \& Tredoux, 2007).
+On the other hand, fostering more inclusive identities could distract disadvantaged-group members from differences in resources and power, and thus reduce their support for social change (Dovidio, Saguy, Gaertner, \& Thomas, 2012).
+Together, these mechanisms suggest that more inclusive identities could increase support for social change among the advantaged, but decrease support among the disadvantaged.
+
+\section{Present research}
+
+In the present research, we examined how South Indian students construct their social identities from the overlapping categories of caste, religion, and nationality.
+Caste is a system of social relations that concentrates status and power in the hands of dominant castes (Jodhka, 2012).
+This system is maintained by restricting subordinate castes' occupations, by barring subordinate castes from owning land, and by enforcing endogamy and segregation.
+This system is underpinned by a tradition that ranks castes according to their supposed ritual purity, and condemns contact with less pure castes as polluting.
+Untouchability excludes some castes from public life, and consigns them to landlessness and menial labour.
+Dalits---members of castes that have been affected by untouchability---still face economic inequalities based on this history of exploitation, as well as interpersonal discrimination based on the practice of untouchability.
+Since Independence, the Indian State has sought to redress caste-based injustices by reserving seats in state-run universities and state-sector jobs for disadvantaged groups.
+Specifically, the Indian State recognises Dalits as Scheduled Castes (SCs), Adivasi---India’s indigenous peoples---as Scheduled Tribes (STs), and other disadvantaged castes (who fall above the so-called `line of pollution') as Other Backward Classes (OBCs).
+Members of historically advantaged castes compete for these opportunities in the General Merit (GM) category.
+Reservation policies, alongside ongoing discrimination, have resulted in caste identities remaining important in electoral politics and political organising.
+
+\section{Method}
 
@@
 
+\section{Results}
+
 \begin{table}
@@
 Estimated probability of participants categorizing a target as ``us'' versus ``not us'' by targets' nationality, religion, and caste (vertical), and participants' caste membership (horizontal).
-Dots (•) indicate the most plausible \emph{estimate} for a given target's probability of being included in participants' ingroup (in Model~2, Table~\ref{tab:t2}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most plausible estimates of that probability.
+Dots (•) indicate the most likely \emph{estimate} for a given target's probability of being included in participants' ingroup (in Model~2, Table~\ref{tab:t2}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most likely estimates of that probability.
 Pluses (+) indicate the \emph{observed} proportion of participants who included a given target in their ingroup.
-Comparing predicted and observed proportion shows that the model represents the data reasonably well.
 GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+% Add sentence about posterior predictive checking.
 }
@@
 \centering
-\includegraphics[scale=1]{../figures/figure-7}
-\caption{
-Posterior probabilities of perceived life difficulty ratings for different target groups (right) by participants' caste ingroup (left).
-Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.
-GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
-}
+%\includegraphics[scale=1]{../figures/figure-7}
+\caption{\ldots GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.}
 \label{fig:f7}
@@
 \centering
-\includegraphics[scale=1]{../figures/figure-8}
-\caption{
-Posterior probabilities of policy support ratings for different target groups (right) by participants' caste ingroup (left).
-Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.
-GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
-}
+%\includegraphics[scale=1]{../figures/figure-8}
+\caption{\ldots GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.}
 \label{fig:f8}
@@
 
+\section{Discussion}
+
 \end{document}

### 2018-09-13 data/determine_sample_size.R

@@ -1,0 +1,88 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+  # Reanalysing data from van Dommelen et al.'s (2015) studies, we found
+  # that 100 responses allowed reasonably precise estimates of the proportion
+  # of "us" categorizations in each of eight target categories. Posterior
+  # probabilities for these estimates had a precision of SD < 0.50 on the 
+  # log odds scale.
+
+  # This R script is included for review purposes only as we are not able to
+  # make the underlying data available.
+
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(rstan); library(tidybayes)
+  
+  # Stan options
+  options(mc.cores = parallel::detectCores())
+  rstan_options(auto_write = TRUE)
+  seeds = c(35702546)
+  
+
+# Import ------------------------------------------------------------------
+  # Import wide format
+  dw <- haven::read_spss("data/old/d_old.sav") %>%
+        haven::zap_formats() %>%
+        select(participant, card1:card24)
+  
+  # Spread to long format
+  dl <- dw %>% 
+        gather("target", "q1", card1:card24) %>%
+        mutate(target = str_extract(target, "[0-9]+")) %>%
+        mutate_at(vars(target, q1), as.integer) %>%
+        arrange(participant, target)
+  
+  # Exclude completely missing cases
+  dl <- dl %>%
+        group_by(participant) %>%
+        mutate(missing = sum(is.na(q1))) %>%
+        filter(missing < 24) %>%
+        ungroup() %>%
+        select(-missing)
+  
+
+# Bootstrap ---------------------------------------------------------------
+  # Bootstrap a sample of n = 100
+  dl <- dl %>%
+        spread(target, q1) %>%
+        sample_n(size = 100, replace = TRUE) %>%
+        mutate(participant = 1:n()) %>%
+        gather("target", "q1", -participant)
+  
+  # Code target categories
+  dl <- dl %>% mutate(
+    category = case_when(
+      target %in% 1:6   ~ 1L,
+      target %in% 7:8   ~ 2L,
+      target %in% 9:10  ~ 3L,
+      target %in% 11:12 ~ 4L,
+      target %in% 13:14 ~ 5L,
+      target %in% 15:16 ~ 6L,
+      target %in% 17:18 ~ 7L,
+      target %in% 19:24 ~ 8L
+    )
+  )
+  
+  # Compose data list
+  data_list <- list(
[…]

### 2018-09-13 data/prepare_data_ic.R

@@ -17,7 +17,9 @@
 
 # Merge Part 1 and Part 2 data (intergroup contact)
   dl <- left_join(dl, d2_imp, by = c("participant", "category"))
-
+  
+# Summaries used to standardise contact variables
+  ds <- read_rds("data/d2_impute.rds") %>% distinct(item, mean, sd)
   
 # Export
   write_rds(dl, "dl_ic.rds")

### 2018-09-13 data/prepare_data_sdo.R

@@ -1,0 +1,59 @@
+# Library -----------------------------------------------------------------
+  library(lavaan)
+
+
+# Import ------------------------------------------------------------------
+  d2 <- read_rds("data/d2.rds") %>%
+        select(participant, starts_with("q60")) %>%
+        arrange(participant) %>%
+        rename_at(vars(starts_with("q60")), ~str_replace(., "q60", "sdo")) %>%
+        mutate_at(vars(sdo_3, sdo_4, sdo_7, sdo_8), ~ 8 - .)
+
+
+# Models ------------------------------------------------------------------
+  m4_model <- '
+  # Loadings
+  sdo_d =~ sdo_1 + sdo_2 + sdo_3 + sdo_4
+  sdo_e =~ sdo_5 + sdo_6 + sdo_7 + sdo_8
+  pro_t =~ sdo_1 + sdo_2 + sdo_5 + sdo_6
+  con_t =~ sdo_3 + sdo_4 + sdo_7 + sdo_8
+
+  # Covariances
+  sdo_d ~~ 0*pro_t
+  sdo_d ~~ 0*con_t
+  sdo_e ~~ 0*pro_t
+  sdo_e ~~ 0*con_t
+
+  # Variances
+  sdo_d ~~ 1*sdo_d
+  sdo_e ~~ 1*sdo_e
+  pro_t ~~ 1*pro_t
+  con_t ~~ 1*con_t
+  '
+  m4_fit <- cfa(m4_model, estimator = "mlr", missing = "fiml", data = d2)
+
+
+# Export ------------------------------------------------------------------
+  dl <- lavPredict(m4_fit) %>% 
+    matrix(., nrow = 302, ncol = 4, dimnames = list(NULL, c("sdo_d", "sdo_e", "pro_t", "con_t"))) %>%
+    as_tibble() %>% 
+    bind_cols(d2, .) %>%
+    select(participant, sdo_d, sdo_e) %>% 
+    left_join(dl, ., "participant")
+  
+  # Transform
+  dl <- dl %>% mutate(
+    gs = case_when(
+      ig_caste == "gm"   & category %in% 2:6 ~ 1L,
+      ig_caste == "obc"  & category %in% 3:6 ~ 1L,
+      ig_caste == "scst" & category %in% 4:6 ~ 1L,
+      TRUE ~ 0L
+    )
+  ) %>% select(
+    session:og, gs, cq:sdo_e
+  )
+
+
[…]

### 2018-09-13 figures/figure-2.R

@@ -1,132 +1,0 @@
-rm(list = ls())
-
-# Library -----------------------------------------------------------------
-  library(tidyverse); library(tidybayes)
-
-
-# Import ------------------------------------------------------------------
-  # Observed proportions
-  dl   <- read_rds("data/d1.rds") %>% 
-          filter(!is.na(q1)) %>%
-          mutate(ig_caste = recode_factor(
-            ig_caste, "gm" = "GM", "obc" = "OBC", "scst" = "SC/ST", .ordered = TRUE
-          )) %>%
-          mutate(caste = recode_factor(
-            caste, "GM" = "GM", "OBC" = "OBC", "SCST" = "SC/ST", "N/A" = NA_character_, .ordered = TRUE
-          ))
-  
-  # Estimated probabilites
-  post <- read_rds("models/q1_post.rds") %>%
-          unnest(p_est) %>%
-          mutate(ig_caste = recode_factor(
-            ig_caste, "1" = "GM", "2" = "OBC", "3" = "SC/ST", .ordered = TRUE
-          ))
-  
-
-# Summarise ---------------------------------------------------------------
-  # Observed proportions
-  d_obs <- dl %>% 
-    group_by(target, category, lname, nation, religion, caste, ig_caste) %>%
-    summarise(p_obs = mean(q1))
-  
-  # Estimated probabilities
-  d_est <- post %>%
-    rename(p_est = p_k) %>%
-    group_by(model, category, ig_caste) %>%
-    median_hdi(.width = c(.67, .89, .97))
-
-
-# Plot --------------------------------------------------------------------
-  p1 <- d_est %>%
-    left_join(d_obs, ., by = c("category", "ig_caste")) %>%
-    filter(model == 2) %>%
-  ggplot(., aes(x = target, y = p_est, ymin = .lower, ymax = .upper)) +
-    geom_ribbon(aes(group = .width), fill = "white", colour = NA) +
-    geom_ribbon(aes(fill = ig_caste, group = 1-.width), colour = NA, alpha = 0.20) +
-    geom_path(aes(colour = ig_caste)) +
-    geom_point(aes(y = p_obs), shape = 3, colour = "grey60") +
-    geom_point(aes(colour = ig_caste)) +
-    geom_vline(xintercept = c(4.5, 8.5, 12.5, 16.5, 20.5), colour = "white", size = 2) +
-    geom_vline(xintercept = 0.5, colour = "black") +
[…]

### 2018-09-13 figures/figure-3.R

@@ -1,0 +1,132 @@
+rm(list = ls())
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(tidybayes)
+
+
+# Import ------------------------------------------------------------------
+  # Observed proportions
+  dl   <- read_rds("data/d1.rds") %>% 
+          filter(!is.na(q1)) %>%
+          mutate(ig_caste = recode_factor(
+            ig_caste, "gm" = "GM", "obc" = "OBC", "scst" = "SC/ST", .ordered = TRUE
+          )) %>%
+          mutate(caste = recode_factor(
+            caste, "GM" = "GM", "OBC" = "OBC", "SCST" = "SC/ST", "N/A" = NA_character_, .ordered = TRUE
+          ))
+  
+  # Estimated probabilites
+  post <- read_rds("models/q1_post.rds") %>%
+          unnest(p_est) %>%
+          mutate(ig_caste = recode_factor(
+            ig_caste, "1" = "GM", "2" = "OBC", "3" = "SC/ST", .ordered = TRUE
+          ))
+  
+
+# Summarise ---------------------------------------------------------------
+  # Observed proportions
+  d_obs <- dl %>% 
+    group_by(target, category, lname, nation, religion, caste, ig_caste) %>%
+    summarise(p_obs = mean(q1))
+  
+  # Estimated probabilities
+  d_est <- post %>%
+    rename(p_est = p_k) %>%
+    group_by(model, category, ig_caste) %>%
+    median_hdi(.width = c(.67, .89, .97))
+
+
+# Plot --------------------------------------------------------------------
+  p3 <- d_est %>%
+    left_join(d_obs, ., by = c("category", "ig_caste")) %>%
+    filter(model == 2) %>%
+  ggplot(., aes(x = target, y = p_est, ymin = .lower, ymax = .upper)) +
+    geom_ribbon(aes(group = .width), fill = "white", colour = NA) +
+    geom_ribbon(aes(fill = ig_caste, group = 1-.width), colour = NA, alpha = 0.20) +
+    geom_path(aes(colour = ig_caste)) +
+    geom_point(aes(y = p_obs), shape = 3, colour = "grey60") +
+    geom_point(aes(colour = ig_caste)) +
+    geom_vline(xintercept = c(4.5, 8.5, 12.5, 16.5, 20.5), colour = "white", size = 2) +
+    geom_vline(xintercept = 0.5, colour = "black") +
[…]

### 2018-09-13 figures/figure-4.R

@@ -1,0 +1,71 @@
+rm(list = ls())
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(tidybayes)
+
+
+# Import ------------------------------------------------------------------
+  # Estimated probabilites
+  post <- read_rds("models/q1_ic_post.rds")
+  
+
+# Summarise ---------------------------------------------------------------
+  # Estimated probabilities
+  d_est <- post %>%
+    group_by(category, ig_caste, item, response) %>%
+    median_hdi(.width = c(.67, .89, .97)) %>%
+    ungroup() %>%
+    mutate(
+      ig_caste = case_when(
+        category %in% 3:4 & ig_caste %in% 1:2 ~ "GM/OBC",
+        ig_caste == 1 ~ "GM",
+        ig_caste == 2 ~ "OBC",
+        ig_caste == 3 ~ "SC/ST"
+      ),
+      category = recode_factor(
+        category,
+        "1" = "Hindu, GM",
+        "2" = "Hindu, OBC",
+        "3" = "Hindu, SC/ST",
+        "4" = "Muslim, OBC",
+        .ordered = TRUE
+      ),
+      item = case_when(
+        item == "nc" ~ "Negative contact",
+        item == "of" ~ "Outgroup friendship"
+      )
+    ) %>% 
+    distinct()
+
+
+# Figure ------------------------------------------------------------------
+  d_est %>%
+    ggplot(., aes(x = response, y = p_est, ymin = .lower, ymax = .upper, 
+                  colour = ig_caste, fill = ig_caste)) +
+    geom_ribbon(aes(group = interaction(.width, ig_caste)), colour = NA, fill = "white") +
+    geom_ribbon(aes(group = interaction(.width, ig_caste)), colour = NA, alpha = 0.20) +
+    geom_line() +
+    geom_point(size = 1) +
+    scale_x_continuous(limits = c(1, 5), breaks = 1:5, minor_breaks = 0) +
+    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.5)) +
+    scale_colour_viridis_d(begin = 0.0, end = 0.7) +
+    scale_fill_viridis_d(begin = 0.0, end = 0.7) +
+    labs(
+      x = "Amount",
+      y ='Pr("us"|M5)',
+      colour = "Ingroup:",
+      fill = "Ingroup:"
+    ) +
+    facet_grid(item ~ category) +
+    coord_fixed(4) +
[…]

### 2018-09-13 figures/figures-5-and-6.R

@@ -1,0 +1,114 @@
+rm(list = ls())
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(tidybayes)
+
+
+# Import ------------------------------------------------------------------
+  post <- read_rds("models/q2q3_post.rds") %>%
+    gather("standardized", "m_est", m_est:m_est_z) %>%
+    mutate(standardized = (standardized == "m_est_z")) %>%
+    mutate(
+      ig_caste = recode_factor(
+        ig_caste, 
+        "1" = "GM",
+        "2" = "OBC",
+        "3" = "SC/ST",
+        .ordered = TRUE
+      ),
+      category = recode_factor(
+        category,
+        "6" = "Foreign, Muslim",
+        "5" = "Foreign, Hindu",
+        "4" = "Indian, Muslim, OBC",
+        "3" = "Indian, Hindu, SC/ST",
+        "2" = "Indian, Hindu, OBC",
+        "1" = "Indian, Hindu, GM",
+        .ordered = TRUE
+      ),
+      x_q1 = recode_factor(
+        x_q1,
+        "1" = "us",
+        "0" = "not us",
+        .ordered = TRUE
+      )
+    ) %>%
+    group_by(category, ig_caste, x_q1, x_obc, x_scst, item, standardized)
+  
+
+# Figure 5 ----------------------------------------------------------------
+  post %>%
+    filter(!standardized, item == "q2") %>%
+  ggplot(., aes(x = m_est, y = category, group = x_q1)) +
+    geom_halfeyeh(
+      aes(shape = x_q1),
+      colour = NA, fill = "white",
+      point_interval = median_hdi, .width = 0.97,
+      size = 0
+    ) +
+    geom_halfeyeh(
+      aes(shape = x_q1, colour = ig_caste, fill = ig_caste), 
+      point_interval = median_hdi, .width = 0.97,
+      size = 1
+    ) +
+    scale_x_continuous(breaks = seq(1, 7, 3), minor_breaks = seq(1, 7, 1)) +
+    scale_fill_viridis_d(begin = 0, end = 0.7, alpha = 2/5) +
+    scale_colour_viridis_d(begin = 0, end = 0.7) +
+    coord_cartesian(xlim = c(0.5, 7.5), ylim = c(0.9, 7), expand = FALSE) +
+    facet_grid(. ~ ig_caste) + labs(
+      x = "Social distance"
+    ) +
+    theme_grey(base_size = 10) +
+    theme(
[…]

### 2018-09-13 figures/figures-7-and-8.R

@@ -1,0 +1,143 @@
+rm(list = ls())
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(tidybayes)
+
+
+# Import ------------------------------------------------------------------
+  post <- read_rds("models/ldps_post.rds") 
+  
+  # Prepare for figures
+  post <- post %>%
+    separate(item, c("item", "group"), sep = "_") %>%
+    mutate(
+      group = recode_factor(
+        group,
+        "ig" = "...from your\nown background",
+        "scst" = "SC/ST",
+        "obc" = "OBC",
+        "gm" = "GM",
+        "hindu" = "Hindus",
+        "muslim" = "Muslims",
+        .ordered = TRUE
+      ),
+      ig_caste = recode_factor(
+        ig_caste,
+        "scst" = "SC/ST",
+        "obc" = "OBC",
+        "gm" = "GM",
+        .ordered = TRUE
+      )
+    )
+  
+
+# Figure 7 ----------------------------------------------------------------
+  # Labels for Figure 7
+  d_lbl <- tibble(
+    x = c(2.5, 5.5), xend = c(1.5, 6.5),
+    ig_caste = "SC/ST", group = ordered("Muslims", levels = unique(post$group)),
+    label = c("harder", "easier")
+  )
+  
+  # Figure 7
+  post %>%
+    filter(item == "ld") %>%
+  ggplot(., aes(x = m_est, y = ig_caste)) +
+    geom_vline(xintercept = 4, colour = "white", size = 1) +
+    geom_halfeyeh(
+      aes(shape = "estimate"),
+      colour = "white", fill = "white",
+      point_interval = median_hdi, .width = 0.97,
+      rel_min_height = 0.01, size = 0
+    ) +
+    geom_halfeyeh(
+      aes(colour = ig_caste, fill = ig_caste, shape = "estimate"),
+      point_interval = median_hdi, .width = 0.97,
+      rel_min_height = 0.01, size = 0.5, fatten_point = 2.5
+    ) +
+    geom_segment(
+      data = d_lbl, aes(x = x, xend = xend, yend = ig_caste),
+      arrow = arrow(length = unit(0.1, "cm"), type = "closed")
+    ) +
+    geom_text(
+      data = d_lbl, aes(label = label), x = c(2, 6), y = c(1, 1),
+      size = 10*0.8/.pt, vjust = -0.5
+    ) +
[…]

### 2018-09-13 impute_data.R

@@ -1,7 +1,7 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-  # This script imputes missing responses (n = 66) to the intergroup contact
+  # This script imputes missing responses (n = 66) for the intergroup contact
   # variables, and returns a data frame with both observed responses and 
   # draws from the posterior distribution for missing responses. 
 

### 2018-09-13 results_consequences.R

@@ -1,0 +1,156 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(rstan); library(tidybayes); library(loo)
+
+  # Stan options
+  options(mc.cores = parallel::detectCores())
+  rstan_options(auto_write = TRUE)
+  seeds = c(1157744, 2691555, 4045395, 2910499, 5195618, 5975015, 2391421)
+  
+
+# Functions ---------------------------------------------------------------
+
+
+# Import ------------------------------------------------------------------
+  dl <- read_rds("data/d1.rds") %>%
+        filter(!is.na(q1)) %>%
+        mutate_at(vars(q2, q3), funs(mean, sd), na.rm = TRUE) %>%
+        mutate(q2_z = (q2 - q2_mean) / q2_sd, q3_z = (q3 - q3_mean) / q3_sd) %>%
+        arrange(participant, target)
+  
+  # Prepare for imputation
+  dl_imp <- dl %>% 
+            select(participant, target, q2_z, q3_z) %>%
+            gather("item", "y", q2_z, q3_z) %>%
+            mutate(ii = 1:n())
+
+  # Compose data list
+  data_list <- with(dl, list(
+    # Numbers
+    N_row = length(participant),
+    N_col = 2,
+    J = n_distinct(participant),
+    K = n_distinct(category),
+    N_obs = sum(!is.na(dl_imp$y)),
+    N_mis = sum(is.na(dl_imp$y)),
+    N_all_obs = dl %>% filter(!is.na(q2), !is.na(q3)) %>% nrow(),
+    # Indices
+    jj = participant,
+    kk = category,
+    ii_obs = dl_imp$ii[!is.na(dl_imp$y)],
+    ii_mis = dl_imp$ii[is.na(!dl_imp$y)],
+    nn_obs = dl %>% mutate(nn = 1:n()) %>% filter(!is.na(q2), !is.na(q3)) %>% pull(nn),
+    # Vectors
+    x_scst = ifelse(ig_caste == "scst", 1L, 0L),
+    x_obc = ifelse(ig_caste == "obc", 1L, 0L),
+    x_q1 = q1,
+    y_obs = dl_imp$y[!is.na(dl_imp$y)]
+  ))
+
+
+# Models ------------------------------------------------------------------
[…]

### 2018-09-13 results_group_differences.R

@@ -6,12 +6,13 @@ rm(list = ls())
   # Stan options
   options(mc.cores = parallel::detectCores())
   rstan_options(auto_write = TRUE)
-  seed = 0892561437
+  seeds = c(5477649, 3984665, 8989566, 9363790)
 
 
 # Import ------------------------------------------------------------------
   dl <- read_rds("data/d1.rds") %>%
-        filter(!is.na(q1))
+        filter(!is.na(q1)) %>%
+        arrange(participant, target)
   
   # Compose data list
   data_list <- with(dl, list(
@@ -28,23 +29,23 @@ rm(list = ls())
 
 # Models ------------------------------------------------------------------
   # Model: Varying Intercept (Participant)
-  m0_stan <- stan("models/q1_m0.stan", data = data_list, seed = seed,
-                  iter = 2000, warmup = 1000, 
+  m0_stan <- stan("models/q1_m0.stan", data = data_list, seed = seeds[1],
+                  iter = 2000, warmup = 1000,
                   pars = c("alpha"), include = FALSE)
   
   # Model: + Varying Intercept (Target: Category)
-  m1_stan <- stan("models/q1_m1.stan", data = data_list, seed = seed,
-                  iter = 2000, warmup = 1000, 
+  m1_stan <- stan("models/q1_m1.stan", data = data_list, seed = seeds[2],
+                  iter = 2000, warmup = 1000,
                   pars = c("alpha"), include = FALSE)
   
   # Model: + Participant: SCST * Target: Category (4)
-  m2_stan <- stan("models/q1_m2.stan", data = data_list, seed = seed,
-                  iter = 2000, warmup = 1000, 
+  m2_stan <- stan("models/q1_m2.stan", data = data_list, seed = seeds[3],
+                  iter = 2000, warmup = 1000,
                   pars = c("alpha"), include = FALSE)
   
   # Model: + Participant: OBC * Target: Category (4)
-  m3_stan <- stan("models/q1_m3.stan", data = data_list, seed = seed,
-                  iter = 2000, warmup = 1000, 
+  m3_stan <- stan("models/q1_m3.stan", data = data_list, seed = seeds[4],
[…]

### 2018-09-13 results_individual_differences.R

@@ -3,25 +3,32 @@ rm(list = ls())
 # Notes -------------------------------------------------------------------
   # In total, I considered 5 * 4 = 20 items measuring intergroup contact. Across
   # items, less than 1.6% (n = 66) of individual responses were missing - though
-  # about 20% of all participants failed to respond to at least one item. As 
+  # about 13% of all participants failed to respond to at least one item. As 
   # item-by-item missingness was negligible, I used single imputation rather 
   # than (computationally demanding) full imputation. Before running Models 4 to 
-  # 7, I imputed missing values from a multivariate normal distribution (see 
+  # 6, I imputed missing values from a multivariate normal distribution (see 
   # "impute_data.R"). For all subsequent analyses, I substituted the most likely
   # value (from the posterior distribution of the imputation model) for each 
   # missing value (in the original dataset).
 
+  # Add note about SDO.
+
 # Library -----------------------------------------------------------------
-  library(tidyverse); library(tidybayes); library(rstan); library(loo)
+  library(tidyverse); library(rstan); library(tidybayes); library(loo)
 
   # Stan options
   options(mc.cores = parallel::detectCores())
   rstan_options(auto_write = TRUE)
-  seed = 0892561437
+  seeds = c(6678002, 8970252,	9556204, 8660009)
+  
 
+# Functions ---------------------------------------------------------------
+  inv_logit <- function(x) exp(x) / ( 1 + exp(x) )
+  
 
 # Import ------------------------------------------------------------------
   source("data/prepare_data_ic.R")
+  source("data/prepare_data_sdo.R")
 
   # Compose data list
   data_list <- with(dl, list(
@@ -40,53 +47,95 @@ rm(list = ls())
     x_pc = replace_na(pc, -99), # Replace NAs for foreign targets
     x_nc = replace_na(nc, -99), # Replace NAs for foreign targets
     x_of = replace_na(of, -99), # Replace NAs for foreign targets
+    x_gs = gs,
+    x_sdo_d = sdo_d,
+    x_sdo_e = sdo_e,
     y = q1
   ))
 
 
[…]

### 2018-09-13 results_socialchange_consequences.R

@@ -1,0 +1,128 @@
+rm(list = ls())
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(tidybayes); library(rstan); library(loo)
+
+  # Stan options
+  options(mc.cores = parallel::detectCores())
+  rstan_options(auto_write = TRUE)
+  seeds = c(6096624, 7239687, 8749870, 6124014, 6071342,
+            6890159, 9814684, 1014316, 5004873, 6578813)
+
+
+# Import ------------------------------------------------------------------
+  dw <- read_rds("data/d2.rds") %>%
+    transmute(
+      participant,
+      ig_caste,
+      ld_ig     = q24_1,
+      ld_scst   = (q24_2 + q24_3)/2,
+      ld_obc    = q24_4,
+      ld_gm     = q24_5,
+      ld_hindu  = q24_6,
+      ld_muslim = q24_7,
+      ps_scst   = (q25 + q26)/2,
+      ps_obc    = (q27 + q28)/2,
+      ps_muslim = q29
+    ) %>%
+    arrange(participant)
+  
+  # Prepare for imputation
+  dl_imp <- dw %>% 
+    gather("item", "y", -participant:-ig_caste) %>%
+    mutate(ii = 1:n()) %>%
+    group_by(item) %>%
+    mutate_at(vars(y), funs(mean, sd), na.rm = TRUE) %>%
+    mutate(y_z = (y - mean) / sd) %>%
+    ungroup() %>%
+    group_by(participant) %>% 
+    mutate(missing = 9 - sum(!is.na(y))) %>%
+    ungroup()
+  
+  # Compose data list
+  data_list <- list(
+    # Numbers
+    N_row = length(dw$participant),
+    N_col = 9,
+    N_obs = sum(!is.na(dl_imp$y)),
+    N_mis = sum(is.na(dl_imp$y)),
+    N_all_obs = dl_imp %>% filter(missing == 0) %>% distinct(participant) %>% nrow(),
+    # Indices
+    ii_obs = dl_imp$ii[!is.na(dl_imp$y)],
+    ii_mis = dl_imp$ii[is.na(!dl_imp$y)],
+    nn_obs = dl_imp %>% filter(missing == 0) %>% distinct(participant) %>% pull(participant),
+    # Vectors
+    x_scst = ifelse(dw$ig_caste == "scst", 1L, 0L),
[…]

### 2018-10-11 manuscript/figures_and_tables.tex
add stratified kfold cv

@@
 We selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.
-% Appendix~X describes all models in detail.
+$w$ are stacking weights based on the models' expected log predictive densities (Yao et al., 2018).% Appendix~X describes all models in detail.
 }
@@
 \small
-\begin{tabularx}{\linewidth}{r@{~}rXrrrrr} \toprule
-\# &  & Description & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
-0 &      & Varying intercept (Participant) & -4262.7 & 33.1 & - & - & - \\
-1 & vs 0 & Varying intercept (Category) & -3156.2 & 46.6 & 1106.5 & 42.7 & 25.9 \\
-2 & vs 1 & Group differences (SC/ST) & -3074.5 & 47.3 &   81.7 & 12.0 &  6.8 \\
-3 & vs 2 & Group differences (OBC) & -3069.2 & 47.4 &    5.3 &  3.4 &  1.7 \\ \midrule
-4 & vs 2 & Intergroup contact (4) & -3047.6 & 47.5 &   26.9 &  8.2 &  3.3 \\
-5 & vs 4 & Intergroup contact (2) & -3045.4 & 47.5 &    2.2 &  0.4 &  5.5 \\
-6 & vs 5 & Intergroup contact (OBC, SC/ST) & -3048.9 & 47.5 &   -3.4 &  2.5 & -1.4 \\
-7 & vs 2 & Social dominance orientation & -3076.0 & 47.5 &   -1.5 &  1.5 & -1.0 \\
+\begin{tabularx}{\linewidth}{r@{~}rXrrrrrr} \toprule
+\# &  & Description & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule 
+0 &      & Intercept (Participant) & -4703.5 & 23.7 &     - &    - &    - & .00 \\ 
+1 & vs 0 & Intercept (Category)    & -3853.5 & 41.6 & 850.1 & 37.4 & 22.7 & .00 \\
+2 & vs 1 & Group differences (SC/ST)       & -3791.3 & 42.0 &  62.1 & 11.1 &  5.6 & .00 \\
+3 & vs 2 & Group differences (OBC)         & -3792.1 & 42.2 &  -0.8 &  3.6 & -0.2 & .07 \\ \midrule
+4 & vs 2 & Intergroup contact (4) & -3743.4 & 42.8 &  47.9 &  8.8 &  5.4 & .00 \\
+5 & vs 4 & Intergroup contact (2) & -3736.7 & 42.6 &   6.7 &  1.8 &  3.8 & .92 \\
+6 & vs 5 & Intergroup contact (2) & -3747.8 & 42.7 & -11.1 &  3.2 & -3.5 & .00 \\
+7 & vs 2 & Social dominance orientation & -3791.0 & 42.1 &   0.4 &  3.3 &  0.1 & .00 \\
 \bottomrule
@@
 \small	
-\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrr} \toprule
-\# &  & Description & $R^2_\text{SD}$ & $R^2_\text{FT}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
-0 &      & \ldots~(Participant) & .23 & .26 & -15203.4 & 111.8 &     - &    - &    - \\
-1 & vs 0 & \ldots~(Category)    & .38 & .42 & -14300.1 & 117.9 & 903.3 & 39.6 & 22.8 \\
-2 & vs 1 & \ldots~(SC/ST)       & .38 & .43 & -14248.7 & 118.2 &  51.4 &  8.8 &  5.8 \\
-3 & vs 2 & \ldots~(OBC)         & .39 & .43 & -14222.2 & 118.4 &  26.5 &  7.2 &  3.7 \\ \midrule
-4 & vs 3 & Categorization       & .42 & .47 & -14004.5 & 120.6 & 217.7 & 22.7 &  9.6 \\
-5 & vs 4 & \ldots~(Category)    & .42 & .47 & -13986.9 & 120.9 &  17.6 &  7.7 &  2.3 \\
-6 & vs 5 & \ldots~(OBC, SC/ST)  & .42 & .47 & -13988.9 & 120.8 &  -2.0 &  3.6 & -0.6 \\
+\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrrr} \toprule
+\# &  & Description & $R^2_\text{SD}$ & $R^2_\text{FT}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule 
+0 &      & Participant & .23 & .26 & -16964 & 71.0 & - & - & - & .00 \\
+1 & vs 0 & Category & .38 & .42 & -16338 & 79.6 & 626.8 & 40.2 & 15.6 & .00 \\
+2 & vs 1 & SC/ST    & .38 & .43 & -16317 & 79.6 &  20.1 &  9.8 &  2.1 & .00 \\
+3 & vs 2 & OBC      & .39 & .43 & -16293 & 80.5 &  24.2 &  9.7 &  2.5 & .00 \\ \midrule
+4 & vs 3 & Categorization & .42 & .47 & -14004 & 120.6 & 217.7 & 22.7 &  9.6 & .00 \\
+5 & vs 4 & \ldots~(Category) & .42 & .47 & -13986 & 120.9 &  17.6 &  7.7 &  2.3 & .00 \\
+6 & vs 5 & \ldots~(Ingroup) & .42 & .47 & -13988 & 120.8 &  -2.0 &  3.6 & -0.6 & .00 \\
 \bottomrule    

### 2018-10-11 models/kfold/kfold_consequences.R

@@ -1,0 +1,268 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(rstan); library(tidybayes); library(loo)
+  
+  # Stan options
+  options(mc.cores = parallel::detectCores())
+  rstan_options(auto_write = TRUE)
+  seeds = c(1157744, 2691555, 4045395, 2910499, 5195618, 5975015, 2391421)
+
+
+# Import ------------------------------------------------------------------
+  dl <- read_rds("data/d1.rds") %>%
+        filter(!is.na(q1)) %>%
+        mutate_at(vars(q2, q3), funs(mean, sd), na.rm = TRUE) %>%
+        mutate(q2_z = (q2 - q2_mean) / q2_sd, q3_z = (q3 - q3_mean) / q3_sd) %>%
+        arrange(participant, target)
+  
+  # Single (median) imputation
+  Y           <- as.matrix(dl[,c("q2_z", "q3_z")])
+  Y[is.na(Y)] <- read_rds("models/q2q3_mc_fit.rds")[[6]] %>%
+                 spread_draws(y_mis[ii]) %>%
+                 summarise(y_mis = median(y_mis)) %>%
+                 pull(y_mis)
+
+  # Compose data list
+  data_list <- with(dl, list(
+    # Numbers
+    N_row = length(participant),
+    N_col = ncol(Y),
+    J = n_distinct(participant),
+    K = n_distinct(category),
+    # Indices
+    jj = participant,
+    kk = category,
+    # Vectors
+    x_scst = ifelse(ig_caste == "scst", 1L, 0L),
+    x_obc = ifelse(ig_caste == "obc", 1L, 0L),
+    x_q1 = q1,
+    Y = Y
+  ))
+  
+  # Generate indeces for 10-fold cross-validation
+  set.seed(24987504)
+  d_kfold <- tibble(
+    ii   = 1:data_list$N_row, 
+    jj   = data_list$jj, 
+    fold = kfold_split_stratified(K = 10, x = jj),
+    na   = is.na(dl$q2_z) | is.na(dl$q3_z)
+  ) %>% mutate(
+    fold = ifelse(na, 0, fold)
+  )
+  
+
[…]

### 2018-10-11 models/kfold/kfold_group_differences.R

@@ -1,0 +1,165 @@
+rm(list = ls())
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(rstan); library(loo)
+  
+  # Stan options
+  options(mc.cores = parallel::detectCores())
+  rstan_options(auto_write = TRUE)
+  seeds = c(5477649, 3984665, 8989566, 9363790)
+
+
+# Import ------------------------------------------------------------------
+  dl <- read_rds("data/d1.rds") %>%
+        filter(!is.na(q1)) %>%
+        arrange(participant, target)
+  
+  # Compose data list
+  data_list <- with(dl, list(
+    N = length(participant),
+    J = n_distinct(participant),
+    K = n_distinct(category),
+    jj = participant,
+    kk = category,
+    x_scst = ifelse(ig_caste == "scst", 1L, 0L),
+    x_obc = ifelse(ig_caste == "obc", 1L, 0L),
+    y = q1
+  ))
+  
+  # Generate indeces for 10-fold cross-validation
+  set.seed(24987504)
+  d_kfold <- tibble(
+    ii   = 1:data_list$N, 
+    jj   = data_list$jj, 
+    fold = kfold_split_stratified(K = 10, x = jj)
+  )
+
+
+# Functions ---------------------------------------------------------------
+  data_fold <- function(k) {
+    append(data_list, list(
+      N_t = d_kfold %>% filter(fold != k) %>% nrow(),
+      N_h = d_kfold %>% filter(fold == k) %>% nrow(),
+      ii_t = d_kfold %>% filter(fold != k) %>% pull(ii),
+      ii_h = d_kfold %>% filter(fold == k) %>% pull(ii)
+    ))
+  }
+  
+  compare_kfold <- function(elpd1, elpd2) {
+    d_elpd  <- sum(elpd2 - elpd1)
+    d_se    <- sd(elpd2 - elpd1) * sqrt(length(elpd1))
+    d_ratio <- d_elpd / d_se
+    return(tibble(d_elpd = d_elpd, d_se = d_se, d_ratio = d_ratio))
+  }
+  
+
+# Models ------------------------------------------------------------------
+  # Model 0: Varying Intercept (Participant)
+  for (k in 1:10) {
[…]

### 2018-10-11 models/kfold/kfold_individual_differences.R

@@ -1,0 +1,191 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+  library(tidyverse); library(rstan); library(loo)
+  
+  # Stan options
+  options(mc.cores = parallel::detectCores())
+  rstan_options(auto_write = TRUE)
+  seeds = c(6678002, 8970252,	9556204, 8660009)
+
+
+# Import ------------------------------------------------------------------
+  source("data/prepare_data_ic.R")
+  source("data/prepare_data_sdo.R")
+
+  # Compose data list
+  data_list <- with(dl, list(
+    # Numbers
+    N = length(participant),
+    J = n_distinct(participant),
+    K = n_distinct(category),
+    # Indices
+    jj = participant,
+    kk = category,
+    # Vectors
+    x_scst = ifelse(ig_caste == "scst", 1L, 0L),
+    x_obc = ifelse(ig_caste == "obc", 1L, 0L),
+    x_og = og,
+    x_cq = replace_na(cq, -99), # Replace NAs for foreign targets 
+    x_pc = replace_na(pc, -99), # Replace NAs for foreign targets
+    x_nc = replace_na(nc, -99), # Replace NAs for foreign targets
+    x_of = replace_na(of, -99), # Replace NAs for foreign targets
+    x_gs = gs,
+    x_sdo_d = sdo_d,
+    x_sdo_e = sdo_e,
+    y = q1
+  ))
+
+  # Generate indeces for 10-fold cross-validation
+  set.seed(24987504)
+  d_kfold <- tibble(
+    ii   = 1:data_list$N, 
+    jj   = data_list$jj, 
+    fold = kfold_split_stratified(K = 10, x = jj)
+  )
+  
+  
+# Functions ---------------------------------------------------------------
+  data_fold <- function(k) {
+    append(data_list, list(
+      N_t = d_kfold %>% filter(fold != k) %>% nrow(),
+      N_h = d_kfold %>% filter(fold == k) %>% nrow(),
+      ii_t = d_kfold %>% filter(fold != k) %>% pull(ii),
[…]

### 2018-10-19 manuscript/figures_and_tables.tex
update kfold cv

@@
 \# &  & Description & $R^2_\text{SD}$ & $R^2_\text{FT}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule 
-0 &      & Participant & .23 & .26 & -16964 & 71.0 & - & - & - & .00 \\
-1 & vs 0 & Category & .38 & .42 & -16338 & 79.6 & 626.8 & 40.2 & 15.6 & .00 \\
+0 &      & Participant & .23 & .26 & -16964 & 71.0 & - & - & - & .12 \\
+1 & vs 0 & Category & .38 & .42 & -16338 & 79.6 & 626.8 & 40.2 & 15.6 & .02 \\
 2 & vs 1 & SC/ST    & .38 & .43 & -16317 & 79.6 &  20.1 &  9.8 &  2.1 & .00 \\
 3 & vs 2 & OBC      & .39 & .43 & -16293 & 80.5 &  24.2 &  9.7 &  2.5 & .00 \\ \midrule
-4 & vs 3 & Categorization & .42 & .47 & -14004 & 120.6 & 217.7 & 22.7 &  9.6 & .00 \\
-5 & vs 4 & \ldots~(Category) & .42 & .47 & -13986 & 120.9 &  17.6 &  7.7 &  2.3 & .00 \\
-6 & vs 5 & \ldots~(Ingroup) & .42 & .47 & -13988 & 120.8 &  -2.0 &  3.6 & -0.6 & .00 \\
+4 & vs 3 & Categorization    & .42 & .47 & -16028 & 83.5 & 264.8 & 24.5 & 10.8 & .19 \\
+5 & vs 4 & \ldots~(Category) & .42 & .47 & -16007 & 83.6 &  21.1 &  8.7 &  2.4 & .67 \\
+6 & vs 5 & \ldots~(Ingroup)  & .42 & .47 & -16025 & 84.3 & -17.4 &  5.9 & -3.0 & .00 \\
 \bottomrule    

### 2018-10-19 figures/figure-4.R

@@ -45,16 +45,18 @@ rm(list = ls())
     geom_ribbon(aes(group = interaction(.width, ig_caste)), colour = NA, fill = "white") +
     geom_ribbon(aes(group = interaction(.width, ig_caste)), colour = NA, alpha = 0.20) +
     geom_line() +
-    geom_point(size = 1) +
+    geom_point(aes(shape = ig_caste), size = 0.75) +
     scale_x_continuous(limits = c(1, 5), breaks = 1:5, minor_breaks = 0) +
     scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.5)) +
     scale_colour_viridis_d(begin = 0.0, end = 0.7) +
     scale_fill_viridis_d(begin = 0.0, end = 0.7) +
+    scale_shape_manual(values = c("circle", "triangle", "square", "diamond filled")) +
     labs(
       x = "Amount",
       y ='Pr("us"|M5)',
       colour = "Ingroup:",
-      fill = "Ingroup:"
+      fill = "Ingroup:",
+      shape = "Ingroup:"
     ) +
     facet_grid(item ~ category) +
     coord_fixed(4) +

### 2018-10-19 models/kfold/kfold_consequences.R

@@ -1,7 +1,8 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-
+  # Caution! Running this script will take several days on most computers.
+  # Run read_rds("models/kfold/q2q3_elpd_kfold.rds") to skip to the results.
 
 # Library -----------------------------------------------------------------
   library(tidyverse); library(rstan); library(tidybayes); library(loo)
@@ -73,111 +74,111 @@ rm(list = ls())
   }
 
 # Models ------------------------------------------------------------------
-  # # Model 0
-  # for (k in 1:10) {
-  #   print(paste("[", k, "/10] - Model 1", sep = ""))
-  #   fit <- stan(
-  #     "models/kfold/q2q3_m0_kfold.stan",
-  #     data = data_fold(k),
-  #     seed = seeds[1],
-  #     iter = 1000,
-  #     warmup = 750,
-  #     pars = c("log_lik_h")
-  #   )
-  #   if (k == 1) {
-  #     extract_log_lik(fit, parameter_name = "log_lik_h") %>%
-  #     list(.) %>%
-  #     write_rds(., "models/kfold/q2q3_m0_llk.rds")
-  #   } else {
-  #     extract_log_lik(fit, parameter_name = "log_lik_h") %>%
-  #     list(.) %>%
-  #     append(read_rds("models/kfold/q2q3_m0_llk.rds"), .) %>%
-  #     write_rds(., "models/kfold/q2q3_m0_llk.rds")
-  #   }
-  # }
-
-  # # Model 1
-  # for (k in 1:10) {
-  #   print(paste("[", k, "/10] - Model 1", sep = ""))
-  #   fit <- stan(
-  #     "models/kfold/q2q3_m1_kfold.stan",
-  #     data = data_fold(k),
-  #     seed = seeds[2],
-  #     iter = 1000,
-  #     warmup = 750,
-  #     pars = c("log_lik_h")
-  #   )
-  #   if (k == 1) {
-  #     extract_log_lik(fit, parameter_name = "log_lik_h") %>%
-  #     list(.) %>%
-  #     write_rds(., "models/kfold/q2q3_m1_llk.rds")
-  #   } else {
-  #     extract_log_lik(fit, parameter_name = "log_lik_h") %>%
-  #     list(.) %>%
[…]

### 2018-10-19 models/kfold/kfold_group_differences.R

@@ -1,5 +1,10 @@
 rm(list = ls())
 
+# Notes -------------------------------------------------------------------
+  # Caution! Running this script will take several days on most computers.
+  # Run read_rds("models/kfold/q1_elpd_kfold.rds") to skip to the results.
+
+
 # Library -----------------------------------------------------------------
   library(tidyverse); library(rstan); library(loo)
   

### 2018-10-19 models/kfold/kfold_individual_differences.R

@@ -1,7 +1,8 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-
+  # Caution! Running this script will take several days on most computers.
+  # Run read_rds("models/kfold/q1_elpd_kfold.rds") to skip to the results.
 
 # Library -----------------------------------------------------------------
   library(tidyverse); library(rstan); library(loo)

### 2018-10-19 results_consequences.R
remove loo

@@ -93,22 +93,10 @@ rm(list = ls())
   # Compare models
   mc_fit <- list(m0_stan, m1_stan, m2_stan, m3_stan, m4_stan, m5_stan, m6_stan)
   mc_R2  <- map(mc_fit, ~gather_draws(., R2[item]) %>% median_hdi(.width = .97))
-  mc_llk <- map(mc_fit, extract_log_lik, merge_chains = FALSE)
-  mc_loo <- map(mc_llk, ~loo(., r_eff = relative_eff(exp(.)), cores = 4))
 
   # Export
   write_rds(mc_fit, "models/q2q3_mc_fit.rds")
-  write_rds(mc_loo, "models/q2q3_mc_loo.rds")
-  
-  # Compare
-  compare(x = mc_loo)
-  compare(mc_loo[[1]], mc_loo[[2]])
-  compare(mc_loo[[2]], mc_loo[[3]])
-  compare(mc_loo[[3]], mc_loo[[4]])
-  compare(mc_loo[[4]], mc_loo[[5]])
-  compare(mc_loo[[5]], mc_loo[[6]])
-  compare(mc_loo[[6]], mc_loo[[7]])
-  
+
   
 # Predict -----------------------------------------------------------------
   # Posterior draws

### 2018-10-19 results_group_differences.R

@@ -52,14 +52,9 @@ rm(list = ls())
 # Compare -----------------------------------------------------------------
   # Compare models
   mc_fit <- list(m0_stan, m1_stan, m2_stan, m3_stan)
-  mc_llk <- map(mc_fit, extract_log_lik, merge_chains = FALSE)
-  mc_loo <- map(mc_llk, ~loo(., r_eff = relative_eff(exp(.)), cores = 4))
-
-  compare(x = mc_loo)
   
   # Export
   write_rds(mc_fit, "models/q1_mc_fit.rds")
-  write_rds(mc_loo, "models/q1_mc_loo.rds")
 
 
 # Predict -----------------------------------------------------------------

### 2018-10-19 results_individual_differences.R

@@ -91,24 +91,12 @@ rm(list = ls())
 # Compare -----------------------------------------------------------------
   # Compare models
   mc_fit <- list(m4_stan, m5_stan, m6_stan, m7_stan)
-  mc_llk <- map(mc_fit, extract_log_lik, merge_chains = FALSE)
-  mc_loo <- map(mc_llk, ~loo(., r_eff = relative_eff(exp(.)), cores = 4))
 
   # Merge with m0_stan to m3_stan
   mc_fit <- append(read_rds("models/q1_mc_fit.rds"), mc_fit)
-  mc_loo <- append(read_rds("models/q1_mc_loo.rds"), mc_loo)
-  compare(x = mc_loo)
 
   # Export
   write_rds(mc_fit, "models/q1_mc_fit.rds")
-  write_rds(mc_loo, "models/q1_mc_loo.rds")
-  
-  # Compare
-  compare(x = mc_loo)
-  compare(mc_loo[[3]], mc_loo[[5]])
-  compare(mc_loo[[5]], mc_loo[[6]])
-  compare(mc_loo[[6]], mc_loo[[7]])
-  compare(mc_loo[[3]], mc_loo[[8]])
 
 
 # Predict -----------------------------------------------------------------

### 2018-10-26 manuscript/appendices.tex
add appendices

\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}

% Format
\usepackage{layout}
\setlength{\parindent}{0.5in}
\setcounter{secnumdepth}{0}
\usepackage{lineno}
%\usepackage{authblk}

% Font
\usepackage{MinionPro}
\input glyphtounicode
\pdfgentounicode=1
\usepackage{microtype}
\usepackage[super]{nth}

% Language
\usepackage[british]{babel}

% References
\usepackage[nosectionbib, tocbib, unnumberedbib]{apacite}

% Figures
\usepackage{graphicx}
\usepackage[small, labelfont=it, labelsep=period]{caption}

% Tables
\usepackage{booktabs}
\usepackage{tabularx}

% Commands
\newcommand{\pest}[4]{$ \text{Pr} (\text{``us''} | \text{#1}) = #2$, $[#3, #4]$}
\newcommand{\pdif}[4]{$ \Delta\text{Pr} (\text{``us''} | \text{#1}) = #2$, $[#3, #4]$}

% Frontmatter
\title{\emph{Appendices for}\\Intergroup contact fosters\\more inclusive social identities}
\date{November 5, 2018}
%\author{Nils Karl Reimer}
%\author[2]{Shanmukh V. Kamble}
%\author[3]{Katharina Schmid}
%\author[1]{Miles Hewstone}
%\affil[1]{University of Oxford}
%\affil[2]{Karnatak University}
%\affil[3]{ESEADE Business School, Ramon Llull University}
%\renewcommand\Affilfont{\small}

\begin{document}

\maketitle

\section{Appendix A: Pilot Study}

Informed by local knowledge, we intended to rely on last names to unobtrusively communicate caste membership in the crossed-categorization task. To find the most prototypical stimuli, wecompiled an initial set of 50 surnames, drawing on local knowledge, databases on naming preferences, and publicly available archives of Facebook usernames. We selected 10 surnames for each of five combinations of nationality, religion, and caste: (1) Indian Hindus of upper-caste backgrounds, (2) Indian Hindus of lower-caste backgrounds (Dalits), (3) Indian Muslims, (4) foreign Hindus, and (5) foreign Muslims. From these 50 names, we created 100 stimuli resembling identity cards, 50 with female first names and 50 with male first names. Each card had the target's first and last name, age (21--26 years), and religion (Hindu, Muslim) printed on them, as well as a flag corresponding to the target's nationality (Indian, Nepali, Sri Lankan, Bangladeshi) and a silhouette corresponding to the target's gender \cite<adapted~from>{ma_chicago_2015}. Cards for female and male targets were identical in all attributes except first name and silhouette.

We asked 26 students (19 women, 7 men) of diverse caste groups (\emph{SC/ST}: 8, \emph{GM}: 10, \emph{OBC}: 8) and religious backgrounds (\emph{Hinduism}: 16, \emph{Islam}: 4, \emph{Christianity}: 5, \emph{Jainism}: 1) to review 25 of the 50 stimuli corresponding to their gender. For each stimulus, we asked participants which caste they thought the target most likely belonged to (\emph{SC/ST}, \emph{GM}, \emph{OBC}, \emph{GM or OBC}, \emph{Can't tell/Don't know}), how typical or unusual they considered the target's name for someone of that particular nationality, religion, and (if applicable) caste $(1 = \textit{very typical}, 6 = \textit{very unusual})$, and whether the target's name reminded them of anyone in particular (\emph{yes}, \emph{no}) and, if so, of whom.

Participants' responses had important implications for designing the crossed-categorization task. On average, participants regarded all targets' names as at least ``somewhat typical'' $(1.42 \le \textit{Ms} \le 3.50)$. Names, however, were not enough to reliably cue caste membership---only $55\%$ to $83\%$ of participants identified even the most distinctive Dalit targets as Scheduled Caste~/ Scheduled Tribe (see Figure~\ref{fig:a-1}). Further, participants consistently categorized Muslim targets as Other Backward Class (see Figure~\ref{fig:a-2}), introducing a potential confound when comparing Muslim (OBC) and Hindu (GM) targets. Considering these findings, we decided to explicitly state caste membership (as reservation categories: GM, OBC, SC/ST) for Indian targets, and to add \emph{Indian, Hindu, OBC} targets as a sixth category.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/appendices/appendices-a-1}
\caption[Proportion of SC/ST vs GM classifications per target stimulus (Pilot study)]{Proportion of SC/ST vs GM classifications per target stimulus. Targets in the upper-left quadrant were most often classified as SC/ST, while targets in the lower-right quadrant were most often classified as GM. Targets in the lower-left quadrant were more often classified as GM or OBC, or OBC than as SC/ST or GM, or could not be classified reliably. Colours highlight Indian targets selected as GM, OBC, and SC/ST stimuli, respectively, based on participants' categorizations in the pilot study. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste~/ Scheduled Tribe}
\label{fig:a-1}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/appendices/appendices-a-2}
\caption[Foreign targets selected based on participants' average typicality ratings (Pilot study)]{Foreign targets selected as Sri Lankan, Hindu (2), Nepali, Hindu (2), and Bangladeshi, Muslim (4) stimuli, respectively, based on participants' average typicality ratings.}
\label{fig:a-2}
\end{figure}

For the final set of stimuli, we chose the four most prototypical targets for each of the six categories under study. We ranked Indian targets by the proportion of ``correct'' categorizations (e.g., $\Pr(\textit{OBC})$ for \emph{Muslim, OBC} targets) weighted by the inversed proportions of ``incorrect'' categorizations (e.g., $1 - \Pr(\textit{SCST})$ and $1 - \Pr(\textit{GM})$ for \emph{Muslim, OBC} targets). We selected the four highest-ranked (Category 1) \emph{Hindu, GM}, (2) \emph{Hindu, OBC}, (3) \emph{Hindu, SC/ST}, and (4) \emph{Muslim, OBC} targets (see Figure~\ref{fig:a-1}). We ranked foreign targets by their average typicality rating, and excluded targets who were categorized as General Merit or Scheduled Caste~/ Scheduled Tribe by $\ge 50\%$ of participants (to avoid obvious caste associations). We selected the two most typical (Category 5) \emph{Nepali, Hindu} and \emph{Sri Lankan, Hindu} targets, and the four most typical (6) \emph{Bangladeshi, Muslim} targets (see Figure~\ref{fig:a-2}). Based on the pilot study, we thus used $6~(\text{categories}) \times 4~(\text{targets}) = 24$ stimuli in the final study. Between $0\%$ and $44\%$ of participants ($\textit{Mdn} = 10\%$) recognised each selected name as familiar---in most cases, participants reported that targets reminded them of fellow students, former classmates, or co-workers.

\section{Appendix B: Social Identity Structures}

Van Dommelen et al. \citeyear{dommelen_construing_2015} analysed participants' responses as \emph{Social Identity Inclusiveness}, i.e. the total number of 24 targets a participant had categorized as ``us'', and as \emph{Social Identity Structures}, i.e. the specific structures proposed by \citeA{roccas_social_2002}. Neither measure translated well to the present study. As participants had different caste backgrounds, comparing their inclusiveness scores ($M = 15.34$, $\textit{SD} = 4.88$, $\textit{Mdn} = 16$) was less meaningful than in \citeauthor{dommelen_construing_2015}'s sample. Coding structures was interesting in principle, but proved difficult in practice.  Few (9\%, $n = 26$) participants consistently classified all targets in each category as either ``us'' or ``not us''. Relatedly, how participants classified targets within a category was correlated, but only moderately so ($.41 \leq rs \leq.66$, see Table ~\ref{tab:ch4-s4-2}). The inconsistency in participants' responses made hard and fast coding rules, as used by \citeauthor{dommelen_construing_2015}, impractical.

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Mean intra and inter-category correlations for target categorizations]{Mean \emph{intra}-category (\textbf{diagonal}) and \emph{inter}-category correlations between participants' categorizations of targets in the respective categories.}
\small	
\begin{tabular}{rlrrrr|rr} \toprule
\# & Category            & 1   & 2   & 3   & 4   & 5   & 6   \\ \midrule \addlinespace
1  & Indian, Hindu, GM   & \textbf{.48} & .56 & .33 & .43 & .16 & .08 \\
2  & Indian, Hindu, OBC  & .56 & \textbf{.41} & .29 & .46 & .09 & .06 \\
3  & Indian, Hindu, SCST & .33 & .29 & \textbf{.66} & .35 & .03 & .16 \\
4  & Indian, Muslim, OBC & .43 & .46 & .35 & \textbf{.52} & .01 & .24 \\ \midrule
5  & Foreign, Hindu      & .16 & .09 & .03 & .01 & \textbf{.50} & .47 \\
6  & Foreign, Muslim     & .08 & .06 & .16 & .24 & .47 & \textbf{.51} \\ \addlinespace \bottomrule
\end{tabular}
\label{tab:ch4-s4-2}
\end{table}

Instead, we quantified the (dis)similarity between a participant's responses and various proposed social identity structures by calculating edit distances. We operationalised \emph{edit distance} as the number of a participant's categorizations that would need to change from ``us'' to ``not us'' (and vice versa) to make them identical to the categorizations implied by a certain structure. Figure~\ref{fig:b-1} shows the distributions of participants' edit distances from each structure, as well as median edit distances.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/appendices/appendices-b-1}
\caption[Edit distances between social identity structures and participants' responses]{Edit distances between each social identity structure and participants' responses. Edit distance is the sum of all categorizations in which a participant's responses differed from the ones implied by the proposed structure. Numbers (on the right) show the median edit distance per structure. %Points indicate the median \emph{social identity inclusiveness} of participants' responses at a specific edit distance.
}
\label{fig:b-1}
\end{figure}

Overall, participants' responses most closely resembled the Indian-Hindu merger structure ($\textit{Mdn} = 5.0$), in which participants include all targets who are \emph{either} Indian \emph{or} Hindu \emph{or} both in the ingroup. This was closely followed by inclusive nationalism ($\textit{Mdn} = 6.5$), i.e. participants include all targets who are Indian, and Hindu nationalism ($\textit{Mdn} = 7.0$), i.e. participants include only Indian Hindu targets. In addition, Pan-Hinduism ($\textit{Mdn} = 8.0$), i.e. participants include all Hindu targets, and egalitarianism ($\textit{Mdn} = 8.0$), i.e. participants include all targets, somewhat described participants' responses. Caste did not seem to dominate participants' responses ($\textit{Mdn} = 12.0$). Together, these observations suggested that, on the broadest level of analysis, participants relied on nationality and religion, rather than caste, to define their ingroup.

\section{Appendix C: Intergroup Threat}

We tested whether participants' perceptions of \emph{realistic} and \emph{symbolic threat} differed depending on the inclusiveness of their ingroup construals. Specifically, we examined whether participants reported feeling less threatened by Muslims and Dalits if they categorized more targets from these outgroups as ``us'' versus ``not us''. We excluded responses from Scheduled Caste/Scheduled Tribe participants to Scheduled Caste/Scheduled Tribe targets as we were interested in perceptions of \emph{inter}group threat. Models~0 to 7 estimated participants' mean responses, between $1 = \textit{strongly disagree}$ and $5 = \textit{strongly agree}$, to each of the $ 5 (\text{items}) \times 2 (\text{outgroups}) = 10$ items. Models derived the likelihood of the observed responses from the normal likelihood distribution: $$ y_{ij} \sim \text{Normal} (\mu_{ij}, \sigma) $$ where $y$ is the vector of participants' responses to each item, and $\mu_{ij}$ is the estimated mean response to item $i$ by participant $j$, $\sigma$ is the estimated residual variance (expressed as standard deviation).

Models~0 to 3 tested whether participants' responses differed across the two subscales (realistic vs symbolic threat) and across the two outgroups (Muslims vs Dalits).  Model 0 estimated item responses as varying between participants but fixed across all items: $$ \mu_{ij} = \beta_0 + \beta_{j} $$ where $\mu_{ij}$, the estimated mean response to item $i$ by participant $j$, equals $\beta_0$, the fixed intercept across items and participants, plus $\beta_j$, the varying intercept for participant $j$. Instead of assigning the same mean to all items, Model~1 included distinct intercepts for the two subscales: $$ \mu_{ij} = \beta_k + \beta_{j} $$ where $\beta_k$ is the fixed intercept for all items $i$ in subscale $k$, with $k = 1$ for realistic threat and $k = 2$ for symbolic threat. Model 2 instead estimated distinct intercepts for items concerning the two outgroups: $$ \mu_{ij} = \beta_l + \beta_{j} $$ where $\beta_l$ is the fixed intercept for all items $i$ for outgroup $l$, with $l = 1$ for Dalits and $l = 2$ for Muslims as the relevant outgroup. Model 3 tested the interaction of the two factors, and estimated distinct intercepts for all four combinations of subscales and outgroups: $$ \mu_{ij} = \beta_m + \beta_{j} $$ where $\beta_m$ is the fixed intercept for realistic threat from Dalits (when $m = 1$), for symbolic threat from Dalits (when $m = 2$), for realistic threat from Muslims (when $m = 3$), and for symbolic threat from Muslims (when $m = 4$).

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Model comparison for intergroup threat]{Comparison of models estimating participants' intergroup threat. We preferred a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.}
\small	
\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrr} \toprule
\# &  &  Description &  $R^2$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule \addlinespace
0 &      & \textit{Varying intercept} & .31 & -3368.1 & 32.9 & - & - & - & .11 \\
1 & vs 0 & \textit{Subscales}         & .31 & -3368.9 & 32.9 & -0.8 & 0.6 & -1.3 & .00 \\
2 & vs 0 & \textit{Outgroups} & .32 & -3363.7 & 33.0 & 4.4 & 3.3 & 1.3 & .00 \\
3 & vs 0 & \textit{Subscales $\times$ Outgroups} & .33 & -3335.1 & 34.0 & 33.0 & 8.4 & 3.9 & .19 \\ \midrule
4 & vs 3 & \textit{Categorizations}   & .33 & -3335.5 & 34.0 & -0.3 & 0.6 & -0.5 & .00 \\
5 & vs 3 & \textit{Categorizations}   & .34 & -3330.5 & 34.0 & 4.7 & 3.6 & 1.3 & .71 \\
6 & vs 3 & \textit{Categorizations}   & .33 & -3336.7 & 34.0 & -1.5 & 0.7 & -2.1 & .00 \\
7 & vs 3 & \textit{Categorizations}   & .34 & -3332.8 & 34.0 & 2.3 & 3.6 & 0.6 & .00 \\ \addlinespace \bottomrule
\end{tabularx}
\label{tab:c-1}
\end{table}

Model~3, but not Models 1 and 2, improved upon the predictions of Model~0 (Table~\ref{tab:c-1}), showing that participants' perceptions of symbolic and realistic threat depended on whether the relevant outgroup was Muslims or Dalits. Specifically, participants reported more realistic ($ \beta_1 = 3.62$, $[3.49, 3.75]$) than symbolic ($\beta_2 = 3.21$, $[3.09, 3.33]$) threat from (same-religion) Dalits, $\text{Pr} (\beta_1 > \beta_2|M3) > .99$, but less realistic ($\beta_3 = 3.23$, $[3.06, 3.38]$) than symbolic ($\beta_4 = 3.47$, $[3.34, 3.61]$) threat from (different-religion) Muslims, $\text{Pr} (\beta_3 < \beta_4| M3) > .99$.

Models 4 to 7 tested whether the proportion of \emph{Indian, Muslim, OBC} and \emph{Indian, Hindu, SC/ST} targets participants had categorized as ``us'' was associated with less perceived threat from, respectively, Muslims and Dalits. Model~4 estimated this relationship as constant across outgroups and subscales: $$ \mu_{ij} = \beta_m + \beta_{j} + \beta_{Q1}x_{Q1,jl} $$ where $x_{Q1,jl}$ is the proportion [0--1] of targets belonging to outgroup $l$ that participant $j$ categorized as ``us'', and $\beta_{Q1}$ estimates the difference in threat perceptions between participants who categorized all four targets of outgroup $l$ as ``us'' and participants who categorized all targets of outgroup $l$ as ``not us''. Models~5 to 7 instead estimated distinct coefficients $\beta_{Q1,k}$ for each of the two subscales (M5), $\beta_{Q1,l}$ for each of the two outgroups (M6), or $\beta_{Q1,m}$ for each of the four combinations of subscales and outgroups (M7). Other than expected, Models~4 to 7 did not make better out-of-sample predictions than Model 3, indicating that whom participants considered ``us'' and ``not us'' was not associated with their perceptions of intergroup threat.

\section{Appendix D: Support for Social Change}

We used the following analytic strategy: First, we tested for \emph{group differences} in participants' perceptions of (dis-)advantage and in their support for affirmative action. Second, we analysed to what extent contact experiences and ingroup construals explained \emph{individual differences} in participants' responses. We examined participants' responses to measures concerning outgroup members to test the \emph{solidarity hypothesis} (that positive contact encourages advantaged-group members to support social change). We examined participants' responses to measures concerning their ingroup to test the \emph{demobilisation hypothesis} (that positive contact discourages disadvantaged-group members from supporting social change) and the \emph{mobilisation hypothesis} (that negative contact encourages disadvantaged-group members to support social change).

\subsubsection{Group differences}

We investigated how participants' caste memberships shaped their perceptions of life difficulty and their support for reservations. To that end, we estimated two Bayesian multivariate models in \emph{RStan} \cite{rstan_package} with participants' responses to six perceived life difficulty and three policy support measures as outcome variables.\footnote{For this analysis, we aggregated items so that target groups corresponded across the two outcome measures. For perceived life difficulty, we aggregated items for Scheduled Caste and Scheduled Tribe groups, resulting in six variables. For policy support, We aggregated items for Scheduled Castes / Scheduled Tribes reservations, and for Other Backward Classes reservations, resulting in three variables.} Both models estimated how participant $j$ responded to each of the nine outcomes. Models derived the likelihood of the observed responses from a multivariate normal distribution: $$ \textbf{Y} \sim \text{MVNormal} (\mu_{jk}, \textbf{S} ) $$ where $\textbf{Y}$ is the matrix of observed variable scores (columns) across participants (rows), $\mu_{jk}$ is the estimated response to item $k$ by participant $j$, and $\textbf{S}$ is the variance-covariance matrix across variables. This means that models estimated distinct means and residual variances for each outcome, as well as residual correlations between all outcomes. Models assigned weakly informative priors to all intercepts, coefficients, and residual variances: 
\begin{align*} 
\beta & \sim \text{Normal} (0, 1) \\ 
\sigma & \sim \text{Cauchy} (0, 1)
\end{align*}
allowing a wide range of plausible effect sizes. Model~0 estimated distinct means for each outcome, but did not consider participants' group memberships: $ \mu_{jk} =  \beta_k $, where $\mu_{jk}$ equals $\beta_{k}$, the fixed intercept for outcome $k$. Model~1 estimated distinct means across participants' ingroups: $ \mu_{jk} =  \beta_k + \beta_{k,\text{OBC}} + \beta_{k,\text{SCST}} $, where $\mu_{jk}$ equals $\beta_k$, the fixed intercept for outcome $k$, plus $\beta_{k,\text{OBC}}$ and $\beta_{k,\text{SCST}}$, the coefficients estimating by how much Other Backward Class and Scheduled Caste~/ Scheduled Tribe participants' responses differed from General Merit participants'. Model~1 made better out-of-sample predictions than Model~0, $\Delta\textit{ELPD} = 94.7$, $SE = 14.1$, $\frac{\Delta\textit{ELPD}}{\textit{SE}} = 6.7$. This comparison shows that participants' caste memberships shaped their perceived discrimination and policy support ratings.

Figure \ref{fig:ch5-s4-1} shows estimated mean ratings of perceived life difficulty for all target groups as a function of participants' caste memberships in Model~1. For most target groups, General Merit and Other Backward Class participants' responses closely resembled each other. On average, General Merit~/ Other Backward Class participants thought that it was somewhat hard (below the midpoint) for ``people from [their] own background'' to succeed. General Merit~/ Other Backward Class participants agreed with each other that it was a lot easier for people from Scheduled Caste~/ Scheduled Tribe backgrounds to succeed, compared to people from their own background. General Merit~/ Other Backward Class participants also agreed that, of all target groups, life was most difficult for people from General Merit backgrounds. Other Backward Class participants disagreed with General Merit participants when rating life difficulty for people from Other Backward Class backgrounds. General Merit participants rated life difficulty for Other Backward Class people as somewhat easy, while Other Backward Class participants tended toward ``neither easy nor hard'' and ``somewhat hard''. Scheduled Caste~/ Scheduled Tribe participants' responses differed markedly from General Merit and Other Backward Class participants'. For all target groups, Scheduled Caste~/ Scheduled Tribe participants rated life difficulty as ``neither easy nor hard'', on average. General Merit, Other Backward Class, and Scheduled Caste~/ Scheduled Tribe participants all tended to rate life difficulty for Muslims as around the midpoint. Overall, participants' responses seemed to contradict, or even reverse, persisting social inequalities (see Chapter~4, \emph{Caste, religion, and nation in South India}).

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/figure-7}
\caption{
Posterior probabilities of perceived (dis-)advantage ratings for different target groups (right) by participants' caste ingroup (left). Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
}
\label{fig:ch5-s4-1}
\end{figure}

Figure \ref{fig:ch5-s4-2} shows estimated policy support---that is, support for reservations benefiting Scheduled Caste~/ Scheduled Tribe, Other Backward Class, and Muslim students---as a function of participants' caste memberships in Model~1. General Merit and Other Backward Class participants' responses did not provide evidence for cross-group solidarity. General Merit participants tended to oppose reservations for Scheduled Caste~/ Scheduled Tribe ($M = 1.87$, $[1.63, 2.12]$), Other Backward Class ($M = 2.70$, $[2.44, 2.96]$), and Muslim students ($M = 2.75$, $[2.46, 3.01]$). Other Backward Class participants tended to support reservations for their own group ($M = 3.72$, $[3.50, 3.95]$), but not for Scheduled Caste~/ Scheduled Tribe ($M = 2.31$, $[2.10, 2.53]$) or Muslim ($M = 2.79$, $[2.55, 3.04]$) students. Scheduled Caste~/ Scheduled Tribe participants tended to support reservations for their own group ($M = 4.16$, $[3.88, 4.45]$), for Other Backward Class students ($M = 3.57$, $[3.27, 3.86]$), and, to a lesser extent, for Muslim students ($M = 3.24$, $[2.92, 3.57]$). Overall, participants' responses provided evidence for solidarity from Scheduled Caste~/ Scheduled Tribe participants to Other Backward Class students, but not for solidarity from General Merit and Other Backward Class participants to Scheduled Caste~/ Scheduled Tribe students.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/figure-8}
\caption{
Posterior probabilities of policy support ratings for different target groups (right) by participants' caste ingroup (left). Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
}
\label{fig:ch5-s4-2}
\end{figure}

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Estimated residual correlations in Models 0 and 1 for Study 4]{Estimated residual correlations between six \emph{perceived life difficulty} (PD) ratings and three \emph{policy support} (PS) ratings in Model~0 (below the diagonal) and Model~1 (above the diagonal) for Study 4.}
\small	
\begin{tabularx}{\linewidth}{rl@{~}Xrrrrrr|rrr} \toprule
\# & \multicolumn{2}{l}{Variable} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ \midrule \addlinespace
1 & PD, & \ldots own background & \textbf{}  & .14 & .30 & .45 & .43 & .05 & .28 & .12 & .14 \\
2 & PD, & SC/ST  & .10 & \textbf{} & .33 & -.13 & -.09 & .28 & -.12 & -.10 & -.05 \\
3 & PD, & OBC    & .28 & .33 & \textbf{} & .20 & .16 & .32 & .05 & -.17 & -.13  \\
4 & PD, & GM     & .47 & -.18 & .18 & \textbf{} & .61 & -.08 & .24 & .15 & .02 \\
5 & PD, & Hindu  & .44 & -.12 & .15 & .62 & \textbf{} & -.01 & .29 & .11 & .03  \\
6 & PD, & Muslim & .04 & .28 & .31 & -.10 & -.02 & \textbf{} & .02 & -.17 & -.15 \\ \midrule
7 & PS, & SC/ST  & .29 & -.24 & -.03 & .33 & .30 & -.03 & \textbf{} & .24 & .34 \\
8 & PS, & OBC    & .11 & -.13 & -.25 & .17 & .12 & -.16 & .28 & \textbf{} & .47 \\
9 & PS, & Muslim & .16 & -.09 & -.13 & .06 & .05 & -.16 & .36 & .45 & \textbf{}   \\ \addlinespace \bottomrule
\end{tabularx}
\label{tab:ch5-s4-1}
\end{table}

Table~\ref{tab:ch5-s4-1} shows the estimated residual correlations before (Model~0) and after (Model~1) accounting for group differences. Perceiving a group to be disadvantaged correlated weakly with more support for reservations benefiting Scheduled Caste~/ Scheduled Tribe ($r = -.12 $, $[-.24,.01]$), Other Backward Class ($r = -.17$, $[-.30,-.05]$), and Muslim ($r = -.15$, $[-.28,-.03]$) students in Model~1. Support for reservations for one target group correlated moderately with support for reservations for the other target groups, $.24 < r < .47$. These correlations provided evidence for systematic variation in policy support ratings across participants, even after accounting for group differences. In the next section, we examine to what extent contact experiences and ingroup construals explain this variation across individuals.

\subsubsection{Individual differences}

We examined to what extent contact experiences and ingroup construals (measured as participants' responses in the crossed-categorization task) accounted for individual differences in perceived life difficulty and policy support. To that end, we estimated a series of Bayesian multilevel models with either perceived life difficulty or policy support as outcome variable. Models derived the likelihood of the observed responses from a normal distribution: $$ y_{ij} \sim \text{Normal} (\mu_{ij}, \sigma) $$ where $y_{ij}$ is the observed response to item $i$ by participant $j$, and $\mu_{ij}$ is the estimated response to item $i$ by participant $j$, $\sigma$ is the estimated residual variance (expressed as standard deviation). We used the same weakly informative priors as for the multivariate models.

First, we estimated participants' responses to each of five perceived life difficulty items, with General Caste (GM), Scheduled Caste (SC), Scheduled Tribe (ST), Other Backward Class (OBC), and Muslims as target groups. Model~0 estimated item responses as varying across participants and target groups, and estimated differences across participants' ingroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} $$ where $\mu_{ij}$, the estimated mean response to item $i$ by participant $j$, equals $\beta_j$, the varying intercept for participant $j$, and $\beta_{kl}$, the varying intercept for target group~$k$ ($1 = \text{GM}$, $2 = \text{OBC}$, $3 = \text{SC/ST}$, $4 = \text{Muslims}$) and ingroup~$l$ ($1 = \text{GM}$, $2 = \text{OBC}$, $2 = \text{SC/ST}$). Model~0 thus resembled the multivariate model estimated above.

Model~1 extended Model~0 by estimating to what extent outgroup friendship and negative contact with outgroup members were associated with perceptions of life difficulty for outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{OF}x_{\text{OG},k}x_\text{OF,jk} + \beta_\text{NC}x_{\text{OG},jk}x_\text{OF,jk}$$ where $x_{\text{OG},jk}$ codes whether target group $k$ is an outgroup [1] or ingroup [0] for participant $j$, $x_\text{OF,jk}$ and $x_\text{NC,jk}$ are, respectively, participant $j$'s outgroup friendship and negative contact with target group $k$, and $\beta_\text{OF}$ and $\beta_\text{NC}$ estimate the increase in participants' ratings for each additional standard deviation of reported contact. Model~2 estimated the effects of outgroup friendship and negative contact on outgroup ratings as varying across target outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_{\text{OF},k}x_{\text{OG},k}x_\text{OF,jk} + \beta_{\text{NC},k}x_{\text{OG},jk}x_\text{OF,jk}$$ where $\beta_{\text{OF},k}$ and $\beta_{\text{NC},k}$ estimate effects of contact on ratings for outgroup $k$. Neither Model~1 nor Model~2 improved upon the out-of-sample predictions of Model~0, showing that intergroup contact neither increased nor decreased participants' perceptions of discrimination against ethnoreligious or caste outgroups (see Table~\ref{tab:ch5-s4-2}).

Models~3 and 4 tested whether participants' ingroup construals were associated with their perceptions of life difficulty for various outgroups. Model~3 estimated this relationship as constant across target groups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1}x_{\text{OG},k}x_\text{Q1,jk} $$ where $x_{Q1,jk}$ is the proportion [0--1] of targets belonging to outgroup $k$ that participant $j$ categorized as ``us'', and $\beta_{Q1}$ estimates the difference in perceived life difficulty between participants who categorized all four targets of an outgroup as ``us'' and participants who categorized all targets of an outgroup as ``not us''. Model~4 estimated this relationship as varying across outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1,k}x_{\text{OG},k}x_\text{Q1,jk} $$ where $\beta_{Q1,k}$ estimates the difference in perceived perceived life difficulty between participants who categorized all four targets of outgroup $k$ as ``us'' and participants who categorized all targets of outgroup $k$ as ``not us''. Neither Model~3 nor Model~4 improved upon the out-of-sample predictions of Model~0, showing that more inclusive identities neither increased nor decreased participants' perceptions of life difficulty for ethnoreligious an caste outgroups. % Overall, Models~1 to 4 did not provide evidence for the solidarity hypothesis or, more specifically, for the solidarity-by-inclusion hypothesis.

Models~5 to 8 tested to what extent contact with (Models~5, 6) and inclusion of advantaged-group members (Models~7, 8) was associated with perceptions of life difficulty for the ingroup. Model~5 estimated how contact with General Merit people affected Scheduled Caste~/ Scheduled Tribe participants' perceptions of life difficulty for their ingroup: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{OF,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{OF,GM,j} + \beta_\text{NC,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{NC,GM,j} $$ where $x_{\text{IG},jk}$ codes whether target group $k$ is an ingroup [1] or outgroup [0] for participant $j$, $x_{\text{SCST,j}}$ codes whether participant $j$ is from an Scheduled Caste~/ Scheduled Tribe background [1] or not [0], $x_\text{OF,j,GM}$ and $x_\text{NC,j,GM}$ are, respectively, participant $j$'s outgroup friendship and negative contact with General Merit people, and $\beta_\text{OF,GM}$ and $\beta_\text{NC,GM}$ estimate the increase in participants' ratings for each additional standard deviation of reported contact with General Merit people. Model~6 extended Model~5 by estimating how contact with General Merit people affected Other Backward Class participants' perceptions of life difficulty for their ingroup: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \ldots + \beta_\text{OF,GM}x_{\text{IG,jk}}x_{\text{OBC,j}}x_\text{OF,GM,j} + \beta_\text{NC,GM}x_{\text{IG,jk}}x_{\text{OBC,j}}x_\text{NC,GM,j} $$ where $x_{\text{OBC,j}}$ codes whether participant $j$ is from an Other Backward Class background [1] or not [0]. Neither Model~5 nor Model~6 improved upon the out-of-sample predictions of Model~0, showing that intergroup contact with advantaged-group members did not increase or decrease disadvantaged-group members' perceptions of life difficulty for their ingroup. Model~7 estimated whether including General Merit targets in their ingroup reduced perceptions of life difficulty among Scheduled Caste~/ Scheduled Tribe participants: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{Q1,GM,j} $$ where $x_{Q1,GM,j}$ is the proportion [0--1] of General Merit targets that participant $j$ categorized as ``us'', and $\beta_{Q1,GM}$ estimates the difference in perceived life difficulty between participants who categorized all four General Merit targets as ``us'' and participants who categorized all General Merit targets as ``not us''. Model~8 extended Model~7 by estimating this relationship among Other Backward Class participants: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{Q1,GM,j} + \beta_\text{Q1,GM}x_{\text{IG,jk}}x_{\text{OBC,j}}x_\text{Q1,GM,j} $$ where $x_{\text{OBC,j}}$ codes whether participant $j$ is from an Other Backward Class background [1] or not [0]. Neither Model~7 nor Model~8 improved upon Model~0, showing that including advantaged-group members in the ingroup did not increase or decrease disadvantaged-group members' perceptions of their ingroup's life difficulty (see Table~\ref{tab:ch5-s4-2}).

\begin{table}
\centering
\figureversion{lining, tabular}
\caption{
Comparison of models estimating participants' group-wise perceived life difficulty ratings. We preferred a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.
}
\small	
\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrr} \toprule
\# &  &  Description & $R^2$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule \addlinespace
0 &      & \textit{Group differences} & .35 & -1789.5 & 24.6 & - & - & - & .00 \\ \addlinespace
1 & vs 0 & \textit{Solidarity}       & .35 & -1791.2 & 24.5 & -1.8 & 1.5 & -1.2 & .00 \\
2 & vs 1 & \textit{Solidarity}       & .35 & -1788.3 & 24.4 & 3.0 & 2.5 & 1.2 & .33 \\
3 & vs 0 & \textit{Solidarity}       & .35 & -1787.0 & 24.7 & 2.5 & 2.4 & 1.0 & .32 \\
4 & vs 3 & \textit{Solidarity}       & .35 & -1787.6 & 24.7 & -0.7 & 2.4 & -0.3 & .23 \\ \addlinespace
5 & vs 0 & \textit{(De)mobilisation} & .35 & -1791.5 & 24.6 & -2.0 & 1.2 & -1.7 & .00 \\
6 & vs 5 & \textit{(De)mobilisation} & .35 & -1792.6 & 24.6 & -1.1 & 0.9 & -1.2 & .00 \\
7 & vs 0 & \textit{(De)mobilisation} & .35 & -1788.9 & 24.5 & 0.5 & 1.4 & 0.4 & .00 \\
8 & vs 7 & \textit{(De)mobilisation} & .35 & -1788.4 & 24.5 & 0.5 & 1.4 & 0.4 & .12 \\ \addlinespace \bottomrule
\end{tabularx}
\label{tab:ch5-s4-2}
\end{table}

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Model comparison for individual differences in policy support for Study 4]{Comparison of models estimating participants' group-wise policy support ratings. As in Table~\ref{tab:ch5-s4-2}, we preferred a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.}
\small	
\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrr} \toprule
\# &  &  Description & $R^2$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule \addlinespace
0 &      & \textit{Group differences} & .49 & -1741.0 & 26.8 & - & - & - & .00 \\ \addlinespace
1 & vs 0 & \textit{Solidarity}       & .50 & -1736.1 & 26.7 &  4.9 & 2.7 & 1.8 & .60 \\
2 & vs 1 & \textit{Solidarity}       & .50 & -1739.9 & 26.8 &   -3.8 & 2.0 & -1.9 & .00 \\
3 & vs 0 & \textit{Solidarity}       & .49 & -1741.0 & 26.9 & 0.0 & 0.7 & 0.0 & .00 \\
4 & vs 3 & \textit{Solidarity}       & .49 & -1741.6 & 26.9 &  -0.6 & 1.1 & -0.5 & .00 \\ \addlinespace
5 & vs 0 & \textit{(De)mobilisation} & .49 & -1742.0 & 26.9 & -0.9 & 1.7 & -0.5 & .03 \\
6 & vs 5 & \textit{(De)mobilisation} & .49 & -1743.3 & 26.9 & -1.3 & 0.8 & -1.6 & .00\\
7 & vs 0 & \textit{(De)mobilisation} & .49 & -1741.6 & 26.8 & -0.6 & 0.8 & -0.8 & .00\\
8 & vs 7 & \textit{(De)mobilisation} & .50 & -1740.0 & 26.8 &  1.6 & 2.0 & 0.8 & .37 \\ \addlinespace \bottomrule
\end{tabularx}
\label{tab:ch5-s4-3}
\end{table}

Second, we estimated participants' responses to each of five policy support items, with Scheduled Caste and Scheduled Tribe (SC/ST), Other Backward Class (OBC), and Muslims as target groups. Model~0 estimated item responses as varying across participants and target groups, and estimated differences across participants' ingroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} $$ where $\mu_{ij}$, the estimated mean response to item $i$ by participant $j$, equals $\beta_j$, the varying intercept for participant $j$, plus $\beta_{kl}$, the varying intercept for target group~$k$ ($1 = \text{SC/ST}$, $2 = \text{OBC}$, $3 = \text{Muslims}$) and ingroup~$l$ ($1 = \text{GM}$, $2 = \text{OBC}$, $2 = \text{SC/ST}$). Model~0 thus resembled the multivariate model estimated in the previous section. Models~1 to 8 were identical to the models for perceived discrimination (described above). Models~1 to 4 did not improve upon the out-of-sample predictions of Model~0, showing that neither intergroup contact (Models~1, 2) nor inclusive identities (Models~3, 4) foster support for policies benefiting a disadvantaged outgroup.  Models~5 to 8 did not improve upon the out-of-sample predictions of Model~0, showing that neither contact with (Models~5, 6) nor inclusion of (Models~7, 8) General Merit people affected Scheduled Caste~/ Scheduled Tribe and Other Backward Class participants' support for policies benefiting their ingroups (see Table~\ref{tab:ch5-s4-3}).

Overall, these findings show that neither intergroup contact nor ingroup construals could explain individual differences in support for social change. Contrary to the \emph{demobilisation hypothesis}, positive contact did not decrease disadvantaged-group participants' support for social change. Contrary to the \emph{mobilisation hypothesis}, negative contact did not increase disadvantaged-group participants' support for social change. Contrary to predictions, neither positive contact nor more inclusive identities were associated with support for policies benefiting (other) disadvantaged outgroups.

\section{Appendix E: Additional Measures}

\subsection{Measures}

Group identification was measured with one item per ingroup \cite{postmes_single_2013}: ``I identify with my [nationality/religion/caste group]'' ($1 = \textit{strongly disagree}$, $7 = \textit{strongly agree}$).

Social identity complexity \cite{roccas_social_2002, schmid_antecedents_2009} was operationalised as the extent to which participants perceived their different group memberships as conceptually interrelated (\emph{similarity complexity}) and numerically overlapping (\emph{overlap complexity}). Two items measured similarity complexity for religion/nationality and for nationality/caste: ``How similar or different are the typical [Hindu/Indian] and the typical [Indian/person from your caste group] to each other?'' ($1 = \textit{very different}$, $5 = \textit{very similar}$, reverse coded), and ``Do you think that being [Hindu/Indian] means the same as being [Indian/from your caste group]?'' ($1 = \textit{means something very similar}$, $5 = \textit{means something very different}$).  Two items measured overlap complexity for religion/nationality: ``How many [Indians/ Hindus] do you think are [Hindus/Indian]?” (\%, $r = .63$). Three items measured overlap complexity for nationality and caste: ``How many Indians do you think are [GC, OBC, SC/ST]?'' (\%, $.33 \leq rs \leq .50$). Overlap items were reverse coded, so that higher scores indicated less perceived overlap.

\emph{Entitativity} \cite{lickel_varieties_2000} was measured with six items: ``Being Indian is important to each Indian, no matter their caste or religion'', ``Indians of all castes and religions interact often with each other.'', ``Indians of all castes and religions are working towards shared goals'', ``What happens to one Indian also impacts other Indians'', ``Indians of all castes and religions depend on one another'', and ``Indians are similar to one another'' ($1 = \textit{strongly disagree}$, $7 = \textit{strongly agree}$, $\alpha = .80$). Participants were encouraged to ``take Indian/Indians to mean Indian citizens of all castes and religions'' when reading the items of this scale. This scale thus measured an inclusive conception of entitativity.

\subsection{Correlates of categorisation}

Aside from testing potential antecedents and consequences, I explored how participants' responses in the crossed-categorisation task related to other measures of social identification. To that end, I estimated the correlations between, on the one hand, the proportions of targets that participants had categorised as ``us'' in each of the six categories, and, on the other hand, the (aggregated) social identification variables described in the \emph{Measures} section. I derived the likelihood of the observed responses from a multivariate normal distribution: $$ \textbf{Y} \sim \text{MVNormal} (\mu , \textbf{S} ) $$ where $\textbf{Y}$ is the matrix of observed variable scores (columns) across participants (rows), $\mu$ is the vector of all variable means, and $\textbf{S}$ is the variance-covariance matrix across variables.

Figure~\ref{fig:ch4-appendix-1} shows the estimated correlations between participants' categorisations in the crossed-categorisation task (from left to right) and various social identification variables (from top to bottom). Entitativity---the extent to which participants saw Indians of \emph{all} castes and religions as similar to one another, as depending on each other, as sharing a common fate, as working towards shared goals, and as valuing their shared identity---was positively correlated with the proportion of \emph{Indian, Hindu, GM} ($r = .16$, $[.04, .27]$, $\text{Pr} (r > 0|M) > .99$), \emph{Indian, Hindu, OBC} ($r = .21$, $[.09, .31]$, $\text{Pr} (r > 0| M) > .99$), \emph{Indian, Hindu, SC/ST} ($r = .10$, $[-.02, .22]$, $\text{Pr} (r > 0| M) = .97$), and \emph{Indian, Muslim, OBC} ($r = .18$, $[.07, .30]$, $\text{Pr} (r > 0| M) > .99$) targets participants categorised as ``us''.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/appendices/appendices-e-1}
\caption[Correlations between social identity variables and target categorisations]{Correlations between various social identity variables (top to bottom) and the proportion of targets that participants had categorised as ``us'' in each target category (left to right). Points indicate the most likely estimate for a given correlation, while lines encompass the 97\% most likely estimates of that correlation. Curves show the density distributions of the posterior probabilities, based on all samples from the posterior probability distribution. Correlations for which $\text{Pr} (r > 0| M) > .99$ or $\text{Pr} (r < 0| M) > .99$ are shown in a darker shade.}
\label{fig:ch4-appendix-1}
\end{figure}

Group identification was only associated with participants' categorisations of foreign targets, not their categorisations of Indian targets. The extent to which participants identified with their religion was negatively correlated with how many \emph{foreign, Hindu} ($r = -.14$, $[-.25, -.02]$, $\text{Pr} (r > 0| M) > .99$) and \emph{foreign, Muslim} ($r = -.18$, $[-.29, -.07]$, $\text{Pr} (r > 0| M) > .99$) targets participant categorised as ``us''. I obtained similar correlations for the extent to which participants identified with their caste group, $r = -.15$, $[-.27, -.04]$, $\text{Pr} (r > 0| M) > .99$ and $r = -.17$, $[-.29, -.06]$, $\text{Pr} (r > 0| M) > .99$, respectively. The extent to which participants identified with their nationality was not associated with participants' categorisations---perhaps because there was a little variation in participants responses, with 81\% of participants strongly agreeing with the statement. Other variables were not systematically correlated with participants' responses in the crossed-categorisation task (see Figure~\ref{fig:ch4-appendix-1}).

Correlations thus confirmed that participants' categorisations were more than a straight-forward reflection of the strength of their group identification, affirming the value of the crossed-categorisation task for studying identification in contexts with multiple, cross-cutting group memberships. Furthermore, participants' perceptions of entitativity across caste and religions were associated with more inclusive construals of national identity, providing tentative evidence for its potential for fostering more inclusive identities.

\bibliographystyle{apacite}
\bibliography{references}

\end{document}

### 2018-10-26 manuscript/figures_and_tables.tex
add appendices

@@
 \caption{
-Schematic representations of social identity structures, ordered by social identity inclusiveness.
+Schematic representations of social identity structures, ordered by social identity inclusiveness (van Dommelen, Schmid, Hewstone, Gonsalkorale, \& Brewer , 2015).
 Shaded regions represent the groups which a participant has to categorize as ``us'' to be assigned that structure.
@@
 \caption{
-Posterior probabilities of perceived life difficulty ratings for different target groups (right) by participants' caste ingroup (left).
+Posterior probabilities of perceived (dis-)advantage ratings for different target groups (right) by participants' caste ingroup (left).
 Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.

### 2018-10-26 manuscript/manuscript.tex
add stratified kfold cv
add appendices

--- 2018-08-16 manuscript/figures_and_tables.tex
@@
 \usepackage{layout}
+\setlength{\parindent}{0.5in}
+\setcounter{secnumdepth}{0}
+\usepackage{lineno}
+%\usepackage{authblk}
 
@@
 \usepackage[super]{nth}
-\usepackage{tfrupee}
 
@@
 
+% Frontmatter
+\title{Intergroup contact fosters\\more inclusive social identities}
+\date{November 5, 2018}
+%\author{Nils Karl Reimer}
+%\author[2]{Shanmukh V. Kamble}
+%\author[3]{Katharina Schmid}
+%\author[1]{Miles Hewstone}
+%\affil[1]{University of Oxford}
+%\affil[2]{Karnatak University}
+%\affil[3]{ESEADE Business School, Ramon Llull University}
+%\renewcommand\Affilfont{\small}
+
 \begin{document}
 
-% Captions
-\captionsetup[figure]{font={small},labelfont={it},labelformat={default}, labelsep=period}
-\captionsetup[table]{font={small},labelfont={it},labelformat={default}, labelsep=period}
+\maketitle
 
-\begin{table}[h]
-\caption[Participants by gender, age, nationality, religion, and caste]{Participants by gender, age, nationality, religion, and caste.
-Categories in \textit{italics} were excluded from the final sample.
-N/A marks missing responses.}
-\centering
-\figureversion{lining, tabular}
-\small	
-\begin{tabular}{llrr} \addlinespace \toprule
-\multicolumn{2}{l}{Category} & $n$ & \% \\ \midrule \addlinespace 
-Gender      & Woman      & 215 & 61 \\
-            & Man & 121 & 34 \\
-            & Other & 0 & 0 \\
-            & N/A & 15 & 4 \\ \addlinespace \addlinespace
-Age         & 18--20 & 1 & 0 \\
-            & 21--23 & 254 & 72 \\
-            & 24--26 &  77 & 22 \\
-            & 27--29 &  10 &  3 \\
-            & 30--32 &   1 &  0 \\
-            & 33--35 &   0 &  0 \\
-            & 36 or older & 1 & 0 \\ 
-            & N/A & 7 & 2 \\ \addlinespace \addlinespace
-Nationality & Indian & 339 & 97 \\
-            & Other & 0 & 0 \\
-            & N/A & 12 & 3 \\ \addlinespace \addlinespace
-Religion    & Buddhism & 1 & 0 \\ 
-            & Christianity & 11 & 3 \\ 
-            & Hinduism & 297 & 85 \\ 
-            & \textit{Islam} & \textit{27} & \textit{8} \\ 
-            & Jainism & 8 & 2 \\ 
-            & Other & 2 & 1 \\ 
-            & N/A & 5 & 1 \\ \addlinespace \addlinespace
-Caste       & General Caste & 104 & 30 \\ 
-            & Other Backward Class & 143 & 41 \\ 
-            & Scheduled Caste & 54 & 15 \\ 
-            & Scheduled Tribe & 23 & 7 \\ 
-            & \textit{Other / Not applicable} & \textit{20} & \textit{6} \\ 
-            & \textit{N/A} & \textit{7} & \textit{2} \\ \addlinespace \midrule
-Total       &   & 351 & 100 \\ \bottomrule
-\end{tabular}
-\label{tab:t1}
-\end{table}
+\begin{abstract}
+\noindent We examined how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce bias by fostering more inclusive identities.
+Participants ($N = 351$) viewed 24 identity cards, each representing a person with whom participants shared none, one, two, or all three group memberships.
+Participants reported whether they considered each person as ``us'' or ``not us'', showing whom they included in their ingroup, and whom they excluded.
+We found that participants from diverse caste backgrounds tended to exclude caste and religious outgroups, replicating persistent social divides in South India.
+Bridging these divides, cross-group friendship was associated with more inclusive identities which, in turn, were associated with more favourable outgroup attitudes.
+Negative contact was associated with less inclusive identities, showing that past experiences shaped whom participants considered ``us'' and ``not us''.
+Contact and identity processes were unrelated to support for affirmative action in advantaged and disadvantaged groups.\\[1ex]
+\noindent \textbf{Keywords:} intergroup contact, social identity, multiple categorization, intergroup relations, affirmative action, caste, nationalism \\[1ex]
+\end{abstract}
+
+\linenumbers
+
+\noindent How we feel about and act toward others depends on whom we consider ``us'' and ``them''---that is, whom we include in our ingroup, and whom we exclude (for a review, see \citeNP{authors_theories_inpress}).
+In some situations, it is clear who is in the ingroup and who is not.
+On a football pitch, for example, players tend to think of their own team as ``us'', and of the other team as ``them'', and try their best to make their own team win.
+In diverse settings, this distinction is less clear because people belong to multiple, overlapping groups.
+Individuals differ in how they construct their ingroup from these group memberships.
+Some espouse narrow definitions of who is ``us'' and ``them'', while others adopt more inclusive identities (see Figure~\ref{fig:f1}).
+Many Americans, for example, associate being American with being White American \cite{devos_american_2005}.
+This suggests that whom Americans consider ``us'' and ``them'' might depend on someone's race \emph{and} nationality.
+In this paper, we examine how group memberships shape whom people consider ``us'' and ``not us'', and whether intergroup contact can reduce prejudice by fostering inclusive social identities.
 
@@
 \includegraphics[scale=1]{../figures/figure-1}
-\caption{Examples of targets used in the triple crossed-categorization task.
-Based on ratings in pilot study ($N = 26$), we selected the four most prototypical targets (out of fifty initial targets) for each of six plausible combinations of caste, religion, and nationality (for details, see Appendix~A).
-Each target showed a person's caste (GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe), religion (Hindu, Muslim), and nationality (Indian, Nepali, Sri Lankan, Bangladeshi).
-Each target also showed the person's first and last name, age (21--26 years), and a silhouette corresponding to the person's gender (adapted from Ma, Correll \& Wittenbrink, 2015).
-Each target's age and silhouette, as well as the order in which the targets were presented, varied across sessions.}
+\caption{
+Schematic representations of social identity structures, ordered by social identity inclusiveness \protect\cite{dommelen_construing_2015}.
+Shaded regions represent the groups which a participant has to categorize as ``us'' to be assigned that structure.
+An Indian Hindu, for example, may consider only people who share their nationality, religion, and caste as ingroup members (intersection).
+Someone else may consider all their fellow Indians, whatever their religion or caste, as ingroup members (dominance).
+Another person may consider anyone who shares their nationality or religion as ingroup members (merger).
+}
 \label{fig:f1}
@@
 
-\begin{table}
-\caption{}
-\centering
-\figureversion{lining, tabular}
-\small	
-\begin{tabularx}{\linewidth}{r@{~}rXrrrrr} \toprule
-\# &  & Description & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
-0 &      & \ldots & -4262.5 & 33.0 & - & - & - \\
-1 & vs 0 & \ldots & -3156.0 & 46.7 & 1106.6 & 42.7 & 25.9 \\
-2 & vs 1 & \ldots & -3073.5 & 47.3 &   82.5 & 11.9 &  6.9 \\
-3 & vs 2 & \ldots & -3068.1 & 47.4 &    5.4 &  3.4 &  1.6 \\ \midrule
-4 & vs 2 & \ldots & . & . & . & . & . \\
-5 & vs 4 & \ldots & . & . & . & . & . \\
-6 & vs 5 & \ldots & . & . & . & . & . \\
-7 & vs 2 & \ldots & . & . & . & . & . \\
-\bottomrule
-\end{tabularx}
-\label{tab:t2}
-\end{table}
+\nolinenumbers
 
-\begin{figure}
-\centering
-\includegraphics[scale=1]{../figures/figure-2}
-\caption{
-Estimated probability of participants categorizing a target as ``us'' versus ``not us'' by targets' nationality, religion, and caste (vertical), and participants' caste membership (horizontal).
-Dots (•) indicate the most likely \emph{estimate} for a given target's probability of being included in participants' ingroup (in Model~2, Table~\ref{tab:t2}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most likely estimates of that probability.
-Pluses (+) indicate the \emph{observed} proportion of participants who included a given target in their ingroup.
-% Add sentence about posterior predictive checking.
-}
-\label{fig:f2}
-\end{figure}
-
-\begin{figure}
-\centering
-%\includegraphics[scale=1]{../figures/figure-3}
-\caption{Estimated probability of participants categorising a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship with the relevant groups         (in Model~5, Table~\ref{tab:t2}).}
-\label{fig:f3}
-\end{figure}
-
-\begin{table}
-\caption{}
-\centering
-\figureversion{lining, tabular}
-\small	
-\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrr} \toprule
-\# &  & Description & $R^2_\text{Q2}$ & $R^2_\text{Q3}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
-0 &      & \ldots & . & . & . & . & . & . & . \\
-1 & vs 0 & \ldots & . & . & . & . & . & . & . \\
-2 & vs 1 & \ldots & . & . & . & . & . & . & . \\
-3 & vs 2 & \ldots & . & . & . & . & . & . & . \\ \midrule
-4 & vs 3 & \ldots & . & . & . & . & . & . & . \\
-5 & vs 4 & \ldots & . & . & . & . & . & . & . \\
-6 & vs 5 & \ldots & . & . & . & . & . & . & . \\
-\bottomrule
-\end{tabularx}
-\label{tab:t3}
-\end{table}
+\bibliographystyle{apacite}
+\bibliography{references}
 

### 2018-10-26 figures/figures-7-and-8.R

@@ -70,7 +70,7 @@ rm(list = ls())
     coord_fixed(ratio = 1/2, xlim = c(0.9,7.1), ylim = c(0.8, 4), expand = FALSE) +
     facet_grid(group ~ .) +
     labs(
-      x = "Perceived life difficulty",
+      x = "Perceived (dis-)advantage",
       y = "Ingroup"
     ) +
     theme_grey(base_size = 10) +

### 2018-10-26 results_consequences.R

@@ -10,9 +10,6 @@ rm(list = ls())
   options(mc.cores = parallel::detectCores())
   rstan_options(auto_write = TRUE)
   seeds = c(1157744, 2691555, 4045395, 2910499, 5195618, 5975015, 2391421)
-  
-
-# Functions ---------------------------------------------------------------
 
 
 # Import ------------------------------------------------------------------

### 2018-10-26 results_individual_differences.R

@@ -11,7 +11,6 @@ rm(list = ls())
   # value (from the posterior distribution of the imputation model) for each 
   # missing value (in the original dataset).
 
-  # Add note about SDO.
 
 # Library -----------------------------------------------------------------
   library(tidyverse); library(rstan); library(tidybayes); library(loo)

### 2018-10-26 manuscript/appendices.tex
update appendices

@@
 
-Informed by local knowledge, we intended to rely on last names to unobtrusively communicate caste membership in the crossed-categorization task.
-To find the most prototypical stimuli, wecompiled an initial set of 50 surnames, drawing on local knowledge, databases on naming preferences, and publicly available archives of Facebook usernames.
+Informed by local knowledge, we intended to rely on last names to unobtrusively communicate caste membership in the triple crossed-categorization task.
+To find the most prototypical stimuli, we compiled an initial set of 50 surnames, drawing on local knowledge, databases on naming preferences, and publicly available archives of Facebook usernames.
 We selected 10 surnames for each of five combinations of nationality, religion, and caste: (1) Indian Hindus of upper-caste backgrounds, (2) Indian Hindus of lower-caste backgrounds (Dalits), (3) Indian Muslims, (4) foreign Hindus, and (5) foreign Muslims.
@@
 
-Participants' responses had important implications for designing the crossed-categorization task.
+Participants' responses had important implications for designing the triple crossed-categorization task.
 On average, participants regarded all targets' names as at least ``somewhat typical'' $(1.42 \le \textit{Ms} \le 3.50)$.
@@
 Few (9\%, $n = 26$) participants consistently classified all targets in each category as either ``us'' or ``not us''.
-Relatedly, how participants classified targets within a category was correlated, but only moderately so ($.41 \leq rs \leq.66$, see Table ~\ref{tab:ch4-s4-2}).
+Relatedly, how participants classified targets within a category was correlated, but only moderately so ($.41 \leq rs \leq.66$, see Table ~\ref{tab:b-1}).
 The inconsistency in participants' responses made hard and fast coding rules, as used by \citeauthor{dommelen_construing_2015}, impractical.
@@
 \end{tabular}
-\label{tab:ch4-s4-2}
+\label{tab:b-1}
 \end{table}
@@
 
-We used the following analytic strategy: First, we tested for \emph{group differences} in participants' perceptions of (dis-)advantage and in their support for affirmative action.
+We tested whether more inclusive identities increase support for affirmative action among advantaged-group members, but decrease support for these policies among disadvantaged-group members.
+First, we tested for \emph{group differences} in participants' perceptions of (dis-)advantages and in their support for affirmative action.
 Second, we analysed to what extent contact experiences and ingroup construals explained \emph{individual differences} in participants' responses.
@@
 
-We investigated how participants' caste memberships shaped their perceptions of life difficulty and their support for reservations.
-To that end, we estimated two Bayesian multivariate models in \emph{RStan} \cite{rstan_package} with participants' responses to six perceived life difficulty and three policy support measures as outcome variables.\footnote{For this analysis, we aggregated items so that target groups corresponded across the two outcome measures.
-For perceived life difficulty, we aggregated items for Scheduled Caste and Scheduled Tribe groups, resulting in six variables.
+We investigated how participants' caste memberships shaped their perceptions of (dis-)advantages and their support for reservations.
+To that end, we estimated two Bayesian multivariate models in \emph{RStan} \cite{rstan_package} with participants' responses to six perceived (dis-)advantage and three policy support measures as outcome variables.\footnote{For this analysis, we aggregated items so that target groups corresponded across the two outcome measures.
+For perceived (dis-)advantage, we aggregated items for Scheduled Caste and Scheduled Tribe groups, resulting in six variables.
 For policy support, We aggregated items for Scheduled Castes / Scheduled Tribes reservations, and for Other Backward Classes reservations, resulting in three variables.} Both models estimated how participant $j$ responded to each of the nine outcomes.
@@
 Model~1 made better out-of-sample predictions than Model~0, $\Delta\textit{ELPD} = 94.7$, $SE = 14.1$, $\frac{\Delta\textit{ELPD}}{\textit{SE}} = 6.7$.
-This comparison shows that participants' caste memberships shaped their perceived discrimination and policy support ratings.
+This comparison shows that participants' caste memberships shaped their perceived (dis-)advantage and policy support ratings.
 
-Figure \ref{fig:ch5-s4-1} shows estimated mean ratings of perceived life difficulty for all target groups as a function of participants' caste memberships in Model~1.
+Figure \ref{fig:d-1} shows estimated mean ratings of perceived (dis-)advantage for all target groups as a function of participants' caste memberships in Model~1.
 For most target groups, General Merit and Other Backward Class participants' responses closely resembled each other.
@@
 General Merit, Other Backward Class, and Scheduled Caste~/ Scheduled Tribe participants all tended to rate life difficulty for Muslims as around the midpoint.
-Overall, participants' responses seemed to contradict, or even reverse, persisting social inequalities (see Chapter~4, \emph{Caste, religion, and nation in South India}).
+Overall, participants' responses seemed to contradict, or even reverse, persisting social inequalities.
 
@@
 }
-\label{fig:ch5-s4-1}
+\label{fig:d-1}
 \end{figure}
 
-Figure \ref{fig:ch5-s4-2} shows estimated policy support---that is, support for reservations benefiting Scheduled Caste~/ Scheduled Tribe, Other Backward Class, and Muslim students---as a function of participants' caste memberships in Model~1.
+Figure \ref{fig:d-2} shows estimated policy support---that is, support for reservations benefiting Scheduled Caste~/ Scheduled Tribe, Other Backward Class, and Muslim students---as a function of participants' caste memberships in Model~1.
 General Merit and Other Backward Class participants' responses did not provide evidence for cross-group solidarity.
@@
 }
-\label{fig:ch5-s4-2}
+\label{fig:d-2}
 \end{figure}
@@
 \end{tabularx}
-\label{tab:ch5-s4-1}
+\label{tab:d-1}
 \end{table}
 
-Table~\ref{tab:ch5-s4-1} shows the estimated residual correlations before (Model~0) and after (Model~1) accounting for group differences.
+Table~\ref{tab:d-1} shows the estimated residual correlations before (Model~0) and after (Model~1) accounting for group differences.
 Perceiving a group to be disadvantaged correlated weakly with more support for reservations benefiting Scheduled Caste~/ Scheduled Tribe ($r = -.12 $, $[-.24,.01]$), Other Backward Class ($r = -.17$, $[-.30,-.05]$), and Muslim ($r = -.15$, $[-.28,-.03]$) students in Model~1.
@@
 
-We examined to what extent contact experiences and ingroup construals (measured as participants' responses in the crossed-categorization task) accounted for individual differences in perceived life difficulty and policy support.
-To that end, we estimated a series of Bayesian multilevel models with either perceived life difficulty or policy support as outcome variable.
+We examined to what extent contact experiences and ingroup construals (measured as participants' responses in the triple crossed-categorization task) accounted for individual differences in perceived (dis-)advantage and policy support.
+To that end, we estimated a series of Bayesian multilevel models with either perceived (dis-)advantage or policy support as outcome variable.
 Models derived the likelihood of the observed responses from a normal distribution: $$ y_{ij} \sim \text{Normal} (\mu_{ij}, \sigma) $$ where $y_{ij}$ is the observed response to item $i$ by participant $j$, and $\mu_{ij}$ is the estimated response to item $i$ by participant $j$, $\sigma$ is the estimated residual variance (expressed as standard deviation).
@@
 
-First, we estimated participants' responses to each of five perceived life difficulty items, with General Caste (GM), Scheduled Caste (SC), Scheduled Tribe (ST), Other Backward Class (OBC), and Muslims as target groups.
+First, we estimated participants' responses to each of five perceived (dis-)advantage items, with General Caste (GM), Scheduled Caste (SC), Scheduled Tribe (ST), Other Backward Class (OBC), and Muslims as target groups.
 Model~0 estimated item responses as varying across participants and target groups, and estimated differences across participants' ingroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} $$ where $\mu_{ij}$, the estimated mean response to item $i$ by participant $j$, equals $\beta_j$, the varying intercept for participant $j$, and $\beta_{kl}$, the varying intercept for target group~$k$ ($1 = \text{GM}$, $2 = \text{OBC}$, $3 = \text{SC/ST}$, $4 = \text{Muslims}$) and ingroup~$l$ ($1 = \text{GM}$, $2 = \text{OBC}$, $2 = \text{SC/ST}$).
@@
 
-Model~1 extended Model~0 by estimating to what extent outgroup friendship and negative contact with outgroup members were associated with perceptions of life difficulty for outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{OF}x_{\text{OG},k}x_\text{OF,jk} + \beta_\text{NC}x_{\text{OG},jk}x_\text{OF,jk}$$ where $x_{\text{OG},jk}$ codes whether target group $k$ is an outgroup [1] or ingroup [0] for participant $j$, $x_\text{OF,jk}$ and $x_\text{NC,jk}$ are, respectively, participant $j$'s outgroup friendship and negative contact with target group $k$, and $\beta_\text{OF}$ and $\beta_\text{NC}$ estimate the increase in participants' ratings for each additional standard deviation of reported contact.
+Model~1 extended Model~0 by estimating to what extent outgroup friendship and negative contact with outgroup members were associated with perceptions of (dis-)advantages for outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{OF}x_{\text{OG},k}x_\text{OF,jk} + \beta_\text{NC}x_{\text{OG},jk}x_\text{OF,jk}$$ where $x_{\text{OG},jk}$ codes whether target group $k$ is an outgroup [1] or ingroup [0] for participant $j$, $x_\text{OF,jk}$ and $x_\text{NC,jk}$ are, respectively, participant $j$'s outgroup friendship and negative contact with target group $k$, and $\beta_\text{OF}$ and $\beta_\text{NC}$ estimate the increase in participants' ratings for each additional standard deviation of reported contact.
 Model~2 estimated the effects of outgroup friendship and negative contact on outgroup ratings as varying across target outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_{\text{OF},k}x_{\text{OG},k}x_\text{OF,jk} + \beta_{\text{NC},k}x_{\text{OG},jk}x_\text{OF,jk}$$ where $\beta_{\text{OF},k}$ and $\beta_{\text{NC},k}$ estimate effects of contact on ratings for outgroup $k$.
-Neither Model~1 nor Model~2 improved upon the out-of-sample predictions of Model~0, showing that intergroup contact neither increased nor decreased participants' perceptions of discrimination against ethnoreligious or caste outgroups (see Table~\ref{tab:ch5-s4-2}).
+Neither Model~1 nor Model~2 improved upon the out-of-sample predictions of Model~0, showing that intergroup contact neither increased nor decreased participants' perceptions of discrimination against ethnoreligious or caste outgroups (see Table~\ref{tab:d-2}).
 
-Models~3 and 4 tested whether participants' ingroup construals were associated with their perceptions of life difficulty for various outgroups.
-Model~3 estimated this relationship as constant across target groups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1}x_{\text{OG},k}x_\text{Q1,jk} $$ where $x_{Q1,jk}$ is the proportion [0--1] of targets belonging to outgroup $k$ that participant $j$ categorized as ``us'', and $\beta_{Q1}$ estimates the difference in perceived life difficulty between participants who categorized all four targets of an outgroup as ``us'' and participants who categorized all targets of an outgroup as ``not us''.
+Models~3 and 4 tested whether participants' ingroup construals were associated with their perceptions of (dis-)advantages for various outgroups.
+Model~3 estimated this relationship as constant across target groups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1}x_{\text{OG},k}x_\text{Q1,jk} $$ where $x_{Q1,jk}$ is the proportion [0--1] of targets belonging to outgroup $k$ that participant $j$ categorized as ``us'', and $\beta_{Q1}$ estimates the difference in perceived (dis-)advantage between participants who categorized all four targets of an outgroup as ``us'' and participants who categorized all targets of an outgroup as ``not us''.
 Model~4 estimated this relationship as varying across outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1,k}x_{\text{OG},k}x_\text{Q1,jk} $$ where $\beta_{Q1,k}$ estimates the difference in perceived perceived life difficulty between participants who categorized all four targets of outgroup $k$ as ``us'' and participants who categorized all targets of outgroup $k$ as ``not us''.
-Neither Model~3 nor Model~4 improved upon the out-of-sample predictions of Model~0, showing that more inclusive identities neither increased nor decreased participants' perceptions of life difficulty for ethnoreligious an caste outgroups.
+Neither Model~3 nor Model~4 improved upon the out-of-sample predictions of Model~0, showing that more inclusive identities neither increased nor decreased participants' perceptions of (dis-)advantages for ethnoreligious an caste outgroups.
 % Overall, Models~1 to 4 did not provide evidence for the solidarity hypothesis or, more specifically, for the solidarity-by-inclusion hypothesis.
 
-Models~5 to 8 tested to what extent contact with (Models~5, 6) and inclusion of advantaged-group members (Models~7, 8) was associated with perceptions of life difficulty for the ingroup.
-Model~5 estimated how contact with General Merit people affected Scheduled Caste~/ Scheduled Tribe participants' perceptions of life difficulty for their ingroup: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{OF,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{OF,GM,j} + \beta_\text{NC,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{NC,GM,j} $$ where $x_{\text{IG},jk}$ codes whether target group $k$ is an ingroup [1] or outgroup [0] for participant $j$, $x_{\text{SCST,j}}$ codes whether participant $j$ is from an Scheduled Caste~/ Scheduled Tribe background [1] or not [0], $x_\text{OF,j,GM}$ and $x_\text{NC,j,GM}$ are, respectively, participant $j$'s outgroup friendship and negative contact with General Merit people, and $\beta_\text{OF,GM}$ and $\beta_\text{NC,GM}$ estimate the increase in participants' ratings for each additional standard deviation of reported contact with General Merit people.
-Model~6 extended Model~5 by estimating how contact with General Merit people affected Other Backward Class participants' perceptions of life difficulty for their ingroup: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \ldots + \beta_\text{OF,GM}x_{\text{IG,jk}}x_{\text{OBC,j}}x_\text{OF,GM,j} + \beta_\text{NC,GM}x_{\text{IG,jk}}x_{\text{OBC,j}}x_\text{NC,GM,j} $$ where $x_{\text{OBC,j}}$ codes whether participant $j$ is from an Other Backward Class background [1] or not [0].
-Neither Model~5 nor Model~6 improved upon the out-of-sample predictions of Model~0, showing that intergroup contact with advantaged-group members did not increase or decrease disadvantaged-group members' perceptions of life difficulty for their ingroup.
-Model~7 estimated whether including General Merit targets in their ingroup reduced perceptions of life difficulty among Scheduled Caste~/ Scheduled Tribe participants: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{Q1,GM,j} $$ where $x_{Q1,GM,j}$ is the proportion [0--1] of General Merit targets that participant $j$ categorized as ``us'', and $\beta_{Q1,GM}$ estimates the difference in perceived life difficulty between participants who categorized all four General Merit targets as ``us'' and participants who categorized all General Merit targets as ``not us''.
+Models~5 to 8 tested to what extent contact with (Models~5, 6) and inclusion of advantaged-group members (Models~7, 8) was associated with perceptions of (dis-)advantage for the ingroup.
+Model~5 estimated how contact with General Merit people affected Scheduled Caste~/ Scheduled Tribe participants' perceptions of (dis-)advantage for their ingroup: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{OF,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{OF,GM,j} + \beta_\text{NC,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{NC,GM,j} $$ where $x_{\text{IG},jk}$ codes whether target group $k$ is an ingroup [1] or outgroup [0] for participant $j$, $x_{\text{SCST,j}}$ codes whether participant $j$ is from an Scheduled Caste~/ Scheduled Tribe background [1] or not [0], $x_\text{OF,j,GM}$ and $x_\text{NC,j,GM}$ are, respectively, participant $j$'s outgroup friendship and negative contact with General Merit people, and $\beta_\text{OF,GM}$ and $\beta_\text{NC,GM}$ estimate the increase in participants' ratings for each additional standard deviation of reported contact with General Merit people.
+Model~6 extended Model~5 by estimating how contact with General Merit people affected Other Backward Class participants' perceptions of (dis-)advantage for their ingroup: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \ldots + \beta_\text{OF,GM}x_{\text{IG,jk}}x_{\text{OBC,j}}x_\text{OF,GM,j} + \beta_\text{NC,GM}x_{\text{IG,jk}}x_{\text{OBC,j}}x_\text{NC,GM,j} $$ where $x_{\text{OBC,j}}$ codes whether participant $j$ is from an Other Backward Class background [1] or not [0].
+Neither Model~5 nor Model~6 improved upon the out-of-sample predictions of Model~0, showing that intergroup contact with advantaged-group members did not increase or decrease disadvantaged-group members' perceptions of (dis-)advantage for their ingroup.
+Model~7 estimated whether including General Merit targets in their ingroup reduced perceptions of (dis-)advantage among Scheduled Caste~/ Scheduled Tribe participants: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{Q1,GM,j} $$ where $x_{Q1,GM,j}$ is the proportion [0--1] of General Merit targets that participant $j$ categorized as ``us'', and $\beta_{Q1,GM}$ estimates the difference in perceived (dis-)advantage between participants who categorized all four General Merit targets as ``us'' and participants who categorized all General Merit targets as ``not us''.
 Model~8 extended Model~7 by estimating this relationship among Other Backward Class participants: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{Q1,GM,j} + \beta_\text{Q1,GM}x_{\text{IG,jk}}x_{\text{OBC,j}}x_\text{Q1,GM,j} $$ where $x_{\text{OBC,j}}$ codes whether participant $j$ is from an Other Backward Class background [1] or not [0].
-Neither Model~7 nor Model~8 improved upon Model~0, showing that including advantaged-group members in the ingroup did not increase or decrease disadvantaged-group members' perceptions of their ingroup's life difficulty (see Table~\ref{tab:ch5-s4-2}).
+Neither Model~7 nor Model~8 improved upon Model~0, showing that including advantaged-group members in the ingroup did not increase or decrease disadvantaged-group members' perceptions of their ingroup's disadvantage (see Table~\ref{tab:d-2}).
 
@@
 \end{tabularx}
-\label{tab:ch5-s4-2}
+\label{tab:d-2}
 \end{table}
@@
 \figureversion{lining, tabular}
-\caption[Model comparison for individual differences in policy support for Study 4]{Comparison of models estimating participants' group-wise policy support ratings.
-As in Table~\ref{tab:ch5-s4-2}, we preferred a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.}
+\caption{Comparison of models estimating participants' group-wise policy support ratings.
+As in Table~\ref{tab:d-2}, we preferred a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.}
 \small	
@@
 \end{tabularx}
-\label{tab:ch5-s4-3}
+\label{tab:d-3}
 \end{table}
@@
 Models~1 to 4 did not improve upon the out-of-sample predictions of Model~0, showing that neither intergroup contact (Models~1, 2) nor inclusive identities (Models~3, 4) foster support for policies benefiting a disadvantaged outgroup.
-Models~5 to 8 did not improve upon the out-of-sample predictions of Model~0, showing that neither contact with (Models~5, 6) nor inclusion of (Models~7, 8) General Merit people affected Scheduled Caste~/ Scheduled Tribe and Other Backward Class participants' support for policies benefiting their ingroups (see Table~\ref{tab:ch5-s4-3}).
+Models~5 to 8 did not improve upon the out-of-sample predictions of Model~0, showing that neither contact with (Models~5, 6) nor inclusion of (Models~7, 8) General Merit people affected Scheduled Caste~/ Scheduled Tribe and Other Backward Class participants' support for policies benefiting their ingroups (see Table~\ref{tab:d-3}).
 
@@
 \section{Appendix E: Additional Measures}
+
+We included additional measures to validate the triple crossed-categorization task and to replicate earlier research.
+We tested to what extent various social identity measures correlated with responses in the triple crossed-categorization task.
+We also assessed Karmic beliefs to replicate \citeauthor{cotterill_ideological_2014}'s \citeyear{cotterill_ideological_2014} finding that Karmic beliefs mediate the relationship between social dominance orientation and support for hierarchy-enhancing policies.
+We do not report results from this replication here, but make all data available online.
 
@@
 
-\subsection{Correlates of categorisation}
+\emph{Karmic beliefs} \cite{cotterill_ideological_2014} were measured with three items: ``my current caste group position reflects
+my actions or deeds in my past life'', ``if I do good deeds in my current life they will positively influence my caste status in my future life'', and ``the caste group position I was born into reflects the Karma of my past life'' ($1 = \textit{strongly disagree}$, $7 = \textit{strongly agree}$).
 
-Aside from testing potential antecedents and consequences, I explored how participants' responses in the crossed-categorisation task related to other measures of social identification.
-To that end, I estimated the correlations between, on the one hand, the proportions of targets that participants had categorised as ``us'' in each of the six categories, and, on the other hand, the (aggregated) social identification variables described in the \emph{Measures} section.
-I derived the likelihood of the observed responses from a multivariate normal distribution: $$ \textbf{Y} \sim \text{MVNormal} (\mu , \textbf{S} ) $$ where $\textbf{Y}$ is the matrix of observed variable scores (columns) across participants (rows), $\mu$ is the vector of all variable means, and $\textbf{S}$ is the variance-covariance matrix across variables.
+\subsection{Correlates of categorization}
 
-Figure~\ref{fig:ch4-appendix-1} shows the estimated correlations between participants' categorisations in the crossed-categorisation task (from left to right) and various social identification variables (from top to bottom).
-Entitativity---the extent to which participants saw Indians of \emph{all} castes and religions as similar to one another, as depending on each other, as sharing a common fate, as working towards shared goals, and as valuing their shared identity---was positively correlated with the proportion of \emph{Indian, Hindu, GM} ($r = .16$, $[.04, .27]$, $\text{Pr} (r > 0|M) > .99$), \emph{Indian, Hindu, OBC} ($r = .21$, $[.09, .31]$, $\text{Pr} (r > 0| M) > .99$), \emph{Indian, Hindu, SC/ST} ($r = .10$, $[-.02, .22]$, $\text{Pr} (r > 0| M) = .97$), and \emph{Indian, Muslim, OBC} ($r = .18$, $[.07, .30]$, $\text{Pr} (r > 0| M) > .99$) targets participants categorised as ``us''.
+We explored how participants' responses in the triple crossed-categorization task related to other measures of social identification.
+To that end, we estimated the correlations between, on the one hand, the proportions of targets that participants had categorized as ``us'' in each of the six categories, and, on the other hand, the (aggregated) social identification variables described in the \emph{Measures} section.
+We derived the likelihood of the observed responses from a multivariate normal distribution: $$ \textbf{Y} \sim \text{MVNormal} (\mu , \textbf{S} ) $$ where $\textbf{Y}$ is the matrix of observed variable scores (columns) across participants (rows), $\mu$ is the vector of all variable means, and $\textbf{S}$ is the variance-covariance matrix across variables.
+
+Figure~\ref{fig:e-1} shows the estimated correlations between participants' categorizations in the triple crossed-categorization task (from left to right) and various social identification variables (from top to bottom).
+Entitativity---the extent to which participants saw Indians of \emph{all} castes and religions as similar to one another, as depending on each other, as sharing a common fate, as working towards shared goals, and as valuing their shared identity---was positively correlated with the proportion of \emph{Indian, Hindu, GM} ($r = .16$, $[.04, .27]$, $\text{Pr} (r > 0|M) > .99$), \emph{Indian, Hindu, OBC} ($r = .21$, $[.09, .31]$, $\text{Pr} (r > 0| M) > .99$), \emph{Indian, Hindu, SC/ST} ($r = .10$, $[-.02, .22]$, $\text{Pr} (r > 0| M) = .97$), and \emph{Indian, Muslim, OBC} ($r = .18$, $[.07, .30]$, $\text{Pr} (r > 0| M) > .99$) targets participants categorized as ``us''.
 
@@
 \centering
-\includegraphics[scale=1]{../figures/appendices/appendices-e-1}
-\caption[Correlations between social identity variables and target categorisations]{Correlations between various social identity variables (top to bottom) and the proportion of targets that participants had categorised as ``us'' in each target category (left to right).
+\includegraphics{../figures/appendices/appendices-e-1}
+\caption[Correlations between social identity variables and target categorizations]{Correlations between various social identity variables (top to bottom) and the proportion of targets that participants had categorized as ``us'' in each target category (left to right).
 Points indicate the most likely estimate for a given correlation, while lines encompass the 97\% most likely estimates of that correlation.
@@
 Correlations for which $\text{Pr} (r > 0| M) > .99$ or $\text{Pr} (r < 0| M) > .99$ are shown in a darker shade.}
-\label{fig:ch4-appendix-1}
+\label{fig:e-1}
 \end{figure}
 
-Group identification was only associated with participants' categorisations of foreign targets, not their categorisations of Indian targets.
-The extent to which participants identified with their religion was negatively correlated with how many \emph{foreign, Hindu} ($r = -.14$, $[-.25, -.02]$, $\text{Pr} (r > 0| M) > .99$) and \emph{foreign, Muslim} ($r = -.18$, $[-.29, -.07]$, $\text{Pr} (r > 0| M) > .99$) targets participant categorised as ``us''.
+Group identification was only associated with participants' categorizations of foreign targets, not their categorizations of Indian targets.
+The extent to which participants identified with their religion was negatively correlated with how many \emph{foreign, Hindu} ($r = -.14$, $[-.25, -.02]$, $\text{Pr} (r > 0| M) > .99$) and \emph{foreign, Muslim} ($r = -.18$, $[-.29, -.07]$, $\text{Pr} (r > 0| M) > .99$) targets participant categorized as ``us''.
 I obtained similar correlations for the extent to which participants identified with their caste group, $r = -.15$, $[-.27, -.04]$, $\text{Pr} (r > 0| M) > .99$ and $r = -.17$, $[-.29, -.06]$, $\text{Pr} (r > 0| M) > .99$, respectively.
-The extent to which participants identified with their nationality was not associated with participants' categorisations---perhaps because there was a little variation in participants responses, with 81\% of participants strongly agreeing with the statement.
-Other variables were not systematically correlated with participants' responses in the crossed-categorisation task (see Figure~\ref{fig:ch4-appendix-1}).
+The extent to which participants identified with their nationality was not associated with participants' categorizations---perhaps because there was a little variation in participants responses, with 81\% of participants strongly agreeing with the statement.
+Other variables were not systematically correlated with participants' responses in the crossed-categorization task (see Figure~\ref{fig:e-1}).
 
-Correlations thus confirmed that participants' categorisations were more than a straight-forward reflection of the strength of their group identification, affirming the value of the crossed-categorisation task for studying identification in contexts with multiple, cross-cutting group memberships.
+Correlations thus confirmed that participants' categorizations were more than a straight-forward reflection of the strength of their group identification, affirming the value of the crossed-categorization task for studying identification in contexts with multiple, cross-cutting group memberships.
 Furthermore, participants' perceptions of entitativity across caste and religions were associated with more inclusive construals of national identity, providing tentative evidence for its potential for fostering more inclusive identities.

### 2018-11-02 manuscript/manuscript.tex
revision 2

@@
 \usepackage{lineno}
-%\usepackage{authblk}
+\usepackage{authblk}
 
@@
 \date{November 5, 2018}
-%\author{Nils Karl Reimer}
-%\author[2]{Shanmukh V. Kamble}
-%\author[3]{Katharina Schmid}
-%\author[1]{Miles Hewstone}
-%\affil[1]{University of Oxford}
-%\affil[2]{Karnatak University}
-%\affil[3]{ESEADE Business School, Ramon Llull University}
-%\renewcommand\Affilfont{\small}
+\author{Nils Karl Reimer}
+\author[2]{Shanmukh V. Kamble}
+\author[3]{Katharina Schmid}
+\author[1]{Miles Hewstone}
+\affil[1]{University of Oxford}
+\affil[2]{Karnatak University, Dharwad}
+\affil[3]{ESADE Business School, Ramon Llull University}
+\renewcommand\Affilfont{\small}
 
@@
 \begin{abstract}
-\noindent We examined how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce bias by fostering more inclusive identities.
-Participants ($N = 351$) viewed 24 identity cards, each representing a person with whom participants shared none, one, two, or all three group memberships.
-Participants reported whether they considered each person as ``us'' or ``not us'', showing whom they included in their ingroup, and whom they excluded.
-We found that participants from diverse caste backgrounds tended to exclude caste and religious outgroups, replicating persistent social divides in South India.
+\noindent We examined how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce bias by fostering more inclusive social identities.
+South Indian participants ($N = 351$) from diverse caste backgrounds viewed 24 identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships (caste, religion, nationality).
+Participants judged each person as ``us'' or ``not us'', showing whom they included in their ingroup, and whom they excluded.
+Participants tended to exclude caste and religious minorities, replicating persistent social divides.
 Bridging these divides, cross-group friendship was associated with more inclusive identities which, in turn, were associated with more favourable outgroup attitudes.
-Negative contact was associated with less inclusive identities, showing that past experiences shaped whom participants considered ``us'' and ``not us''.
-Contact and identity processes were unrelated to support for affirmative action in advantaged and disadvantaged groups.\\[1ex]
-\noindent \textbf{Keywords:} intergroup contact, social identity, multiple categorization, intergroup relations, affirmative action, caste, nationalism \\[1ex]
+Negative contact was associated with less inclusive identities, showing that past experiences shaped whom participants considered ``us'' or ``not us''.
+Contact and identity processes were unrelated to support for affirmative action in advantaged and disadvantaged caste groups.\\[1ex]
+\noindent \textbf{Keywords:} intergroup contact, social identity, multiple categorization, intergroup relations, affirmative action \\[1ex]
 \end{abstract}
@@
 
-\noindent How we feel about and act toward others depends on whom we consider ``us'' and ``them''---that is, whom we include in our ingroup, and whom we exclude (for a review, see \citeNP{authors_theories_inpress}).
-In some situations, it is clear who is in the ingroup and who is not.
-On a football pitch, for example, players tend to think of their own team as ``us'', and of the other team as ``them'', and try their best to make their own team win.
-In diverse settings, this distinction is less clear because people belong to multiple, overlapping groups.
-Individuals differ in how they construct their ingroup from these group memberships.
-Some espouse narrow definitions of who is ``us'' and ``them'', while others adopt more inclusive identities (see Figure~\ref{fig:f1}).
-Many Americans, for example, associate being American with being White American \cite{devos_american_2005}.
-This suggests that whom Americans consider ``us'' and ``them'' might depend on someone's race \emph{and} nationality.
-In this paper, we examine how group memberships shape whom people consider ``us'' and ``not us'', and whether intergroup contact can reduce prejudice by fostering inclusive social identities.
+\noindent (for a review, see \citeNP{authors_theories_inpress}) (see Figure~\ref{fig:f1}) \cite{devos_american_2005}
 
@@
 \caption{
-Schematic representations of social identity structures, ordered by social identity inclusiveness \protect\cite{dommelen_construing_2015}.
+Schematic representations of social identity structures, ordered by social identity inclusiveness \protect\fullcite{dommelen_construing_2015}.
 Shaded regions represent the groups which a participant has to categorize as ``us'' to be assigned that structure.

### 2018-11-06 manuscript/manuscript.tex
submit

@@
 % Format
-\usepackage{layout}
 \setlength{\parindent}{0.5in}
@@
 \usepackage{lineno}
-\usepackage{authblk}
+%\usepackage{authblk}
 
@@
 
+% Links
+\usepackage[colorlinks=true, linkcolor=black, urlcolor=black, citecolor=black]{hyperref}
+
 % Language
@@
 % References
-\usepackage[nosectionbib, tocbib, unnumberedbib]{apacite}
+\usepackage[nosectionbib, bibnewpage, tocbib, unnumberedbib]{apacite}
 
@@
 \date{November 5, 2018}
-\author{Nils Karl Reimer}
-\author[2]{Shanmukh V. Kamble}
-\author[3]{Katharina Schmid}
-\author[1]{Miles Hewstone}
-\affil[1]{University of Oxford}
-\affil[2]{Karnatak University, Dharwad}
-\affil[3]{ESADE Business School, Ramon Llull University}
-\renewcommand\Affilfont{\small}
 
@@
 \begin{abstract}
-\noindent We examined how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce bias by fostering more inclusive social identities.
+\noindent We examined how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce prejudice by fostering more inclusive social identities.
 South Indian participants ($N = 351$) from diverse caste backgrounds viewed 24 identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships (caste, religion, nationality).
@@
 
-\linenumbers
+%\linenumbers
 
-\noindent (for a review, see \citeNP{authors_theories_inpress}) (see Figure~\ref{fig:f1}) \cite{devos_american_2005}
+\noindent How we feel about and act toward others depends on whom we consider ``us'' and ``them''---that is, whom we include in, and exclude from, our ingroup (for a review, see \citeNP{authors_theories_inpress}).
+In some situations, this distinction rests on one salient categorization, for example, someone’s nationality at an international border.
+In diverse societies, however, this distinction often depends on multiple, overlapping group memberships.
+Individuals differ in how they construct their ingroup from these group memberships.
+Some espouse narrow definitions of who is ``us'' and ``them'', while others adopt more inclusive identities (see Figure~\ref{fig:f1}).
+Many Americans, for example, associate being American with being White American \cite{devos_american_2005}.
+This suggests that whom Americans consider ``us'' and ``them'' might depend on someone's race \emph{and} nationality.
+In this paper, we examine how group memberships shape whom people consider ``us'' and ``not us'', and whether intergroup contact can reduce prejudice by fostering inclusive social identities.
 
@@
 
+Social psychologists have argued for the importance of considering two \cite{berry_immigration_1997, crisp_multiple_2007, dovidio_commonality_2009} or more \cite{roccas_social_2002} social categories for understanding intergroup relations.
+Broadly, these perspectives recognise that we are part of multiple overlapping groups; that we have a subjective sense of who is ``us'' and ``them'' that goes beyond the objective facts of group membership; and that identification across multiple categories affects our attitudes toward people with whom we share some, but not all, group memberships.
+However, these perspectives have lacked methods for measuring identification across multiple categories.
+Our research uses a novel method for studying subjective identity construals, as well as their antecedents (intergroup contact) and consequences (outgroup attitudes, intergroup threat, policy support).
+
+Past research \shortcite{dommelen_construing_2015} studied whom individuals considered ``us'' and ``not us'', and observed substantial individual differences in how inclusive participants' social identities were.
+In this research, all participants belonged to the same groups.
+Group memberships, however, likely influences whom people consider ``us'' and ``not us''.
+For majority-group members, negotiating their ethnic and national identities means something different than for minority-group members \cite{dovidio_commonality_2009}.
+We expect that group differences are as great as, if not greater than, individual differences in social identity construals---especially if groups differ in status and power.
+Our research includes participants from diverse backgrounds to estimate these group differences.
+
+Contact experiences could overcome group differences in social identity construals.
+Encountering diverse others could initiate a process of cognitive differentiation \cite{schmid_social_2011} whereby individuals become aware of complex interrelations between their group memberships, and thus start to question narrow identity construals.
+Further, positive intergroup interactions motivate people to include the outgroup of an interaction partner in their self-concept \cite{page_understanding_2010}.
+If contact motivates people to include partial outgroups in the self, it should encourage social identities that include the interaction partner's combination of group memberships.
+Together, these mechanisms suggest that contact could foster more inclusive identities.
+
+Fostering more inclusive identities, in turn, could reduce intergroup bias.
+Dividing others into ``us'' and ``not us'' is a necessary and sufficient condition for ingroup favouritism \cite{tajfel_human_1981}.
+Considering more people as ``us'' should extend ingroup favouritism to a wider range of people, and thus reduce discrimination \cite{gaertner_common_2016}.
+Ingroup favouritism can turn into outgroup derogation when an outgroup threatens the ingroup \cite{brewer_psychology_1999}.
+Considering fewer people as ``not us'' should reduce the number of groups which are perceived to threaten the ingroup.
+Together, these mechanisms suggest that fostering inclusive identities could improve outgroup attitudes and reduce intergroup threat.
+
+Beyond prejudice, researchers have debated whether fostering inclusive identities helps or hinders social change.
+Social change often requires advantaged and disadvantaged groups to strive for redistributive policies.
+On the one hand, fostering inclusive identities could break down the boundaries between the advantaged ingroup and the disadvantaged outgroup---turning injustice faced by ``them'' into ``our'' problem.
+This process could narrow the gap between advantaged-group members' support for the principle of equality and their opposition to its implementation \cite{dixon_intergroup_2007}.
+On the other hand, fostering more inclusive identities could distract disadvantaged-group members from differences in resources and power, and thus reduce their support for social change \cite{dovidio_darker_2012}.
+Together, these mechanisms suggest that more inclusive identities could increase support for social change among the advantaged, but decrease support among the disadvantaged.
+
+\subsection{Caste, Religion, Nation in South India}
+
+We tested these predictions among South Indian students, examining the cross-cutting categories of caste, religion, and nationality.
+Caste is a system of social relations that concentrates resources in the hands of dominant castes by restricting subordinate castes' occupations and land ownership, and by enforcing endogamy and segregation \cite{jodhka_caste_2012}.
+This system is underpinned by a tradition that ranks castes according to their supposed ritual purity, and condemns contact with less pure castes.
+Since Independence, the Indian State has sought to redress caste-based injustices by enforcing `reservations' of seats in state-run universities and state-sector jobs for disadvantaged groups.
+It recognises Dalits---members of castes affected by untouchability---as Scheduled Castes (SCs), Adivasi---India's indigenous peoples---as Scheduled Tribes (STs), and other disadvantaged groups---who occupy an intermediate position in the caste hierarchy---as Other Backward Classes (OBCs).
+Historically advantaged castes do not have access to reservations (GM: General Merit).
+Reservation policies, alongside ongoing discrimination, mean that caste identities remain important.
+
+South India is religiously diverse.
+In Karnataka, where we conducted this research, 84\% of inhabitants are Hindus, while 13\% are Muslims.
+Muslims face both structural inequalities and communal violence.
+In 2002, for example, a pogrom killed over a thousand Muslims in Gujarat \cite{dhattiwala_political_2012}.
+In recent years, anti-Muslim violence has been increasing \cite{amnesty_india_2017}.
+Religion is intertwined with two currents of Indian nationalism \cite{menski_hindu_2009}.
+On the one hand, the secular foundations of the Indian State resulted from an inclusive nationalism that strives to include Indians of all religions.
+On the other hand, Hindu nationalism (Hindutva) is an ideology that equates being Indian with being Hindu, thus excluding Muslims from the national identity.
+Narendra Modi's BJP government espouses Hindutva, and enjoys broad support in the Indian population \cite{pew_three_2017}.
+
+\section{Present research}
+
+We examined how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce prejudice, and increase support for social change, by fostering more inclusive identities.
+Our research used a novel method to study social identification across multiple categories in a sample of South Indians from various caste backgrounds.
+
+First, we examined how participants' objective group memberships shaped their subjective construals of social identity.
+We hypothesised that participants would exclude targets from religious and national outgroups---and that participants from advantaged castes would exclude targets from disadvantaged castes, and vice versa.
+We did not have a clear prediction for participants from intermediate caste groups.
+Second, we tested potential antecedents of more inclusive social identities.
+We hypothesised that positive contact and cross-group friendship would be associated with more, and negative contact with less, inclusive identities.
+As an alternative hypothesis, we tested whether ideological preferences for social dominance \cite{sidanius_social_1999} could have motivated individuals to exclude lower-status outgroups.
+Third, we examined potential consequences of participants' identity construals.
+We hypothesised that categorizing someone as ``us'' would be associated with more favourable attitudes and less social distance toward that person.
+More broadly, we expected more inclusive identities to be associated with less perceived intergroup threat.
+We also tested whether more inclusive identities would be associated with increased support for affirmative action among advantaged-group members, but decreased support among disadvantaged-group members.
+
+We tested these predictions in a triple crossed-categorisation task (adapted from \citeNP{dommelen_construing_2015}).
+In this task, participants viewed identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships.
+Participants reported whether they considered each person as ``us'' or ``not us'', showing whom they included in, or excluded from, their ingroup.
+This task thus measured how participants combined multiple group memberships to construct their social identities.
+We tested to what extent participants' responses were associated with past contact experiences, ideological preferences, and various outcome measures.
+
+\section{Method}
+
+All materials, data, analysis scripts, and appendices are available online (\href{https://osf.io/ekb8z/?view_only=05b6a5c5cf5e43d9a7bba5e192f53f87}{https://osf.io/ ekb8z/?view\_only=05b6a5c5cf5e43d9a7bba5e192f53f87}).
+Here, we only report measures testing our hypotheses, omitting measures replicating earlier research or validating the categorization task (Appendix~E).
+Reanalysing existing data \cite{dommelen_construing_2015}, we determined that $\sim$100 respondents per group would allow reasonably precise estimates of model parameters.\footnote{Models estimated posterior probabilities with precision $\textit{SD} < 0.5$ on the log odds scale.}
+
+\subsection{Participants}
+
+We recruited 351 students at Karnatak University (Dharwad, India).
+Of these, we excluded 49 participants who did not belong to any of four caste groups ($n = 20$), failed to indicate their caste group ($n = 7$), or reported Islam as their own or their family's religion ($n = 27$).\footnote{We excluded Muslim participants as this subsample was too small for meaningful analyses.} This left 302 participants who reported Hinduism ($n = 286$), Jainism ($n = 8$), or Christianity ($n = 8$) as their or their family's religion, and General Caste ($n = 99$), Other Backward Class ($n = 127$), Scheduled Caste ($n = 54$), or Scheduled Tribe ($n = 22$) as their caste group.
+Table~\ref{tab:t1} summarises participants by gender, age, nationality, religion, and caste.
+
+\begin{table}    
+\caption[Participants by gender, age, nationality, religion, and caste]{Participants by gender, age, nationality, religion, and caste.
+Categories in \textit{italics} were excluded from the final sample.
+N/A marks missing responses.}
+\centering
+\figureversion{lining, tabular}
+\small	
+\begin{tabular}{llrr} \addlinespace \toprule
+\multicolumn{2}{l}{Category} & $n$ & \% \\ \midrule \addlinespace 
+Gender      & Woman      & 215 & 61 \\
+            & Man & 121 & 34 \\
+            & Other & 0 & 0 \\
+            & N/A & 15 & 4 \\ \addlinespace \addlinespace
+Age         & 18--20 & 1 & 0 \\
+            & 21--23 & 254 & 72 \\
+            & 24--26 &  77 & 22 \\
+            & 27--29 &  10 &  3 \\
+            & 30--32 &   1 &  0 \\
+            & 33--35 &   0 &  0 \\
+            & 36 or older & 1 & 0 \\ 
+            & N/A & 7 & 2 \\ \addlinespace \addlinespace
+Nationality & Indian & 339 & 97 \\
+            & Other & 0 & 0 \\
+            & N/A & 12 & 3 \\ \addlinespace \addlinespace
+Religion    & Buddhism & 1 & 0 \\ 
+            & Christianity & 11 & 3 \\ 
+            & Hinduism & 297 & 85 \\ 
+            & \textit{Islam} & \textit{27} & \textit{8} \\ 
+            & Jainism & 8 & 2 \\ 
+            & Other & 2 & 1 \\ 
+            & N/A & 5 & 1 \\ \addlinespace \addlinespace
+Caste       & General Caste & 104 & 30 \\ 
+            & Other Backward Class & 143 & 41 \\ 
+            & Scheduled Caste & 54 & 15 \\ 
+            & Scheduled Tribe & 23 & 7 \\ 
+            & \textit{Other / Not applicable} & \textit{20} & \textit{6} \\ 
+            & \textit{N/A} & \textit{7} & \textit{2} \\ \addlinespace \midrule
+Total       &   & 351 & 100 \\ \bottomrule
+\end{tabular}
+\label{tab:t1}
+\end{table}
+
+\subsection{Procedure}
+
+Participants completed a triple crossed-categorization task, in which they viewed 24 identity cards.
+Each showed a fictitious person's name, age, religion, nationality, caste reservation, and a head-and-shoulders silhouette.
+Based on a pilot study, we manipulated the target's caste, religion, and nationality such that each target represented a person with whom participants shared none, one, two, or three group memberships (Figure~\ref{fig:f2}).
+We tested participants in classrooms of 24--71 students by presenting targets in a slide-based presentation.
+Each slide contained a male and a female target with participants focusing on the target corresponding to their gender.
+Slides also contained a number identifying each target, and the response scale(s) corresponding to the question(s) participants answered at the time.
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-2}
+\caption{Examples of targets used in the triple crossed-categorization task.
+Based on ratings in a pilot study ($N = 26$), we selected the four most prototypical targets (out of fifty initial targets) for each of six plausible combinations of caste, religion, and nationality (for details, see Appendix~A).
+Each target showed a person's caste (GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe), religion (Hindu, Muslim), and nationality (Indian, Nepali, Sri Lankan, Bangladeshi).
+Each target also showed the person's first and last name, age (21--26 years), and a silhouette corresponding to the person's gender (adapted from \protect\citeNP{ma_chicago_2015}).
+Each target's age and silhouette, as well as the order in which the targets were presented, varied across sessions.}
+\label{fig:f2}
+\end{figure}
+
+In each session, participants first familiarised themselves with each target (for 7s) in an automated slideshow.
+Participants viewed targets (in the same order) for a second time, noting for each target whether they felt that this person was one of their own group (1 = ``us''), or not one of their own group (0 = ``not us'').
+Participants viewed targets for a third time, rating how comfortable or uncomfortable they would feel to share a room with this person (social distance; $1 = \textit{very uncomfortable}$, $7 = \textit{very comfortable}$), and how they felt toward this person (feeling thermometer; $0 = \textit{cold}$, $\textit{100 = warm}$).
+Participants then completed a questionnaire containing the measures described below.
+
+\subsection{Measures}
+
+We measured intergroup contact as: how often, from $1 = \textit{never}$ to $5 = \textit{very often}$, participants meet outgroup members in their everyday life (contact quantity), and how often, on average, they have positive/good contact and negative/bad contact with outgroup members \cite{barlow_contact_2012}.
+We preceded these items with examples of positive and negative contact experiences.
+We measured cross-group friendship with two items \cite{turner_reducing_2007}: ``How many close friends do you have who are [outgroup members]?'' ($1 = \textit{none}$, $5 = \textit{more than ten}$), and ``How often do you spend time with [outgroup] friends?'' ($1 = \textit{never}$ to $5 = \textit{very often}$; $.47\leq\textit{rs}\leq.58$).
+Participants reported contact with four groups: Dalits, people from other backward classes, people from general castes, and Muslims.
+
+We measured social dominance orientation as how much, between $1 = \textit{strongly oppose}$ and $7 = \textit{strongly favour}$, participants endorsed eight statements about social hierarchies \cite{ho_nature_2015}.
+Four items measured support for group-based dominance (SDO-Dominance), e.g., ``some groups of people are simply inferior to other groups''.
+Four items measured opposition to egalitarian ideologies (SDO-Egalitarianism), e.g., ``it is unjust to try to make groups equal''.\footnote{Replicating \citeauthor{ho_nature_2015}’s \citeyear{ho_nature_2015} findings, we found a four-factor model (with two method factors) to represent the data better than the one-factor ($\Delta\chi^2 = 155.14$, $p < .001$) or two-factor ($\Delta\chi^2 = 138.67$, $p < .001$) alternatives.
+Accounting for this structure, we used latent factor scores for SDO-Dominance and SDO-Egalitarianism in our analyses.}
+
+We measured realistic threat---from Muslims and Dalits---with three items per outgroup \cite{schmid_reducing_2014}, e.g., ``the more power [Muslims/Dalits] gain in this country, the more difficult it is for [Hindus/people from my caste group]'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $\alpha_\textit{Muslims} = .71$, $\alpha_\textit{Dalits} = .79$).
+Two items measured symbolic threat, e.g., ``[Muslims/Dalits] threaten [Hindus'/my caste group's] way of life'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $r_\textit{Muslims} = .44$, $r_\textit{Dalits} = .48$).
+
+We measured perceived (dis-)advantage as how easy or hard participants thought it was, on average, for people from various groups to succeed in India today ($1 = \textit{very hard}$, $7 = \textit{very easy}$).
+Participants rated seven groups: People from your own background, Scheduled Caste, Scheduled Tribe, Other Backward Class, General Caste, Hindus, and Muslims.
+
+Five items measured policy support.
+Participants read that ``currently, 22.5\% of seats in central-government funded universities are reserved for Scheduled Caste and Scheduled Tribe students'', and that ``an additional 27.5\% of seats in central-government funded universities are reserved for students from Other Backward Classes''.
+Participants indicated to what extent they opposed or supported reservation in higher education for students from each group ($1 = \textit{strongly oppose}$, $5 = \textit{strongly support}$), and whether they thought that reservation in higher education for students from that group should increase, decrease, or remain unchanged ($1 = \textit{decrease a lot}$, $5 = \textit{increase a lot}$; $r_\textit{SC/ST} = .67$, $r_\textit{OBC} = .67$).
+Participants then read that ``no seats in central-government funded universities are reserved for Muslim students nationally, though some states have introduced quotas for Muslim students''.
+Participants indicated to what extent they opposed or supported reservation for Muslim students.
+
+\section{Results}
+
+We used the following analysis strategy: First, we estimated group differences in whom participants categorized as ``us'' and ``not us''.
+Second, we examined to what extent intergroup contact and ideological orientations explained individual differences in participants' categorizations.
+Third, we tested whether participants' categorizations were associated with their attitudes and beliefs.
+
+\subsection{Group differences}
+
+We compared \emph{how likely} participants were to categorize \emph{which} target as ``us'' versus ``not us''---and how that probability varied across targets' and participants' group memberships.\footnote{In Appendix~B, we report analyses using \citeauthor{dommelen_construing_2015}'s \citeyear{dommelen_construing_2015} operationalisation who analysed which and how many targets participants included as distinct questions.
+}
+
+We estimated a series of Bayesian multilevel models in RStan \cite{rstan_package} with participants' target categorizations ($1 = \text{``us''}$, $0 = \text{``not us''}$) as outcome variable.
+Models derived the likelihood of the observed proportions of ``us'' categorizations from the Bernoulli likelihood with a logit link function.
+Models assigned weakly informative prior distributions to all fixed parameters \cite{gelman_prior_2017}.\footnote{Models assigned the following priors: $\beta \sim \text{Student}(2.5, 0, 1)$ for fixed effects, and $\sigma \sim \text{Cauchy}(0, 1)$ for standard deviations of varying effects.} Models used the non-centred parameterisation for all varying effects \cite{betancourt_hamilton_2015}.
+We compared models using stratified 10-fold cross-validation to estimate each model's out-of-sample predictive accuracy \shortcite{vehtari_practical_2017}.
+We selected more complex over simpler models when the difference in predictive accuracy was at least twice its standard error.
+
+Models~0 to 3 estimated the probabilities of ``us'' categorizations as varying between participants but fixed across target categories (M0), as varying across participants and target categories (M1), and tested whether SC/ST participants' categorizations of Indian targets differed from GM and OBC participants' (M2) and whether OBC participants’ categorizations differed from GM participants' (M3).
+Models~1 and 2, but not Model~3, made more accurate predictions than less complex models (Table~\ref{tab:t2}).
+This suggests that the targets' group memberships shaped participants' categorizations, and that GM and OBC participants' categorizations resembled each other but differed from SC/ST participants'.
+Below, we report median point estimates, with 97\% highest posterior density intervals \cite{coda_package}, from the model's posterior distribution.
+
+\begin{table}
+\caption{
+Comparison of models estimating the probability of participants categorising targets as ``us'' versus ``not us''.
+$\textit{ELPD}$ is the expected log predictive density, with higher numbers indicating that a model is expected to make more accurate out-of-sample predictions \protect\fullcite{vehtari_practical_2017}.
+$\Delta\textit{ELPD}$ is the difference in $\textit{ELPD}$ between the current and previous model, with positive values indicating that the current model is expected to make more accurate out-of-sample predictions.
+We selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.
+$w$ are stacking weights based on the models' expected log predictive densities \protect\cite{yao_using_2018}.
+}
+\centering
+\figureversion{lining, tabular}
+\small
+\begin{tabularx}{\linewidth}{r@{~}rXrrrrrr} \toprule
+\# &  & Description & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule 
+0 &      & Intercept (Participant) & -4703.5 & 23.7 &     - &    - &    - & .00 \\ 
+1 & vs 0 & Intercept (Category)    & -3853.5 & 41.6 & 850.1 & 37.4 & 22.7 & .00 \\
+2 & vs 1 & Group differences (SC/ST)       & -3791.3 & 42.0 &  62.1 & 11.1 &  5.6 & .00 \\
+3 & vs 2 & Group differences (OBC)         & -3792.1 & 42.2 &  -0.8 &  3.6 & -0.2 & .07 \\ \midrule
+4 & vs 2 & Intergroup contact (4) & -3743.4 & 42.8 &  47.9 &  8.8 &  5.4 & .00 \\
+5 & vs 4 & Intergroup contact (2) & -3736.7 & 42.6 &   6.7 &  1.8 &  3.8 & .92 \\
+6 & vs 5 & Intergroup contact (2) & -3747.8 & 42.7 & -11.1 &  3.2 & -3.5 & .00 \\
+7 & vs 2 & Social dominance orientation & -3791.0 & 42.1 &   0.4 &  3.3 &  0.1 & .00 \\
+\bottomrule
+\end{tabularx}
+\label{tab:t2}
+\end{table}
+
+Figure~\ref{fig:f3} shows the estimated probabilities of General Merit (GM), Other Backward Class (OBC), and Scheduled Caste/Scheduled Tribe (SC/ST) participants categorizing a target as ``us''.
+Participants tended to define their ingroup in terms of nationality, though about half of the responses indicated more inclusive identities.
+Few participants considered Bangladeshi Muslims part of their ingroup, \pest{M2}{.17}{.14}{.21}.
+Roughly half of the participants included Sri Lankan and Nepali Hindus in their ingroup, \pest{M2}{.46}{.41}{.52}.
+Participants were thus more likely to include foreign targets when they were Hindu, \pdif{M2}{.29}{.25}{.34}.
+Still, GM/OBC and SC/ST participants were, respectively, $1.95$, $[1.73, 2.18]$ and $1.90$, $[1.71, 2.14]$ times more likely to categorize Indian, Hindu targets as ``us'' compared to foreign, Hindu targets.
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-3}
+\caption{
+Estimated probability of participants categorizing a target as ``us'' versus ``not us'' by targets' nationality, religion, and caste (vertical), and participants' caste membership (horizontal).
+Dots (•) indicate the most plausible \emph{estimate} for a given target's probability of being included in participants' ingroup (in Model~2, Table~\ref{tab:t2}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most plausible estimates of that probability.
+Pluses (+) indicate the \emph{observed} proportion of participants who included a given target in their ingroup.
+Comparing predicted and observed proportion shows that the model represents the data reasonably well.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f3}
+\end{figure}
+
+As expected, participants' caste membership shaped how they categorized Indians of different castes and religions.
+Most GM and OBC participants included \emph{Hindu, GM} and \emph{Hindu, OBC} targets in their ingroup, \pest{M2}{.94}{.92}{.96} and \pest{M2}{.93}{.91}{.95}.
+Fewer GM and OBC participants categorized \emph{Hindu, SC/ST} targets as ``us'', \pest{M2}{.84}{.80}{.87}.
+They were least likely to categorize \emph{Muslim, OBC} targets as ``us'', \pest{M2}{.75}{.70}{.80}.
+Dalit/Adivasi (SC/ST) participants' responses differed from GM and OBC participants'.
+Almost all SC/ST participants included \emph{Hindu, SC/ST} targets in their ingroup, \pest{M2}{.97}{.95}{.99}.
+Fewer SC/ST participants included \emph{Hindu, GM} and \emph{Hindu, OBC} in their ingroup, \pest{M2}{.88}{.83}{.92} and  and \pest{M2}{.80}{.73}{.86}.
+SC/ST participants were less likely than others to include \emph{Muslim, OBC} targets as ``us'', \pest{M2}{.47}{.38}{.57}.
+These findings showed that participants from advantaged backgrounds tended to exclude targets from disadvantaged backgrounds (and vice versa), while all participants tended to exclude targets from the Muslim minority.
+
+\subsection{Individual differences}
+
+We examined to what extent individual differences in past experiences and ideological orientations explain why some participants excluded targets from caste and religious outgroups---and why others did not.
+
+Models~4 to 6 tested whether intergroup contact was associated with how participants categorized Indian targets of caste or religious outgroups.
+Model~4 extended Model~2 by including contact quantity, positive contact, negative contact, and outgroup friendship as predictors of participants' categorizations.
+Model~4 made more accurate predictions than Model~2.
+Negative contact ($e^\beta = 0.81$, $[0.72, 0.90]$) and outgroup friendship ($e^\beta = 1.50$, $[1.28, 1.72]$) were associated with participants' categorizations, but neither positive contact ($e^\beta = 1.01$, $[0.87, 1.16]$) nor contact quantity ($e^\beta = 0.99$, $[0.86, 1.15]$) were.
+Model~5 included only negative contact and outgroup friendship, and made more accurate predictions than Model~4.
+Model~6 estimated the relationships between contact and categorizations as varying across the four combinations of target caste and religion.
+Model~6 made less accurate predictions than Model~5.
+
+Figure~\ref{fig:f4} shows the estimated probabilities of participants categorizing targets as ``us'' as a function of contact experiences.
+Across targets and participants, the odds of categorizing an outgroup target as ``us'' were $e^\beta = 1.50$, $[1.32, 1.69]$ times higher for each additional standard deviation of outgroup friendship.
+These odds were $e^\beta = 0.81$, $[0.72, 0.90]$ times lower for each standard deviation of negative contact.
+This means, for example, that GM/OBC participants who reported ``never'' having any negative contact with Muslims were more likely to categorize Indian Muslims as ``us'' than participants who reported ``sometimes'' having negative contact, \pdif{M5}{.05}{.09}{.03}.
+GM/OBC participants who reported no friendships with Muslims were a lot less likely to include Indian Muslims in their ingroup than participants who had 2--5 Muslim friends with whom they ``sometimes'' spent time, \pdif{M5}{.18}{.12}{.24}.
+Contact experiences were thus associated with whom participants categorized as ``us'' and ``not us''.
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-4}
+\caption{Estimated probability of participants categorising a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship with the relevant groups (in Model~5, Table~\ref{tab:t2}).
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.}
+\label{fig:f4}
+\end{figure}
+
+Models~7 tested whether social dominance orientation was associated with participants' categorizations of targets from lower status outgroups.
+Model~7 found little evidence for associations between participants' categorizations and their SDO-Dominance scores ($e^\beta = 0.87$, $[0.69, 1.06]$) or SDO-Egalitarianism scores ($e^\beta = 0.98$, $[0.78, 1.21]$).
+Together, these findings show that group and individual differences explained whom participants included in their ingroup.
+As expected, past experiences with outgroup members explained why some participants included targets of (objective) caste or religions outgroups in their (subjective) ingroup, when others did not.
+In contrast, ideological orientations did not motivate participants to exclude lower-status groups.
+
+\subsection{Consequences}
+
+We analysed how participants' categorizations related to their warmth and social distance ratings for each target in the categorization task, to intergroup threat, and to their perceived (dis-)advantage and policy support.
+
+We estimated multivariate models with participants' target-wise social distance and feeling thermometer ratings as outcome variables (Table~\ref{tab:t3}).
+Models~0 to 3 estimated ratings (on either outcome) as varying between participants but fixed across targets (M0), as varying across participants and targets (M1), and tested whether SC/ST participants' responses differed from GM and OBC participants' (M2), and whether OBC participants' responses differed from GM participants (M3).
+Models~1 to 3 improved upon the predictions of simpler models, showing that participants' ratings depended on targets' and participants' group memberships.
+
+\begin{table}
+\caption{Comparison of models estimating participants' social distance (SD) and feeling thermometer (FT) ratings for each target as a function of group differences and target categorizations.
+As in Table~\ref{tab:t2}, we selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.
+$R^2$ is a Bayesian analogue to $R^2$ in maximum likelihood estimation \protect\fullcite{gelman_rsquared_2017}.}
+\centering
+\figureversion{lining, tabular}
+\small	
+\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrrr} \toprule
+\# &  & Description & $R^2_\text{SD}$ & $R^2_\text{FT}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule 
+0 &      & Participant & .23 & .26 & -16964 & 71.0 & - & - & - & .12 \\
+1 & vs 0 & Category & .38 & .42 & -16338 & 79.6 & 626.8 & 40.2 & 15.6 & .02 \\
+2 & vs 1 & SC/ST    & .38 & .43 & -16317 & 79.6 &  20.1 &  9.8 &  2.1 & .00 \\
+3 & vs 2 & OBC      & .39 & .43 & -16293 & 80.5 &  24.2 &  9.7 &  2.5 & .00 \\ \midrule
+4 & vs 3 & Categorization    & .42 & .47 & -16028 & 83.5 & 264.8 & 24.5 & 10.8 & .19 \\
+5 & vs 4 & \ldots~(Category) & .42 & .47 & -16007 & 83.6 &  21.1 &  8.7 &  2.4 & .67 \\
+6 & vs 5 & \ldots~(Ingroup)  & .42 & .47 & -16025 & 84.3 & -17.4 &  5.9 & -3.0 & .00 \\
+\bottomrule    
+\end{tabularx}
+\label{tab:t3}
+\end{table}
+
+Models~4 to 6 tested whether participants who categorized a target as ``us'' rated that target more favourably than participants categorizing the same target as ``not us''.
+Models estimated this difference as constant across targets and participants (M4), as varying across target categories (M5), and tested whether this difference depended on participants' caste memberships (M6).
+Models 4 and 5, but not Model 6, made better predictions than less complex models, showing that how favourably participants felt toward a target depended on whether they had categorized that target as ``us'' or ``not us'', and that the size of this difference depended on the targets'---but not the participants'---group memberships.
+
+Figures~\ref{fig:f5} and \ref{fig:f6} show, respectively, the estimated social distance and feeling thermometer ratings as a function of target categorizations and participants' caste memberships.
+For all categories, participants felt more comfortable sharing a room with targets that they categorized as ``us'' than with targets they categorized as ``not us''.
+This difference was smallest for \emph{Indian, Hindu, GM} targets ($\beta = 0.55$, $[0.19, 0.90]$; $d = 0.24$, $[0.08, 0.39]$) and greatest for \emph{foreign, Muslim} targets ($\beta = 1.46$, $[1.21, 1.70]$; $d = 0.63$, $[0.52, 0.73]$).
+We found a similar pattern for feeling thermometer ratings.
+The difference was smallest for \emph{Indian, Hindu, OBC} targets ($\beta = 6.5$, $[2.1, 11.0]$, $d = 0.20$, $[0.06, 0.33]$) and greatest for \emph{foreign, Hindu} targets ($\beta = 21.8$, $[18.6, 25.0]$, $d = 0.66$, $[0.56, 0.76]$).
+Feeling thermometer and social distance ratings were highly correlated ($r = .58$, $[.56, .60]$).
+Categorizing a target as ``us'' was thus associated with more warmth and less social distance toward that target.
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-5}
+\caption{
+Posterior probabilities of social distance ratings as a function of target categorizations (in Model~5, Table~\ref{tab:t3}).
+Points are the estimated mean ratings for targets categorized as ``us''; triangles are the estimated mean ratings for targets categorized as ``not us''.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f5}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-6}
+\caption{
+Posterior probabilities of feeling thermometer ratings as a function of target categorizations (in Model~5, Table~\ref{tab:t3}).
+Points are the estimated mean ratings for targets categorized as ``us''; triangles are the estimated mean ratings for targets categorized as ``not us''.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f6}
+\end{figure}
+
+Next, we tested whether participants' perceptions of realistic and symbolic threat depended on how inclusive their identity construals were.
+Results from a series of multilevel models showed that participants reported more realistic ($M = 3.62$, $[3.49, 3.75]$) than symbolic ($M = 3.21$, $[3.09, 3.33]$) threat from (same-religion) Dalits, but more symbolic ($M = 3.47$, $[3.34, 3.61]$) than realistic ($M = 3.23$, $[3.06, 3.38]$) threat from (different-religion) Muslims.
+Contrary to predictions, we did not find that participants felt less threatened by Muslims and Dalits if they categorized more targets from these outgroups as ``us''.
+For details, see Appendix~C.
+
+Finally, we estimated group differences in perceived (dis-)advantage and policy support.
+Figures~\ref{fig:f7} and \ref{fig:f8} show the estimated group differences in both outcomes.
+Contradicting prevailing social inequalities, GM and OBC participants rated their own groups' lives as substantially harder than SC/ST members' lives.
+Policy support strongly aligned with participants' caste interests.
+SC/ST participants supported reservations for both SC/ST and OBC students, while OBC participants only supported reservations for their own group.
+Contrary to predictions, we did not find more inclusive identities to be associated with either perceived (dis-)advantage or policy support.
+Contrary to past research \cite{dixon_beyond_2012}, intergroup contact was similarly unrelated to these outcomes.
+For details, see Appendix~D.
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-7}
+\caption{
+Posterior probabilities of perceived (dis-)advantage ratings for different target groups (right) by participants' caste ingroup (left).
+Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f7}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-8}
+\caption{
+Posterior probabilities of policy support ratings for different target groups (right) by participants' caste ingroup (left).
+Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f8}
+\end{figure}
+
+Overall, we found that when participants included a person in their ingroup, they had, on average, more favourable attitudes to and desired less social distance from that person.
+Participants' categorizations, however, were unrelated to perceptions of intergroup threat and relative (dis-)advantage, and to support for affirmative action.
+
+\subsection{Discussion}
+
+This research examined how people construct their social identities from multiple cross-cutting categories, and how these identities relate to intergroup contact and intergroup attitudes.
+As hypothesised, we found that cross-group friendship was associated with more inclusive identities which, in turn, were associated with more favourable outgroup attitudes.
+Negative contact was associated with less inclusive identities.
+Below, we discuss strengths, limitations, and implications of the research.
+
+Our findings show that the triple crossed-categorization task \cite{dommelen_construing_2015} is an intuitive and informative method for studying social identification across multiple categories.
+We adapted the task to answer new questions about social identification.
+First, we recruited respondents from multiple groups, allowing us to study both individual and group differences (see also \citeNP{brankovic_social_2015}).
+Second, we estimated responses as varying across targets and participants using multilevel models.
+This allowed more fine-grained analyses than \citeauthor{dommelen_construing_2015}’s quantitative and qualitative summaries, and may explain why we found more consistent effects of intergroup contact.
+Overall, these changes open the triple crossed-categorization task to a broader range of research questions.
+
+Still, our research is qualified by some methodological limitations.
+We presented all participants with the same combination of target groups.
+This design cannot determine whether the observed construals generalise beyond the specific combination of stimuli used.
+Relatedly, we did not control for factors that correlate with the categories under study, but were not made explicit.
+Class, rather than caste, could explain why some participants excluded targets from disadvantaged outgroups.
+Further, we measured categorization and attitudes for the same targets.
+This design cannot rule out that these variables measure the same construct, rather than represent an association across constructs.
+Intergroup threat, a more distal measure, did not correlate with participants' categorizations.\footnote{An explanation for this finding might be that threat perceptions stem from economic anxieties (e.g., fearing affirmative action as a threat to one's career) and ideological beliefs (e.g., Hindutva), rather than identity processes.} Future research should address these limitations by varying target categories across participants, by including more target categories, by assessing intergroup bias with proximal and distal measures, and by testing the hypothesised relationships over time.
+
+Our research has implications for understanding intergroup relations in unequal societies.
+Among advantaged groups, our research documented patterns of inclusion and exclusion that map onto persistent social divides.
+Participants from dominant caste groups tended to exclude subordinate caste groups from the common ingroup.
+Hindu participants tended to exclude Indian Muslims.
+Among disadvantaged groups, we found more complex patterns of inclusion and exclusion.
+Participants from intermediate caste groups (OBC) faced the choice of aligning themselves with dominant caste groups (GM), or forming a coalition with subordinate caste groups (SC/ST).
+OBC participants tended to include dominant GM targets and exclude subordinate SC/ST targets, thus choosing derogation over coalition \cite{craig_coalition_2012}.
+Similarly, SC/ST participants rejected a solidarity-based identity that includes Indian Muslims.
+
+Our findings suggest that cross-group friendship can overcome these divisions by fostering social identities that include Indians of all castes and religions.
+As more inclusive identities were related to less social distance and more warmth toward caste and religious minorities, our research suggests that positive contact could help reduce interpersonal discrimination and violence against these groups.
+In line with recent research (e.g., \citeNP{hayward_how_2018}), we found that negative contact could exacerbate social divisions by fostering less inclusive identities.
+More broadly, our research speaks to \emph{how} contact reduces prejudice \cite{pettigrew_how_2008}.
+Our findings support arguments \cite{gaertner_reducing_2000, pettigrew_intergroup_1998} that contact can reduce prejudice by changing how we understand our social identities.
+
+Our research also examined support for social change.
+Contrary to past research, neither positive nor negative contact \cite{reimer_intergroup_2017} were associated with support for social change in advantaged \cite{dixon_intergroup_2007} and disadvantaged \cite{dixon_beyond_2012} groups.
+Similarly, more inclusive identities were not associated with opposition to affirmative action among the disadvantaged \cite{dovidio_darker_2012}.
+Features of the participants' situation might explain this discrepancy.
+As university students, participants have personally experienced the impact of reservation policies.
+For SC/ST and OBC students, reservation policies facilitated admission to state-funded universities.
+This experience  might explain why these students strongly support reservation (at least for their own group).
+For GM students, reservation policies thwarted admission to state-funded universities.
+This experience might explain why, in contrast to societal realities, GM students saw themselves at a disadvantage relative to other caste groups (see \citeNP{norton_whites_2011}).
+
+To conclude, we found correlational evidence that intergroup contact can change not only how we see others, but also how we see ourselves.
+That is, intergroup contact can foster more inclusive social identities---and thus improve intergroup relations.
+Fostering more inclusive identities, however, does not seem to overcome entrenched opposition to (or undermine support for) affirmative action.
+
 \nolinenumbers
-
 \bibliographystyle{apacite}

### 2018-11-06 prepare_data.R

@@ -61,9 +61,5 @@ rm(list = ls())
 # Export ------------------------------------------------------------------
   write_rds(d1, "data/d1.rds")
   write_rds(d2, "data/d2.rds")
-  
-  
-# Prepare -----------------------------------------------------------------
-  # Prepare data for analyses
-  # source("data/prepare_data_sdo.R")
-  # source("data/prepare_data_it.R")
+  write_csv(d1, "data/export/d1.csv")
+  write_csv(d2, "data/export/d2.csv")

### 2018-11-09 manuscript/manuscript.tex
prepare for submission

@@
 \setcounter{secnumdepth}{0}
-\usepackage{lineno}
+\usepackage[pagewise]{lineno}
 %\usepackage{authblk}
@@
 
-%\linenumbers
+\linenumbers
 
@@
 
-We tested these predictions in a triple crossed-categorisation task (adapted from \citeNP{dommelen_construing_2015}).
+We tested these predictions in a triple crossed-categorization task (adapted from \citeNP{dommelen_construing_2015}).
 In this task, participants viewed identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships.
@@
 Based on ratings in a pilot study ($N = 26$), we selected the four most prototypical targets (out of fifty initial targets) for each of six plausible combinations of caste, religion, and nationality (for details, see Appendix~A).
-Each target showed a person's caste (GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe), religion (Hindu, Muslim), and nationality (Indian, Nepali, Sri Lankan, Bangladeshi).
+Each target showed a person's caste reservation (GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe), religion (Hindu, Muslim), and nationality (Indian, Nepali, Sri Lankan, Bangladeshi).
 Each target also showed the person's first and last name, age (21--26 years), and a silhouette corresponding to the person's gender (adapted from \protect\citeNP{ma_chicago_2015}).
@@
 
-We compared \emph{how likely} participants were to categorize \emph{which} target as ``us'' versus ``not us''---and how that probability varied across targets' and participants' group memberships.\footnote{In Appendix~B, we report analyses using \citeauthor{dommelen_construing_2015}'s \citeyear{dommelen_construing_2015} operationalisation who analysed which and how many targets participants included as distinct questions.
-}
+We compared \emph{how likely} participants were to categorize \emph{which} target as ``us'' versus ``not us''---and how that probability varied across targets' and participants' group memberships.\footnote{In Appendix~B, we report analyses using \citeauthor{dommelen_construing_2015}'s \citeyear{dommelen_construing_2015} operationalisation; they analysed \emph{which} and \emph{how many} targets participants included as distinct questions.}
 
@@
 \caption{
-Comparison of models estimating the probability of participants categorising targets as ``us'' versus ``not us''.
+Comparison of models estimating the probability of participants categorizing targets as ``us'' versus ``not us''.
 $\textit{ELPD}$ is the expected log predictive density, with higher numbers indicating that a model is expected to make more accurate out-of-sample predictions \protect\fullcite{vehtari_practical_2017}.
@@
 Almost all SC/ST participants included \emph{Hindu, SC/ST} targets in their ingroup, \pest{M2}{.97}{.95}{.99}.
-Fewer SC/ST participants included \emph{Hindu, GM} and \emph{Hindu, OBC} in their ingroup, \pest{M2}{.88}{.83}{.92} and  and \pest{M2}{.80}{.73}{.86}.
+Fewer SC/ST participants included \emph{Hindu, GM} and \emph{Hindu, OBC} targets in their ingroup, \pest{M2}{.88}{.83}{.92} and  and \pest{M2}{.80}{.73}{.86}.
 SC/ST participants were less likely than others to include \emph{Muslim, OBC} targets as ``us'', \pest{M2}{.47}{.38}{.57}.
@@
 \includegraphics[scale=1]{../figures/figure-4}
-\caption{Estimated probability of participants categorising a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship with the relevant groups (in Model~5, Table~\ref{tab:t2}).
+\caption{Estimated probability of participants categorizing a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship with the relevant groups (in Model~5, Table~\ref{tab:t2}).
 GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.}
@@
 
-We analysed how participants' categorizations related to their warmth and social distance ratings for each target in the categorization task, to intergroup threat, and to their perceived (dis-)advantage and policy support.
+We analysed how participants' categorizations related to their feeling thermometerhttps://www.dur.ac.uk/jobs/recruitment/vacancies/psyc18-10/Over and social distance ratings for each target in the categorization task, to intergroup threat, and to their perceived (dis-)advantage and policy support.
 
@@
 This allowed more fine-grained analyses than \citeauthor{dommelen_construing_2015}’s quantitative and qualitative summaries, and may explain why we found more consistent effects of intergroup contact.
-Overall, these changes open the triple crossed-categorization task to a broader range of research questions.
+Together, these changes open the triple crossed-categorization task to a broader range of research questions.
 

### 2018-11-09 scripts/import_data.R

@@ -1,7 +1,7 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-  # See materials/script.pdf (Appendix D) for items and answer options.
+  # See materials/materials.pdf (Appendix D) for items and answer options.
 
   # To protect participants, we do not provide the raw data (data/sessions/)
   # with verbatim comments; this R script is thus not functional. Please import 

### 2018-11-09 scripts/prepare_data.R

@@ -1,7 +1,7 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-  #  See materials/script.pdf (Appendix D) for items and answer options.
+  #  See materials/materials.pdf (Appendix D) for items and answer options.
 
 
 # Library -----------------------------------------------------------------

### 2019-07-30 manuscript/appendices.tex
revision

@@
 \usepackage{tabularx}
+\usepackage{subcaption}
 
@@
 \title{\emph{Appendices for}\\Intergroup contact fosters\\more inclusive social identities}
-\date{November 5, 2018}
-%\author{Nils Karl Reimer}
-%\author[2]{Shanmukh V. Kamble}
-%\author[3]{Katharina Schmid}
-%\author[1]{Miles Hewstone}
-%\affil[1]{University of Oxford}
-%\affil[2]{Karnatak University}
-%\affil[3]{ESEADE Business School, Ramon Llull University}
-%\renewcommand\Affilfont{\small}
+\date{July 30, 2019}
 
@@
 
-\section{Appendix B: Social Identity Structures}
+\section{Appendix B: Descriptive Statistics}
+
+Table~\ref{tab:b-1} reports means and standard deviations for all variables. Tables~\ref{tab:b-2} to \ref{tab:b-5} report correlations between all variables for various ingroups and outgroups.
+
+\begin{table}[!hp]
+\centering
+\figureversion{lining, tabular}
+\caption{Means and standard deviations (in brackets) for all measured combinations of outgroups (rows) and ingroups (columns).}
+\small	
+\begin{tabular}{llrrr} \toprule
+Variable & Outgroup & GM & OBC & SC/ST \\ \midrule \addlinespace
+  Contact quantity & GM & - & 4.21 (0.96) & 3.84 (1.02) \\ 
+  Contact quantity & OBC & 3.74 (1.12) & - & 4.04 (0.94) \\ 
+  Contact quantity & SC/ST & 3.76 (1.10) & 3.92 (0.98) & - \\ 
+  Contact quantity & Muslims & 3.49 (1.30) & 3.54 (1.17) & 3.49 (1.19) \\ \addlinespace
+  Positive contact & GM & - & 4.03 (1.01) & 3.91 (1.05) \\ 
+  Positive contact & OBC & 3.83 (1.01) & - & 3.84 (1.13) \\ 
+  Positive contact & SC/ST & 3.68 (0.98) & 3.70 (1.19) & - \\ 
+  Positive contact & Muslims & 3.40 (1.21) & 3.64 (1.13) & 3.53 (1.29) \\ \addlinespace
+  Negative contact & GM & - & 2.17 (1.30) & 2.27 (1.30) \\ 
+  Negative contact & OBC & 1.96 (1.19) & - & 2.38 (1.32) \\ 
+  Negative contact & SC/ST & 1.99 (1.13) & 1.88 (1.13) & - \\ 
+  Negative contact & Muslims & 2.44 (1.30) & 2.20 (1.20) & 2.28 (1.23) \\ \addlinespace
+  Friendship & GM & - & 4.21 (0.84) & 3.95 (0.85) \\ 
+  Friendship & OBC & 3.58 (1.00) & - & 4.03 (0.85) \\ 
+  Friendship & SC/ST & 3.43 (0.96) & 3.66 (1.00) & - \\ 
+  Friendship & Muslims & 3.20 (1.12) & 3.37 (0.95) & 3.30 (0.93) \\ \addlinespace
+  (Dis-)advantage & GM & 2.83 (2.13) & 2.86 (2.02) & 4.08 (1.96) \\ 
+  (Dis-)advantage & OBC & 4.89 (1.68) & 3.90 (1.81) & 4.11 (1.70) \\ 
+  (Dis-)advantage & SC/ST & 5.44 (1.65) & 5.40 (1.79) & 4.30 (2.01) \\ 
+  (Dis-)advantage & Muslims & 4.26 (1.83) & 4.34 (1.77) & 3.84 (1.96) \\ \addlinespace
+  Policy support & OBC & 2.66 (1.35) & 3.79 (1.03) & 3.54 (0.94) \\ 
+  Policy support & SC/ST & 1.91 (1.15) & 2.28 (1.18) & 4.22 (0.88) \\ 
+  Policy support & Muslims & 2.62 (1.23) & 2.82 (1.17) & 3.28 (1.30) \\ \addlinespace
+  Realistic threat & SC/ST & 3.79 (1.16) & 3.48 (1.06) & - \\ 
+  Realistic threat & Muslims & 3.39 (1.09) & 3.06 (1.00) & 3.24 (1.10) \\ \addlinespace
+  Symbolic threat & SC/ST & 3.28 (1.07) & 3.18 (1.06) & - \\ 
+  Symbolic threat & Muslims & 3.60 (1.17) & 3.37 (1.12) & 3.53 (1.27) \\ \addlinespace
+  SDO-D &  & 0.02 (0.71) & -0.04 (0.74) & 0.05 (0.78) \\ 
+  SDO-E &  & 0.14 (0.72) & -0.06 (0.68) & -0.07 (0.82) \\  \bottomrule
+\end{tabular}
+\label{tab:b-1}
+\end{table}
+
+\begin{table}[!hp]
+\centering
+\figureversion{lining, tabular}
+\caption{Correlations between variables for GM (above the diagonal) and SC/ST (below the diagonal) participants with people from other backward classes (OBCs) as the relevant outgroup.}
+\small	
+\begin{tabular}{rlrrrrrrrr} \toprule
+\# & Variable & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\ \midrule 
+1 & Contact quantity &  &  .63 &  .01 &  .67 &  .22 & -.12 & -.06 & -.02 \\ 
+  2 & Positive contact &  &  & -.12 &  .55 &  .04 &  .02 & -.08 & -.03 \\ 
+  3 & Negative contact & -.28 &  &  &  .01 &  .01 &  .11 &  .13 &  .10 \\ 
+  4 & Friendship &  .41 &  .49 &  &  &  .16 & -.06 & -.10 & -.06 \\ 
+  5 & (Dis-)advantage &  .14 &  .12 & -.05 &  &  & -.22 & -.09 & -.03 \\ 
+  6 & Policy support &  .11 &  .12 & -.19 &  .13 &  &  &  .14 &  .15 \\ 
+  7 & SDO-D &  .11 &  .06 &  .15 &  .13 &  .14 &  &  &  .43 \\ 
+  8 & SDO-E & -.05 &  .17 & -.03 &  .03 &  .14 &  .15 &  &  \\ 
+\bottomrule
+\end{tabular}
+\label{tab:b-2}
+\end{table}
+
+\begin{table}[!hp]
+\centering
+\figureversion{lining, tabular}
+\caption{Correlations between variables for OBC (above the diagonal) and SC/ST (below the diagonal) participants with people from general castes (GM) as the relevant outgroup.}
+\small	
+\begin{tabular}{rlrrrrrrr} \toprule
+\# & Variable & 1 & 2 & 3 & 4 & 5 & 6 & 7  \\ \midrule 
+1 & Contact quantity &  &  .64 & -.31 &  .60 & -.00 & -.10 & -.03 \\ 
+  2 & Positive contact &  &  & -.27 &  .63 & -.12 & -.07 & -.11 \\ 
+  3 & Negative contact & -.03 &  &  & -.27 & -.04 &  .00 & -.05 \\ 
+  4 & Friendship &  .17 &  .42 &  &  & -.07 & -.08 & -.12 \\ 
+  5 & (Dis-)advantage &  .06 & -.02 & -.04 &  &  &  .09 &  .01 \\ 
+  6 & SDO-D &  .15 &  .08 &  .14 &  .14 &  &  &  .46 \\ 
+  7 & SDO-E &  .06 & -.02 &  .15 & -.06 &  .10 &  &  \\  
+\bottomrule
+\end{tabular}
+\label{tab:b-3}
+\end{table}
+
+\newpage
+
+\begin{table}[!hp]
+\centering
+\figureversion{lining, tabular}
+\caption{Correlations between variables for GM (above the diagonal) and OBC (below the diagonal) participants with Dalits (SC/ST) as the relevant outgroup.}
+\small	
+\begin{tabularx}{\linewidth}{r@{~~}X@{~~}rrrrrrrrrr} \toprule
+\# & Variable & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \midrule 
+1 & Contact quantity &  &  .47 & -.14 &  .41 &  .28 & -.20 &  .25 &  .09 & -.03 & -.06 \\ 
+  2 & Positive contact &  &  & -.30 &  .18 &  .31 &  .02 & -.08 & -.08 & -.03 & -.09 \\ 
+  3 & Negative contact &  .05 &  &  & -.01 & -.15 &  .03 &  .16 &  .22 &  .13 & -.10 \\ 
+  4 & Friendship &  .31 &  .40 &  &  &  .06 & -.10 &  .07 & -.05 & -.12 & -.10 \\ 
+  5 & (Dis-)advantage & -.03 & -.02 & -.23 &  &  & -.21 &  .24 & -.06 &  .06 &  .14 \\ 
+  6 & Policy support &  .13 &  .21 &  .12 & -.03 &  &  & -.33 &  .06 &  .30 &  .04 \\ 
+  7 & Realistic threat &  .04 &  .10 &  .03 & -.03 &  .08 &  &  &  .39 & -.03 &  .02 \\ 
+  8 & Symbolic threat & -.12 &  .02 &  .16 & -.08 & -.04 & -.05 &  &  &  .35 & -.03 \\ 
+  9 & SDO-D & -.11 &  .01 &  .18 &  .09 &  .11 &  .07 &  .14 &  &  &  .43 \\ 
+  10 & SDO-E & -.08 &  .11 &  .02 &  .04 &  .13 &  .15 &  .13 &  .10 &  &  \\ 
+\bottomrule
+\end{tabularx}
+\label{tab:b-4}
+\end{table}
+
+\begin{table}[!hp]
+\centering
+\figureversion{lining, tabular}
+\caption{Correlations between variables for all non-Muslims participants with Muslims as the relevant outgroup.}
+\small	
+\begin{tabularx}{\linewidth}{r@{~~}X@{~~}rrrrrrrrrr} \toprule
+\# & Variable & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \midrule 
+1 & Contact quantity &  &  .64 & -.11 &  .61 &  .17 &  .10 & -.11 & -.18 & -.04 & -.01 \\ 
+  2 & Positive contact &  .64 &  & -.18 &  .65 &  .14 &  .15 & -.19 & -.22 & -.04 & -.06 \\ 
+  3 & Negative contact & -.11 & -.18 &  & -.12 & -.01 & -.08 &  .14 &  .22 &  .17 &  .02 \\ 
+  4 & Friendship &  .61 &  .65 & -.12 &  &  .03 &  .11 & -.21 & -.25 &  .01 & -.03 \\ 
+  5 & (Dis-)advantage &  .17 &  .14 & -.01 &  .03 &  & -.16 &  .11 &  .06 &  .02 &  .00 \\ 
+  6 & Policy support &  .10 &  .15 & -.08 &  .11 & -.16 &  & -.17 & -.14 &  .05 & -.01 \\ 
+  7 & Realistic threat & -.11 & -.19 &  .14 & -.21 &  .11 & -.17 &  &  .51 &  .10 &  .08 \\ 
+  8 & Symbolic threat & -.18 & -.22 &  .22 & -.25 &  .06 & -.14 &  .51 &  &  .13 &  .07 \\ 
+  9 & SDO-D & -.04 & -.04 &  .17 &  .01 &  .02 &  .05 &  .10 &  .13 &  &  .46 \\ 
+  10 & SDO-E & -.01 & -.06 &  .02 & -.03 &  .00 & -.01 &  .08 &  .07 &  .46 &  \\ 
+\bottomrule
+\end{tabularx}
+\label{tab:b-5}
+\end{table}
+
+\newpage
+
+\section{Appendix C: Social Identity Structures}
 
@@
 Few (9\%, $n = 26$) participants consistently classified all targets in each category as either ``us'' or ``not us''.
-Relatedly, how participants classified targets within a category was correlated, but only moderately so ($.41 \leq rs \leq.66$, see Table ~\ref{tab:b-1}).
+Relatedly, how participants classified targets within a category was correlated, but only moderately so ($.41 \leq rs \leq.66$, see Table ~\ref{tab:c-1}).
 The inconsistency in participants' responses made hard and fast coding rules, as used by \citeauthor{dommelen_construing_2015}, impractical.
+
+Instead, we quantified the (dis)similarity between a participant's responses and various proposed social identity structures by calculating edit distances.
+We operationalized \emph{edit distance} as the number of a participant's categorizations that would need to change from ``us'' to ``not us'' (and vice versa) to make them identical to the categorizations implied by a certain structure.
+Figure~\ref{fig:c-1} shows the distributions of participants' edit distances from each structure, as well as median edit distances.
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/appendices/appendices-b-1}
+\caption[Edit distances between social identity structures and participants' responses]{Edit distances between each social identity structure and participants' responses.
+Edit distance is the sum of all categorizations in which a participant's responses differed from the ones implied by the proposed structure.
+Numbers (on the right) show the median edit distance per structure.
+%Points indicate the median \emph{social identity inclusiveness} of participants' responses at a specific edit distance.
+}
+\label{fig:c-1}
+\end{figure}
+
+Overall, participants' responses most closely resembled the Indian-Hindu merger structure ($\textit{Mdn} = 5.0$), in which participants include all targets who are \emph{either} Indian \emph{or} Hindu \emph{or} both in the ingroup.
+This was closely followed by inclusive nationalism ($\textit{Mdn} = 6.5$), i.e.
+participants include all targets who are Indian, and Hindu nationalism ($\textit{Mdn} = 7.0$), i.e.
+participants include only Indian Hindu targets.
+In addition, Pan-Hinduism ($\textit{Mdn} = 8.0$), i.e.
+participants include all Hindu targets, and egalitarianism ($\textit{Mdn} = 8.0$), i.e.
+participants include all targets, somewhat described participants' responses.
+Caste did not seem to dominate participants' responses ($\textit{Mdn} = 12.0$).
+Together, these observations suggested that, on the broadest level of analysis, participants relied on nationality and religion, rather than caste, to define their ingroup.
 
@@
 \end{tabular}
-\label{tab:b-1}
+\label{tab:c-1}
 \end{table}
 
-Instead, we quantified the (dis)similarity between a participant's responses and various proposed social identity structures by calculating edit distances.
-We operationalised \emph{edit distance} as the number of a participant's categorizations that would need to change from ``us'' to ``not us'' (and vice versa) to make them identical to the categorizations implied by a certain structure.
-Figure~\ref{fig:b-1} shows the distributions of participants' edit distances from each structure, as well as median edit distances.
-
-\begin{figure}
-\centering
-\includegraphics[scale=1]{../figures/appendices/appendices-b-1}
-\caption[Edit distances between social identity structures and participants' responses]{Edit distances between each social identity structure and participants' responses.
-Edit distance is the sum of all categorizations in which a participant's responses differed from the ones implied by the proposed structure.
-Numbers (on the right) show the median edit distance per structure.
-%Points indicate the median \emph{social identity inclusiveness} of participants' responses at a specific edit distance.
-}
-\label{fig:b-1}
-\end{figure}
-
-Overall, participants' responses most closely resembled the Indian-Hindu merger structure ($\textit{Mdn} = 5.0$), in which participants include all targets who are \emph{either} Indian \emph{or} Hindu \emph{or} both in the ingroup.
-This was closely followed by inclusive nationalism ($\textit{Mdn} = 6.5$), i.e.
-participants include all targets who are Indian, and Hindu nationalism ($\textit{Mdn} = 7.0$), i.e.
-participants include only Indian Hindu targets.
-In addition, Pan-Hinduism ($\textit{Mdn} = 8.0$), i.e.
-participants include all Hindu targets, and egalitarianism ($\textit{Mdn} = 8.0$), i.e.
-participants include all targets, somewhat described participants' responses.
-Caste did not seem to dominate participants' responses ($\textit{Mdn} = 12.0$).
-Together, these observations suggested that, on the broadest level of analysis, participants relied on nationality and religion, rather than caste, to define their ingroup.
-
-\section{Appendix C: Intergroup Threat}
+\section{Appendix D: Intergroup Threat}
 
@@
 \end{tabularx}
-\label{tab:c-1}
+\label{tab:d-1}
 \end{table}
 
-Model~3, but not Models 1 and 2, improved upon the predictions of Model~0 (Table~\ref{tab:c-1}), showing that participants' perceptions of symbolic and realistic threat depended on whether the relevant outgroup was Muslims or Dalits.
+Model~3, but not Models 1 and 2, improved upon the predictions of Model~0 (Table~\ref{tab:d-1}), showing that participants' perceptions of symbolic and realistic threat depended on whether the relevant outgroup was Muslims or Dalits.
 Specifically, participants reported more realistic ($ \beta_1 = 3.62$, $[3.49, 3.75]$) than symbolic ($\beta_2 = 3.21$, $[3.09, 3.33]$) threat from (same-religion) Dalits, $\text{Pr} (\beta_1 > \beta_2|M3) > .99$, but less realistic ($\beta_3 = 3.23$, $[3.06, 3.38]$) than symbolic ($\beta_4 = 3.47$, $[3.34, 3.61]$) threat from (different-religion) Muslims, $\text{Pr} (\beta_3 < \beta_4| M3) > .99$.
@@
 
-\section{Appendix D: Support for Social Change}
+\section{Appendix E: Support for Social Change}
 
@@
 We examined participants' responses to measures concerning outgroup members to test the \emph{solidarity hypothesis} (that positive contact encourages advantaged-group members to support social change).
-We examined participants' responses to measures concerning their ingroup to test the \emph{demobilisation hypothesis} (that positive contact discourages disadvantaged-group members from supporting social change) and the \emph{mobilisation hypothesis} (that negative contact encourages disadvantaged-group members to support social change).
+We examined participants' responses to measures concerning their ingroup to test the \emph{demobilization hypothesis} (that positive contact discourages disadvantaged-group members from supporting social change) and the \emph{mobilization hypothesis} (that negative contact encourages disadvantaged-group members to support social change).
 
@@
 
-Figure \ref{fig:d-1} shows estimated mean ratings of perceived (dis-)advantage for all target groups as a function of participants' caste memberships in Model~1.
+Figure \ref{fig:e-1} shows estimated mean ratings of perceived (dis-)advantage for all target groups as a function of participants' caste memberships in Model~1.
 For most target groups, General Merit and Other Backward Class participants' responses closely resembled each other.
@@
 }
-\label{fig:d-1}
+\label{fig:e-1}
 \end{figure}
 
-Figure \ref{fig:d-2} shows estimated policy support---that is, support for reservations benefiting Scheduled Caste~/ Scheduled Tribe, Other Backward Class, and Muslim students---as a function of participants' caste memberships in Model~1.
+Figure \ref{fig:e-2} shows estimated policy support---that is, support for reservations benefiting Scheduled Caste~/ Scheduled Tribe, Other Backward Class, and Muslim students---as a function of participants' caste memberships in Model~1.
 General Merit and Other Backward Class participants' responses did not provide evidence for cross-group solidarity.
@@
 }
-\label{fig:d-2}
+\label{fig:e-2}
 \end{figure}
@@
 \end{tabularx}
-\label{tab:d-1}
+\label{tab:e-1}
 \end{table}
 
-Table~\ref{tab:d-1} shows the estimated residual correlations before (Model~0) and after (Model~1) accounting for group differences.
+Table~\ref{tab:e-1} shows the estimated residual correlations before (Model~0) and after (Model~1) accounting for group differences.
 Perceiving a group to be disadvantaged correlated weakly with more support for reservations benefiting Scheduled Caste~/ Scheduled Tribe ($r = -.12 $, $[-.24,.01]$), Other Backward Class ($r = -.17$, $[-.30,-.05]$), and Muslim ($r = -.15$, $[-.28,-.03]$) students in Model~1.
@@
 4 & vs 3 & \textit{Solidarity}       & .35 & -1787.6 & 24.7 & -0.7 & 2.4 & -0.3 & .23 \\ \addlinespace
-5 & vs 0 & \textit{(De)mobilisation} & .35 & -1791.5 & 24.6 & -2.0 & 1.2 & -1.7 & .00 \\
-6 & vs 5 & \textit{(De)mobilisation} & .35 & -1792.6 & 24.6 & -1.1 & 0.9 & -1.2 & .00 \\
-7 & vs 0 & \textit{(De)mobilisation} & .35 & -1788.9 & 24.5 & 0.5 & 1.4 & 0.4 & .00 \\
-8 & vs 7 & \textit{(De)mobilisation} & .35 & -1788.4 & 24.5 & 0.5 & 1.4 & 0.4 & .12 \\ \addlinespace \bottomrule
+5 & vs 0 & \textit{(De)mobilization} & .35 & -1791.5 & 24.6 & -2.0 & 1.2 & -1.7 & .00 \\
+6 & vs 5 & \textit{(De)mobilization} & .35 & -1792.6 & 24.6 & -1.1 & 0.9 & -1.2 & .00 \\
+7 & vs 0 & \textit{(De)mobilization} & .35 & -1788.9 & 24.5 & 0.5 & 1.4 & 0.4 & .00 \\
+8 & vs 7 & \textit{(De)mobilization} & .35 & -1788.4 & 24.5 & 0.5 & 1.4 & 0.4 & .12 \\ \addlinespace \bottomrule
 \end{tabularx}
-\label{tab:d-2}
+\label{tab:e-2}
 \end{table}
@@
 4 & vs 3 & \textit{Solidarity}       & .49 & -1741.6 & 26.9 &  -0.6 & 1.1 & -0.5 & .00 \\ \addlinespace
-5 & vs 0 & \textit{(De)mobilisation} & .49 & -1742.0 & 26.9 & -0.9 & 1.7 & -0.5 & .03 \\
-6 & vs 5 & \textit{(De)mobilisation} & .49 & -1743.3 & 26.9 & -1.3 & 0.8 & -1.6 & .00\\
-7 & vs 0 & \textit{(De)mobilisation} & .49 & -1741.6 & 26.8 & -0.6 & 0.8 & -0.8 & .00\\
-8 & vs 7 & \textit{(De)mobilisation} & .50 & -1740.0 & 26.8 &  1.6 & 2.0 & 0.8 & .37 \\ \addlinespace \bottomrule
+5 & vs 0 & \textit{(De)mobilization} & .49 & -1742.0 & 26.9 & -0.9 & 1.7 & -0.5 & .03 \\
+6 & vs 5 & \textit{(De)mobilization} & .49 & -1743.3 & 26.9 & -1.3 & 0.8 & -1.6 & .00\\
+7 & vs 0 & \textit{(De)mobilization} & .49 & -1741.6 & 26.8 & -0.6 & 0.8 & -0.8 & .00\\
+8 & vs 7 & \textit{(De)mobilization} & .50 & -1740.0 & 26.8 &  1.6 & 2.0 & 0.8 & .37 \\ \addlinespace \bottomrule
 \end{tabularx}
-\label{tab:d-3}
+\label{tab:e-3}
 \end{table}
@@
 Models~1 to 4 did not improve upon the out-of-sample predictions of Model~0, showing that neither intergroup contact (Models~1, 2) nor inclusive identities (Models~3, 4) foster support for policies benefiting a disadvantaged outgroup.
-Models~5 to 8 did not improve upon the out-of-sample predictions of Model~0, showing that neither contact with (Models~5, 6) nor inclusion of (Models~7, 8) General Merit people affected Scheduled Caste~/ Scheduled Tribe and Other Backward Class participants' support for policies benefiting their ingroups (see Table~\ref{tab:d-3}).
+Models~5 to 8 did not improve upon the out-of-sample predictions of Model~0, showing that neither contact with (Models~5, 6) nor inclusion of (Models~7, 8) General Merit people affected Scheduled Caste~/ Scheduled Tribe and Other Backward Class participants' support for policies benefiting their ingroups (see Table~\ref{tab:e-3}).
 
 Overall, these findings show that neither intergroup contact nor ingroup construals could explain individual differences in support for social change.
-Contrary to the \emph{demobilisation hypothesis}, positive contact did not decrease disadvantaged-group participants' support for social change.
-Contrary to the \emph{mobilisation hypothesis}, negative contact did not increase disadvantaged-group participants' support for social change.
+Contrary to the \emph{demobilization hypothesis}, positive contact did not decrease disadvantaged-group participants' support for social change.
+Contrary to the \emph{mobilization hypothesis}, negative contact did not increase disadvantaged-group participants' support for social change.
 Contrary to predictions, neither positive contact nor more inclusive identities were associated with support for policies benefiting (other) disadvantaged outgroups.
 
-\section{Appendix E: Additional Measures}
+\section{Appendix F: Additional Measures}
 
@@
 
-Social identity complexity \cite{roccas_social_2002, schmid_antecedents_2009} was operationalised as the extent to which participants perceived their different group memberships as conceptually interrelated (\emph{similarity complexity}) and numerically overlapping (\emph{overlap complexity}).
+Social identity complexity \cite{roccas_social_2002, schmid_antecedents_2009} was operationalized as the extent to which participants perceived their different group memberships as conceptually interrelated (\emph{similarity complexity}) and numerically overlapping (\emph{overlap complexity}).
 Two items measured similarity complexity for religion/nationality and for nationality/caste: ``How similar or different are the typical [Hindu/Indian] and the typical [Indian/person from your caste group] to each other?'' ($1 = \textit{very different}$, $5 = \textit{very similar}$, reverse coded), and ``Do you think that being [Hindu/Indian] means the same as being [Indian/from your caste group]?'' ($1 = \textit{means something very similar}$, $5 = \textit{means something very different}$).
@@
 
-Figure~\ref{fig:e-1} shows the estimated correlations between participants' categorizations in the triple crossed-categorization task (from left to right) and various social identification variables (from top to bottom).
+Figure~\ref{fig:f-1} shows the estimated correlations between participants' categorizations in the triple crossed-categorization task (from left to right) and various social identification variables (from top to bottom).
 Entitativity---the extent to which participants saw Indians of \emph{all} castes and religions as similar to one another, as depending on each other, as sharing a common fate, as working towards shared goals, and as valuing their shared identity---was positively correlated with the proportion of \emph{Indian, Hindu, GM} ($r = .16$, $[.04, .27]$, $\text{Pr} (r > 0|M) > .99$), \emph{Indian, Hindu, OBC} ($r = .21$, $[.09, .31]$, $\text{Pr} (r > 0| M) > .99$), \emph{Indian, Hindu, SC/ST} ($r = .10$, $[-.02, .22]$, $\text{Pr} (r > 0| M) = .97$), and \emph{Indian, Muslim, OBC} ($r = .18$, $[.07, .30]$, $\text{Pr} (r > 0| M) > .99$) targets participants categorized as ``us''.
@@
 Correlations for which $\text{Pr} (r > 0| M) > .99$ or $\text{Pr} (r < 0| M) > .99$ are shown in a darker shade.}
-\label{fig:e-1}
+\label{fig:f-1}
 \end{figure}

### 2019-07-30 manuscript/manuscript.tex
revision

--- 2018-11-02 manuscript/manuscript.tex
@@
 % Format
-\usepackage{layout}
 \setlength{\parindent}{0.5in}
 \setcounter{secnumdepth}{0}
-\usepackage{lineno}
-\usepackage{authblk}
+\usepackage[pagewise]{lineno}
+%\usepackage{authblk}
 
@@
 \title{Intergroup contact fosters\\more inclusive social identities}
-\date{November 5, 2018}
-\author{Nils Karl Reimer}
-\author[2]{Shanmukh V. Kamble}
-\author[3]{Katharina Schmid}
-\author[1]{Miles Hewstone}
-\affil[1]{University of Oxford}
-\affil[2]{Karnatak University, Dharwad}
-\affil[3]{ESADE Business School, Ramon Llull University}
-\renewcommand\Affilfont{\small}
+\date{July 30, 2019}
 
@@
 
-\linenumbers
+%\linenumbers
 
-\noindent (for a review, see \citeNP{authors_theories_inpress}) (see Figure~\ref{fig:f1}) \cite{devos_american_2005}
+\noindent How we feel about and act toward others depends on whom we consider ``us'' and ``them''---that is, whom we include in, and exclude from, our ingroup (for a review, see \citeNP{schmid_theories_2011}).
+In some situations, this distinction rests on one salient categorization, for example, someone's nationality at an international border.
+In diverse societies, however, this distinction often depends on multiple, overlapping group memberships.
+Individuals differ in how they construct their ingroup from these group memberships.
+Some espouse narrow definitions of who is ``us'' and ``them'', while others adopt more inclusive identities.
+Many Americans, for example, associate being American with being White American \cite{devos_american_2005}.
+This suggests that whom Americans consider ``us'' and ``them'' might depend on someone's race \emph{and} nationality.
+In this paper, we examine how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce prejudice by fostering more inclusive social identities.
+We use a novel method to study social identification across multiple social categories and to examine possible antecedents (intergroup contact, social dominance orientation) and consequences (outgroup attitudes, intergroup threat, support for affirmative action) of more inclusive identities.
 
@@
 \caption{
-Schematic representations of social identity structures, ordered by social identity inclusiveness \protect\fullcite{dommelen_construing_2015}.
+Schematic representations of social identity structures \protect\cite{roccas_social_2002}, ordered by their social identity inclusiveness \protect\cite{dommelen_construing_2015}.
 Shaded regions represent the groups which a participant has to categorize as ``us'' to be assigned that structure.
-An Indian Hindu, for example, may consider only people who share their nationality, religion, and caste as ingroup members (intersection).
-Someone else may consider all their fellow Indians, whatever their religion or caste, as ingroup members (dominance).
-Another person may consider anyone who shares their nationality or religion as ingroup members (merger).
+An Indian Hindu, for example, might consider only people who share their nationality, religion, and caste as ingroup members (intersection).
+Someone else might consider all their fellow Indians, whatever their religion or caste, as ingroup members (dominance).
+Another person might consider anyone who shares their nationality or religion as ingroup members (merger).
 }
@@
 
+Social psychologists highlighted the importance of considering two \cite{berry_immigration_1997, crisp_multiple_2007, dovidio_commonality_2009} or more \cite{roccas_social_2002} social categories for understanding intergroup relations.
+\citeA{crisp_multiple_2007} reviewed evidence that we tend to have more favourable attitudes towards people with whom we share some, but not all, group memberships than towards people with whom we do not share any group memberships.
+\citeA{gaertner_reducing_2000} showed that espousing a more inclusive common ingroup identity (e.g., Indian) over a narrower identity (e.g., Hindu, Muslim) can extend the benefits of ingroup favouritism to outgroup members and thus reduce intergroup bias.
+\citeA{roccas_social_2002} recognized that, though we all hold multiple overlapping group memberships, we differ in how we construct our social identities from these group memberships.
+Broadly, these perspectives recognize that we are part of multiple overlapping groups; that we use these group memberships to construct a subjective sense of who is ``us'' and ``them''; and that espousing more inclusive social identities can reduce prejudice and discrimination.
+
+Diverse societies confront their members with the decision of which intersections of various group memberships they include in their subjective ingroup.
+One Indian Hindu, for example, might constrict their ingroup to people of the same nationality, religion, and caste.
+Another Indian Hindu might consider all Indians, whatever their religion or caste, as ingroup members (see Figure~\ref{fig:f1}).
+Past research \cite{dommelen_construing_2015} indeed observed substantial individual differences in whom participants considered ``us'' and ``not us''.
+Some participants espoused more inclusive social identities---that is, they included more people in their subjective ingroup.
+Other participants espoused less inclusive social identities---that is, they included fewer people in their subjective ingroup.
+All participants, however, belonged to the same disadvantaged minority group.
+Past research thus provided evidence for \emph{individual differences}, but did not examine \emph{group differences} in whom people consider ``us'' and ``not us''.
+
+Group membership, however, often shapes whom people include in, and exclude from, their subjective ingroup.
+For majority-group members, negotiating their ethnic and national identities means something different than for minority-group members (for a review, see \citeNP{dovidio_commonality_2009}).
+Majority-group members face the choice of including or excluding ethnic, religious, and other minorities from their subjective ingroup.
+Choosing to include or exclude minorities could, for example, reflect whether a majority-group member holds multicultural or nativist views.
+Minority-group members face the choice of aligning themselves with the dominant majority group, or seeking a common ingroup identity with other subordinate minority groups.
+Choosing an identity that includes either the majority group or other minority groups could, for example, reflect whether minority-group members seek to derogate or form a coalition with other minority groups \cite{craig_coalition_2012}.
+We expect that group differences are as great as, if not greater than, individual differences in social identity construals---especially if groups differ in status and power.
+Our research includes participants from advantaged, intermediate, and disadvantaged backgrounds to study how groups differ in whom their members consider ``us'' and ``not us''.
+
+How we think and feel about others depends on whether we include them in our ingroup.
+Dividing others into ``us'' and ``not us'' is thus a necessary and sufficient condition for ingroup favouritism \cite{tajfel_human_1981}.
+Past research has shown that people favour ingroup members in resource allocation \cite{tajfel_social_1971}, in causal attribution \cite{hewstone_ultimate_1990, taylor_ethnocentrism_1974}, in helping behaviour \cite{levine_identity_2005}, in information processing \cite{bavel_neural_2008}, and in evaluation \cite{otten_evidence_2000}.
+Considering more people as ``us'' should extend ingroup favouritism to a wider range of people, and thus reduce prejudice and discrimination (for a review, see \citeNP{gaertner_common_2016}).
+Our research examines whether fostering more inclusive social identities leads to more favourable attitudes and less social distance toward national, religious, and caste outgroups.
+
+Contact with members of other groups changes how we think and feel about them.
+Past research has shown that intergroup contact reduces prejudice \cite{pettigrew_meta_2006} by decreasing intergroup anxiety, increasing empathy and perspective-taking, and by increasing knowledge about the other group \cite{pettigrew_how_2008}.
+In addition, researchers have proposed that contact could reduce prejudice by changing how we see ourselves
+\cite{pettigrew_generalized_1997, pettigrew_intergroup_1998}.
+Encountering diverse others could initiate a process of cognitive differentiation \cite{schmid_social_2011} whereby individuals become aware of complex interrelations between their group memberships and thus adopt more complex social identities \cite{schmid_antecedents_2009}---that is, they become aware that they belong to multiple categories and recognize that these multiple categories do not always overlap \cite{roccas_social_2002}.
+Other research has found that intergroup contact can, under the right conditions, motivate people to adopt a more inclusive common ingroup identity \cite{gaertner_contact_1994} and to include the relevant outgroup in their self-concept \cite{page_understanding_2010}.
+If intergroup contact motivates people to adopt social identities that include outgroup members, it should reduce prejudice and discrimination against them.
+Our research examines whether intergroup contact can reduce prejudice against religious and caste outgroups by fostering social identities that include them as ingroup members.
+
+Beyond prejudice, researchers have debated whether, by fostering more inclusive identities, intergroup contact helps or hinders social change.
+Social change often requires advantaged and disadvantaged groups to strive for redistributive policies.
+On the one hand, fostering inclusive identities could break down the boundaries between the advantaged ingroup and the disadvantaged outgroup---turning injustice faced by ``them'' into ``our'' problem.
+This process could narrow the gap between advantaged-group members' support for the principle of equality and their opposition to its implementation \cite{dixon_intergroup_2007}.
+On the other hand, fostering more inclusive identities could distract disadvantaged-group members from differences in resources and power, and thus reduce their demands for and support for action aimed at social change \cite{dovidio_darker_2012, saguy_irony_2009}.
+Together, these mechanisms suggest that fostering more inclusive identities could increase support for social change among the advantaged, but decrease support among the disadvantaged.
+Our research examines how intergroup contact, by fostering more inclusive social identities, affects support for affirmative action policies, as well as perceptions of relative advantage and disadvantage, in advantaged and disadvantaged groups.
+
+\subsection{Caste, Religion, Nation in South India}
+
+We investigated these questions in the context of caste, religion, and nationality in South India.
+South India provides an important context for studying social identification across multiple social categories.
+India is diverse.
+South Indians belong to different castes, religions, and other groups that converge, diverge, and intersect in interesting ways.
+India is also underrepresented in psychological research.\footnote{Among the non-WEIRD \cite{henrich_weirdest_2010} countries underrepresented in social psychological research, India is a prominent omission as it spans almost a fifth of the world's population.} Few studies \cite<e.g.,>{ghosh_hindu_1991, tausch_relationships_2009} of intergroup relations focus on religious relations in India.
+Even fewer \cite<e.g.,>{cotterill_ideological_2014} focus on caste relations.
+Our research examined the cross-cutting categories of caste, religion, and nationality in a diverse sample of South Indian students.
+
+Caste is a system of social relations that concentrates resources in the hands of dominant castes by restricting subordinate castes' occupations and land ownership, and by enforcing endogamy and segregation \cite{jodhka_caste_2012}.
+This system is underpinned by a tradition that ranks castes according to their supposed ritual purity, and condemns contact with supposedly less pure castes.
+Since Independence, the Indian State has sought to redress caste-based injustices by enforcing `reservations' of seats in state-run universities and state-sector jobs for disadvantaged groups.
+It recognizes Dalits, members of castes affected by untouchability, as `Scheduled Castes' (SCs); Adivasi, India's indigenous peoples, as `Scheduled Tribes' (STs); and other disadvantaged groups, who occupy an intermediate position in the caste hierarchy, as `Other Backward Classes' (OBCs).
+Historically advantaged castes do not have access to reserved seats and jobs (GM: `General Merit').
+Reservation policies, alongside ongoing discrimination, mean that caste identities remain important in electoral politics and political organizing.
+
+South India is religiously diverse.
+In Karnataka, where we conducted this research, 84\% of inhabitants are Hindus, while 13\% are Muslims.
+Muslims face both structural inequalities and communal violence.
+In 2002, for example, over a thousand Muslims were killed in a pogrom in Gujarat \cite{dhattiwala_political_2012}.
+In recent years, anti-Muslim violence has been increasing \cite{amnesty_india_2017}.
+Religion is intertwined with two currents of Indian nationalism \cite{menski_hindu_2009}.
+On the one hand, the secular foundations of the Indian State resulted from an inclusive nationalism that strives to include Indians of all religions.
+On the other hand, Hindu nationalism (Hindutva) is an ideology that equates being Indian with being Hindu, thus excluding Muslims from the national identity.
+Narendra Modi's Bharatiya Janata Party (BJP) government espouses Hindutva and enjoys broad support in the Indian population \cite{pew_three_2017}.
+Indians thus face a choice between two ideologies that either include Indian Muslims in the national identity or exclude them from it.
+
+\section{Present research}
+
+We examined how people construct their social identities from multiple group memberships, whether intergroup contact is associated with more inclusive social identities, and how more inclusive social identities relate to prejudice and support for social change.
+Our research used a novel method to study social identification across multiple categories in a sample of South Indians from diverse caste backgrounds.
+Below, we first introduce this experimental task before reviewing the research questions and hypotheses guiding the present research.
+
+We adapted the triple crossed-categorization task \cite{dommelen_construing_2015} to assess how participants construct their social identities from multiple group memberships.
+In this task, participants view identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships.
+Participants report whether they consider each person as ``us'' or ``not us'', showing whom they include in, or exclude from, their ingroup.
+This task allowed us to study identification across multiple social categories and how it relates to the predictors and outcomes in our hypotheses.
+Van Dommelen and colleagues \citeyear{dommelen_construing_2015} used a similar task to examine whom participants considered ``us'' and ``not us''.
+However, their research included participants from only one group, aggregated participants' categorizations into a single score, and tested whether that score correlated with aggregated responses to contact and attitude measures.\footnote{Van Dommelen et al.
+\citeyear{dommelen_construing_2015} summarized participants' responses qualitatively by categorizing them into distinct \emph{social identity structures} and quantitatively by counting the total number of ``us'' responses as \emph{social identity inclusiveness}.} Our research included participants from multiple groups and used multilevel modeling to test whether contact with and attitudes toward \emph{each} group were associated with the inclusion of \emph{that} group in one's social identity.
+This allowed for a more fine-grained analysis of individual and group differences in identification across multiple social categories.
+
+We pursued four substantive research questions.
+First, we examined how participants' group memberships shaped whom they included in, and excluded from, their ingroup.
+We hypothesized that participants would exclude targets from religious and national outgroups---and that participants from advantaged castes would exclude targets from disadvantaged castes, and vice versa.
+We did not have a clear prediction for participants from intermediate caste backgrounds.
+Second, we examined whether past experiences with members of caste and religious outgroups shaped whom participants included in, and excluded from, their ingroup.
+We hypothesized that positive contact and cross-group friendship would be associated with more---and negative contact \cite{barlow_contact_2012, hayward_toward_2017} with less---inclusive social identities.
+Third, we examined whether, by fostering more inclusive social identities, intergroup contact would be associated with less prejudice.
+We hypothesized that categorizing someone as ``us'' would be associated with more favourable attitudes and less social distance toward that person.
+Fourth, we examined how intergroup contact, by fostering more inclusive social identities, affects support for affirmative action in advantaged and disadvantaged groups.
+We hypothesized that more inclusive social identities would be associated with less perceived discrimination and less support for affirmative action among the disadvantaged, and with more perceived privilege and more support for affirmative action among the advantaged.
+
+We examined two other constructs that might be related to more and less inclusive social identities.
+First, we included ideological preferences for group dominance \cite{sidanius_social_1999} as an additional predictor variable to rule out a potential confound, whereby people high in social dominance orientation might both eschew contact with caste and religious minorities and exclude them from the common ingroup.
+Second, we included perceptions of intergroup threat as an additional outcome variable to test whether more inclusive social identities were associated with this more distal outcome.
+Perceptions of intergroup threat play an important role in shaping intergroup relations (for a review, see \citeNP{stephan_intergroup_2016}).
+We tested whether participants who included caste and religious minorities in their ingroup would, in addition to feeling more warmth and less social distance toward them, feel less threatened by them in terms of both realistic and symbolic threat.
+
+\section{Method}
+
+All materials, data, analysis scripts, and appendices are available online (\href{https://osf.io/ekb8z/?view_only=05b6a5c5cf5e43d9a7bba5e192f53f87}{https://osf.io/ ekb8z/?view\_only=05b6a5c5cf5e43d9a7bba5e192f53f87}).
+Here, we only report measures testing our hypotheses, omitting measures replicating earlier research or validating the categorization task (Appendix~F).
+Reanalysing existing data \cite{dommelen_construing_2015}, we determined that $\sim$100 respondents per group would allow reasonably precise estimates of model parameters.\footnote{Models estimated posterior probabilities with precision $\textit{SD} < 0.5$ on the log odds scale.} We report descriptive statistics and interscale correlations in Appendix~B.
+
+\subsection{Participants}
+
+We recruited 351 students at Karnatak University (Dharwad, India).
+Of these, we excluded 49 participants who did not belong to any of four caste groups ($n = 20$), failed to indicate their caste group ($n = 7$), or reported Islam as their own or their family's religion ($n = 27$).\footnote{We excluded Muslim participants as this subsample was too small for meaningful analyses.} This left 302 participants who reported Hinduism ($n = 286$), Jainism ($n = 8$), or Christianity ($n = 8$) as their or their family's religion, and General Caste ($n = 99$), Other Backward Class (n = $127$), Scheduled Caste ($n = 54$), or Scheduled Tribe ($n = 22$) as their caste group.
+Table~\ref{tab:t1} summarizes participants by gender, age, nationality, religion, and caste.
+
+\begin{table}    
+\caption[Participants by gender, age, nationality, religion, and caste]{Participants by gender, age, nationality, religion, and caste.
+Categories in \textit{italics} were excluded from the final sample.
+N/A marks missing responses.}
+\centering
+\figureversion{lining, tabular}
+\small	
+\begin{tabular}{llrr} \addlinespace \toprule
+\multicolumn{2}{l}{Category} & $n$ & \% \\ \midrule \addlinespace 
+Gender      & Woman      & 215 & 61 \\
+            & Man & 121 & 34 \\
+            & Other & 0 & 0 \\
+            & N/A & 15 & 4 \\ \addlinespace \addlinespace
+Age         & 18--20 & 1 & 0 \\
+            & 21--23 & 254 & 72 \\
+            & 24--26 &  77 & 22 \\
+            & 27--29 &  10 &  3 \\
+            & 30--32 &   1 &  0 \\
+            & 33--35 &   0 &  0 \\
+            & 36 or older & 1 & 0 \\ 
+            & N/A & 7 & 2 \\ \addlinespace \addlinespace
+Nationality & Indian & 339 & 97 \\
+            & Other & 0 & 0 \\
+            & N/A & 12 & 3 \\ \addlinespace \addlinespace
+Religion    & Buddhism & 1 & 0 \\ 
+            & Christianity & 11 & 3 \\ 
+            & Hinduism & 297 & 85 \\ 
+            & \textit{Islam} & \textit{27} & \textit{8} \\ 
+            & Jainism & 8 & 2 \\ 
+            & Other & 2 & 1 \\ 
+            & N/A & 5 & 1 \\ \addlinespace \addlinespace
+Caste       & General Caste & 104 & 30 \\ 
+            & Other Backward Class & 143 & 41 \\ 
+            & Scheduled Caste & 54 & 15 \\ 
+            & Scheduled Tribe & 23 & 7 \\ 
+            & \textit{Other / Not applicable} & \textit{20} & \textit{6} \\ 
+            & \textit{N/A} & \textit{7} & \textit{2} \\ \addlinespace \midrule
+Total       &   & 351 & 100 \\ \bottomrule
+\end{tabular}
+\label{tab:t1}
+\end{table}
+
+\subsection{Procedure}
+
+Participants completed a triple crossed-categorization task, in which they viewed 24 identity cards.
+Each showed a fictitious person's name, age, religion, nationality, caste reservation, and a head-and-shoulders silhouette.
+Based on a pilot study, we manipulated the target's caste, religion, and nationality such that each target represented a person with whom participants shared none, one, two, or three group memberships (Figure~\ref{fig:f2}).
+We tested participants in classrooms of 24--71 students by presenting targets in a slide-based presentation and by handing each student a pen-and-paper questionnaire.
+Each slide contained a male and a female target with participants focusing on the target corresponding to their gender.
+Slides also contained a number identifying each target, and the response scale(s) corresponding to the question(s) participants answered at the time.
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-2}
+\caption{Examples of targets used in the triple crossed-categorization task.
+Based on ratings in a pilot study ($N = 26$), we selected the four most prototypical targets (out of fifty initial targets) for each of six plausible combinations of caste, religion, and nationality (for details, see Appendix~A).
+Each target showed a person's caste reservation (GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe), religion (Hindu, Muslim), and nationality (Indian, Nepali, Sri Lankan, Bangladeshi).
+Each target also showed the person's first and last name, age (21--26 years), and a silhouette corresponding to the person's gender (adapted from \protect\citeNP{ma_chicago_2015}).
+Each target's age and silhouette, as well as the order in which the targets were presented, varied across sessions.}
+\label{fig:f2}
+\end{figure}
+
+In each session, participants first familiarized themselves with each target (shown for 7 s in a randomized order) in an automated slideshow.
+Participants viewed targets (in the same order) for a second time, noting for each target whether they felt that this person was one of their own group (1 = ``us''), or not one of their own group (0 = ``not us'').
+Participants viewed targets for a third time, rating how comfortable or uncomfortable they would feel to share a room with this person (social distance; $1 = \textit{very uncomfortable}$, $7 = \textit{very comfortable}$), and how they felt toward this person (feeling thermometer; $0 = \textit{cold}$, $100 = \textit{warm}$).
+Participants then completed the measures described below.
+
+\subsection{Measures}
+
+We measured intergroup contact as: how often, from $1 = \textit{never}$ to $5 = \textit{very often}$, participants meet outgroup members in their everyday life (contact quantity), and how often, on average, they have positive/good contact and negative/bad contact with outgroup members \cite{barlow_contact_2012}.
+We preceded these items with examples of positive and negative contact experiences.
+We measured cross-group friendship with two items \cite{turner_reducing_2007}: ``How many close friends do you have who are [outgroup members]?'' ($1 = \textit{none}$, $5 = \textit{more than ten}$), and ``How often do you spend time with [outgroup] friends?'' ($1 = \textit{never}$ to $5 = \textit{very often}$; $.47\leq\textit{rs}\leq.58$).
+Participants reported contact with four groups: Dalits, people from other backward classes, people from general castes, and Muslims.
+
+We measured social dominance orientation as how much, between $1 = \textit{strongly oppose}$ and $7 = \textit{strongly favour}$, participants endorsed eight statements about social hierarchies \cite{ho_nature_2015}.
+Four items measured support for group-based dominance (SDO-Dominance), for example, ``some groups of people are simply inferior to other groups''.
+Four items measured opposition to egalitarian ideologies (SDO-Egalitarianism), for example, ``it is unjust to try to make groups equal''.\footnote{Replicating \citeauthor{ho_nature_2015}’s \citeyear{ho_nature_2015} findings, we found a four-factor model (with two method factors) to represent the data better than the one-factor ($\Delta\chi^2 = 155.14$, $p < .001$) or two-factor ($\Delta\chi^2 = 138.67$, $p < .001$) alternatives.
+Accounting for this structure, we used latent factor scores for SDO-Dominance and SDO-Egalitarianism in our analyses.}
+
+We measured realistic threat---from Muslims and Dalits---with three items per outgroup \cite{schmid_reducing_2014}, for example, ``the more power [Muslims/Dalits] gain in this country, the more difficult it is for [Hindus/people from my caste group]'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $\alpha_\textit{Muslims} = .71$, $\alpha_\textit{Dalits} = .79$).
+Two items measured symbolic threat, e.g., ``[Muslims/ Dalits] threaten [Hindus'/my caste group's] way of life'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $r_\textit{Muslims} = .44$, $r_\textit{Dalits} = .48$).
+
+We measured perceived (dis-)advantage as how easy or hard participants thought it was, on average, for people from various groups to succeed in India today ($1 = \textit{very hard}$, $7 = \textit{very easy}$).
+Participants rated seven groups: People from your own background, Scheduled Caste, Scheduled Tribe, Other Backward Class, General Caste, Hindus, and Muslims.
+
+Five items measured policy support.
+Participants read that ``currently, 22.5\% of seats in central-government funded universities are reserved for Scheduled Caste and Scheduled Tribe students'', and that ``an additional 27.5\% of seats in central-government funded universities are reserved for students from Other Backward Classes''.
+Participants indicated to what extent they opposed or supported reservation in higher education for students from each group ($1 = \textit{strongly oppose}$, $5 = \textit{strongly support}$), and whether they thought that reservation in higher education for students from that group should increase, decrease, or remain unchanged ($1 = \textit{decrease a lot}$, $5 = \textit{increase a lot}$; $r_\textit{SC/ST} = .67$, $r_\textit{OBC} = .67$).
+Participants then read that ``no seats in central-government funded universities are reserved for Muslim students nationally, though some states have introduced quotas for Muslim students''.
+Participants indicated to what extent they opposed or supported reservation for Muslim students.
+
+\section{Results}
+
+We used the following analysis strategy: First, we estimated group differences in whom participants categorized as ``us'' and ``not us''.
+Second, we examined to what extent intergroup contact and ideological orientations explained individual differences in participants' categorizations.
+Third, we tested whether participants' categorizations were associated with their attitudes and beliefs.
+
+\subsection{Group differences}
+
+We examined \emph{how likely} participants were to categorize \emph{which} target as ``us'' versus ``not us''---and how that probability varied as a function of the participants' and the targets' group memberships (\emph{group differences}) and of the participants' past experiences and ideological orientations (\emph{individual differences}).\footnote{Van Dommelen et al.
+\citeyear{dommelen_construing_2015} analysed \emph{which} and \emph{how many} targets participants included in their ingroup as distinct questions; in Appendix~C, we report analyses using their operationalization.}
+
+To answer these questions, we ran a series of multilevel logistic regression models with participants' target categorizations (1 = ``us'', 0 = ``not us'') as outcome variable.
+We estimated these models in RStan \cite{rstan_package} using Bayesian statistical methods.
+Bayesian inference involves choosing a likelihood function and prior distributions.
+The likelihood function links the observed data to one or more model parameters (e.g., regression coefficients) and states how likely the observed data are given different values of said model parameters.
+Prior distributions state how plausible different values of said model parameters are before considering the observed data.
+Our models derived the likelihood of the observed responses from a generalized linear model with a logit link function.
+Our models assigned weakly informative prior distributions to all model parameters \cite{gelman_prior_2017}.\footnote{Our models assigned the following priors: $\beta \sim \text{Student}(2.5, 0, 1)$ for fixed effects and $\sigma \sim \text{Half-Cauchy}(0, 1)$ for standard deviations of varying effects.}  Bayesian inference applies Bayes' theorem to update prior distributions in light of the observed data to produce posterior distributions.
+Other than $p$-values and confidence intervals, the resulting posterior distributions have a straight-forward interpretation as stating how plausible different values of the model parameters are given the observed data.\footnote{For a detailed introduction, consult \citeA{gelman_bayesian_2014}, \citeA{lambert_student_2018}, and	 \citeA{mcelreath_statistical_2016}.}
+
+To test our hypotheses, we compared a series of nested models.
+We used stratified 10-fold cross-validation to estimate how accurately each model predicts observations outside of the sample used to estimate said model \cite{vehtari_practical_2017}.
+We selected more complex over simpler models when the difference in predictive accuracy was at least twice its standard error.\footnote{Selecting models based on their out-of-sample predictive accuracy balances the risks of underfitting and overfitting \cite<see also>{yarkoni_choosing_2017}.
+Standard errors, in this case, come from treating the observed data as a sample from a population and, as such, have the same interpretation as standard errors in classical statistics \cite{vehtari_practical_2017}.} Model~0 estimated the probability of participants categorizing a target as ``us'' as a function of a fixed intercept and varying (random) intercepts for all participants.\footnote{Models used the used the non-centred parameterization to represent all varying effects \cite{betancourt_hamilton_2015}.} Model~1 estimated this probability as varying across participants and target categories.
+Models~2 and 3 estimated, respectively, how SC/ST participants' categorizations of Indian targets differed from GM and OBC participants' and how OBC participants' categorizations differed from GM participants'.
+Models~1 and 2, but not Model~3, made more accurate predictions than less complex models (Table~\ref{tab:t2}).
+This suggests that the targets' group memberships shaped participants' categorizations, and that GM and OBC participants' categorizations resembled each other but differed from SC/ST participants'.
+Below, we report and compare the estimated probabilities of ``us'' categorizations for different combinations of targets' and participants' group memberships.
+We report uncertainty intervals spanning the 97\% most plausible estimates \cite{coda_package}.
+
+\begin{table}
+\caption{
+Comparison of models estimating the probability of participants categorizing targets as ``us'' versus ``not us''.
+$\textit{ELPD}$ is the expected log predictive density, with higher numbers indicating that a model is expected to make more accurate out-of-sample predictions \protect\cite{vehtari_practical_2017}.
+$\Delta\textit{ELPD}$ is the difference in $\textit{ELPD}$ between the current and previous model, with positive values indicating that the current model is expected to make more accurate out-of-sample predictions.
+We selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.%$w$ are stacking weights based on the models' expected log predictive densities \protect\cite{yao_using_2018}.
+}
+\centering
+\figureversion{lining, tabular}
+\small
+\begin{tabularx}{\linewidth}{r@{~}rXrrrrr} \toprule
+\# &  & Description & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
+0 &      & Intercept (Participant) & -4703.5 & 23.7 &     - &    - &    - \\ 
+1 & vs 0 & Intercept (Category)    & -3853.5 & 41.6 & 850.1 & 37.4 & 22.7 \\
+2 & vs 1 & Group differences (SC/ST)       & -3791.3 & 42.0 &  62.1 & 11.1 &  5.6 \\
+3 & vs 2 & Group differences (OBC)         & -3792.1 & 42.2 &  -0.8 &  3.6 & -0.2 \\ \midrule
+4 & vs 2 & Intergroup contact (4) & -3743.4 & 42.8 &  47.9 &  8.8 &  5.4 \\
+5 & vs 4 & Intergroup contact (2) & -3736.7 & 42.6 &   6.7 &  1.8 &  3.8 \\
+6 & vs 5 & Intergroup contact (2) & -3747.8 & 42.7 & -11.1 &  3.2 & -3.5 \\
+7 & vs 2 & Social dominance orientation & -3791.0 & 42.1 &   0.4 &  3.3 &  0.1 \\
+\bottomrule
+\end{tabularx}
+\label{tab:t2}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-3}
+\caption{
+Estimated probability of participants categorizing a target as ``us'' versus ``not us'' by targets' nationality, religion, and caste (vertical), and participants' caste membership (horizontal).
+Dots (•) indicate the most plausible \emph{estimate} for a given target's probability of being included in participants' ingroup (in Model~2, Table~\ref{tab:t2}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most plausible estimates of that probability.
+Pluses (+) indicate the \emph{observed} proportion of participants who included a given target in their ingroup.
+Comparing predicted and observed proportion shows that the model represents the data reasonably well.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f3}
+\end{figure}
+
+Figure~\ref{fig:f3} shows the estimated probabilities of General Merit (GM), Other Backward Class (OBC), and Scheduled Caste/Scheduled Tribe (SC/ST) participants categorizing a target as ``us''.
+Participants tended to exclude foreigners from their subjective ingroup, though about half of the responses indicated more inclusive identities.
+Few participants considered Bangladeshi Muslims part of their ingroup, \pest{M2}{.17}{.14}{.21}, though roughly half of the participants included Sri Lankan and Nepali Hindus in their ingroup, \pest{M2}{.46}{.41}{.52}.
+Participants were thus more likely to include foreign targets when they were Hindu, \pdif{M2}{.29}{.25}{.34}.
+Still, GM/OBC and SC/ST participants were, respectively, $1.95$, $[1.73, 2.18]$ and $1.90$, $[1.71, 2.14]$ times more likely to categorize Indian, Hindu targets as ``us'' compared to foreign, Hindu targets.
+
+As expected, participants' caste membership shaped how they categorized Indians of different castes and religions.
+Most GM and OBC participants included Hindu, GM and Hindu, OBC targets in their ingroup, \pest{M2}{.94}{.92}{.96} and \pest{M2}{.93}{.91}{.95}.
+Fewer GM and OBC participants categorized Hindu, SC/ST targets as ``us'', \pest{M2}{.84}{.80}{.87}.
+They were least likely to categorize Muslim, OBC targets as ``us'', \pest{M2}{.75}{.70}{.80}.
+As such, participants from advantaged (GM) and intermediate (OBC) caste backgrounds tended to exclude targets from disadvantaged caste groups (SC/ST) and ethnoreligious minorities (Muslims).
+SC/ST participants' responses differed from GM and OBC participants'.
+Almost all SC/ST participants included Hindu, SC/ST targets in their ingroup, \pest{M2}{.97}{.95}{.99}.
+Fewer SC/ST participants included Hindu, GM and Hindu, OBC targets in their ingroup, \pest{M2}{.88}{.83}{.92} and \pest{M2}{.80}{.73}{.86}, respectively.
+SC/ST participants were even less likely than others to include Muslim, OBC targets as ``us'', \pest{M2}{.47}{.38}{.57}.
+Overall, these findings showed that participants from advantaged backgrounds tended to exclude targets from disadvantaged backgrounds (and vice versa), while all participants tended to exclude targets from the Muslim minority.
+
+\subsection{Individual differences}
+
+Group memberships shaped whom participants considered ``us'' and ``not us'', though none of these associations were without exception.
+We examined to what extent individual differences in past experiences and ideological orientations explain why some participants excluded targets from caste and religious outgroups---and why others did not.
+
+Models~4 to 6 tested whether intergroup contact was associated with how participants categorized Indian targets of caste or religious outgroups.
+Model~4 extended Model~2 by including contact quantity, positive contact, negative contact, and outgroup friendship as predictors of participants’ categorizations.
+Model~4 made more accurate predictions than Model~2.
+Negative contact ($e^\beta = 0.81$, $[0.72, 0.90]$) and outgroup friendship ($e^\beta = 1.50$, $[1.28, 1.72]$) were associated with participants' categorizations, but neither positive contact ($e^\beta = 1.01$, $[0.87, 1.16]$) nor contact quantity ($e^\beta = 0.99$, $[0.86, 1.15]$) were.\footnote{An odds ratio of $e^\beta = 1$ means that a predictor does not affect the odds of the relevant outcome; odds ratios of $e^\beta > 1$ and $e^\beta < 1$ mean, respectively, that a predictor makes the relevant outcome more and less likely.} Model~5 included only negative contact and outgroup friendship, and made more accurate predictions than Model~4.
+Model~6 estimated the relationships between contact and categorizations as varying across the four combinations of target caste and religion.
+Model~6 made less accurate predictions than Model~5.
+This shows that outgroup friendship and negative contact---but not contact quantity and positive contact---were associated with whom participants considered ``us'' and ``not us''.
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-4}
+\caption{Estimated probability of participants categorizing a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship with the relevant groups (in Model~5, Table~\ref{tab:t2}).
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.}
+\label{fig:f4}
+\end{figure}
+
+Figure~\ref{fig:f4} shows the estimated probabilities of participants categorizing targets as ``us'' as a function of their contact experiences.
+Across targets and participants, the odds of categorizing an outgroup target as ``us'' were $e^\beta = 1.50$, $[1.32, 1.69]$ times higher for each additional standard deviation of outgroup friendship.
+These odds were $e^\beta = 0.81$, $[0.72, 0.90]$ times lower for each standard deviation of negative contact.
+This means, for example, that GM/OBC participants who reported ``never'' having any negative contact with Muslims were more likely to categorize Indian Muslims as ``us'' than participants who reported ``sometimes'' having negative contact, \pdif{M5}{.05}{.09}{.03}.
+GM/OBC participants who reported no friendships with Muslims were a lot less likely to include Indian Muslims in their ingroup than participants who had 2--5 Muslim friends with whom they ``sometimes'' spent time, \pdif{M5}{.18}{.12}{.24}.
+Contact experiences were thus associated with whom participants categorized as ``us'' and ``not us''.
+
+Model~7 tested whether social dominance orientation was associated with participants’ categorizations of targets from lower-status outgroups.
+Model~7 found little evidence for associations between participants’ categorizations and their SDO-Dominance scores ($e^\beta = 0.87$, $[0.69, 1.06]$) or SDO-Egalitarianism scores ($e^\beta = 0.98$, $[0.78, 1.21]$).
+Together, these findings show that group and individual differences explained whom participants included in their ingroup.
+As expected, past experiences with outgroup members explained why some participants included targets of (objective) caste or religions outgroups in their (subjective) ingroup, when others did not.
+In contrast, ideological orientations did not motivate participants to exclude lower-status groups.
+
+\subsection{Consequences}
+
+After examining potential antecedents, we turned to potential consequences of more inclusive social identities.
+We analysed how participants' categorizations related to their feeling thermometer and social distance ratings for each target in the categorization task---as well as to their responses to the intergroup threat, perceived (dis-)advantage, and policy support measures.
+
+\subsubsection{Intergroup attitudes}
+
+To answer these questions, we first ran a series of multilevel multivariate regression models with participants' target-wise social distance and feeling thermometer ratings as outcome variables (Table~\ref{tab:t3}).\footnote{Linear regression models assigned weakly informative prior distributions: $\beta \sim \text{Normal}(0, 1)$ for fixed effects and $\sigma \sim \text{Half-Cauchy}(0, 1)$ for standard deviations of varying effects.} Models~0 to 3 estimated ratings (on either outcome) as varying between participants but fixed across targets (M0), as varying across participants and target categories (M1), and tested whether SC/ST participants' responses differed from GM and OBC participants' (M2), and whether OBC participants' responses differed from GM participants' (M3).
+Models~1 to 3 improved upon the predictions of simpler models, showing that participants' ratings depended on targets' and participants' group memberships.
+
+\begin{table}
+\caption{Comparison of models estimating participants' social distance (SD) and feeling thermometer (FT) ratings for each target as a function of group differences and target categorizations.
+As in Table~\ref{tab:t2}, we selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.
+$R^2$ is a Bayesian analogue to $R^2$ in maximum likelihood estimation \protect\fullcite{gelman_rsquared_2017}.}
+\centering
+\figureversion{lining, tabular}
+\small	
+\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrrr} \toprule
+\# &  & Description & $R^2_\text{SD}$ & $R^2_\text{FT}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule 
+0 &      & Participant & .23 & .26 & -16964 & 71.0 & - & - & - \\
+1 & vs 0 & Category & .38 & .42 & -16338 & 79.6 & 626.8 & 40.2 & 15.6 \\
+2 & vs 1 & SC/ST    & .38 & .43 & -16317 & 79.6 &  20.1 &  9.8 &  2.1 \\
+3 & vs 2 & OBC      & .39 & .43 & -16293 & 80.5 &  24.2 &  9.7 &  2.5 \\ \midrule
+4 & vs 3 & Categorization    & .42 & .47 & -16028 & 83.5 & 264.8 & 24.5 & 10.8 \\
+5 & vs 4 & \ldots~(Category) & .42 & .47 & -16007 & 83.6 &  21.1 &  8.7 &  2.4 \\
+6 & vs 5 & \ldots~(Ingroup)  & .42 & .47 & -16025 & 84.3 & -17.4 &  5.9 & -3.0 \\
+\bottomrule    
+\end{tabularx}
+\label{tab:t3}
+\end{table}
+
+Models~4 to 6 tested whether participants who categorized a target as ``us'' rated that target more favourably than participants who categorized the same target as ``not us''.
+Models estimated this difference as constant across targets and participants (M4), as varying across target categories (M5), and tested whether this difference depended on participants' caste memberships (M6).
+Models 4 and 5, but not Model 6, made better predictions than less complex models, showing that how favourably participants felt toward a target depended on whether they had categorized that target as ``us'' or ``not us'', and that the size of this difference depended on the targets'---but not the participants'---group memberships.
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-5}
+\caption{
+Posterior probabilities of social distance ratings as a function of target categorizations (in Model~5, Table~\ref{tab:t3}).
+Points are the estimated mean ratings for targets categorized as ``us''; triangles are the estimated mean ratings for targets categorized as ``not us''.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f5}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-6}
+\caption{
+Posterior probabilities of feeling thermometer ratings as a function of target categorizations (in Model~5, Table~\ref{tab:t3}).
+Points are the estimated mean ratings for targets categorized as ``us''; triangles are the estimated mean ratings for targets categorized as ``not us''.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f6}
+\end{figure}
+
+Figures~\ref{fig:f5} and \ref{fig:f6} show, respectively, the estimated social distance and feeling thermometer ratings as a function of target categorizations and participants' caste memberships.
+For all categories, participants felt more comfortable sharing a room with targets that they categorized as ``us'' than with targets they categorized as ``not us''.
+This difference was smallest for Indian, Hindu, GM targets ($\beta = 0.55$, $[0.19, 0.90]$; $\text{Cohen's}~d = 0.24$, $[0.08, 0.39]$) and greatest for foreign, Muslim targets ($\beta = 1.46$, $[1.21, 1.70]$; $\text{Cohen's}~d = 0.63$, $[0.52, 0.73]$).
+We found a similar pattern for feeling thermometer ratings.
+The difference was smallest for Indian, Hindu, OBC targets ($\beta = 6.5$, $[2.1, 11.0]$, $\text{Cohen's}~d = 0.20$, $[0.06, 0.33]$) and greatest for foreign, Hindu targets ($\beta = 21.8$, $[18.6, 25.0]$, $\text{Cohen's}~d = 0.66$, $[0.56, 0.76]$).
+Feeling thermometer and social distance ratings were highly correlated ($r = .58$, $[.56, .60]$).
+Categorizing a target as ``us'' was thus associated with more warmth and less social distance toward that target.
+
+\subsubsection{Intergroup threat}
+
+Next, we tested whether participants' perceptions of realistic and symbolic threat depended on how inclusive their identity construals were.
+Results from a series of multilevel models showed that participants reported more realistic ($M = 3.62$, $[3.49, 3.75]$) than symbolic ($M = 3.21$, $[3.09, 3.33]$) threat from (same-religion) Dalits, but more symbolic ($M = 3.47$, $[3.34, 3.61]$) than realistic ($M = 3.23$, $[3.06, 3.38]$) threat from (different-religion) Muslims.
+Contrary to predictions, we did not find that participants felt less threatened by Muslims and Dalits if they categorized more targets from these outgroups as ``us'' (for details, see Appendix~D).
+
+\subsubsection{Support for social change}
+
+We investigated how participants' caste memberships shaped their perceptions of (dis-)advantages and their support for reservations.
+To that end, we first estimated two multivariate regression models with participants' responses to six perceived (dis-)advantage and three policy support measures as outcome variables.
+Model~0 estimated distinct means for each outcome, but did not consider participants' group memberships.
+Model~1 estimated distinct means across participants' ingroups.
+Model~1 made better out-of-sample predictions than Model~0, $\Delta\textit{ELPD} = 94.7$, $\textit{SE} = 14.1$, $\frac{\Delta\textit{ELPD}}{\textit{SE}} = 6.7$.
+This shows that participants' caste memberships shaped their perceived (dis )advantage and policy support ratings.
+Figures~\ref{fig:f7} and \ref{fig:f8} show the estimated group differences for the respective outcomes.
+Contradicting prevailing social inequalities, GM and OBC participants rated their own groups' lives as substantially harder than SC/ST members' lives.
+Policy support, in turn, strongly aligned with participants' caste interests.
+SC/ST participants supported reservations for both SC/ST and OBC students, while OBC participants only supported reservations for their own group.
+GM participants, for the most part, opposed reservation policies.
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-7}
+\caption{
+Posterior probabilities of perceived (dis-)advantage ratings for different target groups (right) by participants' caste ingroup (left).
+Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f7}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/figure-8}
+\caption{
+Posterior probabilities of policy support ratings for different target groups (right) by participants' caste ingroup (left).
+Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
+}
+\label{fig:f8}
+\end{figure}
+
+We then examined to what extent more inclusive identities and contact experiences accounted for individual differences in perceived (dis-)advantage and policy support ratings.
+To that end, we estimated a series of multilevel models with participants' responses to either the perceived (dis-)advantage or the policy support measure as outcome variable.
+Contrary to predictions, we did not find more inclusive identities to be associated with either perceived (dis-)advantage or policy support.
+Contrary to past research \cite{dixon_beyond_2012}, intergroup contact was similarly unrelated to these outcomes (for details, see Appendix~E).
+
+Overall, we thus found that when participants included a person in their ingroup, they had, on average, more favourable attitudes to and desired less social distance from that person.
+Participants' categorizations, however, were unrelated to perceptions of intergroup threat and relative (dis-)advantage, and to support for and opposition to affirmative action.
+
+\subsection{Discussion}
+
+This research examined how people construct their social identities from multiple cross-cutting categories, and how more inclusive identities relate to intergroup contact, outgroup attitudes, and support for social change.
+As hypothesized, we found that cross-group friendship was associated with more inclusive identities which, in turn, were associated with more favourable outgroup attitudes.
+Negative contact was associated with less inclusive identities.
+Contrary to past research, neither intergroup contact nor more inclusive identities were associated with perceived (dis-)advantages or support for affirmative action.
+Below, we discuss implications, strengths, and limitations of the present research.
+
+Our research has implications for understanding intergroup relations in unequal societies.
+Among advantaged groups, our research documented patterns of inclusion and exclusion that map onto persistent social divides.
+Participants from dominant caste groups tended to exclude subordinate caste groups from the common ingroup; participants from the dominant Hindu religion tended to exclude Indian Muslims.
+Among disadvantaged groups, we found more complex patterns of inclusion and exclusion.
+Participants from intermediate caste groups (OBC, Other Backward Classes) faced the choice of aligning themselves with dominant caste groups (GM, General Merit), or forming a coalition with subordinate caste groups (SC/ST, Scheduled Caste/Scheduled Tribe).
+OBC participants tended to include dominant GM targets and exclude subordinate SC/ST targets, thus choosing derogation over coalition \cite{craig_coalition_2012}.
+Similarly, SC/ST participants rejected a solidarity-based social identity that includes Indian Muslims.\footnote{We did not have a sufficient number of Indian Muslim participants to examine social identification in this disadvantaged religious minority group.}
+
+Our findings suggest that cross-group friendship can help to overcome these divisions by fostering social identities that include Indians of all castes and religions.
+As more inclusive identities were related to less social distance and more warmth toward caste and religious minorities, our research suggests that positive contact could help reduce interpersonal discrimination and violence against these groups.
+In line with recent research \cite<for example,>{hayward_toward_2017}, we found that negative contact could exacerbate social divisions by fostering less inclusive identities.
+More broadly, our research speaks to how contact reduces prejudice \cite{pettigrew_how_2008}.
+Our findings support arguments \cite{gaertner_reducing_2000, pettigrew_intergroup_1998} that contact can reduce prejudice, in part, by changing how we understand our social identities.
+
+Our research also examined support for social change.
+Contrary to past research, neither positive nor negative contact \cite{hayward_how_2018, reimer_intergroup_2017} were associated with support for social change---or perceptions of relative advantage and disadvantage---in advantaged \cite{dixon_intergroup_2007} and disadvantaged \cite{dixon_beyond_2012} groups.
+Similarly, more inclusive identities were not associated with opposition to affirmative action among the disadvantaged \cite{dovidio_darker_2012}.
+Features of the participants' situation might explain this discrepancy.
+As university students, participants have personally experienced the impact of reservation policies.
+For SC/ST and OBC students, reservation policies facilitated admission to state-funded universities.
+This experience might explain why these students strongly support reservation (at least for their own group).
+For GM students, reservation policies thwarted admission to state-funded universities.
+This experience might explain why, in contrast to societal realities, GM students saw themselves at a disadvantage relative to other caste groups \cite<see>{norton_whites_2011}.
+
+Our findings show that the triple crossed-categorization task \cite{dommelen_construing_2015} is an intuitive and informative method for studying social identification across multiple categories.
+We adapted the task to answer new questions about social identification.
+First, we recruited respondents from multiple groups, allowing us to study both individual and group differences \cite<see also>{brankovic_social_2015}.
+Second, we estimated responses as varying across targets and participants using multilevel models.
+This allowed more fine-grained analyses than the quantitative and qualitative summaries provided by van Dommelen and colleagues, and may explain why we found more consistent effects of intergroup contact than they did.
+Together, these changes open the triple crossed-categorization task to a broader range of research questions.
+
+Our research also improves upon other approaches to studying identification across multiple social categories.
+For example, we could have tested our hypotheses by examining whether intergroup contact leads participants to identify with a more inclusive common ingroup (Indian) instead of their less inclusive subordinate ingroups (Hindu, Muslim).
+A problem with this approach is that a superordinate ingroup is more inclusive in principle, but might not be so in practice.
+People tend to perceive the common ingroup as more similar to their own narrow ingroup than to other outgroups \cite{wenzel_ingroup_2003}, thus excluding outgroup members from the common ingroup.
+We chose instead to let participants decide where to draw the line between ingroup (``us'') and outgroup (``not us'') and to thus determine the content of their subjective ingroup.
+Another strength of our research is that we studied intergroup relations in a context underrepresented in psychological research.
+Our research is one of few studies examining the effects of intergroup contact on Hindu--Muslim relations in South Asia \cite<for other examples, see>{islam_dimensions_1993, tausch_relationships_2009} and is, to our knowledge, the first study examining the effects of intergroup contact on caste relations.
+
+Despite these strengths, our research is qualified by some methodological limitations.
+First, we presented all participants with the same combination of target groups.
+This design cannot determine whether the observed construals generalize beyond the specific combination of stimuli used.
+Relatedly, we did not control for factors that correlate with the categories under study, but were not made explicit.
+Class, rather than caste, could explain why some participants excluded targets from disadvantaged outgroups.
+Second, we measured categorization and attitudes for the same targets.
+This design cannot rule out that these variables measure the same construct, rather than represent a genuine association across constructs.
+One reason to think so is that intergroup threat, a more distal measure, did not correlate with participants' categorizations.\footnote{An explanation for this finding might be that threat perceptions stem from economic anxieties (e.g., fearing affirmative action as a threat to one's career) and ideological beliefs (e.g., Hindutva), rather than identity processes.} Third, we did not manipulate intergroup contact.
+This design cannot rule out confounding explanations of the observed relationship between contact and identification.
+Experimental studies tend to manipulate short-term `intergroup interactions' rather than long-term `intergroup contact' (\citeNP{macinnis_how_2015}; for rare exceptions, see \citeNP{laar_effect_2005} and \citeNP{shook_interracial_2008}).
+Our findings suggest, however, that cross-group friendship, not superficial interaction, is required for people to change their social identities.
+Future research should address these limitations by varying target categories across participants, by including more target categories, by assessing intergroup bias with proximal and distal measures, and by testing the hypothesized relationships over time.
+
+To conclude, in a unique study of caste, religion, and nationality in South India, we found correlational evidence that intergroup contact can change not only how we see others, but also how we see ourselves---that is, that intergroup contact can foster more inclusive social identities and thus improve intergroup relations in unequal societies.
+Fostering more inclusive identities, however, does not seem to overcome entrenched opposition to (or undermine support for) affirmative action.
+
 \nolinenumbers
-
 \bibliographystyle{apacite}

### 2019-07-30 read_data.R

@@ -1,0 +1,26 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+  
+  #########################################################################
+  # d1 contains participants' responses from the first part of the study  #
+  # (i.e. the triple crossed-categorization task); d2 contains responses  #
+  # from the second part of the study (i.e. the questionnaire). For item  #
+  # wordings, see materials/materials.pdf.                                #
+  #########################################################################
+
+# Load packages -----------------------------------------------------------
+  library(tidyverse)
+
+
+# Import data -------------------------------------------------------------
+  d1 <- read_rds("data/d1.rds")
+  d2 <- read_rds("data/d2.rds")
+
+
+# Analyze -----------------------------------------------------------------
+
+  #########################################################################
+  # Start your own analyses here.                                         #
+  #########################################################################
+  

### 2019-11-06 manuscript/manuscript.tex
revision

@@
 \title{Intergroup contact fosters\\more inclusive social identities}
-\date{July 30, 2019}
+\date{November 6, 2019}
 
@@
 Participants tended to exclude caste and religious minorities, replicating persistent social divides.
-Bridging these divides, cross-group friendship was associated with more inclusive identities which, in turn, were associated with more favourable outgroup attitudes.
-Negative contact was associated with less inclusive identities, showing that past experiences shaped whom participants considered ``us'' or ``not us''.
-Contact and identity processes were unrelated to support for affirmative action in advantaged and disadvantaged caste groups.\\[1ex]
-\noindent \textbf{Keywords:} intergroup contact, social identity, multiple categorization, intergroup relations, affirmative action \\[1ex]
+Bridging these divides, cross-group friendship was associated with more inclusive identities which, in turn, were associated with more positive relations between an advantaged, an intermediate, and a disadvantaged caste group.
+Negative contact was associated with less inclusive identities.
+Contact and identity processes, however, did not affect entrenched opposition to (or undermine support for) affirmative action in advantaged and disadvantaged groups.\\[1ex]
+\noindent \textbf{Keywords:} intergroup contact, social identity, multiple categorization, intergroup relations, interminority relations, perceived discrimination, affirmative action \\[1ex]
 \end{abstract}
@@
 Our research examines how intergroup contact, by fostering more inclusive social identities, affects support for affirmative action policies, as well as perceptions of relative advantage and disadvantage, in advantaged and disadvantaged groups.
+
+Most research on intergroup relations examines relations between an advantaged majority-group and a disadvantaged minority-group.
+Most social contexts, however, feature various groups facing various disadvantages.
+\citeA{craig_coalition_2012} argued that racial minorities may respond to the disadvantages they face by  derogating other racial minorities or by forming a coalition with them.
+The researchers showed that perceiving discrimination can, as far as it fosters a shared ingroup identity with other disadvantaged groups, improve interminority relations.
+\citeA{vollhardt_inclusive_2016} observed that South Indians from disadvantaged caste and religious groups were more likely to express support for another disadvantaged group when they recognized similarities between their own and other groups' experiences of discrimination.
+\citeA{dixon_contact_2017} found that Indian Muslims who reported having more contact with other disadvantaged groups were also more likely to recognize shared grievances and to express support for collective action benefiting all disadvantaged groups.
+Our research adds to this literature by examining intergroup relations between two disadvantaged groups, one of which occupies an intermediate position in the social hierarchy.
+We examine whether, by fostering shared ingroup identities, contact between disadvantaged groups can foster more positive intergroup relations, shared perceptions of relative disadvantage, and mutual support for affirmative action.
 
@@
 
-In each session, participants first familiarized themselves with each target (shown for 7 s in a randomized order) in an automated slideshow.
+In each session, participants first familiarized themselves with each target (shown for 7 s in a randomized order) in an automated slide show.
 Participants viewed targets (in the same order) for a second time, noting for each target whether they felt that this person was one of their own group (1 = ``us''), or not one of their own group (0 = ``not us'').
@@
 
+We report two reliability indices for our measures, the Spearman-Brown statistic ($\rho$) for two-item measures \cite{eisinga_reliability_2013} and McDonald's omega ($\omega$) for multi-item measures \cite{dunn_alpha_2014}.
+
 We measured intergroup contact as: how often, from $1 = \textit{never}$ to $5 = \textit{very often}$, participants meet outgroup members in their everyday life (contact quantity), and how often, on average, they have positive/good contact and negative/bad contact with outgroup members \cite{barlow_contact_2012}.
 We preceded these items with examples of positive and negative contact experiences.
-We measured cross-group friendship with two items \cite{turner_reducing_2007}: ``How many close friends do you have who are [outgroup members]?'' ($1 = \textit{none}$, $5 = \textit{more than ten}$), and ``How often do you spend time with [outgroup] friends?'' ($1 = \textit{never}$ to $5 = \textit{very often}$; $.47\leq\textit{rs}\leq.58$).
+We measured cross-group friendship with two items \cite{turner_reducing_2007}: ``How many close friends do you have who are [outgroup members]?'' ($1 = \textit{none}$, $5 = \textit{more than ten}$), and ``How often do you spend time with [outgroup] friends?'' ($1 = \textit{never}$ to $5 = \textit{very often}$; $.65 < \rho < .71$).
 Participants reported contact with four groups: Dalits, people from other backward classes, people from general castes, and Muslims.
@@
 
-We measured realistic threat---from Muslims and Dalits---with three items per outgroup \cite{schmid_reducing_2014}, for example, ``the more power [Muslims/Dalits] gain in this country, the more difficult it is for [Hindus/people from my caste group]'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $\alpha_\textit{Muslims} = .71$, $\alpha_\textit{Dalits} = .79$).
-Two items measured symbolic threat, e.g., ``[Muslims/ Dalits] threaten [Hindus'/my caste group's] way of life'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $r_\textit{Muslims} = .44$, $r_\textit{Dalits} = .48$).
+We measured realistic threat---from Muslims and Dalits---with three items per outgroup \cite{schmid_reducing_2014}, for example, ``the more power [Muslims/Dalits] gain in this country, the more difficult it is for [Hindus/people from my caste group]'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $\omega_\textit{Muslims} = .71$, $\omega_\textit{Dalits} = .79$).
+Two items measured symbolic threat, e.g., ``[Muslims/ Dalits] threaten [Hindus'/my caste group's] way of life'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $\rho_\textit{Muslims} = .61$, $\rho_\textit{Dalits} = .65$).
 
@@
 Participants read that ``currently, 22.5\% of seats in central-government funded universities are reserved for Scheduled Caste and Scheduled Tribe students'', and that ``an additional 27.5\% of seats in central-government funded universities are reserved for students from Other Backward Classes''.
-Participants indicated to what extent they opposed or supported reservation in higher education for students from each group ($1 = \textit{strongly oppose}$, $5 = \textit{strongly support}$), and whether they thought that reservation in higher education for students from that group should increase, decrease, or remain unchanged ($1 = \textit{decrease a lot}$, $5 = \textit{increase a lot}$; $r_\textit{SC/ST} = .67$, $r_\textit{OBC} = .67$).
+Participants indicated to what extent they opposed or supported reservation in higher education for students from each group ($1 = \textit{strongly oppose}$, $5 = \textit{strongly support}$), and whether they thought that reservation in higher education for students from that group should increase, decrease, or remain unchanged ($1 = \textit{decrease a lot}$, $5 = \textit{increase a lot}$; $\rho_\textit{SC/ST} = .80$, $\rho_\textit{OBC} = .80$).
 Participants then read that ``no seats in central-government funded universities are reserved for Muslim students nationally, though some states have introduced quotas for Muslim students''.
@@
 Our models derived the likelihood of the observed responses from a generalized linear model with a logit link function.
-Our models assigned weakly informative prior distributions to all model parameters \cite{gelman_prior_2017}.\footnote{Our models assigned the following priors: $\beta \sim \text{Student}(2.5, 0, 1)$ for fixed effects and $\sigma \sim \text{Half-Cauchy}(0, 1)$ for standard deviations of varying effects.}  Bayesian inference applies Bayes' theorem to update prior distributions in light of the observed data to produce posterior distributions.
+Our models assigned conservative, weakly informative prior distributions to all model parameters \cite{gelman_prior_2017}.\footnote{Our models assigned the following priors: $\beta \sim \text{Student}(2.5, 0, 1)$ for fixed effects and $\sigma \sim \text{Half-Cauchy}(0, 1)$ for standard deviations of varying effects.}  Bayesian inference applies Bayes' theorem to update prior distributions in light of the observed data to produce posterior distributions.
 Other than $p$-values and confidence intervals, the resulting posterior distributions have a straight-forward interpretation as stating how plausible different values of the model parameters are given the observed data.\footnote{For a detailed introduction, consult \citeA{gelman_bayesian_2014}, \citeA{lambert_student_2018}, and	 \citeA{mcelreath_statistical_2016}.}
-
-To test our hypotheses, we compared a series of nested models.
-We used stratified 10-fold cross-validation to estimate how accurately each model predicts observations outside of the sample used to estimate said model \cite{vehtari_practical_2017}.
-We selected more complex over simpler models when the difference in predictive accuracy was at least twice its standard error.\footnote{Selecting models based on their out-of-sample predictive accuracy balances the risks of underfitting and overfitting \cite<see also>{yarkoni_choosing_2017}.
-Standard errors, in this case, come from treating the observed data as a sample from a population and, as such, have the same interpretation as standard errors in classical statistics \cite{vehtari_practical_2017}.} Model~0 estimated the probability of participants categorizing a target as ``us'' as a function of a fixed intercept and varying (random) intercepts for all participants.\footnote{Models used the used the non-centred parameterization to represent all varying effects \cite{betancourt_hamilton_2015}.} Model~1 estimated this probability as varying across participants and target categories.
-Models~2 and 3 estimated, respectively, how SC/ST participants' categorizations of Indian targets differed from GM and OBC participants' and how OBC participants' categorizations differed from GM participants'.
-Models~1 and 2, but not Model~3, made more accurate predictions than less complex models (Table~\ref{tab:t2}).
-This suggests that the targets' group memberships shaped participants' categorizations, and that GM and OBC participants' categorizations resembled each other but differed from SC/ST participants'.
-Below, we report and compare the estimated probabilities of ``us'' categorizations for different combinations of targets' and participants' group memberships.
-We report uncertainty intervals spanning the 97\% most plausible estimates \cite{coda_package}.
 
@@
 6 & vs 5 & Intergroup contact (2) & -3747.8 & 42.7 & -11.1 &  3.2 & -3.5 \\
-7 & vs 2 & Social dominance orientation & -3791.0 & 42.1 &   0.4 &  3.3 &  0.1 \\
+7 & vs 2 & SDO-D \& SDO-E & -3791.0 & 42.1 &   0.4 &  3.3 &  0.1 \\
 \bottomrule
@@
 \end{figure}
+
+To test our hypotheses, we compared a series of nested models.
+We used stratified 10-fold cross-validation to estimate how accurately each model predicts observations outside of the sample used to estimate said model \cite{vehtari_practical_2017}.
+We selected more complex over simpler models when the difference in predictive accuracy was at least twice its standard error.\footnote{Selecting models based on their out-of-sample predictive accuracy balances the risks of underfitting and overfitting \cite<see also>{yarkoni_choosing_2017}.
+Standard errors, in this case, come from treating the observed data as a sample from a population and, as such, have the same interpretation as standard errors in classical statistics \cite{vehtari_practical_2017}.} Model~0 estimated the probability of participants categorizing a target as ``us'' as a function of a fixed intercept and varying (random) intercepts for all participants.\footnote{Models used the used the non-centred parameterization to represent all varying effects \cite{betancourt_hamilton_2015}.} Model~1 estimated this probability as varying across participants and target categories.
+Models~2 and 3 estimated, respectively, how SC/ST participants' categorizations of Indian targets differed from GM and OBC participants' and how OBC participants' categorizations differed from GM participants'.
+Models~1 and 2, but not Model~3, made more accurate predictions than less complex models (Table~\ref{tab:t2}).
+This suggests that the targets' group memberships shaped participants' categorizations, and that GM and OBC participants' categorizations resembled each other but differed from SC/ST participants'.
+Below, we report and compare the estimated probabilities of ``us'' categorizations for different combinations of targets' and participants' group memberships.
+We report uncertainty intervals spanning the 97\% most plausible estimates \cite{coda_package}.
 
@@
 
-\begin{figure}
+\begin{figure}[t!]
 \centering
@@
 
-After examining potential antecedents, we turned to potential consequences of more inclusive social identities.
-We analysed how participants' categorizations related to their feeling thermometer and social distance ratings for each target in the categorization task---as well as to their responses to the intergroup threat, perceived (dis-)advantage, and policy support measures.
-
-\subsubsection{Intergroup attitudes}
-
-To answer these questions, we first ran a series of multilevel multivariate regression models with participants' target-wise social distance and feeling thermometer ratings as outcome variables (Table~\ref{tab:t3}).\footnote{Linear regression models assigned weakly informative prior distributions: $\beta \sim \text{Normal}(0, 1)$ for fixed effects and $\sigma \sim \text{Half-Cauchy}(0, 1)$ for standard deviations of varying effects.} Models~0 to 3 estimated ratings (on either outcome) as varying between participants but fixed across targets (M0), as varying across participants and target categories (M1), and tested whether SC/ST participants' responses differed from GM and OBC participants' (M2), and whether OBC participants' responses differed from GM participants' (M3).
-Models~1 to 3 improved upon the predictions of simpler models, showing that participants' ratings depended on targets' and participants' group memberships.
-
-\begin{table}
+\begin{table}[t!]
 \caption{Comparison of models estimating participants' social distance (SD) and feeling thermometer (FT) ratings for each target as a function of group differences and target categorizations.
@@
 4 & vs 3 & Categorization    & .42 & .47 & -16028 & 83.5 & 264.8 & 24.5 & 10.8 \\
-5 & vs 4 & \ldots~(Category) & .42 & .47 & -16007 & 83.6 &  21.1 &  8.7 &  2.4 \\
-6 & vs 5 & \ldots~(Ingroup)  & .42 & .47 & -16025 & 84.3 & -17.4 &  5.9 & -3.0 \\
+5 & vs 4 & ... (Category) & .42 & .47 & -16007 & 83.6 &  21.1 &  8.7 &  2.4 \\
+6 & vs 5 & ... (Ingroup)  & .42 & .47 & -16025 & 84.3 & -17.4 &  5.9 & -3.0 \\
 \bottomrule    
@@
 \end{table}
+
+After examining potential antecedents, we turned to potential consequences of more inclusive social identities.
+We analysed how participants' categorizations related to their feeling thermometer and social distance ratings for each target in the categorization task---as well as to their responses to the intergroup threat, perceived (dis-)advantage, and policy support measures.
+
+\subsubsection{Intergroup attitudes}
+
+To answer these questions, we first ran a series of multilevel multivariate regression models with participants' target-wise social distance and feeling thermometer ratings as outcome variables (Table~\ref{tab:t3}).\footnote{Linear regression models assigned weakly informative prior distributions: $\beta \sim \text{Normal}(0, 1)$ for fixed effects and $\sigma \sim \text{Half-Cauchy}(0, 1)$ for standard deviations of varying effects.} Models~0 to 3 estimated ratings (on either outcome) as varying between participants but fixed across targets (M0), as varying across participants and target categories (M1), and tested whether SC/ST participants' responses differed from GM and OBC participants' (M2), and whether OBC participants' responses differed from GM participants' (M3).
+Models~1 to 3 improved upon the predictions of simpler models, showing that participants' ratings depended on targets' and participants' group memberships.
 
@@
 Model~1 made better out-of-sample predictions than Model~0, $\Delta\textit{ELPD} = 94.7$, $\textit{SE} = 14.1$, $\frac{\Delta\textit{ELPD}}{\textit{SE}} = 6.7$.
-This shows that participants' caste memberships shaped their perceived (dis )advantage and policy support ratings.
+This shows that participants' caste memberships shaped their perceived (dis-)advantage and policy support ratings.
 Figures~\ref{fig:f7} and \ref{fig:f8} show the estimated group differences for the respective outcomes.
@@
 Our research also examined support for social change.
-Contrary to past research, neither positive nor negative contact \cite{hayward_how_2018, reimer_intergroup_2017} were associated with support for social change---or perceptions of relative advantage and disadvantage---in advantaged \cite{dixon_intergroup_2007} and disadvantaged \cite{dixon_beyond_2012} groups.
+Contrary to past research, neither positive nor negative contact \cite{hayward_how_2018, reimer_intergroup_2017} were associated with support for social change---or perceptions of relative advantage and disadvantage---in advantaged \cite{dixon_intergroup_2007, selvanathan_whites_2018} and disadvantaged \cite{dixon_beyond_2012} groups.
 Similarly, more inclusive identities were not associated with opposition to affirmative action among the disadvantaged \cite{dovidio_darker_2012}.

### 2020-04-25 manuscript/appendices.tex
resubmit

@@
 \usepackage[utf8]{inputenc}
-
-% Format
-\usepackage{layout}
-\setlength{\parindent}{0.5in}
-\setcounter{secnumdepth}{0}
-\usepackage{lineno}
-%\usepackage{authblk}
 
@@
 \usepackage[super]{nth}
+\usepackage{csquotes}
+
+% Format
+\setlength{\parindent}{0.5in}
+\setcounter{secnumdepth}{0}
 
 % Language
-\usepackage[british]{babel}
+\usepackage[american]{babel}
+
+% Links
+\usepackage[colorlinks=true, linkcolor=black, urlcolor=black, citecolor=black]{hyperref}
 
 % References
-\usepackage[nosectionbib, tocbib, unnumberedbib]{apacite}
-
+\usepackage[style=apa]{biblatex}
+\DeclareSourcemap{
+  \maps[datatype=bibtex]{
+    \map{
+      \pertype{book}
+      \step[fieldset=location, null]
+      \step[fieldset=address, null]
+    }
+    \map{
+      \pertype{incollection}
+      \step[fieldset=location, null]
+      \step[fieldset=address, null]
+    }
+  }
+}
+\addbibresource{appendices.bib}
+\renewcommand*{\bibfont}{\small}
 % Figures
@@
 \title{\emph{Appendices for}\\Intergroup contact fosters\\more inclusive social identities}
-\date{July 30, 2019}
+\date{April 24, 2020}
 
@@
 
-\section{Appendix A: Pilot Study}
+\section{Appendix A: Additional Measures}
 
-Informed by local knowledge, we intended to rely on last names to unobtrusively communicate caste membership in the triple crossed-categorization task.
-To find the most prototypical stimuli, we compiled an initial set of 50 surnames, drawing on local knowledge, databases on naming preferences, and publicly available archives of Facebook usernames.
-We selected 10 surnames for each of five combinations of nationality, religion, and caste: (1) Indian Hindus of upper-caste backgrounds, (2) Indian Hindus of lower-caste backgrounds (Dalits), (3) Indian Muslims, (4) foreign Hindus, and (5) foreign Muslims.
-From these 50 names, we created 100 stimuli resembling identity cards, 50 with female first names and 50 with male first names.
-Each card had the target's first and last name, age (21--26 years), and religion (Hindu, Muslim) printed on them, as well as a flag corresponding to the target's nationality (Indian, Nepali, Sri Lankan, Bangladeshi) and a silhouette corresponding to the target's gender \cite<adapted~from>{ma_chicago_2015}.
-Cards for female and male targets were identical in all attributes except first name and silhouette.
+We included additional measures to validate the triple crossed-categorization task and to replicate earlier research.
+We tested to what extent various social identity measures correlated with responses in the triple crossed-categorization task.
+We also assessed Karmic beliefs to replicate \citeauthor{cotterill_ideological_2014}'s (\citeyear{cotterill_ideological_2014}) finding that Karmic beliefs mediate the relationship between social dominance orientation and support for hierarchy-enhancing policies.
+We do not report results from this replication here, but make all data available online.
 
-We asked 26 students (19 women, 7 men) of diverse caste groups (\emph{SC/ST}: 8, \emph{GM}: 10, \emph{OBC}: 8) and religious backgrounds (\emph{Hinduism}: 16, \emph{Islam}: 4, \emph{Christianity}: 5, \emph{Jainism}: 1) to review 25 of the 50 stimuli corresponding to their gender.
-For each stimulus, we asked participants which caste they thought the target most likely belonged to (\emph{SC/ST}, \emph{GM}, \emph{OBC}, \emph{GM or OBC}, \emph{Can't tell/Don't know}), how typical or unusual they considered the target's name for someone of that particular nationality, religion, and (if applicable) caste $(1 = \textit{very typical}, 6 = \textit{very unusual})$, and whether the target's name reminded them of anyone in particular (\emph{yes}, \emph{no}) and, if so, of whom.
+\subsection{Measures}
 
-Participants' responses had important implications for designing the triple crossed-categorization task.
-On average, participants regarded all targets' names as at least ``somewhat typical'' $(1.42 \le \textit{Ms} \le 3.50)$.
-Names, however, were not enough to reliably cue caste membership---only $55\%$ to $83\%$ of participants identified even the most distinctive Dalit targets as Scheduled Caste~/ Scheduled Tribe (see Figure~\ref{fig:a-1}).
-Further, participants consistently categorized Muslim targets as Other Backward Class (see Figure~\ref{fig:a-2}), introducing a potential confound when comparing Muslim (OBC) and Hindu (GM) targets.
-Considering these findings, we decided to explicitly state caste membership (as reservation categories: GM, OBC, SC/ST) for Indian targets, and to add \emph{Indian, Hindu, OBC} targets as a sixth category.
+Group identification was measured with one item per ingroup \parencite{postmes_single-item_2013}: ``I identify with my [nationality/religion/caste group]'' ($1 = \textit{strongly disagree}$, $7 = \textit{strongly agree}$).
+
+Social identity complexity \parencite{roccas_social_2002, schmid_antecedents_2009} was operationalized as the extent to which participants perceived their different group memberships as conceptually interrelated (\emph{similarity complexity}) and numerically overlapping (\emph{overlap complexity}).
+Two items measured similarity complexity for religion/nationality and for nationality/caste: ``How similar or different are the typical [Hindu/Indian] and the typical [Indian/person from your caste group] to each other?'' ($1 = \textit{very different}$, $5 = \textit{very similar}$, reverse coded), and ``Do you think that being [Hindu/Indian] means the same as being [Indian/from your caste group]?'' ($1 = \textit{means something very similar}$, $5 = \textit{means something very different}$).
+Two items measured overlap complexity for religion/nationality: ``How many [Indians/ Hindus] do you think are [Hindus/Indian]?” (\%, $r = .63$).
+Three items measured overlap complexity for nationality and caste: ``How many Indians do you think are [GC, OBC, SC/ST]?'' (\%, $.33 \leq rs \leq .50$).
+Overlap items were reverse coded, so that higher scores indicated less perceived overlap.
+
+\emph{Entitativity} \parencite{lickel_varieties_2000} was measured with six items: ``Being Indian is important to each Indian, no matter their caste or religion'', ``Indians of all castes and religions interact often with each other.'', ``Indians of all castes and religions are working towards shared goals'', ``What happens to one Indian also impacts other Indians'', ``Indians of all castes and religions depend on one another'', and ``Indians are similar to one another'' ($1 = \textit{strongly disagree}$, $7 = \textit{strongly agree}$, $\alpha = .80$).
+Participants were encouraged to ``take Indian/Indians to mean Indian citizens of all castes and religions'' when reading the items of this scale.
+This scale thus measured an inclusive conception of entitativity.
+
+\emph{Karmic beliefs} \parencite{cotterill_ideological_2014} were measured with three items: ``my current caste group position reflects
+my actions or deeds in my past life'', ``if I do good deeds in my current life they will positively influence my caste status in my future life'', and ``the caste group position I was born into reflects the Karma of my past life'' ($1 = \textit{strongly disagree}$, $7 = \textit{strongly agree}$).
+
+\subsection{Correlates of categorization}
+
+We explored how participants' responses in the triple crossed-categorization task related to other measures of social identification.
+To that end, we estimated the correlations between, on the one hand, the proportions of targets that participants had categorized as ``us'' in each of the six categories, and, on the other hand, the (aggregated) social identification variables described in the \emph{Measures} section.
+We derived the likelihood of the observed responses from a multivariate normal distribution: $$ \textbf{Y} \sim \text{MVNormal} (\mu , \textbf{S} ) $$ where $\textbf{Y}$ is the matrix of observed variable scores (columns) across participants (rows), $\mu$ is the vector of all variable means, and $\textbf{S}$ is the variance-covariance matrix across variables.
+
+Figure~\ref{fig:a-1} shows the estimated correlations between participants' categorizations in the triple crossed-categorization task (from left to right) and various social identification variables (from top to bottom).
+Entitativity---the extent to which participants saw Indians of \emph{all} castes and religions as similar to one another, as depending on each other, as sharing a common fate, as working towards shared goals, and as valuing their shared identity---was positively correlated with the proportion of \emph{Indian, Hindu, GM} ($r = .16$, $[.04, .27]$, $\text{Pr} (r > 0|M) > .99$), \emph{Indian, Hindu, OBC} ($r = .21$, $[.09, .31]$, $\text{Pr} (r > 0| M) > .99$), \emph{Indian, Hindu, SC/ST} ($r = .10$, $[-.02, .22]$, $\text{Pr} (r > 0| M) = .97$), and \emph{Indian, Muslim, OBC} ($r = .18$, $[.07, .30]$, $\text{Pr} (r > 0| M) > .99$) targets participants categorized as ``us''.
 
@@
 \centering
-\includegraphics[scale=1]{../figures/appendices/appendices-a-1}
-\caption[Proportion of SC/ST vs GM classifications per target stimulus (Pilot study)]{Proportion of SC/ST vs GM classifications per target stimulus.
-Targets in the upper-left quadrant were most often classified as SC/ST, while targets in the lower-right quadrant were most often classified as GM.
-Targets in the lower-left quadrant were more often classified as GM or OBC, or OBC than as SC/ST or GM, or could not be classified reliably.
-Colours highlight Indian targets selected as GM, OBC, and SC/ST stimuli, respectively, based on participants' categorizations in the pilot study.
-GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste~/ Scheduled Tribe}
+\includegraphics{../figures/appendices/appendices-e-1}
+\caption[Correlations between social identity variables and target categorizations]{Correlations between various social identity variables (top to bottom) and the proportion of targets that participants had categorized as ``us'' in each target category (left to right).
+Points indicate the most likely estimate for a given correlation, while lines encompass the 97\% most likely estimates of that correlation.
+Curves show the density distributions of the posterior probabilities, based on all samples from the posterior probability distribution.
+Correlations for which $\text{Pr} (r > 0| M) > .99$ or $\text{Pr} (r < 0| M) > .99$ are shown in a darker shade.}
 \label{fig:a-1}
@@
 
-\begin{figure}
+Group identification was only associated with participants' categorizations of foreign targets, not their categorizations of Indian targets.
+The extent to which participants identified with their religion was negatively correlated with how many \emph{foreign, Hindu} ($r = -.14$, $[-.25, -.02]$, $\text{Pr} (r > 0| M) > .99$) and \emph{foreign, Muslim} ($r = -.18$, $[-.29, -.07]$, $\text{Pr} (r > 0| M) > .99$) targets participant categorized as ``us''.
+I obtained similar correlations for the extent to which participants identified with their caste group, $r = -.15$, $[-.27, -.04]$, $\text{Pr} (r > 0| M) > .99$ and $r = -.17$, $[-.29, -.06]$, $\text{Pr} (r > 0| M) > .99$, respectively.
+The extent to which participants identified with their nationality was not associated with participants' categorizations---perhaps because there was a little variation in participants responses, with 81\% of participants strongly agreeing with the statement.
+Other variables were not systematically correlated with participants' responses in the crossed-categorization task (see Figure~\ref{fig:a-1}).
+
+Correlations thus confirmed that participants' categorizations were more than a straight-forward reflection of the strength of their group identification, affirming the value of the crossed-categorization task for studying identification in contexts with multiple, cross-cutting group memberships.
+Furthermore, participants' perceptions of entitativity across caste and religions were associated with more inclusive construals of national identity, providing tentative evidence for its potential for fostering more inclusive identities.
+
+\newpage
+
+\section{Appendix B: Sample Size}
+
+We ran simulations to determine the sample size required to obtain reasonably precise estimates of the model parameters of interest.\footnote{Bayesian data analysis does not usually allow for \textit{analytical} power analyses.} What made these simulations challenging is that multilevel models have more parameters than simple generalized linear models and that no clear default values exist to narrow down the parameter space for our simulations.
+We constrained our simulations in several ways:
+
+\begin{enumerate}
+\item We re-analysed existing data (kindly provided by \nptextcite{van_dommelen_construing_2015}) from a study of 91 Turkish Australians (46 women, 45 men) completing a version of the triple crossed-categorization task with eight target categories.
+We ran a model identical to Model~1 (Table~2, in the main text) which estimated participants' categorizations as varying across participants and across target categories.
+We could not estimate group differences across the participants' ingroup because all participants belonged to the same group.
+\item We decided to focus our simulations on two kinds of parameters of interest.
+First, we considered how participants' categorizations of the eight target categories differed across three participant ingroups.
+Second, we considered how participants' categorizations varied as a function of a continuous predictor variable.
+As we could not estimate these parameters from the existing data, we used informative prior distribution to simulate plausible values for the corresponding model parameters.\footnote{We modeled differences between the three participant ingroups as $\beta_k \sim \text{Normal}(\beta_0, \sigma)$ with the prior distributions $\beta_0 \sim \text{Normal}(0, 1)$ and $\sigma \sim \text{Half-Student-t}(10, 0, 0.2)$, where $1 < k < 8$ was an index for the eight target categories.
+We modeled the fixed coefficient of the continuous predictor with the prior distribution $\beta_x \sim \text{Normal}(0, 1)$.}
+\item We decided to run our simulations for samples of 3 (groups) x 100 (sample size per group) = 300 participants.
+This sample size reflects constraints in the number of potential participants available to us.
+\end{enumerate}
+
+\noindent First, we simulated 4,000 datasets of 300 participants by combining posterior predictive draws from the model fit to the existing data for the varying intercepts across participants and target categories, simulation draws from the informative prior distributions for the varying effects of participant ingroups and the fixed effect of the continuous predictor variable, and simulation draws from a $\text{Normal}(0, 1)$ distribution for values of the continuous predictor variables.
+Second, we randomly selected 10 of these datasets and estimated the relevant model parameters by applying a model akin to Model 4 (Table~2, in the main text).\footnote{We decided to use no more than ten samples as running these models was computationally expensive and as the precision of our estimates did not differ much across samples.} Third, we calculated the standard deviations of the posterior distributions (equivalent to standard errors in classical statistics) for all model parameters and all samples.
+
+Table~\ref{tab:b-1} shows the results of our simulations.
+For $N = 300$, our model estimated the (varying) effects of group differences with an average precision of $\textit{SD} = 0.41$ (0.34--0.50) and the (fixed) effect of a  continuous predictor with an average precision of $\textit{SD} = 0.17$ (0.14--0.21) on the log odds scale.
+As log odds are difficult to interpret, we translated these values to the change in the proportion of ``us'' categorizations that results from a +1\textit{SD} increase in log odds above the average log odds of ``us'' categorizations.
+We thus translate the average precision to $\Delta\Pr = .074$ for group differences and $\Delta\Pr = .033$ for the continuous predictor.
+As we expected group differences to be greater than individual differences in participants' categorizations, we concluded that 100 participants per group would yield reasonably precise estimates of the parameters of interest.
+
+\begin{table}[!p]
 \centering
-\includegraphics[scale=1]{../figures/appendices/appendices-a-2}
-\caption[Foreign targets selected based on participants' average typicality ratings (Pilot study)]{Foreign targets selected as Sri Lankan, Hindu (2), Nepali, Hindu (2), and Bangladeshi, Muslim (4) stimuli, respectively, based on participants' average typicality ratings.}
-\label{fig:a-2}
-\end{figure}
+\figureversion{lining, tabular}
+\caption{Standard deviations of the posterior distributions for 17 parameters across 10 simulations.
+\textit{SD} is the average standard deviation across the 10 simulations while \textit{Min} is the minimum and \textit{Max} is the maximum.
+$\Delta\Pr$ is the change in the proportion of ``us'' categorizations for a +1\textit{SD} increase in log odds.}
+\small	
+\begin{tabular}{lrrrrr} \toprule
+Parameter & $k$ & \textit{SD} & \textit{Min} & \textit{Max} & $\Delta\Pr$ \\
+\midrule \addlinespace
+  $\beta_\text{Group 1 - Group 2}$ & 1 & 0.42 & 0.33 & 0.51 & .076 \\
+  $\beta_\text{Group 1 - Group 2}$ & 2 & 0.41 & 0.34 & 0.49 & .075 \\
+  $\beta_\text{Group 1 - Group 2}$ & 3 & 0.40 & 0.33 & 0.48 & .073 \\
+  $\beta_\text{Group 1 - Group 2}$ & 4 & 0.40 & 0.33 & 0.48 & .072 \\
+  $\beta_\text{Group 1 - Group 2}$ & 5 & 0.40 & 0.32 & 0.46 & .072 \\
+  $\beta_\text{Group 1 - Group 2}$ & 6 & 0.40 & 0.33 & 0.46 & .072 \\
+  $\beta_\text{Group 1 - Group 2}$ & 7 & 0.40 & 0.33 & 0.47 & .073 \\
+  $\beta_\text{Group 1 - Group 2}$ & 8 & 0.39 & 0.32 & 0.47 & .070 \\
+  $\beta_\text{Group 1 - Group 3}$ & 1 & 0.43 & 0.35 & 0.52 & .077 \\
+  $\beta_\text{Group 1 - Group 3}$ & 2 & 0.44 & 0.36 & 0.56 & .079 \\
+  $\beta_\text{Group 1 - Group 3}$ & 3 & 0.42 & 0.35 & 0.53 & .076 \\
+  $\beta_\text{Group 1 - Group 3}$ & 4 & 0.42 & 0.36 & 0.53 & .075 \\
+  $\beta_\text{Group 1 - Group 3}$ & 5 & 0.42 & 0.35 & 0.54 & .075 \\
+  $\beta_\text{Group 1 - Group 3}$ & 6 & 0.42 & 0.35 & 0.52 & .075 \\
+  $\beta_\text{Group 1 - Group 3}$ & 7 & 0.42 & 0.36 & 0.52 & .075 \\
+  $\beta_\text{Group 1 - Group 3}$ & 8 & 0.40 & 0.34 & 0.52 & .073 \\
+	$\beta_x$                        &   & 0.17 & 0.14 & 0.21 & .033 \\
+\addlinespace 
+%\midrule $M$ & & 0.40 & 0.33 & 0.49 & .072 \\ 
+\bottomrule
+\end{tabular}
+\label{tab:b-1}
+\end{table}
 
-For the final set of stimuli, we chose the four most prototypical targets for each of the six categories under study.
-We ranked Indian targets by the proportion of ``correct'' categorizations (e.g., $\Pr(\textit{OBC})$ for \emph{Muslim, OBC} targets) weighted by the inversed proportions of ``incorrect'' categorizations (e.g., $1 - \Pr(\textit{SCST})$ and $1 - \Pr(\textit{GM})$ for \emph{Muslim, OBC} targets).
-We selected the four highest-ranked (Category 1) \emph{Hindu, GM}, (2) \emph{Hindu, OBC}, (3) \emph{Hindu, SC/ST}, and (4) \emph{Muslim, OBC} targets (see Figure~\ref{fig:a-1}).
-We ranked foreign targets by their average typicality rating, and excluded targets who were categorized as General Merit or Scheduled Caste~/ Scheduled Tribe by $\ge 50\%$ of participants (to avoid obvious caste associations).
-We selected the two most typical (Category 5) \emph{Nepali, Hindu} and \emph{Sri Lankan, Hindu} targets, and the four most typical (6) \emph{Bangladeshi, Muslim} targets (see Figure~\ref{fig:a-2}).
-Based on the pilot study, we thus used $6~(\text{categories}) \times 4~(\text{targets}) = 24$ stimuli in the final study.
-Between $0\%$ and $44\%$ of participants ($\textit{Mdn} = 10\%$) recognised each selected name as familiar---in most cases, participants reported that targets reminded them of fellow students, former classmates, or co-workers.
+\newpage
 
-\section{Appendix B: Descriptive Statistics}
+\section{Appendix C: Descriptive Statistics}
 
-Table~\ref{tab:b-1} reports means and standard deviations for all variables. Tables~\ref{tab:b-2} to \ref{tab:b-5} report correlations between all variables for various ingroups and outgroups.
+Table~\ref{tab:c-1} reports means and standard deviations for all variables. Tables~\ref{tab:c-2} to \ref{tab:c-5} report correlations between all variables for various ingroups and outgroups.
 
@@
 \end{tabular}
-\label{tab:b-1}
+\label{tab:c-1}
 \end{table}
@@
 \end{tabular}
-\label{tab:b-2}
+\label{tab:c-2}
 \end{table}
@@
 \end{tabular}
-\label{tab:b-3}
+\label{tab:c-3}
 \end{table}
@@
 \end{tabularx}
-\label{tab:b-4}
+\label{tab:c-4}
 \end{table}
@@
 \end{tabularx}
-\label{tab:b-5}
+\label{tab:c-5}
 \end{table}
@@
 
-\section{Appendix C: Social Identity Structures}
+\section{Appendix D: Pilot Study}
 
-Van Dommelen et al.
-\citeyear{dommelen_construing_2015} analysed participants' responses as \emph{Social Identity Inclusiveness}, i.e.
-the total number of 24 targets a participant had categorized as ``us'', and as \emph{Social Identity Structures}, i.e.
-the specific structures proposed by \citeA{roccas_social_2002}.
-Neither measure translated well to the present study.
-As participants had different caste backgrounds, comparing their inclusiveness scores ($M = 15.34$, $\textit{SD} = 4.88$, $\textit{Mdn} = 16$) was less meaningful than in \citeauthor{dommelen_construing_2015}'s sample.
-Coding structures was interesting in principle, but proved difficult in practice.
-Few (9\%, $n = 26$) participants consistently classified all targets in each category as either ``us'' or ``not us''.
-Relatedly, how participants classified targets within a category was correlated, but only moderately so ($.41 \leq rs \leq.66$, see Table ~\ref{tab:c-1}).
-The inconsistency in participants' responses made hard and fast coding rules, as used by \citeauthor{dommelen_construing_2015}, impractical.
+Informed by local knowledge, we intended to rely on last names to unobtrusively communicate caste membership in the triple crossed-categorization task.
+To find the most prototypical stimuli, we compiled an initial set of 50 surnames, drawing on local knowledge, databases on naming preferences, and publicly available archives of Facebook usernames.
+We selected 10 surnames for each of five combinations of nationality, religion, and caste: (1) Indian Hindus of upper-caste backgrounds, (2) Indian Hindus of lower-caste backgrounds (Dalits), (3) Indian Muslims, (4) foreign Hindus, and (5) foreign Muslims.
+From these 50 names, we created 100 stimuli resembling identity cards, 50 with female first names and 50 with male first names.
+Each card had the target's first and last name, age (21--26 years), and religion (Hindu, Muslim) printed on them, as well as a flag corresponding to the target's nationality (Indian, Nepali, Sri Lankan, Bangladeshi) and a silhouette corresponding to the target's gender (adapted from \nptextcite{ma_chicago_2015}).
+Cards for female and male targets were identical in all attributes except first name and silhouette.
 
-Instead, we quantified the (dis)similarity between a participant's responses and various proposed social identity structures by calculating edit distances.
-We operationalized \emph{edit distance} as the number of a participant's categorizations that would need to change from ``us'' to ``not us'' (and vice versa) to make them identical to the categorizations implied by a certain structure.
-Figure~\ref{fig:c-1} shows the distributions of participants' edit distances from each structure, as well as median edit distances.
+We asked 26 students (19 women, 7 men) of diverse caste groups (\emph{SC/ST}: 8, \emph{GM}: 10, \emph{OBC}: 8) and religious backgrounds (\emph{Hinduism}: 16, \emph{Islam}: 4, \emph{Christianity}: 5, \emph{Jainism}: 1) to review 25 of the 50 stimuli corresponding to their gender.
+For each stimulus, we asked participants which caste they thought the target most likely belonged to (\emph{SC/ST}, \emph{GM}, \emph{OBC}, \emph{GM or OBC}, \emph{Can't tell/Don't know}), how typical or unusual they considered the target's name for someone of that particular nationality, religion, and (if applicable) caste $(1 = \textit{very typical}, 6 = \textit{very unusual})$, and whether the target's name reminded them of anyone in particular (\emph{yes}, \emph{no}) and, if so, of whom.
+
+Participants' responses had important implications for designing the triple crossed-categorization task.
+On average, participants regarded all targets' names as at least ``somewhat typical'' $(1.42 \le \textit{Ms} \le 3.50)$.
+Names, however, were not enough to reliably cue caste membership---only $55\%$ to $83\%$ of participants identified even the most distinctive Dalit targets as Scheduled Caste~/ Scheduled Tribe (see Figure~\ref{fig:d-1}).
+Further, participants consistently categorized Muslim targets as Other Backward Class (see Figure~\ref{fig:d-2}), introducing a potential confound when comparing Muslim (OBC) and Hindu (GM) targets.
+Considering these findings, we decided to explicitly state caste membership (as reservation categories: GM, OBC, SC/ST) for Indian targets, and to add \emph{Indian, Hindu, OBC} targets as a sixth category.
 
@@
 \centering
-\includegraphics[scale=1]{../figures/appendices/appendices-b-1}
-\caption[Edit distances between social identity structures and participants' responses]{Edit distances between each social identity structure and participants' responses.
-Edit distance is the sum of all categorizations in which a participant's responses differed from the ones implied by the proposed structure.
-Numbers (on the right) show the median edit distance per structure.
-%Points indicate the median \emph{social identity inclusiveness} of participants' responses at a specific edit distance.
-}
-\label{fig:c-1}
+\includegraphics[scale=1]{../figures/appendices/appendices-a-1}
+\caption[Proportion of SC/ST vs GM classifications per target stimulus (Pilot study)]{Proportion of SC/ST vs GM classifications per target stimulus.
+Targets in the upper-left quadrant were most often classified as SC/ST, while targets in the lower-right quadrant were most often classified as GM.
+Targets in the lower-left quadrant were more often classified as GM or OBC, or OBC than as SC/ST or GM, or could not be classified reliably.
+Colours highlight Indian targets selected as GM, OBC, and SC/ST stimuli, respectively, based on participants' categorizations in the pilot study.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste~/ Scheduled Tribe}
+\label{fig:d-1}
 \end{figure}
 
-Overall, participants' responses most closely resembled the Indian-Hindu merger structure ($\textit{Mdn} = 5.0$), in which participants include all targets who are \emph{either} Indian \emph{or} Hindu \emph{or} both in the ingroup.
-This was closely followed by inclusive nationalism ($\textit{Mdn} = 6.5$), i.e.
-participants include all targets who are Indian, and Hindu nationalism ($\textit{Mdn} = 7.0$), i.e.
-participants include only Indian Hindu targets.
-In addition, Pan-Hinduism ($\textit{Mdn} = 8.0$), i.e.
-participants include all Hindu targets, and egalitarianism ($\textit{Mdn} = 8.0$), i.e.
-participants include all targets, somewhat described participants' responses.
-Caste did not seem to dominate participants' responses ($\textit{Mdn} = 12.0$).
-Together, these observations suggested that, on the broadest level of analysis, participants relied on nationality and religion, rather than caste, to define their ingroup.
+\begin{figure}
+\centering
+\includegraphics[scale=1]{../figures/appendices/appendices-a-2}
+\caption[Foreign targets selected based on participants' average typicality ratings (Pilot study)]{Foreign targets selected as Sri Lankan, Hindu (2), Nepali, Hindu (2), and Bangladeshi, Muslim (4) stimuli, respectively, based on participants' average typicality ratings.}
+\label{fig:d-2}
+\end{figure}
 
-\begin{table}
-\centering
-\figureversion{lining, tabular}
-\caption[Mean intra and inter-category correlations for target categorizations]{Mean \emph{intra}-category (\textbf{diagonal}) and \emph{inter}-category correlations between participants' categorizations of targets in the respective categories.}
-\small	
-\begin{tabular}{rlrrrr|rr} \toprule
-\# & Category            & 1   & 2   & 3   & 4   & 5   & 6   \\ \midrule \addlinespace
-1  & Indian, Hindu, GM   & \textbf{.48} & .56 & .33 & .43 & .16 & .08 \\
-2  & Indian, Hindu, OBC  & .56 & \textbf{.41} & .29 & .46 & .09 & .06 \\
-3  & Indian, Hindu, SCST & .33 & .29 & \textbf{.66} & .35 & .03 & .16 \\
-4  & Indian, Muslim, OBC & .43 & .46 & .35 & \textbf{.52} & .01 & .24 \\ \midrule
-5  & Foreign, Hindu      & .16 & .09 & .03 & .01 & \textbf{.50} & .47 \\
-6  & Foreign, Muslim     & .08 & .06 & .16 & .24 & .47 & \textbf{.51} \\ \addlinespace \bottomrule
-\end{tabular}
-\label{tab:c-1}
-\end{table}
+For the final set of stimuli, we chose the four most prototypical targets for each of the six categories under study.
+We ranked Indian targets by the proportion of ``correct'' categorizations (e.g., $\Pr(\textit{OBC})$ for \emph{Muslim, OBC} targets) weighted by the inversed proportions of ``incorrect'' categorizations (e.g., $1 - \Pr(\textit{SCST})$ and $1 - \Pr(\textit{GM})$ for \emph{Muslim, OBC} targets).
+We selected the four highest-ranked (Category 1) \emph{Hindu, GM}, (2) \emph{Hindu, OBC}, (3) \emph{Hindu, SC/ST}, and (4) \emph{Muslim, OBC} targets (see Figure~\ref{fig:d-1}).
+We ranked foreign targets by their average typicality rating, and excluded targets who were categorized as General Merit or Scheduled Caste~/ Scheduled Tribe by $\ge 50\%$ of participants (to avoid obvious caste associations).
+We selected the two most typical (Category 5) \emph{Nepali, Hindu} and \emph{Sri Lankan, Hindu} targets, and the four most typical (6) \emph{Bangladeshi, Muslim} targets (see Figure~\ref{fig:d-2}).
+Based on the pilot study, we thus used $6~(\text{categories}) \times 4~(\text{targets}) = 24$ stimuli in the final study.
+Between $0\%$ and $44\%$ of participants ($\textit{Mdn} = 10\%$) recognised each selected name as familiar---in most cases, participants reported that targets reminded them of fellow students, former classmates, or co-workers.
 
-\section{Appendix D: Intergroup Threat}
+\newpage
+
+\section{Appendix E: Intergroup Threat}
 
@@
 \figureversion{lining, tabular}
-\caption[Model comparison for intergroup threat]{Comparison of models estimating participants' intergroup threat.
-We preferred a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.}
+\caption[Model comparison for intergroup threat]{Comparison of models estimating participants' intergroup threat.}
 \small	
-\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrr} \toprule
-\# &  &  Description &  $R^2$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule \addlinespace
-0 &      & \textit{Varying intercept} & .31 & -3368.1 & 32.9 & - & - & - & .11 \\
-1 & vs 0 & \textit{Subscales}         & .31 & -3368.9 & 32.9 & -0.8 & 0.6 & -1.3 & .00 \\
-2 & vs 0 & \textit{Outgroups} & .32 & -3363.7 & 33.0 & 4.4 & 3.3 & 1.3 & .00 \\
-3 & vs 0 & \textit{Subscales $\times$ Outgroups} & .33 & -3335.1 & 34.0 & 33.0 & 8.4 & 3.9 & .19 \\ \midrule
-4 & vs 3 & \textit{Categorizations}   & .33 & -3335.5 & 34.0 & -0.3 & 0.6 & -0.5 & .00 \\
-5 & vs 3 & \textit{Categorizations}   & .34 & -3330.5 & 34.0 & 4.7 & 3.6 & 1.3 & .71 \\
-6 & vs 3 & \textit{Categorizations}   & .33 & -3336.7 & 34.0 & -1.5 & 0.7 & -2.1 & .00 \\
-7 & vs 3 & \textit{Categorizations}   & .34 & -3332.8 & 34.0 & 2.3 & 3.6 & 0.6 & .00 \\ \addlinespace \bottomrule
+\begin{tabularx}{\linewidth}{r@{~}rXrrrrrr} \toprule
+\# &  &  Description &  $R^2$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ \\ \midrule \addlinespace
+0 &      & \textit{Varying intercept} & .31 & -3368.1 & 32.9 & - & - & - \\
+1 & vs 0 & \textit{Subscales}         & .31 & -3368.9 & 32.9 & -0.8 & 0.6 & -1.3 \\
+2 & vs 0 & \textit{Outgroups} & .32 & -3363.7 & 33.0 & 4.4 & 3.3 & 1.3 \\
+3 & vs 0 & \textit{Subscales $\times$ Outgroups} & .33 & -3335.1 & 34.0 & 33.0 & 8.4 & 3.9  \\ \midrule
+4 & vs 3 & \textit{Categorizations}   & .33 & -3335.5 & 34.0 & -0.3 & 0.6 & -0.5  \\
+5 & vs 3 & \textit{Categorizations}   & .34 & -3330.5 & 34.0 & 4.7 & 3.6 & 1.3 \\
+6 & vs 3 & \textit{Categorizations}   & .33 & -3336.7 & 34.0 & -1.5 & 0.7 & -2.1 \\
+7 & vs 3 & \textit{Categorizations}   & .34 & -3332.8 & 34.0 & 2.3 & 3.6 & 0.6 \\ \addlinespace \bottomrule
 \end{tabularx}
@@
 
-\section{Appendix E: Support for Social Change}
+\newpage
 
-We tested whether more inclusive identities increase support for affirmative action among advantaged-group members, but decrease support for these policies among disadvantaged-group members.
-First, we tested for \emph{group differences} in participants' perceptions of (dis-)advantages and in their support for affirmative action.
-Second, we analysed to what extent contact experiences and ingroup construals explained \emph{individual differences} in participants' responses.
-We examined participants' responses to measures concerning outgroup members to test the \emph{solidarity hypothesis} (that positive contact encourages advantaged-group members to support social change).
-We examined participants' responses to measures concerning their ingroup to test the \emph{demobilization hypothesis} (that positive contact discourages disadvantaged-group members from supporting social change) and the \emph{mobilization hypothesis} (that negative contact encourages disadvantaged-group members to support social change).
-
-\subsubsection{Group differences}
-
-We investigated how participants' caste memberships shaped their perceptions of (dis-)advantages and their support for reservations.
-To that end, we estimated two Bayesian multivariate models in \emph{RStan} \cite{rstan_package} with participants' responses to six perceived (dis-)advantage and three policy support measures as outcome variables.\footnote{For this analysis, we aggregated items so that target groups corresponded across the two outcome measures.
-For perceived (dis-)advantage, we aggregated items for Scheduled Caste and Scheduled Tribe groups, resulting in six variables.
-For policy support, We aggregated items for Scheduled Castes / Scheduled Tribes reservations, and for Other Backward Classes reservations, resulting in three variables.} Both models estimated how participant $j$ responded to each of the nine outcomes.
-Models derived the likelihood of the observed responses from a multivariate normal distribution: $$ \textbf{Y} \sim \text{MVNormal} (\mu_{jk}, \textbf{S} ) $$ where $\textbf{Y}$ is the matrix of observed variable scores (columns) across participants (rows), $\mu_{jk}$ is the estimated response to item $k$ by participant $j$, and $\textbf{S}$ is the variance-covariance matrix across variables.
-This means that models estimated distinct means and residual variances for each outcome, as well as residual correlations between all outcomes.
-Models assigned weakly informative priors to all intercepts, coefficients, and residual variances:
-\begin{align*} 
-\beta & \sim \text{Normal} (0, 1) \\ 
-\sigma & \sim \text{Cauchy} (0, 1)
-\end{align*}
-allowing a wide range of plausible effect sizes.
-Model~0 estimated distinct means for each outcome, but did not consider participants' group memberships: $ \mu_{jk} =  \beta_k $, where $\mu_{jk}$ equals $\beta_{k}$, the fixed intercept for outcome $k$.
-Model~1 estimated distinct means across participants' ingroups: $ \mu_{jk} =  \beta_k + \beta_{k,\text{OBC}} + \beta_{k,\text{SCST}} $, where $\mu_{jk}$ equals $\beta_k$, the fixed intercept for outcome $k$, plus $\beta_{k,\text{OBC}}$ and $\beta_{k,\text{SCST}}$, the coefficients estimating by how much Other Backward Class and Scheduled Caste~/ Scheduled Tribe participants' responses differed from General Merit participants'.
-Model~1 made better out-of-sample predictions than Model~0, $\Delta\textit{ELPD} = 94.7$, $SE = 14.1$, $\frac{\Delta\textit{ELPD}}{\textit{SE}} = 6.7$.
-This comparison shows that participants' caste memberships shaped their perceived (dis-)advantage and policy support ratings.
-
-Figure \ref{fig:e-1} shows estimated mean ratings of perceived (dis-)advantage for all target groups as a function of participants' caste memberships in Model~1.
-For most target groups, General Merit and Other Backward Class participants' responses closely resembled each other.
-On average, General Merit~/ Other Backward Class participants thought that it was somewhat hard (below the midpoint) for ``people from [their] own background'' to succeed.
-General Merit~/ Other Backward Class participants agreed with each other that it was a lot easier for people from Scheduled Caste~/ Scheduled Tribe backgrounds to succeed, compared to people from their own background.
-General Merit~/ Other Backward Class participants also agreed that, of all target groups, life was most difficult for people from General Merit backgrounds.
-Other Backward Class participants disagreed with General Merit participants when rating life difficulty for people from Other Backward Class backgrounds.
-General Merit participants rated life difficulty for Other Backward Class people as somewhat easy, while Other Backward Class participants tended toward ``neither easy nor hard'' and ``somewhat hard''.
-Scheduled Caste~/ Scheduled Tribe participants' responses differed markedly from General Merit and Other Backward Class participants'.
-For all target groups, Scheduled Caste~/ Scheduled Tribe participants rated life difficulty as ``neither easy nor hard'', on average.
-General Merit, Other Backward Class, and Scheduled Caste~/ Scheduled Tribe participants all tended to rate life difficulty for Muslims as around the midpoint.
-Overall, participants' responses seemed to contradict, or even reverse, persisting social inequalities.
-
-\begin{figure}
-\centering
-\includegraphics[scale=1]{../figures/figure-7}
-\caption{
-Posterior probabilities of perceived (dis-)advantage ratings for different target groups (right) by participants' caste ingroup (left).
-Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.
-GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
-}
-\label{fig:e-1}
-\end{figure}
-
-Figure \ref{fig:e-2} shows estimated policy support---that is, support for reservations benefiting Scheduled Caste~/ Scheduled Tribe, Other Backward Class, and Muslim students---as a function of participants' caste memberships in Model~1.
-General Merit and Other Backward Class participants' responses did not provide evidence for cross-group solidarity.
-General Merit participants tended to oppose reservations for Scheduled Caste~/ Scheduled Tribe ($M = 1.87$, $[1.63, 2.12]$), Other Backward Class ($M = 2.70$, $[2.44, 2.96]$), and Muslim students ($M = 2.75$, $[2.46, 3.01]$).
-Other Backward Class participants tended to support reservations for their own group ($M = 3.72$, $[3.50, 3.95]$), but not for Scheduled Caste~/ Scheduled Tribe ($M = 2.31$, $[2.10, 2.53]$) or Muslim ($M = 2.79$, $[2.55, 3.04]$) students.
-Scheduled Caste~/ Scheduled Tribe participants tended to support reservations for their own group ($M = 4.16$, $[3.88, 4.45]$), for Other Backward Class students ($M = 3.57$, $[3.27, 3.86]$), and, to a lesser extent, for Muslim students ($M = 3.24$, $[2.92, 3.57]$).
-Overall, participants' responses provided evidence for solidarity from Scheduled Caste~/ Scheduled Tribe participants to Other Backward Class students, but not for solidarity from General Merit and Other Backward Class participants to Scheduled Caste~/ Scheduled Tribe students.
-
-\begin{figure}
-\centering
-\includegraphics[scale=1]{../figures/figure-8}
-\caption{
-Posterior probabilities of policy support ratings for different target groups (right) by participants' caste ingroup (left).
-Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.
-GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
-}
-\label{fig:e-2}
-\end{figure}
-
-\begin{table}
-\centering
-\figureversion{lining, tabular}
-\caption[Estimated residual correlations in Models 0 and 1 for Study 4]{Estimated residual correlations between six \emph{perceived life difficulty} (PD) ratings and three \emph{policy support} (PS) ratings in Model~0 (below the diagonal) and Model~1 (above the diagonal) for Study 4.}
-\small	
-\begin{tabularx}{\linewidth}{rl@{~}Xrrrrrr|rrr} \toprule
-\# & \multicolumn{2}{l}{Variable} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ \midrule \addlinespace
-1 & PD, & \ldots own background & \textbf{}  & .14 & .30 & .45 & .43 & .05 & .28 & .12 & .14 \\
-2 & PD, & SC/ST  & .10 & \textbf{} & .33 & -.13 & -.09 & .28 & -.12 & -.10 & -.05 \\
-3 & PD, & OBC    & .28 & .33 & \textbf{} & .20 & .16 & .32 & .05 & -.17 & -.13  \\
-4 & PD, & GM     & .47 & -.18 & .18 & \textbf{} & .61 & -.08 & .24 & .15 & .02 \\
-5 & PD, & Hindu  & .44 & -.12 & .15 & .62 & \textbf{} & -.01 & .29 & .11 & .03  \\
-6 & PD, & Muslim & .04 & .28 & .31 & -.10 & -.02 & \textbf{} & .02 & -.17 & -.15 \\ \midrule
-7 & PS, & SC/ST  & .29 & -.24 & -.03 & .33 & .30 & -.03 & \textbf{} & .24 & .34 \\
-8 & PS, & OBC    & .11 & -.13 & -.25 & .17 & .12 & -.16 & .28 & \textbf{} & .47 \\
-9 & PS, & Muslim & .16 & -.09 & -.13 & .06 & .05 & -.16 & .36 & .45 & \textbf{}   \\ \addlinespace \bottomrule
-\end{tabularx}
-\label{tab:e-1}
-\end{table}
-
-Table~\ref{tab:e-1} shows the estimated residual correlations before (Model~0) and after (Model~1) accounting for group differences.
-Perceiving a group to be disadvantaged correlated weakly with more support for reservations benefiting Scheduled Caste~/ Scheduled Tribe ($r = -.12 $, $[-.24,.01]$), Other Backward Class ($r = -.17$, $[-.30,-.05]$), and Muslim ($r = -.15$, $[-.28,-.03]$) students in Model~1.
-Support for reservations for one target group correlated moderately with support for reservations for the other target groups, $.24 < r < .47$.
-These correlations provided evidence for systematic variation in policy support ratings across participants, even after accounting for group differences.
-In the next section, we examine to what extent contact experiences and ingroup construals explain this variation across individuals.
-
-\subsubsection{Individual differences}
-
-We examined to what extent contact experiences and ingroup construals (measured as participants' responses in the triple crossed-categorization task) accounted for individual differences in perceived (dis-)advantage and policy support.
-To that end, we estimated a series of Bayesian multilevel models with either perceived (dis-)advantage or policy support as outcome variable.
-Models derived the likelihood of the observed responses from a normal distribution: $$ y_{ij} \sim \text{Normal} (\mu_{ij}, \sigma) $$ where $y_{ij}$ is the observed response to item $i$ by participant $j$, and $\mu_{ij}$ is the estimated response to item $i$ by participant $j$, $\sigma$ is the estimated residual variance (expressed as standard deviation).
-We used the same weakly informative priors as for the multivariate models.
-
-First, we estimated participants' responses to each of five perceived (dis-)advantage items, with General Caste (GM), Scheduled Caste (SC), Scheduled Tribe (ST), Other Backward Class (OBC), and Muslims as target groups.
-Model~0 estimated item responses as varying across participants and target groups, and estimated differences across participants' ingroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} $$ where $\mu_{ij}$, the estimated mean response to item $i$ by participant $j$, equals $\beta_j$, the varying intercept for participant $j$, and $\beta_{kl}$, the varying intercept for target group~$k$ ($1 = \text{GM}$, $2 = \text{OBC}$, $3 = \text{SC/ST}$, $4 = \text{Muslims}$) and ingroup~$l$ ($1 = \text{GM}$, $2 = \text{OBC}$, $2 = \text{SC/ST}$).
-Model~0 thus resembled the multivariate model estimated above.
-
-Model~1 extended Model~0 by estimating to what extent outgroup friendship and negative contact with outgroup members were associated with perceptions of (dis-)advantages for outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{OF}x_{\text{OG},k}x_\text{OF,jk} + \beta_\text{NC}x_{\text{OG},jk}x_\text{OF,jk}$$ where $x_{\text{OG},jk}$ codes whether target group $k$ is an outgroup [1] or ingroup [0] for participant $j$, $x_\text{OF,jk}$ and $x_\text{NC,jk}$ are, respectively, participant $j$'s outgroup friendship and negative contact with target group $k$, and $\beta_\text{OF}$ and $\beta_\text{NC}$ estimate the increase in participants' ratings for each additional standard deviation of reported contact.
-Model~2 estimated the effects of outgroup friendship and negative contact on outgroup ratings as varying across target outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_{\text{OF},k}x_{\text{OG},k}x_\text{OF,jk} + \beta_{\text{NC},k}x_{\text{OG},jk}x_\text{OF,jk}$$ where $\beta_{\text{OF},k}$ and $\beta_{\text{NC},k}$ estimate effects of contact on ratings for outgroup $k$.
-Neither Model~1 nor Model~2 improved upon the out-of-sample predictions of Model~0, showing that intergroup contact neither increased nor decreased participants' perceptions of discrimination against ethnoreligious or caste outgroups (see Table~\ref{tab:d-2}).
-
-Models~3 and 4 tested whether participants' ingroup construals were associated with their perceptions of (dis-)advantages for various outgroups.
-Model~3 estimated this relationship as constant across target groups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1}x_{\text{OG},k}x_\text{Q1,jk} $$ where $x_{Q1,jk}$ is the proportion [0--1] of targets belonging to outgroup $k$ that participant $j$ categorized as ``us'', and $\beta_{Q1}$ estimates the difference in perceived (dis-)advantage between participants who categorized all four targets of an outgroup as ``us'' and participants who categorized all targets of an outgroup as ``not us''.
-Model~4 estimated this relationship as varying across outgroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1,k}x_{\text{OG},k}x_\text{Q1,jk} $$ where $\beta_{Q1,k}$ estimates the difference in perceived perceived life difficulty between participants who categorized all four targets of outgroup $k$ as ``us'' and participants who categorized all targets of outgroup $k$ as ``not us''.
-Neither Model~3 nor Model~4 improved upon the out-of-sample predictions of Model~0, showing that more inclusive identities neither increased nor decreased participants' perceptions of (dis-)advantages for ethnoreligious an caste outgroups.
-% Overall, Models~1 to 4 did not provide evidence for the solidarity hypothesis or, more specifically, for the solidarity-by-inclusion hypothesis.
-
-Models~5 to 8 tested to what extent contact with (Models~5, 6) and inclusion of advantaged-group members (Models~7, 8) was associated with perceptions of (dis-)advantage for the ingroup.
-Model~5 estimated how contact with General Merit people affected Scheduled Caste~/ Scheduled Tribe participants' perceptions of (dis-)advantage for their ingroup: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{OF,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{OF,GM,j} + \beta_\text{NC,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{NC,GM,j} $$ where $x_{\text{IG},jk}$ codes whether target group $k$ is an ingroup [1] or outgroup [0] for participant $j$, $x_{\text{SCST,j}}$ codes whether participant $j$ is from an Scheduled Caste~/ Scheduled Tribe background [1] or not [0], $x_\text{OF,j,GM}$ and $x_\text{NC,j,GM}$ are, respectively, participant $j$'s outgroup friendship and negative contact with General Merit people, and $\beta_\text{OF,GM}$ and $\beta_\text{NC,GM}$ estimate the increase in participants' ratings for each additional standard deviation of reported contact with General Merit people.
-Model~6 extended Model~5 by estimating how contact with General Merit people affected Other Backward Class participants' perceptions of (dis-)advantage for their ingroup: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \ldots + \beta_\text{OF,GM}x_{\text{IG,jk}}x_{\text{OBC,j}}x_\text{OF,GM,j} + \beta_\text{NC,GM}x_{\text{IG,jk}}x_{\text{OBC,j}}x_\text{NC,GM,j} $$ where $x_{\text{OBC,j}}$ codes whether participant $j$ is from an Other Backward Class background [1] or not [0].
-Neither Model~5 nor Model~6 improved upon the out-of-sample predictions of Model~0, showing that intergroup contact with advantaged-group members did not increase or decrease disadvantaged-group members' perceptions of (dis-)advantage for their ingroup.
-Model~7 estimated whether including General Merit targets in their ingroup reduced perceptions of (dis-)advantage among Scheduled Caste~/ Scheduled Tribe participants: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{Q1,GM,j} $$ where $x_{Q1,GM,j}$ is the proportion [0--1] of General Merit targets that participant $j$ categorized as ``us'', and $\beta_{Q1,GM}$ estimates the difference in perceived (dis-)advantage between participants who categorized all four General Merit targets as ``us'' and participants who categorized all General Merit targets as ``not us''.
-Model~8 extended Model~7 by estimating this relationship among Other Backward Class participants: $$ \mu_{ij} = \beta_{j} + \beta_{kl} + \beta_\text{Q1,GM}x_{\text{IG,jk}}x_{\text{SCST,j}}x_\text{Q1,GM,j} + \beta_\text{Q1,GM}x_{\text{IG,jk}}x_{\text{OBC,j}}x_\text{Q1,GM,j} $$ where $x_{\text{OBC,j}}$ codes whether participant $j$ is from an Other Backward Class background [1] or not [0].
-Neither Model~7 nor Model~8 improved upon Model~0, showing that including advantaged-group members in the ingroup did not increase or decrease disadvantaged-group members' perceptions of their ingroup's disadvantage (see Table~\ref{tab:d-2}).
-
-\begin{table}
-\centering
-\figureversion{lining, tabular}
-\caption{
-Comparison of models estimating participants' group-wise perceived life difficulty ratings.
-We preferred a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.
-}
-\small	
-\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrr} \toprule
-\# &  &  Description & $R^2$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule \addlinespace
-0 &      & \textit{Group differences} & .35 & -1789.5 & 24.6 & - & - & - & .00 \\ \addlinespace
-1 & vs 0 & \textit{Solidarity}       & .35 & -1791.2 & 24.5 & -1.8 & 1.5 & -1.2 & .00 \\
-2 & vs 1 & \textit{Solidarity}       & .35 & -1788.3 & 24.4 & 3.0 & 2.5 & 1.2 & .33 \\
-3 & vs 0 & \textit{Solidarity}       & .35 & -1787.0 & 24.7 & 2.5 & 2.4 & 1.0 & .32 \\
-4 & vs 3 & \textit{Solidarity}       & .35 & -1787.6 & 24.7 & -0.7 & 2.4 & -0.3 & .23 \\ \addlinespace
-5 & vs 0 & \textit{(De)mobilization} & .35 & -1791.5 & 24.6 & -2.0 & 1.2 & -1.7 & .00 \\
-6 & vs 5 & \textit{(De)mobilization} & .35 & -1792.6 & 24.6 & -1.1 & 0.9 & -1.2 & .00 \\
-7 & vs 0 & \textit{(De)mobilization} & .35 & -1788.9 & 24.5 & 0.5 & 1.4 & 0.4 & .00 \\
-8 & vs 7 & \textit{(De)mobilization} & .35 & -1788.4 & 24.5 & 0.5 & 1.4 & 0.4 & .12 \\ \addlinespace \bottomrule
-\end{tabularx}
-\label{tab:e-2}
-\end{table}
-
-\begin{table}
-\centering
-\figureversion{lining, tabular}
-\caption{Comparison of models estimating participants' group-wise policy support ratings.
-As in Table~\ref{tab:d-2}, we preferred a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.}
-\small	
-\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrr} \toprule
-\# &  &  Description & $R^2$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule \addlinespace
-0 &      & \textit{Group differences} & .49 & -1741.0 & 26.8 & - & - & - & .00 \\ \addlinespace
-1 & vs 0 & \textit{Solidarity}       & .50 & -1736.1 & 26.7 &  4.9 & 2.7 & 1.8 & .60 \\
-2 & vs 1 & \textit{Solidarity}       & .50 & -1739.9 & 26.8 &   -3.8 & 2.0 & -1.9 & .00 \\
-3 & vs 0 & \textit{Solidarity}       & .49 & -1741.0 & 26.9 & 0.0 & 0.7 & 0.0 & .00 \\
-4 & vs 3 & \textit{Solidarity}       & .49 & -1741.6 & 26.9 &  -0.6 & 1.1 & -0.5 & .00 \\ \addlinespace
-5 & vs 0 & \textit{(De)mobilization} & .49 & -1742.0 & 26.9 & -0.9 & 1.7 & -0.5 & .03 \\
-6 & vs 5 & \textit{(De)mobilization} & .49 & -1743.3 & 26.9 & -1.3 & 0.8 & -1.6 & .00\\
-7 & vs 0 & \textit{(De)mobilization} & .49 & -1741.6 & 26.8 & -0.6 & 0.8 & -0.8 & .00\\
-8 & vs 7 & \textit{(De)mobilization} & .50 & -1740.0 & 26.8 &  1.6 & 2.0 & 0.8 & .37 \\ \addlinespace \bottomrule
-\end{tabularx}
-\label{tab:e-3}
-\end{table}
-
-Second, we estimated participants' responses to each of five policy support items, with Scheduled Caste and Scheduled Tribe (SC/ST), Other Backward Class (OBC), and Muslims as target groups.
-Model~0 estimated item responses as varying across participants and target groups, and estimated differences across participants' ingroups: $$ \mu_{ij} = \beta_{j} + \beta_{kl} $$ where $\mu_{ij}$, the estimated mean response to item $i$ by participant $j$, equals $\beta_j$, the varying intercept for participant $j$, plus $\beta_{kl}$, the varying intercept for target group~$k$ ($1 = \text{SC/ST}$, $2 = \text{OBC}$, $3 = \text{Muslims}$) and ingroup~$l$ ($1 = \text{GM}$, $2 = \text{OBC}$, $2 = \text{SC/ST}$).
-Model~0 thus resembled the multivariate model estimated in the previous section.
-Models~1 to 8 were identical to the models for perceived discrimination (described above).
-Models~1 to 4 did not improve upon the out-of-sample predictions of Model~0, showing that neither intergroup contact (Models~1, 2) nor inclusive identities (Models~3, 4) foster support for policies benefiting a disadvantaged outgroup.
-Models~5 to 8 did not improve upon the out-of-sample predictions of Model~0, showing that neither contact with (Models~5, 6) nor inclusion of (Models~7, 8) General Merit people affected Scheduled Caste~/ Scheduled Tribe and Other Backward Class participants' support for policies benefiting their ingroups (see Table~\ref{tab:e-3}).
-
-Overall, these findings show that neither intergroup contact nor ingroup construals could explain individual differences in support for social change.
-Contrary to the \emph{demobilization hypothesis}, positive contact did not decrease disadvantaged-group participants' support for social change.
-Contrary to the \emph{mobilization hypothesis}, negative contact did not increase disadvantaged-group participants' support for social change.
-Contrary to predictions, neither positive contact nor more inclusive identities were associated with support for policies benefiting (other) disadvantaged outgroups.
-
-\section{Appendix F: Additional Measures}
-
-We included additional measures to validate the triple crossed-categorization task and to replicate earlier research.
-We tested to what extent various social identity measures correlated with responses in the triple crossed-categorization task.
-We also assessed Karmic beliefs to replicate \citeauthor{cotterill_ideological_2014}'s \citeyear{cotterill_ideological_2014} finding that Karmic beliefs mediate the relationship between social dominance orientation and support for hierarchy-enhancing policies.
-We do not report results from this replication here, but make all data available online.
-
-\subsection{Measures}
-
-Group identification was measured with one item per ingroup \cite{postmes_single_2013}: ``I identify with my [nationality/religion/caste group]'' ($1 = \textit{strongly disagree}$, $7 = \textit{strongly agree}$).
-
-Social identity complexity \cite{roccas_social_2002, schmid_antecedents_2009} was operationalized as the extent to which participants perceived their different group memberships as conceptually interrelated (\emph{similarity complexity}) and numerically overlapping (\emph{overlap complexity}).
-Two items measured similarity complexity for religion/nationality and for nationality/caste: ``How similar or different are the typical [Hindu/Indian] and the typical [Indian/person from your caste group] to each other?'' ($1 = \textit{very different}$, $5 = \textit{very similar}$, reverse coded), and ``Do you think that being [Hindu/Indian] means the same as being [Indian/from your caste group]?'' ($1 = \textit{means something very similar}$, $5 = \textit{means something very different}$).
-Two items measured overlap complexity for religion/nationality: ``How many [Indians/ Hindus] do you think are [Hindus/Indian]?” (\%, $r = .63$).
-Three items measured overlap complexity for nationality and caste: ``How many Indians do you think are [GC, OBC, SC/ST]?'' (\%, $.33 \leq rs \leq .50$).
-Overlap items were reverse coded, so that higher scores indicated less perceived overlap.
-
-\emph{Entitativity} \cite{lickel_varieties_2000} was measured with six items: ``Being Indian is important to each Indian, no matter their caste or religion'', ``Indians of all castes and religions interact often with each other.'', ``Indians of all castes and religions are working towards shared goals'', ``What happens to one Indian also impacts other Indians'', ``Indians of all castes and religions depend on one another'', and ``Indians are similar to one another'' ($1 = \textit{strongly disagree}$, $7 = \textit{strongly agree}$, $\alpha = .80$).
-Participants were encouraged to ``take Indian/Indians to mean Indian citizens of all castes and religions'' when reading the items of this scale.
-This scale thus measured an inclusive conception of entitativity.
-
-\emph{Karmic beliefs} \cite{cotterill_ideological_2014} were measured with three items: ``my current caste group position reflects
-my actions or deeds in my past life'', ``if I do good deeds in my current life they will positively influence my caste status in my future life'', and ``the caste group position I was born into reflects the Karma of my past life'' ($1 = \textit{strongly disagree}$, $7 = \textit{strongly agree}$).
-
-\subsection{Correlates of categorization}
-
-We explored how participants' responses in the triple crossed-categorization task related to other measures of social identification.
-To that end, we estimated the correlations between, on the one hand, the proportions of targets that participants had categorized as ``us'' in each of the six categories, and, on the other hand, the (aggregated) social identification variables described in the \emph{Measures} section.
-We derived the likelihood of the observed responses from a multivariate normal distribution: $$ \textbf{Y} \sim \text{MVNormal} (\mu , \textbf{S} ) $$ where $\textbf{Y}$ is the matrix of observed variable scores (columns) across participants (rows), $\mu$ is the vector of all variable means, and $\textbf{S}$ is the variance-covariance matrix across variables.
-
-Figure~\ref{fig:f-1} shows the estimated correlations between participants' categorizations in the triple crossed-categorization task (from left to right) and various social identification variables (from top to bottom).
-Entitativity---the extent to which participants saw Indians of \emph{all} castes and religions as similar to one another, as depending on each other, as sharing a common fate, as working towards shared goals, and as valuing their shared identity---was positively correlated with the proportion of \emph{Indian, Hindu, GM} ($r = .16$, $[.04, .27]$, $\text{Pr} (r > 0|M) > .99$), \emph{Indian, Hindu, OBC} ($r = .21$, $[.09, .31]$, $\text{Pr} (r > 0| M) > .99$), \emph{Indian, Hindu, SC/ST} ($r = .10$, $[-.02, .22]$, $\text{Pr} (r > 0| M) = .97$), and \emph{Indian, Muslim, OBC} ($r = .18$, $[.07, .30]$, $\text{Pr} (r > 0| M) > .99$) targets participants categorized as ``us''.
-
-\begin{figure}
-\centering
-\includegraphics{../figures/appendices/appendices-e-1}
-\caption[Correlations between social identity variables and target categorizations]{Correlations between various social identity variables (top to bottom) and the proportion of targets that participants had categorized as ``us'' in each target category (left to right).
-Points indicate the most likely estimate for a given correlation, while lines encompass the 97\% most likely estimates of that correlation.
-Curves show the density distributions of the posterior probabilities, based on all samples from the posterior probability distribution.
-Correlations for which $\text{Pr} (r > 0| M) > .99$ or $\text{Pr} (r < 0| M) > .99$ are shown in a darker shade.}
-\label{fig:f-1}
-\end{figure}
-
-Group identification was only associated with participants' categorizations of foreign targets, not their categorizations of Indian targets.
-The extent to which participants identified with their religion was negatively correlated with how many \emph{foreign, Hindu} ($r = -.14$, $[-.25, -.02]$, $\text{Pr} (r > 0| M) > .99$) and \emph{foreign, Muslim} ($r = -.18$, $[-.29, -.07]$, $\text{Pr} (r > 0| M) > .99$) targets participant categorized as ``us''.
-I obtained similar correlations for the extent to which participants identified with their caste group, $r = -.15$, $[-.27, -.04]$, $\text{Pr} (r > 0| M) > .99$ and $r = -.17$, $[-.29, -.06]$, $\text{Pr} (r > 0| M) > .99$, respectively.
-The extent to which participants identified with their nationality was not associated with participants' categorizations---perhaps because there was a little variation in participants responses, with 81\% of participants strongly agreeing with the statement.
-Other variables were not systematically correlated with participants' responses in the crossed-categorization task (see Figure~\ref{fig:e-1}).
-
-Correlations thus confirmed that participants' categorizations were more than a straight-forward reflection of the strength of their group identification, affirming the value of the crossed-categorization task for studying identification in contexts with multiple, cross-cutting group memberships.
-Furthermore, participants' perceptions of entitativity across caste and religions were associated with more inclusive construals of national identity, providing tentative evidence for its potential for fostering more inclusive identities.
-
-\bibliographystyle{apacite}
-\bibliography{references}
+\printbibliography
 

### 2020-04-25 manuscript/manuscript.tex
resubmit

--- 2018-11-09 manuscript/manuscript.tex
@@
 \usepackage[utf8]{inputenc}
-
-% Format
-\setlength{\parindent}{0.5in}
-\setcounter{secnumdepth}{0}
-\usepackage[pagewise]{lineno}
-%\usepackage{authblk}
 
@@
 \usepackage[super]{nth}
+\usepackage{csquotes}
+
+% Format
+\setlength{\parindent}{0.5in}
+\setcounter{secnumdepth}{0}
+
+% Language
+\usepackage[american]{babel}
 
@@
 \usepackage[colorlinks=true, linkcolor=black, urlcolor=black, citecolor=black]{hyperref}
-
-% Language
-\usepackage[british]{babel}
-
-% References
-\usepackage[nosectionbib, bibnewpage, tocbib, unnumberedbib]{apacite}
 
@@
 
-% Commands
-\newcommand{\pest}[4]{$ \text{Pr} (\text{``us''} | \text{#1}) = #2$, $[#3, #4]$}
-\newcommand{\pdif}[4]{$ \Delta\text{Pr} (\text{``us''} | \text{#1}) = #2$, $[#3, #4]$}
+% References
+\usepackage[style=apa]{biblatex}
+\DeclareSourcemap{
+  \maps[datatype=bibtex]{
+    \map{
+      \pertype{book}
+      \step[fieldset=location, null]
+      \step[fieldset=address, null]
+    }
+    \map{
+      \pertype{incollection}
+      \step[fieldset=location, null]
+      \step[fieldset=address, null]
+    }
+  }
+}
+\addbibresource{references.bib}
+\renewcommand*{\bibfont}{\small}
 
 % Frontmatter
-\title{Intergroup contact fosters\\more inclusive social identities}
-\date{November 5, 2018}
+\title{Intergroup contact fosters\\more inclusive social identities\thanks{Reimer, N.
+K., Kamble, S.
+V., Schmid, K., \& Hewstone, M.
+(in press).
+Intergroup contact fosters more inclusive social identities.
+\textit{Group Processes \& Intergroup Relations}.
+\href{https://doi.org/10.31234/osf.io/zcgwt}{https://doi.org/10.31234/osf.io/zcgwt}}}
+\date{April 6, 2020}
 
@@
 South Indian participants ($N = 351$) from diverse caste backgrounds viewed 24 identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships (caste, religion, nationality).
-Participants judged each person as ``us'' or ``not us'', showing whom they included in their ingroup, and whom they excluded.
+Participants judged each person as “us” or “not us”, showing whom they included in their ingroup, and whom they excluded.
 Participants tended to exclude caste and religious minorities, replicating persistent social divides.
-Bridging these divides, cross-group friendship was associated with more inclusive identities which, in turn, were associated with more favourable outgroup attitudes.
-Negative contact was associated with less inclusive identities, showing that past experiences shaped whom participants considered ``us'' or ``not us''.
-Contact and identity processes were unrelated to support for affirmative action in advantaged and disadvantaged caste groups.\\[1ex]
-\noindent \textbf{Keywords:} intergroup contact, social identity, multiple categorization, intergroup relations, affirmative action \\[1ex]
+Bridging these divides, cross-group friendship was associated with more inclusive identities which, in turn, were associated with more positive relations between an advantaged, an intermediate, and a disadvantaged caste group.
+Negative contact was associated with less inclusive identities.
+Contact and identity processes, however, did not affect entrenched opposition to (or undermine support for) affirmative action in advantaged and disadvantaged groups.\\[1ex]
+\noindent {\footnotesize \textbf{Keywords:} intergroup contact, social identity, multiple categorization, intergroup relations, interminority relations, perceived discrimination, affirmative action}
 \end{abstract}
 
-\linenumbers
-
-\noindent How we feel about and act toward others depends on whom we consider ``us'' and ``them''---that is, whom we include in, and exclude from, our ingroup (for a review, see \citeNP{authors_theories_inpress}).
-In some situations, this distinction rests on one salient categorization, for example, someone’s nationality at an international border.
+\noindent How we feel about and act toward others depends on whom we consider “us” and “them”---that is, whom we include in, and exclude from, our ingroup (for a review, see \nptextcite{reimer_self-categorization_2020}).
+In some situations, this distinction rests on one salient categorization, for example, someone's nationality at an international border.
 In diverse societies, however, this distinction often depends on multiple, overlapping group memberships.
 Individuals differ in how they construct their ingroup from these group memberships.
-Some espouse narrow definitions of who is ``us'' and ``them'', while others adopt more inclusive identities (see Figure~\ref{fig:f1}).
-Many Americans, for example, associate being American with being White American \cite{devos_american_2005}.
-This suggests that whom Americans consider ``us'' and ``them'' might depend on someone's race \emph{and} nationality.
-In this paper, we examine how group memberships shape whom people consider ``us'' and ``not us'', and whether intergroup contact can reduce prejudice by fostering inclusive social identities.
+Some espouse narrow definitions of who is “us” and “them”, while others adopt more inclusive identities.
+Many Americans, for example, associate being American with being White American \parencite{devos_american_2005}.
+This suggests that whom Americans consider “us” and “them” might depend on someone's race \emph{and} nationality.
+In this paper, we examine how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce prejudice by fostering more inclusive social identities.
+We use a novel method to study social identification across multiple social categories and to examine possible antecedents (intergroup contact, social dominance orientation) and consequences (intergroup attitudes, intergroup threat, support for affirmative action) of more inclusive identities.
 
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \caption{
-Schematic representations of social identity structures, ordered by social identity inclusiveness \protect\fullcite{dommelen_construing_2015}.
-Shaded regions represent the groups which a participant has to categorize as ``us'' to be assigned that structure.
-An Indian Hindu, for example, may consider only people who share their nationality, religion, and caste as ingroup members (intersection).
-Someone else may consider all their fellow Indians, whatever their religion or caste, as ingroup members (dominance).
-Another person may consider anyone who shares their nationality or religion as ingroup members (merger).
+Schematic representations of social identity structures \protect\parencite{roccas_social_2002}, ordered by their social identity inclusiveness \protect\parencite{van_dommelen_construing_2015}.
+Shaded regions represent the groups which a participant has to categorize as “us” to be assigned that structure.
+An Indian Hindu, for example, might consider only people who share their nationality, religion, and caste as ingroup members (\emph{intersection}).
+Someone else might consider all their fellow Indians, whatever their religion or caste, as ingroup members (\emph{dominance}).
+Another person might consider anyone who shares their nationality or religion as ingroup members (\emph{merger}).
 }
 \label{fig:f1}
-\end{figure}
+\end{figure*}
 
-Social psychologists have argued for the importance of considering two \cite{berry_immigration_1997, crisp_multiple_2007, dovidio_commonality_2009} or more \cite{roccas_social_2002} social categories for understanding intergroup relations.
-Broadly, these perspectives recognise that we are part of multiple overlapping groups; that we have a subjective sense of who is ``us'' and ``them'' that goes beyond the objective facts of group membership; and that identification across multiple categories affects our attitudes toward people with whom we share some, but not all, group memberships.
-However, these perspectives have lacked methods for measuring identification across multiple categories.
-Our research uses a novel method for studying subjective identity construals, as well as their antecedents (intergroup contact) and consequences (outgroup attitudes, intergroup threat, policy support).
+Social psychologists highlighted the importance of considering two \parencite{berry_immigration_1997, crisp_multiple_2007, dovidio_commonality_2009} or more \parencite{roccas_social_2002} social categories for understanding intergroup relations.
+\textcite{crisp_multiple_2007} reviewed evidence that we tend to have more favourable attitudes towards people with whom we share some, but not all, group memberships than towards people with whom we do not share any group memberships.
+\textcite{gaertner_reducing_2000} showed that espousing a more inclusive common ingroup identity (e.g., Indian) over a narrower identity (e.g., Hindu, Muslim) can extend the benefits of ingroup favouritism to outgroup members and thus reduce intergroup bias.
+\textcite{roccas_social_2002} recognized that, though we all hold multiple overlapping group memberships, we differ in how we construct our social identities from these group memberships.
+Broadly, these perspectives recognize that we are part of multiple overlapping groups; that we use these group memberships to construct a subjective sense of who is “us” and “them”; and that espousing more inclusive social identities can reduce prejudice and discrimination.
 
-Past research \shortcite{dommelen_construing_2015} studied whom individuals considered ``us'' and ``not us'', and observed substantial individual differences in how inclusive participants' social identities were.
-In this research, all participants belonged to the same groups.
-Group memberships, however, likely influences whom people consider ``us'' and ``not us''.
-For majority-group members, negotiating their ethnic and national identities means something different than for minority-group members \cite{dovidio_commonality_2009}.
-We expect that group differences are as great as, if not greater than, individual differences in social identity construals---especially if groups differ in status and power.
-Our research includes participants from diverse backgrounds to estimate these group differences.
+Diverse societies confront their members with the decision of which intersections of various group memberships to include in their subjective ingroup.
+One Indian Hindu, for example, might constrict their ingroup to people of the same nationality, religion, and caste.
+Another Indian Hindu might consider all Indians, whatever their religion or caste, as ingroup members (see Figure~\ref{fig:f1}).
+Past research \parencite{van_dommelen_construing_2015} indeed observed substantial individual differences in whom participants considered “us” and “not us”.
+Some participants espoused more inclusive social identities---that is, they included more people in their subjective ingroup.
+Other participants espoused less inclusive social identities---that is, they included fewer people in their subjective ingroup.
+All participants, however, belonged to the same disadvantaged minority group.
+Past research thus provided evidence for individual differences, but did not examine group differences in whom people consider “us” and “not us”.
 
-Contact experiences could overcome group differences in social identity construals.
-Encountering diverse others could initiate a process of cognitive differentiation \cite{schmid_social_2011} whereby individuals become aware of complex interrelations between their group memberships, and thus start to question narrow identity construals.
-Further, positive intergroup interactions motivate people to include the outgroup of an interaction partner in their self-concept \cite{page_understanding_2010}.
-If contact motivates people to include partial outgroups in the self, it should encourage social identities that include the interaction partner's combination of group memberships.
-Together, these mechanisms suggest that contact could foster more inclusive identities.
-
-Fostering more inclusive identities, in turn, could reduce intergroup bias.
-Dividing others into ``us'' and ``not us'' is a necessary and sufficient condition for ingroup favouritism \cite{tajfel_human_1981}.
-Considering more people as ``us'' should extend ingroup favouritism to a wider range of people, and thus reduce discrimination \cite{gaertner_common_2016}.
-Ingroup favouritism can turn into outgroup derogation when an outgroup threatens the ingroup \cite{brewer_psychology_1999}.
-Considering fewer people as ``not us'' should reduce the number of groups which are perceived to threaten the ingroup.
-Together, these mechanisms suggest that fostering inclusive identities could improve outgroup attitudes and reduce intergroup threat.
-
-Beyond prejudice, researchers have debated whether fostering inclusive identities helps or hinders social change.
-Social change often requires advantaged and disadvantaged groups to strive for redistributive policies.
-On the one hand, fostering inclusive identities could break down the boundaries between the advantaged ingroup and the disadvantaged outgroup---turning injustice faced by ``them'' into ``our'' problem.
-This process could narrow the gap between advantaged-group members' support for the principle of equality and their opposition to its implementation \cite{dixon_intergroup_2007}.
-On the other hand, fostering more inclusive identities could distract disadvantaged-group members from differences in resources and power, and thus reduce their support for social change \cite{dovidio_darker_2012}.
-Together, these mechanisms suggest that more inclusive identities could increase support for social change among the advantaged, but decrease support among the disadvantaged.
-
-\subsection{Caste, Religion, Nation in South India}
-
-We tested these predictions among South Indian students, examining the cross-cutting categories of caste, religion, and nationality.
-Caste is a system of social relations that concentrates resources in the hands of dominant castes by restricting subordinate castes' occupations and land ownership, and by enforcing endogamy and segregation \cite{jodhka_caste_2012}.
-This system is underpinned by a tradition that ranks castes according to their supposed ritual purity, and condemns contact with less pure castes.
-Since Independence, the Indian State has sought to redress caste-based injustices by enforcing `reservations' of seats in state-run universities and state-sector jobs for disadvantaged groups.
-It recognises Dalits---members of castes affected by untouchability---as Scheduled Castes (SCs), Adivasi---India's indigenous peoples---as Scheduled Tribes (STs), and other disadvantaged groups---who occupy an intermediate position in the caste hierarchy---as Other Backward Classes (OBCs).
-Historically advantaged castes do not have access to reservations (GM: General Merit).
-Reservation policies, alongside ongoing discrimination, mean that caste identities remain important.
-
-South India is religiously diverse.
-In Karnataka, where we conducted this research, 84\% of inhabitants are Hindus, while 13\% are Muslims.
-Muslims face both structural inequalities and communal violence.
-In 2002, for example, a pogrom killed over a thousand Muslims in Gujarat \cite{dhattiwala_political_2012}.
-In recent years, anti-Muslim violence has been increasing \cite{amnesty_india_2017}.
-Religion is intertwined with two currents of Indian nationalism \cite{menski_hindu_2009}.
-On the one hand, the secular foundations of the Indian State resulted from an inclusive nationalism that strives to include Indians of all religions.
-On the other hand, Hindu nationalism (Hindutva) is an ideology that equates being Indian with being Hindu, thus excluding Muslims from the national identity.
-Narendra Modi's BJP government espouses Hindutva, and enjoys broad support in the Indian population \cite{pew_three_2017}.
-
-\section{Present research}
-
-We examined how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce prejudice, and increase support for social change, by fostering more inclusive identities.
-Our research used a novel method to study social identification across multiple categories in a sample of South Indians from various caste backgrounds.
-
-First, we examined how participants' objective group memberships shaped their subjective construals of social identity.
-We hypothesised that participants would exclude targets from religious and national outgroups---and that participants from advantaged castes would exclude targets from disadvantaged castes, and vice versa.
-We did not have a clear prediction for participants from intermediate caste groups.
-Second, we tested potential antecedents of more inclusive social identities.
-We hypothesised that positive contact and cross-group friendship would be associated with more, and negative contact with less, inclusive identities.
-As an alternative hypothesis, we tested whether ideological preferences for social dominance \cite{sidanius_social_1999} could have motivated individuals to exclude lower-status outgroups.
-Third, we examined potential consequences of participants' identity construals.
-We hypothesised that categorizing someone as ``us'' would be associated with more favourable attitudes and less social distance toward that person.
-More broadly, we expected more inclusive identities to be associated with less perceived intergroup threat.
-We also tested whether more inclusive identities would be associated with increased support for affirmative action among advantaged-group members, but decreased support among disadvantaged-group members.
-
-We tested these predictions in a triple crossed-categorization task (adapted from \citeNP{dommelen_construing_2015}).
-In this task, participants viewed identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships.
-Participants reported whether they considered each person as ``us'' or ``not us'', showing whom they included in, or excluded from, their ingroup.
-This task thus measured how participants combined multiple group memberships to construct their social identities.
-We tested to what extent participants' responses were associated with past contact experiences, ideological preferences, and various outcome measures.
-
-\section{Method}
-
-All materials, data, analysis scripts, and appendices are available online (\href{https://osf.io/ekb8z/?view_only=05b6a5c5cf5e43d9a7bba5e192f53f87}{https://osf.io/ ekb8z/?view\_only=05b6a5c5cf5e43d9a7bba5e192f53f87}).
-Here, we only report measures testing our hypotheses, omitting measures replicating earlier research or validating the categorization task (Appendix~E).
-Reanalysing existing data \cite{dommelen_construing_2015}, we determined that $\sim$100 respondents per group would allow reasonably precise estimates of model parameters.\footnote{Models estimated posterior probabilities with precision $\textit{SD} < 0.5$ on the log odds scale.}
-
-\subsection{Participants}
-
-We recruited 351 students at Karnatak University (Dharwad, India).
-Of these, we excluded 49 participants who did not belong to any of four caste groups ($n = 20$), failed to indicate their caste group ($n = 7$), or reported Islam as their own or their family's religion ($n = 27$).\footnote{We excluded Muslim participants as this subsample was too small for meaningful analyses.} This left 302 participants who reported Hinduism ($n = 286$), Jainism ($n = 8$), or Christianity ($n = 8$) as their or their family's religion, and General Caste ($n = 99$), Other Backward Class ($n = 127$), Scheduled Caste ($n = 54$), or Scheduled Tribe ($n = 22$) as their caste group.
-Table~\ref{tab:t1} summarises participants by gender, age, nationality, religion, and caste.
-
-\begin{table}    
-\caption[Participants by gender, age, nationality, religion, and caste]{Participants by gender, age, nationality, religion, and caste.
-Categories in \textit{italics} were excluded from the final sample.
-N/A marks missing responses.}
-\centering
-\figureversion{lining, tabular}
-\small	
-\begin{tabular}{llrr} \addlinespace \toprule
-\multicolumn{2}{l}{Category} & $n$ & \% \\ \midrule \addlinespace 
-Gender      & Woman      & 215 & 61 \\
-            & Man & 121 & 34 \\
-            & Other & 0 & 0 \\
-            & N/A & 15 & 4 \\ \addlinespace \addlinespace
-Age         & 18--20 & 1 & 0 \\
-            & 21--23 & 254 & 72 \\
-            & 24--26 &  77 & 22 \\
-            & 27--29 &  10 &  3 \\
-            & 30--32 &   1 &  0 \\
-            & 33--35 &   0 &  0 \\
-            & 36 or older & 1 & 0 \\ 
-            & N/A & 7 & 2 \\ \addlinespace \addlinespace
-Nationality & Indian & 339 & 97 \\
-            & Other & 0 & 0 \\
-            & N/A & 12 & 3 \\ \addlinespace \addlinespace
-Religion    & Buddhism & 1 & 0 \\ 
-            & Christianity & 11 & 3 \\ 
-            & Hinduism & 297 & 85 \\ 
-            & \textit{Islam} & \textit{27} & \textit{8} \\ 
-            & Jainism & 8 & 2 \\ 
-            & Other & 2 & 1 \\ 
-            & N/A & 5 & 1 \\ \addlinespace \addlinespace
-Caste       & General Caste & 104 & 30 \\ 
-            & Other Backward Class & 143 & 41 \\ 
-            & Scheduled Caste & 54 & 15 \\ 
-            & Scheduled Tribe & 23 & 7 \\ 
-            & \textit{Other / Not applicable} & \textit{20} & \textit{6} \\ 
-            & \textit{N/A} & \textit{7} & \textit{2} \\ \addlinespace \midrule
-Total       &   & 351 & 100 \\ \bottomrule
-\end{tabular}
-\label{tab:t1}
-\end{table}
-
-\subsection{Procedure}
-
-Participants completed a triple crossed-categorization task, in which they viewed 24 identity cards.
-Each showed a fictitious person's name, age, religion, nationality, caste reservation, and a head-and-shoulders silhouette.
-Based on a pilot study, we manipulated the target's caste, religion, and nationality such that each target represented a person with whom participants shared none, one, two, or three group memberships (Figure~\ref{fig:f2}).
-We tested participants in classrooms of 24--71 students by presenting targets in a slide-based presentation.
-Each slide contained a male and a female target with participants focusing on the target corresponding to their gender.
-Slides also contained a number identifying each target, and the response scale(s) corresponding to the question(s) participants answered at the time.
-
-\begin{figure}
-\centering
-\includegraphics[scale=1]{../figures/figure-2}
-\caption{Examples of targets used in the triple crossed-categorization task.
-Based on ratings in a pilot study ($N = 26$), we selected the four most prototypical targets (out of fifty initial targets) for each of six plausible combinations of caste, religion, and nationality (for details, see Appendix~A).
-Each target showed a person's caste reservation (GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe), religion (Hindu, Muslim), and nationality (Indian, Nepali, Sri Lankan, Bangladeshi).
-Each target also showed the person's first and last name, age (21--26 years), and a silhouette corresponding to the person's gender (adapted from \protect\citeNP{ma_chicago_2015}).
-Each target's age and silhouette, as well as the order in which the targets were presented, varied across sessions.}
-\label{fig:f2}
-\end{figure}
-
-In each session, participants first familiarised themselves with each target (for 7s) in an automated slideshow.
-Participants viewed targets (in the same order) for a second time, noting for each target whether they felt that this person was one of their own group (1 = ``us''), or not one of their own group (0 = ``not us'').
-Participants viewed targets for a third time, rating how comfortable or uncomfortable they would feel to share a room with this person (social distance; $1 = \textit{very uncomfortable}$, $7 = \textit{very comfortable}$), and how they felt toward this person (feeling thermometer; $0 = \textit{cold}$, $\textit{100 = warm}$).
-Participants then completed a questionnaire containing the measures described below.
-
-\subsection{Measures}
-
-We measured intergroup contact as: how often, from $1 = \textit{never}$ to $5 = \textit{very often}$, participants meet outgroup members in their everyday life (contact quantity), and how often, on average, they have positive/good contact and negative/bad contact with outgroup members \cite{barlow_contact_2012}.
-We preceded these items with examples of positive and negative contact experiences.
-We measured cross-group friendship with two items \cite{turner_reducing_2007}: ``How many close friends do you have who are [outgroup members]?'' ($1 = \textit{none}$, $5 = \textit{more than ten}$), and ``How often do you spend time with [outgroup] friends?'' ($1 = \textit{never}$ to $5 = \textit{very often}$; $.47\leq\textit{rs}\leq.58$).
-Participants reported contact with four groups: Dalits, people from other backward classes, people from general castes, and Muslims.
-
-We measured social dominance orientation as how much, between $1 = \textit{strongly oppose}$ and $7 = \textit{strongly favour}$, participants endorsed eight statements about social hierarchies \cite{ho_nature_2015}.
-Four items measured support for group-based dominance (SDO-Dominance), e.g., ``some groups of people are simply inferior to other groups''.
-Four items measured opposition to egalitarian ideologies (SDO-Egalitarianism), e.g., ``it is unjust to try to make groups equal''.\footnote{Replicating \citeauthor{ho_nature_2015}’s \citeyear{ho_nature_2015} findings, we found a four-factor model (with two method factors) to represent the data better than the one-factor ($\Delta\chi^2 = 155.14$, $p < .001$) or two-factor ($\Delta\chi^2 = 138.67$, $p < .001$) alternatives.
-Accounting for this structure, we used latent factor scores for SDO-Dominance and SDO-Egalitarianism in our analyses.}
-
-We measured realistic threat---from Muslims and Dalits---with three items per outgroup \cite{schmid_reducing_2014}, e.g., ``the more power [Muslims/Dalits] gain in this country, the more difficult it is for [Hindus/people from my caste group]'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $\alpha_\textit{Muslims} = .71$, $\alpha_\textit{Dalits} = .79$).
-Two items measured symbolic threat, e.g., ``[Muslims/Dalits] threaten [Hindus'/my caste group's] way of life'' ($1 = \textit{strongly disagree}$, $5 = \textit{strongly agree}$; $r_\textit{Muslims} = .44$, $r_\textit{Dalits} = .48$).
-
-We measured perceived (dis-)advantage as how easy or hard participants thought it was, on average, for people from various groups to succeed in India today ($1 = \textit{very hard}$, $7 = \textit{very easy}$).
-Participants rated seven groups: People from your own background, Scheduled Caste, Scheduled Tribe, Other Backward Class, General Caste, Hindus, and Muslims.
-
-Five items measured policy support.
-Participants read that ``currently, 22.5\% of seats in central-government funded universities are reserved for Scheduled Caste and Scheduled Tribe students'', and that ``an additional 27.5\% of seats in central-government funded universities are reserved for students from Other Backward Classes''.
-Participants indicated to what extent they opposed or supported reservation in higher education for students from each group ($1 = \textit{strongly oppose}$, $5 = \textit{strongly support}$), and whether they thought that reservation in higher education for students from that group should increase, decrease, or remain unchanged ($1 = \textit{decrease a lot}$, $5 = \textit{increase a lot}$; $r_\textit{SC/ST} = .67$, $r_\textit{OBC} = .67$).
-Participants then read that ``no seats in central-government funded universities are reserved for Muslim students nationally, though some states have introduced quotas for Muslim students''.
-Participants indicated to what extent they opposed or supported reservation for Muslim students.
-
-\section{Results}
-
-We used the following analysis strategy: First, we estimated group differences in whom participants categorized as ``us'' and ``not us''.
-Second, we examined to what extent intergroup contact and ideological orientations explained individual differences in participants' categorizations.
-Third, we tested whether participants' categorizations were associated with their attitudes and beliefs.
-
-\subsection{Group differences}
-
-We compared \emph{how likely} participants were to categorize \emph{which} target as ``us'' versus ``not us''---and how that probability varied across targets' and participants' group memberships.\footnote{In Appendix~B, we report analyses using \citeauthor{dommelen_construing_2015}'s \citeyear{dommelen_construing_2015} operationalisation; they analysed \emph{which} and \emph{how many} targets participants included as distinct questions.}
-
-We estimated a series of Bayesian multilevel models in RStan \cite{rstan_package} with participants' target categorizations ($1 = \text{``us''}$, $0 = \text{``not us''}$) as outcome variable.
-Models derived the likelihood of the observed proportions of ``us'' categorizations from the Bernoulli likelihood with a logit link function.
-Models assigned weakly informative prior distributions to all fixed parameters \cite{gelman_prior_2017}.\footnote{Models assigned the following priors: $\beta \sim \text{Student}(2.5, 0, 1)$ for fixed effects, and $\sigma \sim \text{Cauchy}(0, 1)$ for standard deviations of varying effects.} Models used the non-centred parameterisation for all varying effects \cite{betancourt_hamilton_2015}.
-We compared models using stratified 10-fold cross-validation to estimate each model's out-of-sample predictive accuracy \shortcite{vehtari_practical_2017}.
-We selected more complex over simpler models when the difference in predictive accuracy was at least twice its standard error.
-
-Models~0 to 3 estimated the probabilities of ``us'' categorizations as varying between participants but fixed across target categories (M0), as varying across participants and target categories (M1), and tested whether SC/ST participants' categorizations of Indian targets differed from GM and OBC participants' (M2) and whether OBC participants’ categorizations differed from GM participants' (M3).
-Models~1 and 2, but not Model~3, made more accurate predictions than less complex models (Table~\ref{tab:t2}).
-This suggests that the targets' group memberships shaped participants' categorizations, and that GM and OBC participants' categorizations resembled each other but differed from SC/ST participants'.
-Below, we report median point estimates, with 97\% highest posterior density intervals \cite{coda_package}, from the model's posterior distribution.
-
-\begin{table}
-\caption{
-Comparison of models estimating the probability of participants categorizing targets as ``us'' versus ``not us''.
-$\textit{ELPD}$ is the expected log predictive density, with higher numbers indicating that a model is expected to make more accurate out-of-sample predictions \protect\fullcite{vehtari_practical_2017}.
-$\Delta\textit{ELPD}$ is the difference in $\textit{ELPD}$ between the current and previous model, with positive values indicating that the current model is expected to make more accurate out-of-sample predictions.
-We selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.
-$w$ are stacking weights based on the models' expected log predictive densities \protect\cite{yao_using_2018}.
-}
-\centering
-\figureversion{lining, tabular}
-\small
-\begin{tabularx}{\linewidth}{r@{~}rXrrrrrr} \toprule
-\# &  & Description & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule 
-0 &      & Intercept (Participant) & -4703.5 & 23.7 &     - &    - &    - & .00 \\ 
-1 & vs 0 & Intercept (Category)    & -3853.5 & 41.6 & 850.1 & 37.4 & 22.7 & .00 \\
-2 & vs 1 & Group differences (SC/ST)       & -3791.3 & 42.0 &  62.1 & 11.1 &  5.6 & .00 \\
-3 & vs 2 & Group differences (OBC)         & -3792.1 & 42.2 &  -0.8 &  3.6 & -0.2 & .07 \\ \midrule
-4 & vs 2 & Intergroup contact (4) & -3743.4 & 42.8 &  47.9 &  8.8 &  5.4 & .00 \\
-5 & vs 4 & Intergroup contact (2) & -3736.7 & 42.6 &   6.7 &  1.8 &  3.8 & .92 \\
-6 & vs 5 & Intergroup contact (2) & -3747.8 & 42.7 & -11.1 &  3.2 & -3.5 & .00 \\
-7 & vs 2 & Social dominance orientation & -3791.0 & 42.1 &   0.4 &  3.3 &  0.1 & .00 \\
-\bottomrule
-\end{tabularx}
-\label{tab:t2}
-\end{table}
-
-Figure~\ref{fig:f3} shows the estimated probabilities of General Merit (GM), Other Backward Class (OBC), and Scheduled Caste/Scheduled Tribe (SC/ST) participants categorizing a target as ``us''.
-Participants tended to define their ingroup in terms of nationality, though about half of the responses indicated more inclusive identities.
-Few participants considered Bangladeshi Muslims part of their ingroup, \pest{M2}{.17}{.14}{.21}.
-Roughly half of the participants included Sri Lankan and Nepali Hindus in their ingroup, \pest{M2}{.46}{.41}{.52}.
-Participants were thus more likely to include foreign targets when they were Hindu, \pdif{M2}{.29}{.25}{.34}.
-Still, GM/OBC and SC/ST participants were, respectively, $1.95$, $[1.73, 2.18]$ and $1.90$, $[1.71, 2.14]$ times more likely to categorize Indian, Hindu targets as ``us'' compared to foreign, Hindu targets.
-
-\begin{figure}
-\centering
-\includegraphics[scale=1]{../figures/figure-3}
-\caption{
-Estimated probability of participants categorizing a target as ``us'' versus ``not us'' by targets' nationality, religion, and caste (vertical), and participants' caste membership (horizontal).
-Dots (•) indicate the most plausible \emph{estimate} for a given target's probability of being included in participants' ingroup (in Model~2, Table~\ref{tab:t2}), while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most plausible estimates of that probability.
-Pluses (+) indicate the \emph{observed} proportion of participants who included a given target in their ingroup.
-Comparing predicted and observed proportion shows that the model represents the data reasonably well.
-GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
-}
-\label{fig:f3}
-\end{figure}
-
-As expected, participants' caste membership shaped how they categorized Indians of different castes and religions.
-Most GM and OBC participants included \emph{Hindu, GM} and \emph{Hindu, OBC} targets in their ingroup, \pest{M2}{.94}{.92}{.96} and \pest{M2}{.93}{.91}{.95}.
-Fewer GM and OBC participants categorized \emph{Hindu, SC/ST} targets as ``us'', \pest{M2}{.84}{.80}{.87}.
-They were least likely to categorize \emph{Muslim, OBC} targets as ``us'', \pest{M2}{.75}{.70}{.80}.
-Dalit/Adivasi (SC/ST) participants' responses differed from GM and OBC participants'.
-Almost all SC/ST participants included \emph{Hindu, SC/ST} targets in their ingroup, \pest{M2}{.97}{.95}{.99}.
-Fewer SC/ST participants included \emph{Hindu, GM} and \emph{Hindu, OBC} targets in their ingroup, \pest{M2}{.88}{.83}{.92} and  and \pest{M2}{.80}{.73}{.86}.
-SC/ST participants were less likely than others to include \emph{Muslim, OBC} targets as ``us'', \pest{M2}{.47}{.38}{.57}.
-These findings showed that participants from advantaged backgrounds tended to exclude targets from disadvantaged backgrounds (and vice versa), while all participants tended to exclude targets from the Muslim minority.
-
-\subsection{Individual differences}
-
-We examined to what extent individual differences in past experiences and ideological orientations explain why some participants excluded targets from caste and religious outgroups---and why others did not.
-
-Models~4 to 6 tested whether intergroup contact was associated with how participants categorized Indian targets of caste or religious outgroups.
-Model~4 extended Model~2 by including contact quantity, positive contact, negative contact, and outgroup friendship as predictors of participants' categorizations.
-Model~4 made more accurate predictions than Model~2.
-Negative contact ($e^\beta = 0.81$, $[0.72, 0.90]$) and outgroup friendship ($e^\beta = 1.50$, $[1.28, 1.72]$) were associated with participants' categorizations, but neither positive contact ($e^\beta = 1.01$, $[0.87, 1.16]$) nor contact quantity ($e^\beta = 0.99$, $[0.86, 1.15]$) were.
-Model~5 included only negative contact and outgroup friendship, and made more accurate predictions than Model~4.
-Model~6 estimated the relationships between contact and categorizations as varying across the four combinations of target caste and religion.
-Model~6 made less accurate predictions than Model~5.
-
-Figure~\ref{fig:f4} shows the estimated probabilities of participants categorizing targets as ``us'' as a function of contact experiences.
-Across targets and participants, the odds of categorizing an outgroup target as ``us'' were $e^\beta = 1.50$, $[1.32, 1.69]$ times higher for each additional standard deviation of outgroup friendship.
-These odds were $e^\beta = 0.81$, $[0.72, 0.90]$ times lower for each standard deviation of negative contact.
-This means, for example, that GM/OBC participants who reported ``never'' having any negative contact with Muslims were more likely to categorize Indian Muslims as ``us'' than participants who reported ``sometimes'' having negative contact, \pdif{M5}{.05}{.09}{.03}.
-GM/OBC participants who reported no friendships with Muslims were a lot less likely to include Indian Muslims in their ingroup than participants who had 2--5 Muslim friends with whom they ``sometimes'' spent time, \pdif{M5}{.18}{.12}{.24}.
-Contact experiences were thus associated with whom participants categorized as ``us'' and ``not us''.
-
-\begin{figure}
-\centering
-\includegraphics[scale=1]{../figures/figure-4}
-\caption{Estimated probability of participants categorizing a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship with the relevant groups (in Model~5, Table~\ref{tab:t2}).
-GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.}
-\label{fig:f4}
-\end{figure}
-
-Models~7 tested whether social dominance orientation was associated with participants' categorizations of targets from lower status outgroups.
-Model~7 found little evidence for associations between participants' categorizations and their SDO-Dominance scores ($e^\beta = 0.87$, $[0.69, 1.06]$) or SDO-Egalitarianism scores ($e^\beta = 0.98$, $[0.78, 1.21]$).
-Together, these findings show that group and individual differences explained whom participants included in their ingroup.
-As expected, past experiences with outgroup members explained why some participants included targets of (objective) caste or religions outgroups in their (subjective) ingroup, when others did not.
-In contrast, ideological orientations did not motivate participants to exclude lower-status groups.
-
-\subsection{Consequences}
-
-We analysed how participants' categorizations related to their feeling thermometerhttps://www.dur.ac.uk/jobs/recruitment/vacancies/psyc18-10/Over and social distance ratings for each target in the categorization task, to intergroup threat, and to their perceived (dis-)advantage and policy support.
-
-We estimated multivariate models with participants' target-wise social distance and feeling thermometer ratings as outcome variables (Table~\ref{tab:t3}).
-Models~0 to 3 estimated ratings (on either outcome) as varying between participants but fixed across targets (M0), as varying across participants and targets (M1), and tested whether SC/ST participants' responses differed from GM and OBC participants' (M2), and whether OBC participants' responses differed from GM participants (M3).
-Models~1 to 3 improved upon the predictions of simpler models, showing that participants' ratings depended on targets' and participants' group memberships.
-
-\begin{table}
-\caption{Comparison of models estimating participants' social distance (SD) and feeling thermometer (FT) ratings for each target as a function of group differences and target categorizations.
-As in Table~\ref{tab:t2}, we selected a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.
-$R^2$ is a Bayesian analogue to $R^2$ in maximum likelihood estimation \protect\fullcite{gelman_rsquared_2017}.}
-\centering
-\figureversion{lining, tabular}
-\small	
-\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrrr} \toprule
-\# &  & Description & $R^2_\text{SD}$ & $R^2_\text{FT}$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule 
-0 &      & Participant & .23 & .26 & -16964 & 71.0 & - & - & - & .12 \\
-1 & vs 0 & Category & .38 & .42 & -16338 & 79.6 & 626.8 & 40.2 & 15.6 & .02 \\
-2 & vs 1 & SC/ST    & .38 & .43 & -16317 & 79.6 &  20.1 &  9.8 &  2.1 & .00 \\
-3 & vs 2 & OBC      & .39 & .43 & -16293 & 80.5 &  24.2 &  9.7 &  2.5 & .00 \\ \midrule
-4 & vs 3 & Categorization    & .42 & .47 & -16028 & 83.5 & 264.8 & 24.5 & 10.8 & .19 \\
-5 & vs 4 & \ldots~(Category) & .42 & .47 & -16007 & 83.6 &  21.1 &  8.7 &  2.4 & .67 \\
-6 & vs 5 & \ldots~(Ingroup)  & .42 & .47 & -16025 & 84.3 & -17.4 &  5.9 & -3.0 & .00 \\
-\bottomrule    
-\end{tabularx}
-\label{tab:t3}
-\end{table}
-
-Models~4 to 6 tested whether participants who categorized a target as ``us'' rated that target more favourably than participants categorizing the same target as ``not us''.
-Models estimated this difference as constant across targets and participants (M4), as varying across target categories (M5), and tested whether this difference depended on participants' caste memberships (M6).
-Models 4 and 5, but not Model 6, made better predictions than less complex models, showing that how favourably participants felt toward a target depended on whether they had categorized that target as ``us'' or ``not us'', and that the size of this difference depended on the targets'---but not the participants'---group memberships.
-
-Figures~\ref{fig:f5} and \ref{fig:f6} show, respectively, the estimated social distance and feeling thermometer ratings as a function of target categorizations and participants' caste memberships.
-For all categories, participants felt more comfortable sharing a room with targets that they categorized as ``us'' than with targets they categorized as ``not us''.
-This difference was smallest for \emph{Indian, Hindu, GM} targets ($\beta = 0.55$, $[0.19, 0.90]$; $d = 0.24$, $[0.08, 0.39]$) and greatest for \emph{foreign, Muslim} targets ($\beta = 1.46$, $[1.21, 1.70]$; $d = 0.63$, $[0.52, 0.73]$).
-We found a similar pattern for feeling thermometer ratings.
-The difference was smallest for \emph{Indian, Hindu, OBC} targets ($\beta = 6.5$, $[2.1, 11.0]$, $d = 0.20$, $[0.06, 0.33]$) and greatest for \emph{foreign, Hindu} targets ($\beta = 21.8$, $[18.6, 25.0]$, $d = 0.66$, $[0.56, 0.76]$).
-Feeling thermometer and social distance ratings were highly correlated ($r = .58$, $[.56, .60]$).
-Categorizing a target as ``us'' was thus associated with more warmth and less social distance toward that target.
-
-\begin{figure}
-\centering
-\includegraphics[scale=1]{../figures/figure-5}
-\caption{
-Posterior probabilities of social distance ratings as a function of target categorizations (in Model~5, Table~\ref{tab:t3}).
-Points are the estimated mean ratings for targets categorized as ``us''; triangles are the estimated mean ratings for targets categorized as ``not us''.
-GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
-}
-\label{fig:f5}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[scale=1]{../figures/figure-6}
-\caption{
-Posterior probabilities of feeling thermometer ratings as a function of target categorizations (in Model~5, Table~\ref{tab:t3}).
-Points are the estimated mean ratings for targets categorized as ``us''; triangles are the estimated mean ratings for targets categorized as ``not us''.
-GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
-}
-\label{fig:f6}
-\end{figure}
-
-Next, we tested whether participants' perceptions of realistic and symbolic threat depended on how inclusive their identity construals were.
-Results from a series of multilevel models showed that participants reported more realistic ($M = 3.62$, $[3.49, 3.75]$) than symbolic ($M = 3.21$, $[3.09, 3.33]$) threat from (same-religion) Dalits, but more symbolic ($M = 3.47$, $[3.34, 3.61]$) than realistic ($M = 3.23$, $[3.06, 3.38]$) threat from (different-religion) Muslims.
-Contrary to predictions, we did not find that participants felt less threatened by Muslims and Dalits if they categorized more targets from these outgroups as ``us''.
-For details, see Appendix~C.
-
-Finally, we estimated group differences in perceived (dis-)advantage and policy support.
-Figures~\ref{fig:f7} and \ref{fig:f8} show the estimated group differences in both outcomes.
-Contradicting prevailing social inequalities, GM and OBC participants rated their own groups' lives as substantially harder than SC/ST members' lives.
-Policy support strongly aligned with participants' caste interests.
-SC/ST participants supported reservations for both SC/ST and OBC students, while OBC participants only supported reservations for their own group.
-Contrary to predictions, we did not find more inclusive identities to be associated with either perceived (dis-)advantage or policy support.
-Contrary to past research \cite{dixon_beyond_2012}, intergroup contact was similarly unrelated to these outcomes.
-For details, see Appendix~D.
-
-\begin{figure}
-\centering
-\includegraphics[scale=1]{../figures/figure-7}
-\caption{
-Posterior probabilities of perceived (dis-)advantage ratings for different target groups (right) by participants' caste ingroup (left).
-Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.
-GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
-}
-\label{fig:f7}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[scale=1]{../figures/figure-8}
-\caption{
-Posterior probabilities of policy support ratings for different target groups (right) by participants' caste ingroup (left).
-Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates.
-GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
-}
-\label{fig:f8}
-\end{figure}
-
-Overall, we found that when participants included a person in their ingroup, they had, on average, more favourable attitudes to and desired less social distance from that person.
-Participants' categorizations, however, were unrelated to perceptions of intergroup threat and relative (dis-)advantage, and to support for affirmative action.
-
-\subsection{Discussion}
-
-This research examined how people construct their social identities from multiple cross-cutting categories, and how these identities relate to intergroup contact and intergroup attitudes.
-As hypothesised, we found that cross-group friendship was associated with more inclusive identities which, in turn, were associated with more favourable outgroup attitudes.
-Negative contact was associated with less inclusive identities.
-Below, we discuss strengths, limitations, and implications of the research.
-
-Our findings show that the triple crossed-categorization task \cite{dommelen_construing_2015} is an intuitive and informative method for studying social identification across multiple categories.
-We adapted the task to answer new questions about social identification.
-First, we recruited respondents from multiple groups, allowing us to study both individual and group differences (see also \citeNP{brankovic_social_2015}).
-Second, we estimated responses as varying across targets and participants using multilevel models.
-This allowed more fine-grained analyses than \citeauthor{dommelen_construing_2015}’s quantitative and qualitative summaries, and may explain why we found more consistent effects of intergroup contact.
-Together, these changes open the triple crossed-categorization task to a broader range of research questions.
-
-Still, our research is qualified by some methodological limitations.
-We presented all participants with the same combination of target groups.
-This design cannot determine whether the observed construals generalise beyond the specific combination of stimuli used.
-Relatedly, we did not control for factors that correlate with the categories under study, but were not made explicit.
-Class, rather than caste, could explain why some participants excluded targets from disadvantaged outgroups.
-Further, we measured categorization and attitudes for the same targets.
-This design cannot rule out that these variables measure the same construct, rather than represent an association across constructs.
-Intergroup threat, a more distal measure, did not correlate with participants' categorizations.\footnote{An explanation for this finding might be that threat perceptions stem from economic anxieties (e.g., fearing affirmative action as a threat to one's career) and ideological beliefs (e.g., Hindutva), rather than identity processes.} Future research should address these limitations by varying target categories across participants, by including more target categories, by assessing intergroup bias with proximal and distal measures, and by testing the hypothesised relationships over time.
-
-Our research has implications for understanding intergroup relations in unequal societies.
-Among advantaged groups, our research documented patterns of inclusion and exclusion that map onto persistent social divides.
-Participants from dominant caste groups tended to exclude subordinate caste groups from the common ingroup.
-Hindu participants tended to exclude Indian Muslims.
-Among disadvantaged groups, we found more complex patterns of inclusion and exclusion.
-Participants from intermediate caste groups (OBC) faced the choice of aligning themselves with dominant caste groups (GM), or forming a coalition with subordinate caste groups (SC/ST).
-OBC participants tended to include dominant GM targets and exclude subordinate SC/ST targets, thus choosing derogation over coalition \cite{craig_coalition_2012}.
-Similarly, SC/ST participants rejected a solidarity-based identity that includes Indian Muslims.
-
-Our findings suggest that cross-group friendship can overcome these divisions by fostering social identities that include Indians of all castes and religions.
-As more inclusive identities were related to less social distance and more warmth toward caste and religious minorities, our research suggests that positive contact could help reduce interpersonal discrimination and violence against these groups.
-In line with recent research (e.g., \citeNP{hayward_how_2018}), we found that negative contact could exacerbate social divisions by fostering less inclusive identities.
-More broadly, our research speaks to \emph{how} contact reduces prejudice \cite{pettigrew_how_2008}.
-Our findings support arguments \cite{gaertner_reducing_2000, pettigrew_intergroup_1998} that contact can reduce prejudice by changing how we understand our social identities.
-
-Our research also examined support for social change.
-Contrary to past research, neither positive nor negative contact \cite{reimer_intergroup_2017} were associated with support for social change in advantaged \cite{dixon_intergroup_2007} and disadvantaged \cite{dixon_beyond_2012} groups.
-Similarly, more inclusive identities were not associated with opposition to affirmative action among the disadvantaged \cite{dovidio_darker_2012}.
-Features of the participants' situation might explain this discrepancy.
-As university students, participants have personally experienced the impact of reservation policies.
-For SC/ST and OBC students, reservation policies facilitated admission to state-funded universities.
-This experience  might explain why these students strongly support reservation (at least for their own group).
-For GM students, reservation policies thwarted admission to state-funded universities.
-This experience might explain why, in contrast to societal realities, GM students saw themselves at a disadvantage relative to other caste groups (see \citeNP{norton_whites_2011}).
-
-To conclude, we found correlational evidence that intergroup contact can change not only how we see others, but also how we see ourselves.
-That is, intergroup contact can foster more inclusive social identities---and thus improve intergroup relations.
-Fostering more inclusive identities, however, does not seem to overcome entrenched opposition to (or undermine support for) affirmative action.
-
-\nolinenumbers
-\bibliographystyle{apacite}
-\bibliography{references}
+\printbibliography
 

### 2020-04-25 data/prepare_data_ic.R

@@ -1,27 +1,0 @@
-# Import Part 1 data (long)
-  dl <- read_rds("data/d1.rds") %>%
-        filter(!is.na(q1)) %>%
-        mutate(og = case_when(
-          category == 1 & ig_caste == "gm" ~ 0L,
-          category == 2 & ig_caste == "obc" ~ 0L,
-          category == 3 & ig_caste == "scst" ~ 0L,
-          TRUE ~ 1L
-        )) %>%
-        arrange(participant, target)
-
-# Import Part 2 data (intergroup contact)
-  d2_imp <- read_rds("data/d2_impute.rds") %>%
-            group_by(participant, category, item) %>%
-            summarise(x_imp = mean(z_response)) %>%
-            spread(item, x_imp)
-
-# Merge Part 1 and Part 2 data (intergroup contact)
-  dl <- left_join(dl, d2_imp, by = c("participant", "category"))
-  
-# Summaries used to standardise contact variables
-  ds <- read_rds("data/d2_impute.rds") %>% distinct(item, mean, sd)
-  
-# Export
-  write_rds(dl, "dl_ic.rds")
-  rm("d2_imp")
-

### 2020-04-25 data/prepare_data_sdo.R

@@ -1,59 +1,0 @@
-# Library -----------------------------------------------------------------
-  library(lavaan)
-
-
-# Import ------------------------------------------------------------------
-  d2 <- read_rds("data/d2.rds") %>%
-        select(participant, starts_with("q60")) %>%
-        arrange(participant) %>%
-        rename_at(vars(starts_with("q60")), ~str_replace(., "q60", "sdo")) %>%
-        mutate_at(vars(sdo_3, sdo_4, sdo_7, sdo_8), ~ 8 - .)
-
-
-# Models ------------------------------------------------------------------
-  m4_model <- '
-  # Loadings
-  sdo_d =~ sdo_1 + sdo_2 + sdo_3 + sdo_4
-  sdo_e =~ sdo_5 + sdo_6 + sdo_7 + sdo_8
-  pro_t =~ sdo_1 + sdo_2 + sdo_5 + sdo_6
-  con_t =~ sdo_3 + sdo_4 + sdo_7 + sdo_8
-
-  # Covariances
-  sdo_d ~~ 0*pro_t
-  sdo_d ~~ 0*con_t
-  sdo_e ~~ 0*pro_t
-  sdo_e ~~ 0*con_t
-
-  # Variances
-  sdo_d ~~ 1*sdo_d
-  sdo_e ~~ 1*sdo_e
-  pro_t ~~ 1*pro_t
-  con_t ~~ 1*con_t
-  '
-  m4_fit <- cfa(m4_model, estimator = "mlr", missing = "fiml", data = d2)
-
-
-# Export ------------------------------------------------------------------
-  dl <- lavPredict(m4_fit) %>% 
-    matrix(., nrow = 302, ncol = 4, dimnames = list(NULL, c("sdo_d", "sdo_e", "pro_t", "con_t"))) %>%
-    as_tibble() %>% 
-    bind_cols(d2, .) %>%
-    select(participant, sdo_d, sdo_e) %>% 
-    left_join(dl, ., "participant")
-  
-  # Transform
-  dl <- dl %>% mutate(
-    gs = case_when(
-      ig_caste == "gm"   & category %in% 2:6 ~ 1L,
-      ig_caste == "obc"  & category %in% 3:6 ~ 1L,
-      ig_caste == "scst" & category %in% 4:6 ~ 1L,
-      TRUE ~ 0L
-    )
-  ) %>% select(
-    session:og, gs, cq:sdo_e
-  )
-
-
[…]

### 2020-04-25 figures/figure-3.R

@@ -1,29 +1,47 @@
 rm(list = ls())
 
 # Library -----------------------------------------------------------------
-  library(tidyverse); library(tidybayes)
+
+  # Load packages
+  library(tidyverse); library(patchwork); library(tidybayes)
 
 
 # Import ------------------------------------------------------------------
+  
   # Observed proportions
-  dl   <- read_rds("data/d1.rds") %>% 
-          filter(!is.na(q1)) %>%
-          mutate(ig_caste = recode_factor(
-            ig_caste, "gm" = "GM", "obc" = "OBC", "scst" = "SC/ST", .ordered = TRUE
-          )) %>%
-          mutate(caste = recode_factor(
-            caste, "GM" = "GM", "OBC" = "OBC", "SCST" = "SC/ST", "N/A" = NA_character_, .ordered = TRUE
-          ))
+  dl <- read_rds("data/d1.rds") %>% 
+    filter(!is.na(q1)) %>%
+    mutate(
+      ig_caste = recode_factor(
+        ig_caste, 
+        "gm" = "GM", 
+        "obc" = "OBC",
+        "scst" = "SC/ST"
+      ),
+      caste = recode_factor(
+        caste, 
+        "GM" = "GM", 
+        "OBC" = "OBC", 
+        "SCST" = "SC/ST", 
+        "N/A" = NA_character_
+      )
+    )
   
   # Estimated probabilites
-  post <- read_rds("models/q1_post.rds") %>%
-          unnest(p_est) %>%
-          mutate(ig_caste = recode_factor(
-            ig_caste, "1" = "GM", "2" = "OBC", "3" = "SC/ST", .ordered = TRUE
-          ))
+  post <- read_rds("results/q1_post.rds") %>%
+    unnest(p_est) %>%
+    mutate(
+      ig_caste = recode_factor(
+        ig_caste,
+        "1" = "GM",
+        "2" = "OBC",
+        "3" = "SC/ST"
+      )
+    )
   
 
 # Summarise ---------------------------------------------------------------
+  
   # Observed proportions
   d_obs <- dl %>% 
     group_by(target, category, lname, nation, religion, caste, ig_caste) %>%
@@ -33,46 +51,102 @@ rm(list = ls())
   d_est <- post %>%
     rename(p_est = p_k) %>%
     group_by(model, category, ig_caste) %>%
-    median_hdi(.width = c(.67, .89, .97))
[…]

### 2020-04-25 figures/figure-4.R

@@ -1,23 +1,26 @@
 rm(list = ls())
 
 # Library -----------------------------------------------------------------
+    
+  # Load packages
   library(tidyverse); library(tidybayes)
 
 
 # Import ------------------------------------------------------------------
+  
   # Estimated probabilites
-  post <- read_rds("models/q1_ic_post.rds")
+  post <- read_rds("results/q1_ic_post.rds")
   
 
 # Summarise ---------------------------------------------------------------
+  
   # Estimated probabilities
   d_est <- post %>%
     group_by(category, ig_caste, item, response) %>%
-    median_hdi(.width = c(.67, .89, .97)) %>%
+    median_hdi(p_est, .width = c(.67, .89, .97)) %>%
     ungroup() %>%
     mutate(
       ig_caste = case_when(
-        category %in% 3:4 & ig_caste %in% 1:2 ~ "GM/OBC",
         ig_caste == 1 ~ "GM",
         ig_caste == 2 ~ "OBC",
         ig_caste == 3 ~ "SC/ST"
@@ -39,9 +42,13 @@ rm(list = ls())
 
 
 # Figure ------------------------------------------------------------------
+
+  # Make figure
   d_est %>%
-    ggplot(., aes(x = response, y = p_est, ymin = .lower, ymax = .upper, 
-                  colour = ig_caste, fill = ig_caste)) +
+    ggplot(., aes(
+      x = response, y = p_est, ymin = .lower, ymax = .upper, 
+      colour = ig_caste, fill = ig_caste
+    )) +
     geom_ribbon(aes(group = interaction(.width, ig_caste)), colour = NA, fill = "white") +
     geom_ribbon(aes(group = interaction(.width, ig_caste)), colour = NA, alpha = 0.20) +
     geom_line() +
@@ -60,14 +67,29 @@ rm(list = ls())
     ) +
     facet_grid(item ~ category) +
     coord_fixed(4) +
-    theme_grey(base_size = 10) +
+    theme_grey(base_size = 10, base_line_size = 0.25) +
     theme(
       legend.position = "bottom",
       strip.background = element_rect(fill = NA, colour = NA),
-      axis.text.x = element_text(colour = "black"),
-      axis.text.y = element_text(colour = "black")
+      axis.text = element_text(colour = "black"),
+      axis.title = element_text(colour = "black"),
+      axis.ticks = element_line(colour = "black")
     )
   
-  # Export
[…]

### 2020-04-25 figures/figure-5.R

@@ -1,0 +1,145 @@
+rm(list = ls())
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(patchwork); library(tidybayes)
+
+
+# Prepare -----------------------------------------------------------------
+
+  # Import posterior draws
+  post <- read_rds("results/q2q3_q1_post.rds")
+
+  # Recode variables
+  post <- post %>% 
+    mutate(
+      category = recode_factor(
+        category,
+        "1" = "Indian, Hindu, GM",
+        "2" = "Indian, Hindu, OBC",
+        "3" = "Indian, Hindu, SC/ST",
+        "4" = "Indian, Muslim, OBC",
+        "5" = "Foreign, Hindu",
+        "6" = "Foreign, Muslim"
+      ),
+      ig_caste = factor(ig_caste, levels = c("GM", "OBC", "SC/ST"))
+    )
+
+
+# Visualize ---------------------------------------------------------------
+
+  # Figure 5a
+  f5a <- post %>% 
+    filter(outcome == "q2") %>% 
+  ggplot(., aes(x = m_est, y = fct_rev(category), group = q1)) +
+    stat_halfeyeh(
+      aes(shape = factor(q1)),
+      .width = .97, size = 0.25, fatten_point = 1,
+      colour = "white", fill = "white"
+    ) +
+    stat_halfeyeh(
+      aes(colour = ig_caste, fill = ig_caste, shape = factor(q1)),
+      .width = .97, size = 0.25, fatten_point = 1,
+      slab_alpha = 2/5
+    ) +
+    scale_x_continuous(
+      limits = c(1, 7),
+      breaks = c(1, 4, 7),
+      minor_breaks = c(2, 3, 5, 6)
+    ) +
+    scale_fill_viridis_d(begin = 0, end = 0.7) +
+    scale_colour_viridis_d(begin = 0, end = 0.7) +
+    scale_shape_manual(
+      values = c("0" = "diamond filled", "1" = "circle")
+    ) +
+    coord_cartesian(xlim = c(0.65, 7.35), ylim = c(0.9, 7), expand = FALSE) +
+    facet_grid(. ~ ig_caste) +
+    theme_grey(base_size = 10) +
+    theme(
+      legend.position = "none",
+      strip.background = element_rect(fill = NA, colour = NA),
+      strip.text = element_text(colour = "black"),
[…]

### 2020-04-25 figures/figures-5-and-6.R

@@ -1,114 +1,0 @@
-rm(list = ls())
-
-# Library -----------------------------------------------------------------
-  library(tidyverse); library(tidybayes)
-
-
-# Import ------------------------------------------------------------------
-  post <- read_rds("models/q2q3_post.rds") %>%
-    gather("standardized", "m_est", m_est:m_est_z) %>%
-    mutate(standardized = (standardized == "m_est_z")) %>%
-    mutate(
-      ig_caste = recode_factor(
-        ig_caste, 
-        "1" = "GM",
-        "2" = "OBC",
-        "3" = "SC/ST",
-        .ordered = TRUE
-      ),
-      category = recode_factor(
-        category,
-        "6" = "Foreign, Muslim",
-        "5" = "Foreign, Hindu",
-        "4" = "Indian, Muslim, OBC",
-        "3" = "Indian, Hindu, SC/ST",
-        "2" = "Indian, Hindu, OBC",
-        "1" = "Indian, Hindu, GM",
-        .ordered = TRUE
-      ),
-      x_q1 = recode_factor(
-        x_q1,
-        "1" = "us",
-        "0" = "not us",
-        .ordered = TRUE
-      )
-    ) %>%
-    group_by(category, ig_caste, x_q1, x_obc, x_scst, item, standardized)
-  
-
-# Figure 5 ----------------------------------------------------------------
-  post %>%
-    filter(!standardized, item == "q2") %>%
-  ggplot(., aes(x = m_est, y = category, group = x_q1)) +
-    geom_halfeyeh(
-      aes(shape = x_q1),
-      colour = NA, fill = "white",
-      point_interval = median_hdi, .width = 0.97,
-      size = 0
-    ) +
-    geom_halfeyeh(
-      aes(shape = x_q1, colour = ig_caste, fill = ig_caste), 
-      point_interval = median_hdi, .width = 0.97,
-      size = 1
-    ) +
-    scale_x_continuous(breaks = seq(1, 7, 3), minor_breaks = seq(1, 7, 1)) +
-    scale_fill_viridis_d(begin = 0, end = 0.7, alpha = 2/5) +
-    scale_colour_viridis_d(begin = 0, end = 0.7) +
-    coord_cartesian(xlim = c(0.5, 7.5), ylim = c(0.9, 7), expand = FALSE) +
-    facet_grid(. ~ ig_caste) + labs(
-      x = "Social distance"
-    ) +
-    theme_grey(base_size = 10) +
-    theme(
[…]

### 2020-04-25 figures/figures-6-and-7.R

@@ -1,0 +1,183 @@
+rm(list = ls())
+
+# Load packages -----------------------------------------------------------
+  library(tidyverse); library(tidybayes)
+
+
+# Import ------------------------------------------------------------------
+  
+  # Load posterior draws
+  post <- bind_rows(
+    read_rds("results/ps_post.rds") %>% mutate(outcome = "ps"), 
+    read_rds("results/pd_post.rds") %>% mutate(outcome = "pd")
+  )
+ 
+  
+  # Prepare for figures
+  post <- post %>%
+    mutate(
+      category = recode_factor(
+        category,
+        "ig" = "...from your\nown background",
+        "scst" = "SC/ST",
+        "obc" = "OBC",
+        "gm" = "GM",
+        "hindu" = "Hindus",
+        "muslim" = "Muslims"
+      ),
+      ig_caste = recode_factor(
+        ig_caste,
+        "scst" = "SC/ST",
+        "obc" = "OBC",
+        "gm" = "GM"
+      )
+    )
+  
+
+# Figure 7 ----------------------------------------------------------------
+  
+  # Labels for Figure 7
+  d_lbl <- tibble(
+    x = c(2.5, 5.5), 
+    xend = c(1.5, 6.5),
+    ig_caste = factor("SC/ST", levels = unique(post$ig_caste)), 
+    category = factor("Muslims", levels = unique(post$category)),
+    label = c("harder", "easier")
+  )
+  
+  # Figure 7
+  post %>%
+    filter(outcome == "pd") %>%
+  ggplot(., aes(x = m_est, y = ig_caste)) +
+    geom_vline(xintercept = 4, colour = "white", size = 1) +
+    geom_halfeyeh(
+      aes(shape = "estimate"),
+      colour = "white", fill = "white",
+      point_interval = median_hdi, .width = 0.97,
+      size = 0
+    ) +
+    geom_halfeyeh(
+      aes(fill = ig_caste, shape = "estimate"),
+      point_interval = median_hdi, .width = 0.97,
+      size = 0.5, fatten_point = 2.5, alpha = 2/5, colour = NA
+    ) +
+    geom_halfeyeh(
+      aes(colour = ig_caste, shape = "estimate"),
+      point_interval = median_hdi, .width = 0.97,
+      size = 0.5, fatten_point = 2.5, fill = NA
+    ) +
+    geom_segment(
[…]

### 2020-04-25 figures/figures-7-and-8.R

@@ -1,143 +1,0 @@
-rm(list = ls())
-
-# Library -----------------------------------------------------------------
-  library(tidyverse); library(tidybayes)
-
-
-# Import ------------------------------------------------------------------
-  post <- read_rds("models/ldps_post.rds") 
-  
-  # Prepare for figures
-  post <- post %>%
-    separate(item, c("item", "group"), sep = "_") %>%
-    mutate(
-      group = recode_factor(
-        group,
-        "ig" = "...from your\nown background",
-        "scst" = "SC/ST",
-        "obc" = "OBC",
-        "gm" = "GM",
-        "hindu" = "Hindus",
-        "muslim" = "Muslims",
-        .ordered = TRUE
-      ),
-      ig_caste = recode_factor(
-        ig_caste,
-        "scst" = "SC/ST",
-        "obc" = "OBC",
-        "gm" = "GM",
-        .ordered = TRUE
-      )
-    )
-  
-
-# Figure 7 ----------------------------------------------------------------
-  # Labels for Figure 7
-  d_lbl <- tibble(
-    x = c(2.5, 5.5), xend = c(1.5, 6.5),
-    ig_caste = "SC/ST", group = ordered("Muslims", levels = unique(post$group)),
-    label = c("harder", "easier")
-  )
-  
-  # Figure 7
-  post %>%
-    filter(item == "ld") %>%
-  ggplot(., aes(x = m_est, y = ig_caste)) +
-    geom_vline(xintercept = 4, colour = "white", size = 1) +
-    geom_halfeyeh(
-      aes(shape = "estimate"),
-      colour = "white", fill = "white",
-      point_interval = median_hdi, .width = 0.97,
-      rel_min_height = 0.01, size = 0
-    ) +
-    geom_halfeyeh(
-      aes(colour = ig_caste, fill = ig_caste, shape = "estimate"),
-      point_interval = median_hdi, .width = 0.97,
-      rel_min_height = 0.01, size = 0.5, fatten_point = 2.5
-    ) +
-    geom_segment(
-      data = d_lbl, aes(x = x, xend = xend, yend = ig_caste),
-      arrow = arrow(length = unit(0.1, "cm"), type = "closed")
-    ) +
-    geom_text(
-      data = d_lbl, aes(label = label), x = c(2, 6), y = c(1, 1),
-      size = 10*0.8/.pt, vjust = -0.5
-    ) +
[…]

### 2020-04-25 figures/table-2.R

@@ -1,0 +1,68 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(loo)
+
+
+# Prepare -----------------------------------------------------------------
+
+  # Import results from k-fold cross-validation
+  q1_elpd <- read_rds("results/q1_elpd.rds")
+  
+  # Calculate pseudo-BMA weights
+  q1_elpd <- q1_elpd %>% 
+    unnest(elpd_i) %>% 
+    group_by(model) %>% 
+    mutate(ii = row_number()) %>% 
+    ungroup() %>% 
+    pivot_wider(
+      names_from = model, 
+      names_prefix = "M", 
+      values_from = elpd_i
+    ) %>% 
+    select(-ii) %>% 
+    as.matrix() %>% 
+    pseudobma_weights() %>% 
+    mutate(q1_elpd, elpd_w = .)
+  
+  # Calculate expected log predictive density (ELPD)
+  q1_elpd <- q1_elpd %>% 
+    mutate(
+      elpd    = map(elpd_i, sum) %>% unlist(),
+      elpd_se = map(elpd_i, ~(sd(.) * sqrt(length(.)))) %>% unlist()
+    )
+  
+  # Calculate differences in difference in ELPD
+  q1_elpd <- q1_elpd %>% 
+    select(model, elpd_i) %>% 
+    crossing(comparison_model = 0:7) %>% 
+    left_join(
+      q1_elpd %>% select(comparison_model = model, comparison_elpd_i = elpd_i),
+      by = "comparison_model"
+    ) %>% 
+    mutate(
+      elpd_d = map2_dbl(elpd_i, comparison_elpd_i, ~sum(.x - .y)),
+      elpd_d_se = map2_dbl(elpd_i, comparison_elpd_i, ~(sd(.x - .y) * sqrt(length(.x)))),
+      elpd_d_z = if_else(elpd_d == 0, 0, elpd_d/elpd_d_se)
+    ) %>% 
+    select(model, comparison_model, elpd_d_z) %>% 
+    pivot_wider(
+      names_from = comparison_model, 
+      names_prefix = "M", 
+      values_from = elpd_d_z
+    ) %>% 
+    left_join(q1_elpd, ., by = "model")
+  
+  # Reformat
[…]

### 2020-04-25 figures/table-3.R

@@ -1,0 +1,68 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(loo)
+
+
+# Prepare -----------------------------------------------------------------
+
+  # Import results from k-fold cross-validation
+  q2q3_elpd <- read_rds("results/q2q3_elpd.rds") %>% filter(model %in% 0:6)
+  
+  # Calculate pseudo-BMA weights
+  q2q3_elpd <- q2q3_elpd %>% 
+    unnest(elpd_i) %>% 
+    group_by(model) %>% 
+    mutate(ii = row_number()) %>% 
+    ungroup() %>% 
+    pivot_wider(
+      names_from = model, 
+      names_prefix = "M", 
+      values_from = elpd_i
+    ) %>% 
+    select(-ii) %>% 
+    as.matrix() %>% 
+    pseudobma_weights() %>% 
+    mutate(q2q3_elpd, elpd_w = .)
+  
+  # Calculate expected log predictive density (ELPD)
+  q2q3_elpd <- q2q3_elpd %>% 
+    mutate(
+      elpd    = map(elpd_i, sum) %>% unlist(),
+      elpd_se = map(elpd_i, ~(sd(.) * sqrt(length(.)))) %>% unlist()
+    )
+  
+  # Calculate differences in difference in ELPD
+  q2q3_elpd <- q2q3_elpd %>% 
+    select(model, elpd_i) %>% 
+    crossing(comparison_model = 0:6) %>% 
+    left_join(
+      q2q3_elpd %>% select(comparison_model = model, comparison_elpd_i = elpd_i),
+      by = "comparison_model"
+    ) %>% 
+    mutate(
+      elpd_d = map2_dbl(elpd_i, comparison_elpd_i, ~sum(.x - .y)),
+      elpd_d_se = map2_dbl(elpd_i, comparison_elpd_i, ~(sd(.x - .y) * sqrt(length(.x)))),
+      elpd_d_z = if_else(elpd_d == 0, 0, elpd_d/elpd_d_se)
+    ) %>% 
+    select(model, comparison_model, elpd_d_z) %>% 
+    pivot_wider(
+      names_from = comparison_model, 
+      names_prefix = "M", 
+      values_from = elpd_d_z
+    ) %>% 
[…]

### 2020-04-25 models/kfold/kfold_consequences.R

@@ -1,269 +1,0 @@
-rm(list = ls())
-
-# Notes -------------------------------------------------------------------
-  # Caution! Running this script will take several days on most computers.
-  # Run read_rds("models/kfold/q2q3_elpd_kfold.rds") to skip to the results.
-
-# Library -----------------------------------------------------------------
-  library(tidyverse); library(rstan); library(tidybayes); library(loo)
-  
-  # Stan options
-  options(mc.cores = parallel::detectCores())
-  rstan_options(auto_write = TRUE)
-  seeds = c(1157744, 2691555, 4045395, 2910499, 5195618, 5975015, 2391421)
-
-
-# Import ------------------------------------------------------------------
-  dl <- read_rds("data/d1.rds") %>%
-        filter(!is.na(q1)) %>%
-        mutate_at(vars(q2, q3), funs(mean, sd), na.rm = TRUE) %>%
-        mutate(q2_z = (q2 - q2_mean) / q2_sd, q3_z = (q3 - q3_mean) / q3_sd) %>%
-        arrange(participant, target)
-  
-  # Single (median) imputation
-  Y           <- as.matrix(dl[,c("q2_z", "q3_z")])
-  Y[is.na(Y)] <- read_rds("models/q2q3_mc_fit.rds")[[6]] %>%
-                 spread_draws(y_mis[ii]) %>%
-                 summarise(y_mis = median(y_mis)) %>%
-                 pull(y_mis)
-
-  # Compose data list
-  data_list <- with(dl, list(
-    # Numbers
-    N_row = length(participant),
-    N_col = ncol(Y),
-    J = n_distinct(participant),
-    K = n_distinct(category),
-    # Indices
-    jj = participant,
-    kk = category,
-    # Vectors
-    x_scst = ifelse(ig_caste == "scst", 1L, 0L),
-    x_obc = ifelse(ig_caste == "obc", 1L, 0L),
-    x_q1 = q1,
-    Y = Y
-  ))
-  
-  # Generate indeces for 10-fold cross-validation
-  set.seed(24987504)
-  d_kfold <- tibble(
-    ii   = 1:data_list$N_row, 
-    jj   = data_list$jj, 
[…]

### 2020-04-25 models/kfold/kfold_group_differences.R

@@ -1,170 +1,0 @@
-rm(list = ls())
-
-# Notes -------------------------------------------------------------------
-  # Caution! Running this script will take several days on most computers.
-  # Run read_rds("models/kfold/q1_elpd_kfold.rds") to skip to the results.
-
-
-# Library -----------------------------------------------------------------
-  library(tidyverse); library(rstan); library(loo)
-  
-  # Stan options
-  options(mc.cores = parallel::detectCores())
-  rstan_options(auto_write = TRUE)
-  seeds = c(5477649, 3984665, 8989566, 9363790)
-
-
-# Import ------------------------------------------------------------------
-  dl <- read_rds("data/d1.rds") %>%
-        filter(!is.na(q1)) %>%
-        arrange(participant, target)
-  
-  # Compose data list
-  data_list <- with(dl, list(
-    N = length(participant),
-    J = n_distinct(participant),
-    K = n_distinct(category),
-    jj = participant,
-    kk = category,
-    x_scst = ifelse(ig_caste == "scst", 1L, 0L),
-    x_obc = ifelse(ig_caste == "obc", 1L, 0L),
-    y = q1
-  ))
-  
-  # Generate indeces for 10-fold cross-validation
-  set.seed(24987504)
-  d_kfold <- tibble(
-    ii   = 1:data_list$N, 
-    jj   = data_list$jj, 
-    fold = kfold_split_stratified(K = 10, x = jj)
-  )
-
-
-# Functions ---------------------------------------------------------------
-  data_fold <- function(k) {
-    append(data_list, list(
-      N_t = d_kfold %>% filter(fold != k) %>% nrow(),
-      N_h = d_kfold %>% filter(fold == k) %>% nrow(),
-      ii_t = d_kfold %>% filter(fold != k) %>% pull(ii),
-      ii_h = d_kfold %>% filter(fold == k) %>% pull(ii)
-    ))
-  }
-  
-  compare_kfold <- function(elpd1, elpd2) {
-    d_elpd  <- sum(elpd2 - elpd1)
-    d_se    <- sd(elpd2 - elpd1) * sqrt(length(elpd1))
-    d_ratio <- d_elpd / d_se
[…]

### 2020-04-25 models/kfold/kfold_individual_differences.R

@@ -1,192 +1,0 @@
-rm(list = ls())
-
-# Notes -------------------------------------------------------------------
-  # Caution! Running this script will take several days on most computers.
-  # Run read_rds("models/kfold/q1_elpd_kfold.rds") to skip to the results.
-
-# Library -----------------------------------------------------------------
-  library(tidyverse); library(rstan); library(loo)
-  
-  # Stan options
-  options(mc.cores = parallel::detectCores())
-  rstan_options(auto_write = TRUE)
-  seeds = c(6678002, 8970252,	9556204, 8660009)
-
-
-# Import ------------------------------------------------------------------
-  source("data/prepare_data_ic.R")
-  source("data/prepare_data_sdo.R")
-
-  # Compose data list
-  data_list <- with(dl, list(
-    # Numbers
-    N = length(participant),
-    J = n_distinct(participant),
-    K = n_distinct(category),
-    # Indices
-    jj = participant,
-    kk = category,
-    # Vectors
-    x_scst = ifelse(ig_caste == "scst", 1L, 0L),
-    x_obc = ifelse(ig_caste == "obc", 1L, 0L),
-    x_og = og,
-    x_cq = replace_na(cq, -99), # Replace NAs for foreign targets 
-    x_pc = replace_na(pc, -99), # Replace NAs for foreign targets
-    x_nc = replace_na(nc, -99), # Replace NAs for foreign targets
-    x_of = replace_na(of, -99), # Replace NAs for foreign targets
-    x_gs = gs,
-    x_sdo_d = sdo_d,
-    x_sdo_e = sdo_e,
-    y = q1
-  ))
-
-  # Generate indeces for 10-fold cross-validation
-  set.seed(24987504)
-  d_kfold <- tibble(
-    ii   = 1:data_list$N, 
-    jj   = data_list$jj, 
-    fold = kfold_split_stratified(K = 10, x = jj)
-  )
-  
-  
-# Functions ---------------------------------------------------------------
-  data_fold <- function(k) {
-    append(data_list, list(
-      N_t = d_kfold %>% filter(fold != k) %>% nrow(),
[…]

### 2020-04-25 read_data.R

@@ -23,4 +23,3 @@ rm(list = ls())
   #########################################################################
   # Start your own analyses here.                                         #
   #########################################################################
-  

### 2020-04-25 scripts/determine_sample_size.R

@@ -1,88 +1,232 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-  # Reanalysing data from van Dommelen et al.'s (2015) studies, we found
-  # that 100 responses allowed reasonably precise estimates of the proportion
-  # of "us" categorizations in each of eight target categories. Posterior
-  # probabilities for these estimates had a precision of SD < 0.50 on the 
-  # log odds scale.
 
-  # This R script is included for review purposes only as we are not able to
-  # make the underlying data available.
-
+  #########################################################################
+  # This R script is included for reference only as we are not able to    #
+  # make the underlying data available. For details, see Appendix B.      #
+  #########################################################################
 
 # Library -----------------------------------------------------------------
+  
+  # Load packages
   library(tidyverse); library(rstan); library(tidybayes)
   
   # Stan options
-  options(mc.cores = parallel::detectCores())
+  n_cores <- 8L
+  options(mc.cores = n_cores)
   rstan_options(auto_write = TRUE)
   seeds = c(35702546)
   
+  # Link function
+  inv_logit <- function(x) exp(x) / (1 + exp(x))
 
-# Import ------------------------------------------------------------------
-  # Import wide format
+
+# Prepare -----------------------------------------------------------------
+
+  # Import data in wide format
   dw <- haven::read_spss("data/old/d_old.sav") %>%
-        haven::zap_formats() %>%
-        select(participant, card1:card24)
-  
+    haven::zap_formats() %>%
+    select(participant, card1:card24)
+
   # Spread to long format
   dl <- dw %>% 
-        gather("target", "q1", card1:card24) %>%
-        mutate(target = str_extract(target, "[0-9]+")) %>%
-        mutate_at(vars(target, q1), as.integer) %>%
-        arrange(participant, target)
+    gather("target", "q1", card1:card24) %>%
+    mutate(target = str_extract(target, "[0-9]+")) %>%
+    mutate_at(vars(target, q1), as.integer) %>%
[…]

### 2020-04-25 scripts/import_data.R

@@ -8,11 +8,13 @@ rm(list = ls())
   # data/d1_raw.rds and data/d2_raw.rds directly.
 
 
-# Library -----------------------------------------------------------------
+# Load packages -----------------------------------------------------------
   library(tidyverse)
 
 
 # Functions ---------------------------------------------------------------
+  
+  # Clean responses
   clean <- function(v, type, range = FALSE) {
     if (is_character(v)) {
       if (type == "n") {
@@ -33,6 +35,7 @@ rm(list = ls())
 
   
 # Import ------------------------------------------------------------------
+  
   # Import and merge csv files
   for (session in 1:8) {
     if (session == 1) {
@@ -73,6 +76,7 @@ rm(list = ls())
 
 
 # Clean -------------------------------------------------------------------
+  
   # Part 1 (TCCT)
   d1 <- d1 %>% mutate(
     session = clean(session, "c"),
@@ -121,6 +125,7 @@ rm(list = ls())
   
 
 # Match -------------------------------------------------------------------
+  
   # Import session-wise target information
   for (session in 1:8) {
     if (session == 1) {
@@ -143,6 +148,7 @@ rm(list = ls())
   
   
 # Transform ---------------------------------------------------------------
+  
   # Assign each participant an unambigious id
   d1 <- d1 %>% mutate(participant = paste(session, participant, sep = ""))
   d2 <- d2 %>% mutate(participant = paste(session, participant, sep = ""))

### 2020-04-25 scripts/impute_data.R

@@ -1,164 +1,147 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-  # This script imputes missing responses (n = 66) for the intergroup contact
-  # variables, and returns a data frame with both observed responses and 
-  # draws from the posterior distribution for missing responses. 
+
+  #########################################################################
+  # This script imputes missing responses (n = 66) for the intergroup     #
+  # contact variables, and returns a data frame with both observed        #
+  # responses and draws from the posterior distribution for missing       #
+  # responses.                                                            # 
+  #########################################################################
 
 # Library -----------------------------------------------------------------
-  library(tidyverse); library(rstan); library(tidybayes)
+  
+  # Load packages
+  library(tidyverse); library(rstan)
 
   # Stan options
-  options(mc.cores = parallel::detectCores())
+  n_cores <- 8L
+  options(mc.cores = n_cores)
   rstan_options(auto_write = TRUE)
   seed = 70475734
 
 
-# Import ------------------------------------------------------------------
-  d2 <- read_rds("data/d2.rds") %>%
-        select(participant, ig_caste, q4:q23)
+# Prepare -----------------------------------------------------------------
+
+  # Import data
+  d2 <- read_rds("data/d2.rds") %>% select(participant, ig_caste, q4:q23)
   
   # Prepare data (long format)
   dl <- d2 %>%
-    gather("item", "response", q4:q23) %>%
-    mutate(item = str_extract(item, "[0-9]+") %>% as.integer()) %>% 
-    arrange(participant, item) %>%
-    mutate(ii = 1:n()) %>%
-    select(ii, participant, item, response)
+    pivot_longer(
+      -participant:-ig_caste,
+      names_to = "item",
+      names_prefix = "q",
+      names_ptypes = list(item = integer()),
+      values_to = "x_obs"
+    ) %>% 
[…]

### 2020-04-25 scripts/prepare_data.R

@@ -4,12 +4,8 @@ rm(list = ls())
   #  See materials/materials.pdf (Appendix D) for items and answer options.
 
 
-# Library -----------------------------------------------------------------
+# Load packages -----------------------------------------------------------
   library(tidyverse)
-
-
-# Functions ---------------------------------------------------------------
-
 
   
 # Import ------------------------------------------------------------------
@@ -18,6 +14,7 @@ rm(list = ls())
 
   
 # Participants ------------------------------------------------------------
+  
   # Count religion, caste (after exclusion)
   d2 %>% count(q36)
   d2 %>% count(q37)
@@ -32,6 +29,7 @@ rm(list = ls())
   
 
 # Transform ---------------------------------------------------------------
+  
   # Code ingroup caste
   d2 <- d2 %>% mutate(
     ig_caste = recode(q37, "1" = "scst", "2" = "scst", "3" = "obc", "4" = "gm")

### 2020-04-25 scripts/prepare_data_sdo.R

@@ -1,0 +1,59 @@
+# Load packages -----------------------------------------------------------
+  library(lavaan)
+
+
+# Import ------------------------------------------------------------------
+  d2 <- read_rds("data/d2.rds") %>%
+        select(participant, starts_with("q60")) %>%
+        arrange(participant) %>%
+        rename_at(vars(starts_with("q60")), ~str_replace(., "q60", "sdo")) %>%
+        mutate_at(vars(sdo_3, sdo_4, sdo_7, sdo_8), ~ 8 - .)
+
+
+# Models ------------------------------------------------------------------
+  m4_model <- '
+  # Loadings
+  sdo_d =~ sdo_1 + sdo_2 + sdo_3 + sdo_4
+  sdo_e =~ sdo_5 + sdo_6 + sdo_7 + sdo_8
+  pro_t =~ sdo_1 + sdo_2 + sdo_5 + sdo_6
+  con_t =~ sdo_3 + sdo_4 + sdo_7 + sdo_8
+
+  # Covariances
+  sdo_d ~~ 0*pro_t
+  sdo_d ~~ 0*con_t
+  sdo_e ~~ 0*pro_t
+  sdo_e ~~ 0*con_t
+
+  # Variances
+  sdo_d ~~ 1*sdo_d
+  sdo_e ~~ 1*sdo_e
+  pro_t ~~ 1*pro_t
+  con_t ~~ 1*con_t
+  '
+  m4_fit <- cfa(m4_model, estimator = "mlr", missing = "fiml", data = d2)
+
+
+# Export ------------------------------------------------------------------
+  dl <- lavPredict(m4_fit) %>% 
+    matrix(., nrow = 302, ncol = 4, dimnames = list(NULL, c("sdo_d", "sdo_e", "pro_t", "con_t"))) %>%
+    as_tibble() %>% 
+    bind_cols(d2, .) %>%
+    select(participant, sdo_d, sdo_e) %>% 
+    left_join(dl, ., "participant")
+  
+  # Transform
+  dl <- dl %>% mutate(
+    gs = case_when(
+      ig_caste == "gm"   & category %in% 2:6 ~ 1L,
+      ig_caste == "obc"  & category %in% 3:6 ~ 1L,
+      ig_caste == "scst" & category %in% 4:6 ~ 1L,
+      TRUE ~ 0L
+    )
+  ) %>% select(
+    session:og, gs, sdo_d:sdo_e
+  )
+
+
[…]

### 2020-04-25 scripts/results_consequences.R

@@ -4,138 +4,262 @@ rm(list = ls())
 
 
 # Library -----------------------------------------------------------------
-  library(tidyverse); library(rstan); library(tidybayes); library(loo)
+  
+  # Load packages
+  library(tidyverse); library(rstan); library(tidybayes)
 
   # Stan options
-  options(mc.cores = parallel::detectCores())
+  n_cores <- 8L
+  options(mc.cores = n_cores)
   rstan_options(auto_write = TRUE)
   seeds = c(1157744, 2691555, 4045395, 2910499, 5195618, 5975015, 2391421)
 
 
 # Import ------------------------------------------------------------------
+  
+  # Import data
   dl <- read_rds("data/d1.rds") %>%
-        filter(!is.na(q1)) %>%
-        mutate_at(vars(q2, q3), funs(mean, sd), na.rm = TRUE) %>%
-        mutate(q2_z = (q2 - q2_mean) / q2_sd, q3_z = (q3 - q3_mean) / q3_sd) %>%
-        arrange(participant, target)
+    filter(!is.na(q1)) %>%
+    mutate_at(
+      vars(q2, q3), 
+      list("mean" = mean, "sd" = sd), 
+      na.rm = TRUE
+    ) %>%
+    mutate(
+      q2_z = (q2 - q2_mean) / q2_sd, 
+      q3_z = (q3 - q3_mean) / q3_sd
+    ) %>%
+    arrange(participant, target)
   
   # Prepare for imputation
   dl_imp <- dl %>% 
-            select(participant, target, q2_z, q3_z) %>%
-            gather("item", "y", q2_z, q3_z) %>%
-            mutate(ii = 1:n())
-
+    select(participant, target, q2_z, q3_z) %>%
+    gather("item", "y", q2_z, q3_z) %>%
+    arrange(item, participant, target) %>% 
+    rowid_to_column("ii")
+    
   # Compose data list
   data_list <- with(dl, list(
-    # Numbers
-    N_row = length(participant),
-    N_col = 2,
-    J = n_distinct(participant),
-    K = n_distinct(category),
-    N_obs = sum(!is.na(dl_imp$y)),
-    N_mis = sum(is.na(dl_imp$y)),
[…]

### 2020-04-25 scripts/results_group_differences.R

@@ -1,15 +1,26 @@
 rm(list = ls())
 
+# Notes -------------------------------------------------------------------
+  
+  #########################################################################
+  # Adjust n_cores to the number of CPU cores you want to use.            #
+  #########################################################################
+
 # Library -----------------------------------------------------------------
-  library(tidyverse); library(tidybayes); library(rstan); library(loo)
+  
+  # Load packages
+  library(tidyverse); library(tidybayes); library(rstan)
 
   # Stan options
-  options(mc.cores = parallel::detectCores())
+  n_cores <- 8L
+  options(mc.cores = n_cores)
   rstan_options(auto_write = TRUE)
-  seeds = c(5477649, 3984665, 8989566, 9363790)
+  seeds <- c(5477649, 3984665, 8989566, 9363790)
 
 
-# Import ------------------------------------------------------------------
+# Prepare -----------------------------------------------------------------
+
+  # Import data
   dl <- read_rds("data/d1.rds") %>%
         filter(!is.na(q1)) %>%
         arrange(participant, target)
@@ -21,50 +32,73 @@ rm(list = ls())
     K = n_distinct(category),
     jj = participant,
     kk = category,
-    x_scst = ifelse(ig_caste == "scst", 1L, 0L),
-    x_obc = ifelse(ig_caste == "obc", 1L, 0L),
+    x_scst = if_else(ig_caste == "scst", 1L, 0L),
+    x_obc = if_else(ig_caste == "obc", 1L, 0L),
     y = q1
   ))
 
 
-# Models ------------------------------------------------------------------
+# Run ---------------------------------------------------------------------
+
   # Model: Varying Intercept (Participant)
-  m0_stan <- stan("models/q1_m0.stan", data = data_list, seed = seeds[1],
-                  iter = 2000, warmup = 1000,
-                  pars = c("alpha"), include = FALSE)
+  m0_fit <- stan(
+    "models/q1_m0.stan", 
+    data = data_list, 
+    iter = 1000 + 8000/n_cores, warmup = 1000, 
+    chains = n_cores,
+    seed = seeds[1],
+    pars = c("alpha"), include = FALSE
+  )
   
   # Model: + Varying Intercept (Target: Category)
[…]

### 2020-04-25 scripts/results_individual_differences.R

@@ -1,22 +1,19 @@
 rm(list = ls())
 
 # Notes -------------------------------------------------------------------
-  # In total, I considered 5 * 4 = 20 items measuring intergroup contact. Across
-  # items, less than 1.6% (n = 66) of individual responses were missing - though
-  # about 13% of all participants failed to respond to at least one item. As 
-  # item-by-item missingness was negligible, I used single imputation rather 
-  # than (computationally demanding) full imputation. Before running Models 4 to 
-  # 6, I imputed missing values from a multivariate normal distribution (see 
-  # "impute_data.R"). For all subsequent analyses, I substituted the most likely
-  # value (from the posterior distribution of the imputation model) for each 
-  # missing value (in the original dataset).
 
+  #########################################################################
+  # Adjust n_cores to the number of CPU cores you want to use.            #
+  #########################################################################
 
 # Library -----------------------------------------------------------------
-  library(tidyverse); library(rstan); library(tidybayes); library(loo)
 
+  # Load packages
+  library(tidyverse); library(tidybayes); library(rstan)
+  
   # Stan options
-  options(mc.cores = parallel::detectCores())
+  n_cores <- 8L
+  options(mc.cores = n_cores)
   rstan_options(auto_write = TRUE)
   seeds = c(6678002, 8970252,	9556204, 8660009)
   
@@ -24,105 +21,241 @@ rm(list = ls())
 # Functions ---------------------------------------------------------------
   inv_logit <- function(x) exp(x) / ( 1 + exp(x) )
   
+  
+# Prepare -----------------------------------------------------------------
 
-# Import ------------------------------------------------------------------
-  source("data/prepare_data_ic.R")
-  source("data/prepare_data_sdo.R")
+  # Import data
+  dl <- read_rds("data/d1.rds") %>%
+    filter(!is.na(q1)) %>%
[…]

### 2020-04-25 scripts/results_kfold_consequences.R

@@ -1,0 +1,255 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+  #########################################################################
+  # Adjust n_cores to the number of CPU cores you want to use.            #
+  # For this analysis, we are only using observed responses.              #
+  # WARNING: Running this script might take several hours/days depending  #
+  #          on the computer you use.                                     #
+  #########################################################################
+
+# Library -----------------------------------------------------------------
+  
+  # Load packages
+  library(tidyverse); library(rstan); library(tidybayes); library(loo)
+
+  # Stan options
+  n_cores <- 8L
+  options(mc.cores = n_cores)
+  Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
+  rstan_options(auto_write = TRUE)
+  seeds = c(1157744, 2691555, 4045395, 2910499, 5195618, 5975015, 2391421)
+
+
+# Import ------------------------------------------------------------------
+  
+  # Import data
+  dl <- read_rds("data/d1.rds") %>%
+    filter(!is.na(q1)) %>%
+    mutate_at(
+      vars(q2, q3), 
+      list("mean" = mean, "sd" = sd), 
+      na.rm = TRUE
+    ) %>%
+    mutate(
+      q2_z = (q2 - q2_mean) / q2_sd, 
+      q3_z = (q3 - q3_mean) / q3_sd
+    ) %>%
+    arrange(participant, target)
+  
+  # Divides data for 10-fold cross-validation
+  set.seed(24987504)
+  dl <- dl %>% mutate(fold = kfold_split_stratified(K = 10, x = participant))
+
+  # Exclude cases with missing responses on either outcome variable
+  dl <- dl %>% filter(!is.na(q2), !is.na(q3))
+
+  # Compose data list
+  data_list <- with(dl, list(
+      N_row = length(participant),
+      N_col = 2L,
+      J = n_distinct(participant),
+      K = n_distinct(category),
+      jj = as.integer(factor(participant)),
+      kk = category,
[…]

### 2020-04-25 scripts/results_kfold_group_differences.R

@@ -1,0 +1,168 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+  
+  #########################################################################
+  # Adjust n_cores to the number of CPU cores you want to use.            #
+  # WARNING: Running this script might take several hours/days depending  #
+  #          on the computer you use.                                     #
+  #########################################################################
+
+# Library -----------------------------------------------------------------
+  
+  # Load packages
+  library(tidyverse); library(rstan); library(loo)
+
+  # Stan options
+  n_cores <- 8L
+  options(mc.cores = n_cores)
+  Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
+  rstan_options(auto_write = FALSE)
+  seeds <- c(5477649, 3984665, 8989566, 9363790)
+
+
+# Prepare -----------------------------------------------------------------
+
+  # Import data
+  dl <- read_rds("data/d1.rds") %>%
+        filter(!is.na(q1)) %>%
+        arrange(participant, target)
+  
+  # Compose data list
+  data_list <- with(dl, list(
+    N = length(participant),
+    J = n_distinct(participant),
+    K = n_distinct(category),
+    jj = participant,
+    kk = category,
+    x_scst = if_else(ig_caste == "scst", 1L, 0L),
+    x_obc = if_else(ig_caste == "obc", 1L, 0L),
+    y = q1
+  ))
+  
+  # Generate indeces for 10-fold cross-validation
+  set.seed(24987504)
+  d_kfold <- tibble(
+    ii   = 1:data_list$N, 
+    jj   = data_list$jj, 
+    fold = kfold_split_stratified(K = 10, x = jj)
+  )
+
+
+# Functions ---------------------------------------------------------------
+
+  # Append indeces for 10-fold cross-validation
+  data_fold <- function(k) {
+    append(data_list, list(
+      N_t = d_kfold %>% filter(fold != k) %>% nrow(),    # training
+      N_h = d_kfold %>% filter(fold == k) %>% nrow(),    # hold out
+      ii_t = d_kfold %>% filter(fold != k) %>% pull(ii), # training
[…]

### 2020-04-25 scripts/results_kfold_individual_differences.R

@@ -1,0 +1,264 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+  #########################################################################
+  # Adjust n_cores to the number of CPU cores you want to use.            #
+  # WARNING: Running this script might take several hours/days depending  #
+  #          on the computer you use.                                     #
+  #########################################################################
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(rstan); library(loo)
+  
+  # Stan options
+  n_cores <- 8L
+  options(mc.cores = n_cores)
+  Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
+  rstan_options(auto_write = FALSE)
+  seeds <- c(5477649, 3984665, 8989566, 9363790)
+  
+
+# Functions ---------------------------------------------------------------
+  inv_logit <- function(x) exp(x) / ( 1 + exp(x) )
+  
+  
+# Prepare -----------------------------------------------------------------
+
+  # Import data
+  dl <- read_rds("data/d1.rds") %>%
+    filter(!is.na(q1)) %>%
+    mutate(og = case_when(
+      category == 1 & ig_caste == "gm" ~ 0L,
+      category == 2 & ig_caste == "obc" ~ 0L,
+      category == 3 & ig_caste == "scst" ~ 0L,
+      TRUE ~ 1L
+    )) %>%
+    arrange(participant, target)
+
+  # Import imputed data
+  dl_imp <- read_rds("results/ic_impute.rds") %>%
+    mutate(og = case_when(
+      category == 1 & ig_caste == "gm" ~ 0L,
+      category == 2 & ig_caste == "obc" ~ 0L,
+      category == 3 & ig_caste == "scst" ~ 0L,
+      TRUE ~ 1L
+    )) %>%
+    select(-z_obs, -z_imp)
+
+  # Summarize/Standardize
+  dl_imp <- dl_imp %>%
+    filter(!is.na(x_obs)) %>%
+    select(-.draw) %>%
+    crossing(.draw = 1:max(dl_imp$.draw, na.rm = TRUE)) %>%
[…]

### 2020-04-25 scripts/results_perceived_disadvantage.R

@@ -1,0 +1,239 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(rstan); library(loo); library(tidybayes)
+  
+  # Stan options
+  n_cores <- 8L
+  options(mc.cores = n_cores)
+  rstan_options(auto_write = TRUE)
+  seeds = c(9658217, 4125367, 9337593, 1407167)
+
+  
+# Prepare -----------------------------------------------------------------
+
+  # Import data
+  dw <- read_rds("data/d2.rds") %>%
+    transmute(
+      participant,
+      ig_caste,
+      pd_ig     = q24_1,
+      pd_scst   = (q24_2 + q24_3)/2,
+      pd_obc    = q24_4,
+      pd_gm     = q24_5,
+      pd_hindu  = q24_6,
+      pd_muslim = q24_7,
+      x_scst      = if_else(ig_caste == "scst", 1L, 0L),
+      x_obc       = if_else(ig_caste == "obc", 1L, 0L),
+      x_gm        = if_else(ig_caste == "gm", 1L, 0L),
+      x_nc_gm     = q16,
+      x_of_gm     = (q17 + q18)/2,
+      x_nc_obc    = q11,
+      x_of_obc    = (q12 + q13)/2,
+      x_nc_scst   = q6,
+      x_of_scst   = (q7 + q8)/2,
+      x_nc_muslim = q21,
+      x_of_muslim = (q22 + q23)/2,
+    ) %>%
+    left_join(
+      read_rds("data/d1.rds") %>% 
+        select(participant, category, q1) %>% 
+        filter(category <= 4L) %>% 
+        mutate(category = recode(
+          category, "1" = "gm", "2" = "obc", "3" = "scst", "4" = "muslim"
+        )) %>% 
+        group_by(participant, category) %>% 
+        summarise(q1 = mean(q1)) %>% 
+        ungroup() %>% 
+        pivot_wider(
+          names_from = category,
+          names_prefix = "x_q1_",
+          values_from = q1
+        ),
+      by = "participant"
+    ) %>% 
+    mutate_at(vars(starts_with("x_")), as.double) %>% 
[…]

### 2020-04-25 scripts/results_policy_support.R

@@ -1,0 +1,233 @@
+rm(list = ls())
+
+# Notes -------------------------------------------------------------------
+
+
+# Library -----------------------------------------------------------------
+
+  # Load packages
+  library(tidyverse); library(rstan); library(loo); library(tidybayes)
+  
+  # Stan options
+  n_cores <- 8L
+  options(mc.cores = n_cores)
+  rstan_options(auto_write = TRUE)
+  seeds = c(9658217, 4125367, 9337593, 1407167)
+
+  
+# Prepare -----------------------------------------------------------------
+
+  # Import data
+  dw <- read_rds("data/d2.rds") %>%
+    transmute(
+      participant,
+      ig_caste,
+      ps_scst     = (q25 + q26)/2,
+      ps_obc      = (q27 + q28)/2,
+      ps_muslim   = q29,
+      x_scst      = if_else(ig_caste == "scst", 1L, 0L),
+      x_obc       = if_else(ig_caste == "obc", 1L, 0L),
+      x_gm        = if_else(ig_caste == "gm", 1L, 0L),
+      x_nc_gm     = q16,
+      x_of_gm     = (q17 + q18)/2,
+      x_nc_obc    = q11,
+      x_of_obc    = (q12 + q13)/2,
+      x_nc_scst   = q6,
+      x_of_scst   = (q7 + q8)/2,
+      x_nc_muslim = q21,
+      x_of_muslim = (q22 + q23)/2,
+    ) %>%
+    left_join(
+      read_rds("data/d1.rds") %>% 
+        select(participant, category, q1) %>% 
+        filter(category <= 4L) %>% 
+        mutate(category = recode(
+          category, "1" = "gm", "2" = "obc", "3" = "scst", "4" = "muslim"
+        )) %>% 
+        group_by(participant, category) %>% 
+        summarise(q1 = mean(q1)) %>% 
+        ungroup() %>% 
+        pivot_wider(
+          names_from = category,
+          names_prefix = "x_q1_",
+          values_from = q1
+        ),
+      by = "participant"
+    ) %>% 
+    mutate_at(vars(starts_with("x_")), as.double) %>% 
+    mutate_at(
+      vars(x_nc_gm, x_of_gm, x_q1_gm), 
[…]

### 2020-04-25 scripts/results_social_change_group_differences.R

@@ -1,128 +1,0 @@
-rm(list = ls())
-
-# Library -----------------------------------------------------------------
-  library(tidyverse); library(tidybayes); library(rstan); library(loo)
-
-  # Stan options
-  options(mc.cores = parallel::detectCores())
-  rstan_options(auto_write = TRUE)
-  seeds = c(6096624, 7239687, 8749870, 6124014, 6071342,
-            6890159, 9814684, 1014316, 5004873, 6578813)
-
-
-# Import ------------------------------------------------------------------
-  dw <- read_rds("data/d2.rds") %>%
-    transmute(
-      participant,
-      ig_caste,
-      ld_ig     = q24_1,
-      ld_scst   = (q24_2 + q24_3)/2,
-      ld_obc    = q24_4,
-      ld_gm     = q24_5,
-      ld_hindu  = q24_6,
-      ld_muslim = q24_7,
-      ps_scst   = (q25 + q26)/2,
-      ps_obc    = (q27 + q28)/2,
-      ps_muslim = q29
-    ) %>%
-    arrange(participant)
-  
-  # Prepare for imputation
-  dl_imp <- dw %>% 
-    gather("item", "y", -participant:-ig_caste) %>%
-    mutate(ii = 1:n()) %>%
-    group_by(item) %>%
-    mutate_at(vars(y), funs(mean, sd), na.rm = TRUE) %>%
-    mutate(y_z = (y - mean) / sd) %>%
-    ungroup() %>%
-    group_by(participant) %>% 
-    mutate(missing = 9 - sum(!is.na(y))) %>%
-    ungroup()
-  
-  # Compose data list
-  data_list <- list(
-    # Numbers
-    N_row = length(dw$participant),
-    N_col = 9,
-    N_obs = sum(!is.na(dl_imp$y)),
-    N_mis = sum(is.na(dl_imp$y)),
-    N_all_obs = dl_imp %>% filter(missing == 0) %>% distinct(participant) %>% nrow(),
-    # Indices
-    ii_obs = dl_imp$ii[!is.na(dl_imp$y)],
-    ii_mis = dl_imp$ii[is.na(!dl_imp$y)],
-    nn_obs = dl_imp %>% filter(missing == 0) %>% distinct(participant) %>% pull(participant),
-    # Vectors
-    x_scst = ifelse(dw$ig_caste == "scst", 1L, 0L),
[…]

### 2020-08-31 manuscript/manuscript.tex
in press

@@
 \documentclass[12pt, a4paper]{article}
-\usepackage[utf8]{inputenc}
 
 % Font
+\usepackage[utf8]{inputenc}
 \usepackage{MinionPro} 
-\input glyphtounicode
+\input{glyphtounicode}
 \pdfgentounicode=1 
@@
 \usepackage[super]{nth}
-\usepackage{csquotes}
 
@@
 \setcounter{secnumdepth}{0}
+\usepackage{authblk}
+\renewcommand\Affilfont{\small}
+\usepackage[hang, flushmargin]{footmisc}
 
 % Language
-\usepackage[american]{babel}
+\usepackage[british]{babel}
 
 % Links
-\usepackage[colorlinks=true, linkcolor=black, urlcolor=black, citecolor=black]{hyperref}
+\usepackage[colorlinks = true, linkcolor = black, urlcolor = black, citecolor = black]{hyperref}
 
@@
 \usepackage{graphicx}
-\usepackage[small, labelfont=it, labelsep=period]{caption}
+\usepackage[small, labelfont = bf, labelsep = newline]{caption}
 
@@
 \usepackage{tabularx}
+\usepackage[table, xcdraw]{xcolor}
 
 % References
-\usepackage[style=apa]{biblatex}
-\DeclareSourcemap{
-  \maps[datatype=bibtex]{
-    \map{
-      \pertype{book}
-      \step[fieldset=location, null]
-      \step[fieldset=address, null]
-    }
-    \map{
-      \pertype{incollection}
-      \step[fieldset=location, null]
-      \step[fieldset=address, null]
-    }
-  }
-}
+\usepackage{csquotes}
+\usepackage[style = apa]{biblatex}
 \addbibresource{references.bib}
-\renewcommand*{\bibfont}{\small}
 
@@
 Intergroup contact fosters more inclusive social identities.
-\textit{Group Processes \& Intergroup Relations}.
-\href{https://doi.org/10.31234/osf.io/zcgwt}{https://doi.org/10.31234/osf.io/zcgwt}}}
-\date{April 6, 2020}
+\textit{Group Processes \& Intergroup Relations.}}}
+\author[1]{Nils Karl Reimer}
+\author[2]{Shanmukh V. Kamble}
+\author[3]{Katharina Schmid}
+\author[1]{Miles Hewstone}
+\affil[1]{University of Oxford, United Kingdom}
+\affil[2]{Karnatak University Dharwad, India}
+\affil[3]{Universitat Ramon Llull, ESADE Business School, Spain}
+\date{June 25, 2020}
 
@@
 Contact and identity processes, however, did not affect entrenched opposition to (or undermine support for) affirmative action in advantaged and disadvantaged groups.\\[1ex]
-\noindent {\footnotesize \textbf{Keywords:} intergroup contact, social identity, multiple categorization, intergroup relations, interminority relations, perceived discrimination, affirmative action}
+\noindent \textbf{Keywords:} intergroup contact, social identity, multiple categorization, interminority relations, perceived discrimination, affirmative action \\[1ex]
 \end{abstract}
 
-\noindent How we feel about and act toward others depends on whom we consider “us” and “them”---that is, whom we include in, and exclude from, our ingroup (for a review, see \nptextcite{reimer_self-categorization_2020}).
-In some situations, this distinction rests on one salient categorization, for example, someone's nationality at an international border.
+\noindent How we feel about and act toward others depends on whom we consider “us” and “them”---that is, whom we include in, and exclude from, our ingroup \parencite[for a review, see][]{reimer_self-categorization_2020}.
+In some situations, this distinction rests on one salient categorization, for example, someone’s nationality at an international border.
 In diverse societies, however, this distinction often depends on multiple, overlapping group memberships.
@@
 Some espouse narrow definitions of who is “us” and “them”, while others adopt more inclusive identities.
-Many Americans, for example, associate being American with being White American \parencite{devos_american_2005}.
-This suggests that whom Americans consider “us” and “them” might depend on someone's race \emph{and} nationality.
+Many Americans, for example, associate being American with being White \parencite{devos_american_2005}.
+This suggests that whom Americans consider “us” and “them” might depend on someone’s race \emph{and} nationality.
 In this paper, we examine how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce prejudice by fostering more inclusive social identities.
-We use a novel method to study social identification across multiple social categories and to examine possible antecedents (intergroup contact, social dominance orientation) and consequences (intergroup attitudes, intergroup threat, support for affirmative action) of more inclusive identities.
+We use a novel method to study social identification across multiple social categories and to examine possible antecedents (intergroup contact, social dominance orientation) and consequences (intergroup attitudes, support for affirmative action, intergroup threat) of more inclusive identities.
 
-\begin{figure*}
-\centering
-\includegraphics[scale=1]{../figures/figure-1}
-\caption{
-Schematic representations of social identity structures \protect\parencite{roccas_social_2002}, ordered by their social identity inclusiveness \protect\parencite{van_dommelen_construing_2015}.
-Shaded regions represent the groups which a participant has to categorize as “us” to be assigned that structure.
-An Indian Hindu, for example, might consider only people who share their nationality, religion, and caste as ingroup members (\emph{intersection}).
-Someone else might consider all their fellow Indians, whatever their religion or caste, as ingroup members (\emph{dominance}).
-Another person might consider anyone who shares their nationality or religion as ingroup members (\emph{merger}).
-}
-\label{fig:f1}
-\end{figure*}
+Social psychologists have highlighted the importance of considering two \parencite{berry_immigration_1997, crisp_multiple_2007, dovidio_commonality_2009} or more \parencite{roccas_social_2002} social categories for understanding intergroup relations.
+\textcite{crisp_multiple_2007} reviewed evidence that we tend to have more favourable attitudes towards people with whom we share some, but not all, group memberships than towards people with whom we do not share any group memberships.
+\textcite{gaertner_reducing_2000} showed that espousing a more inclusive common ingroup identity (e.g., Indian) over a narrower identity (e.g., Hindu) can extend the benefits of ingroup favouritism to outgroup members and thus reduce intergroup bias.
+\textcite{roccas_social_2002} recognized that, though we all hold multiple overlapping group memberships, we differ in how we construct our social identities from them.
+Broadly, these perspectives recognize that we belong to multiple overlapping groups; that we use these group memberships to construct a subjective sense of who is “us” and “them”; and that espousing more inclusive social identities can reduce prejudice and discrimination.
 
-Social psychologists highlighted the importance of considering two \parencite{berry_immigration_1997, crisp_multiple_2007, dovidio_commonality_2009} or more \parencite{roccas_social_2002} social categories for understanding intergroup relations.
-\textcite{crisp_multiple_2007} reviewed evidence that we tend to have more favourable attitudes towards people with whom we share some, but not all, group memberships than towards people with whom we do not share any group memberships.
-\textcite{gaertner_reducing_2000} showed that espousing a more inclusive common ingroup identity (e.g., Indian) over a narrower identity (e.g., Hindu, Muslim) can extend the benefits of ingroup favouritism to outgroup members and thus reduce intergroup bias.
-\textcite{roccas_social_2002} recognized that, though we all hold multiple overlapping group memberships, we differ in how we construct our social identities from these group memberships.
-Broadly, these perspectives recognize that we are part of multiple overlapping groups; that we use these group memberships to construct a subjective sense of who is “us” and “them”; and that espousing more inclusive social identities can reduce prejudice and discrimination.
-
-Diverse societies confront their members with the decision of which intersections of various group memberships to include in their subjective ingroup.
-One Indian Hindu, for example, might constrict their ingroup to people of the same nationality, religion, and caste.
-Another Indian Hindu might consider all Indians, whatever their religion or caste, as ingroup members (see Figure~\ref{fig:f1}).
+Diverse societies confront their members with the decision of which intersections of various group memberships to include in their ingroup.
+One Indian Hindu, for example, might restrict their ingroup to people of the same nationality, religion, and caste.
+Another Indian Hindu might consider all Indians, whatever their caste or religion, as ingroup members (Figure~\ref{fig:f1}).
 Past research \parencite{van_dommelen_construing_2015} indeed observed substantial individual differences in whom participants considered “us” and “not us”.
@@
 Other participants espoused less inclusive social identities---that is, they included fewer people in their subjective ingroup.
-All participants, however, belonged to the same disadvantaged minority group.
+All participants \parencite[studied by][]{van_dommelen_construing_2015}, however, belonged to the same disadvantaged minority group.
 Past research thus provided evidence for individual differences, but did not examine group differences in whom people consider “us” and “not us”.
+
+\begin{figure}
+\centering
+\caption{
+Schematic representations of social identity structures \protect\parencite{roccas_social_2002}, ordered by their social identity inclusiveness \protect\parencite{van_dommelen_construing_2015}
+}
+\includegraphics[scale=1]{../figures/figure-1}
+\caption*{\textit{Note.} Shaded regions represent the groups which a participant has to categorize as “us” to be assigned that structure.
+An Indian Hindu, for example, might consider only people who share their nationality, religion, and caste as ingroup members (\emph{intersection}).
+Someone else might consider all their fellow Indians, whatever their religion or caste, as ingroup members (\emph{dominance}).
+Another person might consider anyone who shares their nationality or religion as ingroup members (\emph{merger}).}
+\label{fig:f1}
+\end{figure}
+
+Group membership, however, often shapes whom people include in, and exclude from, their subjective ingroup.
+For majority-group members, negotiating their ethnic and national identities means something different than for minority-group members \parencite[for a review, see][]{dovidio_commonality_2009}.
+Majority-group members face the choice of including or excluding ethnic, religious, and other minorities from their subjective ingroup.
+Choosing to include or exclude minorities could, for example, reflect whether a majority-group member holds multicultural or nativist views.
+Minority-group members face the choice of aligning themselves with the dominant majority group or seeking a common ingroup identity with other minority groups.
+We expect that group differences are as great as, if not greater than, individual differences in social identity construals---especially if groups differ in status and power.
+Our research includes participants from advantaged, intermediate, and disadvantaged backgrounds to study how groups differ in terms of whom their members consider “us” and “not us”.
+
+How we think and feel about others depends on whether we include them in our ingroup.
+Dividing others into “us” and “not us” is thus a necessary and sufficient condition for ingroup favouritism \parencite{tajfel_human_1981}.
+Past research has shown that people favour ingroup members in resource allocation \parencite{tajfel_social_1971}, in causal attribution \parencite{hewstone_ultimate_1990, taylor_ethnocentrism_1974}, in helping behaviour \parencite{levine_identity_2005}, in information processing \parencite{van_bavel_neural_2008}, and in evaluation \parencite{otten_evidence_2000}.
+Considering more people as “us” should extend ingroup favouritism to a wider range of people, and thus reduce prejudice and discrimination \parencite[for a review, see][]{nelson_common_2016}.
+Our research examines whether fostering more inclusive social identities leads to more favourable attitudes and less social distance toward national, religious, and caste outgroups.
+
+Contact with members of other groups changes how we think and feel about them.
+Past research has shown that intergroup contact reduces prejudice \parencite{pettigrew_meta-analytic_2006} by decreasing intergroup anxiety, increasing empathy and perspective-taking, and by increasing knowledge about the other group \parencite{pettigrew_how_2008}.
+In addition, researchers have proposed that contact could reduce prejudice by changing how we see ourselves \parencite{pettigrew_generalized_1997, pettigrew_intergroup_1998}.
+Encountering diverse others could initiate a process of cognitive differentiation \parencite{kramer_social_2011} whereby individuals become aware of complex interrelations between their group memberships and adopt more complex social identities \parencite{schmid_antecedents_2009}---that is, they become aware that they belong to multiple categories and recognize that these multiple categories do not always overlap \parencite{van_dommelen_construing_2015}.
+Other research has found that intergroup contact can, under the right conditions, motivate people to adopt a more inclusive common ingroup identity \parencite{gaertner_contact_1994} and to include the outgroup in their self-concept \parencite{page-gould_understanding_2010}.
+If intergroup contact motivates people to adopt social identities that include outgroup members, it should reduce prejudice and discrimination against them.
+Our research examines whether intergroup contact can reduce prejudice against religious and caste outgroups by fostering social identities that include them as ingroup members.
+
+Beyond prejudice, researchers have debated whether, by fostering more inclusive identities, intergroup contact helps or hinders social change.
+Social change often requires advantaged and disadvantaged groups to strive for redistributive policies.
+On the one hand, fostering inclusive identities could break down the boundaries between the advantaged ingroup and the disadvantaged outgroup---turning injustice faced by “them” into “our” problem.
+This process could narrow the gap between advantaged-group members’ support for the principle of equality and their opposition to its implementation \parencite{dixon_intergroup_2007}.
+On the other hand, fostering more inclusive identities could distract disadvantaged-group members from differences in resources and power, and thus reduce their demands for and support for social change \parencite{dixon_attitudes_2012, saguy_irony_2009}.
+Together, these mechanisms suggest that fostering more inclusive identities could increase support for social change among the advantaged, but decrease support among the disadvantaged.
+Our research examines how intergroup contact, by fostering more inclusive social identities, affects support for affirmative action policies, as well as perceptions of relative (dis-)advantage, in advantaged and disadvantaged groups.
+
+Most research on intergroup relations examines relations between an advantaged majority group and a disadvantaged minority group.
+Most social contexts, however, feature various groups facing various disadvantages.
+\textcite{craig_coalition_2012} argued that racial minorities may respond to the disadvantages they face by derogating other racial minorities or by forming a coalition with them.
+They showed that perceiving discrimination can, as far as it fosters a shared ingroup identity with other disadvantaged groups, improve interminority relations.
+\textcite{vollhardt_inclusive_2016} observed that South Indians from disadvantaged caste and religious groups were more likely to express support for another disadvantaged group when they recognized similarities between their own and other groups’ experiences of discrimination.
+\textcite{dixon_contact_2017} found that Indian Muslims who reported having more contact with other disadvantaged groups were also more likely to recognize shared grievances and to express support for collective action benefiting all disadvantaged groups.
+Our research adds to this literature by examining intergroup relations between two disadvantaged groups, one of which occupies an intermediate position in the social hierarchy.
+We examine whether, by fostering shared ingroup identities, contact between disadvantaged groups can foster more positive intergroup relations, shared perceptions of disadvantage, and mutual support for affirmative action.
+
+\subsection{Caste, Religion, Nation in South India}
+
+We investigated these questions in the context of caste, religion, and nationality in South India.
+India provides an important context for studying social identification across multiple social categories.
+India is diverse.
+Indians belong to different castes, religions, and other groups that intersect in numerous ways.
+India is also underrepresented in psychological research.\footnote{Among the societies underrepresented in psychological research (Henrich et al., 2010), India is a prominent omission as it spans almost a fifth of the world’s population.} Few studies of intergroup relations \parencite[e.g.,][]{ghosh_hindu-muslim_1991, tausch_relationships_2009} focus on religious relations in India.
+Even fewer \parencite[e.g.,][]{cotterill_ideological_2014} focus on caste relations.
+Our research examined the cross-cutting categories of caste, religion, and nationality in a diverse sample of South Indian students.
+
+Caste is a system of social relations that concentrates resources in the hands of dominant castes by restricting subordinate castes’ occupations and by enforcing segregation and endogamy \parencite{jodhka_caste_2012}.
+This system is underpinned by a tradition that conveys caste through markers such as surname and diet, ranks castes according to their supposed ritual purity, and condemns contact with supposedly less pure castes.
+This tradition includes the practice of untouchability which excludes some castes from public life and consigns them to landlessness and menial labour.
+Dalits, members of castes that have been subjected to untouchability, still face interpersonal discrimination and economic inequalities resulting from this (now illegal) practice.
+Since Independence, the Indian State has sought to redress caste-based injustices by reserving seats in state-run universities and state-sector jobs for ‘Scheduled Castes’ (the official term for Dalits) and ‘Scheduled Tribes’ (the official term for Adivasi, India’s indigenous peoples).
+Reservation policies, along with persistent discrimination, mean that caste identities continue to structure people’s lives.
+
+Caste identities have different meanings for disadvantaged, advantaged, and intermediate groups.
+For the most disadvantaged, caste is often defined by their experience of discrimination and their resistance against it \parencite{jodhka_caste_2012}.
+Dalits have built movements to assert their economic and political rights---founding, for example, the Bahujan Samaj Party in 1984---and thus created a positive identity around their resistance against oppression.
+Dalits, however, often face violent backlash when asserting their rights \parencite[e.g.,][]{noauthor_15_2017}.
+For the most advantaged, Dalit emancipation threatens their social and economic dominance.
+Reservation policies, for example, restrict access to university seats for upper-caste applicants who must compete with all other applicants in the ‘General Merit’ category.
+Other groups occupy an intermediate position in the caste hierarchy.
+In 1990, the government extended reservations to ‘Other Backward Classes’, that is, communities that were socially and educationally disadvantaged, but had not been subjected to untouchability.
+For intermediate groups, caste is often defined by the question whether they can gain or maintain access to reserved university seats and government jobs.
+As a result, caste identities remain important in Indian politics.
+
+South India is religiously diverse.
+In Karnataka, where we conducted this research, 84\% of inhabitants are Hindus, while 13\% are Muslims.
+Muslims face both structural inequalities and communal violence.
+In 2002, for example, over a thousand Muslims were killed in a pogrom in Gujarat \parencite{dhattiwala_political_2012}.
+In recent years, anti-Muslim violence has been increasing \parencite{amnesty_international_india:_2017}.
+Religion is intertwined with two currents of Indian nationalism \parencite{katz_hindu_2009}.
+On the one hand, the secular foundations of the Indian State resulted from an inclusive nationalism that strives to include Indians of all religions.
+On the other hand, Hindu nationalism (Hindutva) is an ideology that equates being Indian with being Hindu, thus excluding Muslims from the national identity.
+Narendra Modi’s Bharatiya Janata Party (BJP) government espouses Hindutva and enjoyed broad support at the time of our study \parencite{pew_research_center_three_2017}.
+Indians thus face a choice between two ideologies that either include Indian Muslims in the national identity or exclude them from it.
+
+\subsection{Present research}
+
+Our research used a novel method to study social identification across multiple categories in a sample of South Indians from diverse caste backgrounds.
+We examined how people construct their social identities from multiple group memberships, whether intergroup contact is associated with more inclusive social identities, and how more inclusive social identities relate to prejudice and support for social change.
+Below, we introduce the experimental task before reviewing our research questions and hypotheses.
+
+We adapted the triple crossed-categorization task \parencite{van_dommelen_construing_2015} to assess how participants construct their social identities from multiple group memberships.
+In this task, participants view identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships.
+Participants report whether they consider each person as “us” or “not us”, showing whom they include in, or exclude from, their ingroup.
+This task allowed us to study identification across multiple social categories and how it relates to the predictors and outcomes in our hypotheses.
+Van Dommelen et al.
+\citeyear{van_dommelen_construing_2015} used a similar task to examine whom participants considered “us” and “not us”.
+However, their research included participants from only one group, aggregated participants’ categorizations into a single score, and tested whether that score correlated with aggregated responses to contact and attitude measures.
+Our research included participants from multiple groups and used multilevel modeling to test whether contact with and attitudes toward \emph{each} group were associated with the inclusion of \emph{that} group in one’s social identity.
+This allowed for a more fine-grained analysis of individual and group differences in identification across multiple social categories.
+
+We pursued four research questions.
+First, we examined how participants’ group memberships shaped whom they included in, and excluded from, their ingroup (\emph{group differences}).
+We hypothesized that participants would exclude targets from religious and national outgroups---and that participants from advantaged castes would exclude targets from disadvantaged castes, and vice versa.
+We did not have a clear prediction for participants from intermediate backgrounds.
+Second, we examined whether past experiences with members of caste and religious outgroups shaped whom participants included in, and excluded from, their ingroup (\emph{individual differences}).
+We hypothesized that positive contact and cross-group friendship would be associated with more---and negative contact \parencite{barlow_contact_2012, hayward_toward_2017} with less---inclusive social identities.
+Third, we examined whether, by fostering more inclusive social identities, intergroup contact would be associated with less prejudice (\emph{intergroup attitudes}).
+We hypothesized that categorizing someone as “us” would be associated with more favourable attitudes and less social distance toward that person.
+Fourth, we examined how intergroup contact, by fostering more inclusive social identities, affects support for affirmative action in advantaged and disadvantaged groups (\emph{support for social change}).
+We hypothesized that more inclusive social identities would be associated with less perceived discrimination and less support for affirmative action among the disadvantaged, and with more perceived privilege and more support for affirmative action among the advantaged.
+
+In addition, we explored how two other constructs related to more inclusive social identities.
+First, we examined ideological preferences for group dominance \parencite{sidanius_social_1999} as an additional predictor variable to rule out a potential confound, whereby people high in social dominance orientation might both eschew contact with caste and religious minorities and exclude them from the common ingroup.
+Second, we examined perceptions of intergroup threat as an additional outcome variable to test whether more inclusive identities were associated with this more distal outcome.
+Perceptions of intergroup threat play an important role in shaping intergroup relations \parencite[for a review, see][]{nelson_intergroup_2016}.
+We examined whether participants who included caste and religious minorities in their ingroup would, in addition to feeling more warmth and less social distance toward them, feel less threatened by them in terms of both realistic and symbolic threat.
+As we had not planned our study with clear directional predictions concerning social dominance orientation and intergroup threat, we consider these additional analyses exploratory.
+
+\section{Method}
+
+All materials, data, analysis scripts, and appendices are available online.\footnote{\protect\href{https://doi.org/10.17605/OSF.IO/QPCRM}{https://doi.org/10.17605/OSF.IO/QPCRM}} Here, we only report measures testing our hypotheses, omitting measures replicating earlier research or validating the experimental task (Appendix A).
+Reanalysing existing data \parencite{van_dommelen_construing_2015}, we determined that $\sim 100$ respondents per group would allow reasonably precise estimates of model parameters (Appendix B).
+We report descriptive statistics and correlations in Appendix C.
+
+\subsection{Participants}
+
+We recruited 351 students at Karnatak University (Dharwad, India).
+Of these, we excluded 49 participants who did not belong to any of four caste groups (n = 20), failed to indicate their caste group ($n = 7$), and/or reported Islam as their own or their family’s religion ($n = 27$).\footnote{Because Muslims---unlike Jains and Christians---featured in the experimental task, we would have had to consider them as a distinct group in the analyses.
+As this subsample was too small for any meaningful analyses, we instead opted to exclude Muslim participants.} This left 302 participants who reported Hinduism ($n = 286$), Jainism ($n = 8$), or Christianity ($n = 8$) as their or their family’s religion, and General Caste ($n = 99$), Other Backward Class ($n = 127$), Scheduled Caste ($n = 54$), or Scheduled Tribe ($n = 22$) as their caste group.
+Table~\ref{tab:t1} summarizes participants by gender, age, nationality, religion, and caste.
+
+\begin{table}    
+\caption{Participants by gender, age, nationality, religion, and caste. Categories in \textit{italics} were excluded from the final sample. N/A marks missing responses.}
+\centering
+\figureversion{lining, tabular}
+\small	
+\begin{tabular}{llrr} \addlinespace \toprule
+\multicolumn{2}{l}{Category} & $n$ & \% \\ \midrule \addlinespace 
+Gender      & Woman      & 215 & 61 \\
+            & Man & 121 & 34 \\
+            & Other & 0 & 0 \\
+            & N/A & 15 & 4 \\ \addlinespace \addlinespace
+Age         & 18--20 & 1 & 0 \\
+            & 21--23 & 254 & 72 \\
+            & 24--26 &  77 & 22 \\
+            & 27--29 &  10 &  3 \\
+            & 30--32 &   1 &  0 \\
+            & 33--35 &   0 &  0 \\
+            & 36 or older & 1 & 0 \\ 
+            & N/A & 7 & 2 \\ \addlinespace \addlinespace
+Nationality & Indian & 339 & 97 \\
+            & Other & 0 & 0 \\
+            & N/A & 12 & 3 \\ \addlinespace \addlinespace
+Religion    & Buddhism & 1 & 0 \\ 
+            & Christianity & 11 & 3 \\ 
+            & Hinduism & 297 & 85 \\ 
+            & \textit{Islam} & \textit{27} & \textit{8} \\ 
+            & Jainism & 8 & 2 \\ 
+            & Other & 2 & 1 \\ 
+            & N/A & 5 & 1 \\ \addlinespace \addlinespace
+Caste       & General Caste & 104 & 30 \\ 
+            & Other Backward Class & 143 & 41 \\ 
+            & Scheduled Caste & 54 & 15 \\ 
+            & Scheduled Tribe & 23 & 7 \\ 
+            & \textit{Other / Not applicable} & \textit{20} & \textit{6} \\ 
+            & \textit{N/A} & \textit{7} & \textit{2} \\ \addlinespace \midrule
+Total       &   & 351 & 100 \\ \bottomrule
+\end{tabular}
+\label{tab:t1}
+\end{table}
+
+\subsection{Procedure}
+
+Participants completed a triple crossed-categorization task, in which they viewed 24 identity cards.
+Each showed a fictitious person’s name, age, religion, nationality, caste reservation, and a head-and-shoulders silhouette.
+Based on a pilot study, we manipulated the target’s caste, religion, and nationality such that each target represented a person with whom participants shared none, one, two, or three group memberships (Figure~\ref{fig:f2}).
+We tested participants in classrooms of 24--71 students by presenting targets in a slide-based presentation and by handing each student a pen-and-paper questionnaire.
+Each slide contained a male and a female target with participants focusing on the target corresponding to their gender.
+Slides also contained a number identifying each target, and response scale(s) corresponding to the question(s) participants answered at the time.
+
+\begin{figure}
+\caption{Examples of targets used in the triple crossed-categorization task}
+\centering
+\includegraphics[scale=1]{../figures/figure-2}
+\caption*{\textit{Note.} Based on ratings in a pilot study ($N = 26$), we selected the four most prototypical targets (out of fifty initial targets) for each of six plausible combinations of caste, religion, and nationality (for details, see Appendix~D).
+Each target showed a person's caste reservation (GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe), religion (Hindu, Muslim), and nationality (Indian, Nepali, Sri Lankan, Bangladeshi).
+Each target also showed the person's first and last name, age (21--26 years), and a silhouette corresponding to the person's gender \protect\parencite[adapted from][]{ma_chicago_2015}.
+Each target's age and silhouette, as well as the order in which the targets were presented, varied across sessions.}
+\label{fig:f2}
+\end{figure}
+
+In each session, participants first familiarized themselves with each target (shown for 7 s in a randomized order) in an automated slide show.
+Participants viewed targets (in the same order) for a second time, noting for each target whether they felt that this person was one of their own group (1 = “us”), or not one of their own group (0 = “not us”).
+Participants viewed targets for a third time, rating how comfortable or uncomfortable they would feel to share a room with this person (social distance; 1 = \textit{very uncomfortable}, 7 = \textit{very comfortable}), and how they felt toward this person (feeling thermometer; 0 = \textit{cold}, 100 = \textit{warm}).
+Participants then completed the measures described below.
+
+\subsection{Measures}
+
+We report one of two reliability indices for our measures, the Spearman-Brown statistic ($\rho$) for two-item measures \parencite{eisinga_reliability_2013} and McDonald’s omega ($\omega$) for multi-item measures \parencite{dunn_alpha_2014}.
+
+We measured intergroup contact as: how often, from 1 = \textit{never} to 5 = \textit{very often,} participants meet outgroup members in their everyday life (contact quantity), and how often, on average, they have positive/good contact and negative/bad contact with outgroup members \parencite{barlow_contact_2012}.
+We preceded these items with examples of positive and negative contact experiences.
+We measured cross-group friendship with two items \parencite{turner_reducing_2007}: “How many close friends do you have who are [outgroup members]?” (1 = \textit{none}, 5 = \textit{more than ten}), and “How often do you spend time with [outgroup] friends?” (1 = \textit{never} to 5 = \textit{very often}; $.65 < \rho < .71$).
+Participants reported contact with four groups: Dalits, people from other backward classes, people from general castes, and Muslims.
+
+We measured social dominance orientation as how much, between 1 = \textit{strongly oppose }and 7 = \textit{strongly favour}, participants endorsed eight statements about social hierarchies \parencite{ho_nature_2015}.
+Four items measured support for group-based dominance (SDO-Dominance), for example, “some groups of people are simply inferior to other groups”.
+Four items measured opposition to egalitarian ideologies (SDO-Egalitarianism), for example, “it is unjust to try to make groups equal”.\footnote{Replicating \protect\textcite['s][]{ho_nature_2015} findings, we found a four-factor model (with two method factors) to represent the data better than the one-factor ($\Delta\chi^2 = 155.14, p < .001$) or two-factor ($\Delta\chi^2 = 138.67, p < .001$) alternatives.
+Accounting for this structure, we used latent factor scores for SDO-Dominance and SDO-Egalitarianism in our analyses.}
+
+We measured realistic threat---from Muslims and Dalits---with three items per outgroup \parencite{schmid_reducing_2014}, e.g., “the more power [Muslims/Dalits] gain in this country, the more difficult it is for [Hindus/people from my caste group]” (1 = \textit{strongly disagree}, 5 = \textit{strongly agree}; $\omega_\textit{Muslims} = .71, \omega_\textit{Dalits} = .79$).
+Two items measured symbolic threat, e.g., “[Muslims/Dalits] threaten [Hindus’/my caste group’s] way of life” (1 = \textit{strongly disagree}, 5 = \textit{strongly agree}; $\rho_\textit{Muslims} = .61, \rho_\textit{Dalits} = .65$).
+
+We measured perceived (dis-)advantage as how easy or hard participants thought it was, on average, for people from various groups to succeed in India today (1 = \textit{very hard}, 7 = \textit{very easy}).
+Participants rated seven groups: People from your own background, Scheduled Caste, Scheduled Tribe, Other Backward Class, General Caste, Hindus, and Muslims.
+
+Five items measured policy support.
+Participants read that “currently, 22.5\% of seats in central-government funded universities are reserved for Scheduled Caste and Scheduled Tribe students”, and that “an additional 27.5\% of seats in central-government funded universities are reserved for students from Other Backward Classes”.
+Participants indicated to what extent they opposed or supported reservation in higher education for students from each group (1 = \textit{strongly oppose}, 5 = \textit{strongly support}), and whether they thought that reservation in higher education for students from that group should increase, decrease, or remain unchanged (1 = \textit{decrease a lot}, 5 = \textit{increase a lot}; $\rho_\text{SC/ST} = .80, \rho_\text{OBC} = .80$).
+Participants then read that “no seats in central-government funded universities are reserved for Muslim students nationally, though some states have introduced quotas for Muslim students”.
+Participants indicated to what extent they opposed or supported reservation for Muslim students.
+
+\subsection{Analysis strategy}
+
+To answer our research questions, we used various (generalized) linear regression models.
+Specifically, we examined: (1) \emph{group} and \emph{individual differences} in how likely participants were to categorize different targets as “us” in a series of multilevel logistic models with participants’ target categorizations (1 = “us”, 0 = “not us”) as outcome variable; (2) consequences of participants’ target categorizations for \emph{intergroup attitudes} in a series of multilevel multivariate linear models with participants’ target-wise social distance and feeling thermometer ratings as outcome variables; and (3) consequences for \emph{support for social change} in a series of multivariate linear models with participants’ group-wise perceived (dis-)advantage and policy support ratings as outcome variables.
+We also explored whether participants’ target categorizations were associated with their intergroup threat ratings using multilevel linear models.
+
+We estimated models in RStan \parencite{stan_development_team_rstan:_2020} using Bayes\-ian statistical methods.
+Bayesian inference involves choosing a likelihood function and prior distributions.
+The likelihood function links the observed data to one or more model parameters (e.g., regression coefficients) and states how likely the observed data are given different values of said model parameters.
+Our models derived the likelihood of the observed responses from a generalized linear model with a logit link function or a linear model with a (multivariate) normal distribution.
+Prior distributions state how plausible different values of said model parameters are before considering the observed data.
+Our models assigned conservative, weakly informative prior distributions to all model parameters \parencite{gelman_prior_2017}.\footnote{Specifically, we used $\beta \sim \text{Student-t}(2.5, 0, 1)$ for fixed effects in logistic models, $\beta \sim \text{Normal}(0, 1)$ for fixed effects in linear models, $\Omega \sim \text{LKJ}(4)$ for residual covariances in multivariate models, and $\sigma \sim \text{Half-Cauchy}(0, 1)$ for standard deviations of varying effects in multilevel models and for residual standard deviations in linear models.} Bayesian inference applies Bayes’ theorem to update prior distributions in light of the observed data to produce posterior distributions.\footnote{For a detailed introduction, consult \textcite{gelman_bayesian_2014}, \textcite{lambert_students_2018}, and \textcite{mcelreath_statistical_2016}.} Other than \textit{p}-values and confidence intervals, the resulting posterior distributions have a straight-forward interpretation as stating how plausible different values of the model parameters are given the observed data.
+
+We tested our hypotheses in two steps.
+First, we compared models that corresponded to our hypotheses and selected the model that made the most accurate predictions.
+For example, we compared a model which estimated the probability of participants’ categorizing a target as “us” in the experimental task as \emph{varying} across the participants’ group memberships to a simpler model which constrained this probability to be \emph{fixed} across the participants’ group memberships.
+When the former made more accurate predictions than the latter, we considered this evidence that, as hypothesized, participants from advantaged and disadvantaged groups differed in how likely they were to categorize targets as “us”.
+Second, we inspected estimates from the selected model to examine whether model estimates were in the hypothesized direction.
+For example, we found that, as hypothesized, the selected model estimated advantaged-group participants to be less likely than disadvantaged-group participants to categorize disadvantaged-group targets as “us” ($\Pr = .80, [.73, .85]$ versus $\Pr =  .97, [.95, .98]$; $\Delta\Pr =  -.17, [-.23, -.12]$).
+For each model estimate, we report a point estimate and an uncertainty interval enclosing the 97\% most plausible estimates.
+
+One way to compare statistical models is to estimate how well each model predicts observations \emph{within} the sample.
+This approach underlies comparison methods based on the relative log-likelihood of each model, such as likelihood-ratio tests or Bayes factors.
+This approach has well-known shortcomings, such as being sensitive to the specific prior distributions \parencite{gelman_bayesian_2014} and prone to overfitting \parencite{yarkoni_choosing_2017}.
+Instead, we compared models by estimating how well each predicts observations \emph{outside} the sample used to estimate it.
+We used 10-fold cross-validation, dividing observations into 10 folds, estimating model parameters using observations from 9 folds, calculating the model’s out-of-sample prediction accuracy for the remaining observations, and repeating the last two steps until we had estimated the model’s out-of-sample prediction accuracy for all observations.\footnote{Specifically, we used \emph{stratified} cross-validation to account for the nestedness of our observations, ensuring that each fold contained a similar number of responses from each participant.} Using cross-validation to compare statistical models balances the risks of underfitting and overfitting models to the available data \parencite{yarkoni_choosing_2017}.
+
+As a measure of out-of-sample prediction accuracy, we calculated each model’s expected log predictive density (\textit{ELPD}), that is, the logarithm of the joint posterior predictive probability of all observations.
+We report two statistics derived from these densities.
+First, we calculated Pseudo Bayesian Model Averaging (Pseudo-BMA) weights \parencite[using the Bayesian bootstrap method;][]{yao_using_2018} which, for a set of models, represent each model’s relative out-of-sample prediction accuracy as a proportion of the total out-of-sample prediction accuracy of all models.
+Second, we calculated the difference in out-of-sample prediction accuracy for each pair of models ($\Delta\textit{ELPD}$), with positive values indicating that a model makes more accurate predictions than a comparison model.
+We divided this difference by its standard error ($\Delta\textit{ELPD}/\text{SE}$) to account for the uncertainty of cross-validation as an estimate of out-of-sample prediction accuracy \parencite{vehtari_practical_2017}.
+We selected a more complex over a simpler model when the more complex model had the greater Pseudo-BMA weight and when the difference in prediction accuracy was much larger than its standard error.
+
+To help readers trained in classical statistics, we also report a Bayesian analogue of $R^2$ \parencite{gelman_r-squared_2019} and critical values that allow readers to conduct null-hypothesis significance tests for model comparisons.
+
+\section{Results}
+
+We followed the analysis strategy described above to estimate \emph{group differences }in whom participants categorized as “us” and “not us”;  to examine to what extent intergroup contact and ideological orientations explained \emph{individual differences} in participants’ categorizations; and to test whether participants’ categorizations were associated with \emph{intergroup attitudes}, \emph{support for social change}, and \emph{intergroup threat}.
+
+\subsection{Group differences}
+
+Across four logistic regression models, we examined \emph{how likely	} participants were to categorize \emph{which} target as “us” versus “not us” and how that probability varied as a function of the participants’ and targets’ group memberships.
+
+First, we compared the four models and selected the model that made the most accurate out-of-sample predictions.
+Model 0 estimated the probability of participants categorizing a target as “us” as varying across participants but as fixed across the targets’ and the participants’ group memberships.
+As such, this model served as a null model to which we compared other models.
+Model 1 estimated the probability of participants categorizing a target as “us” as varying across the targets’ group memberships but as fixed across the participants’ group memberships.
+As Table~\ref{tab:t2} shows, Model 1 made much more accurate out-of-sample predictions than Model 0 ($\Delta\textit{ELPD}/\textit{SE} = 25.9$)---showing that, as hypothesized, the probability of participants categorizing a target as “us” varied across the targets’ group memberships.
+Models 2 and 3 estimated the probability of participants categorizing a target as “us” as varying across both the targets’ and the participants’ group memberships.
+Model 2 estimated this probability as differing between disadvantaged-group participants and all other participants.
+Model 3 extended Model 2 by estimating this probability as differing between participants from disadvantaged (SC/ST: Scheduled Caste/Scheduled Tribe), intermediate (OBC: Other Backward Class), and advantaged (GM: General Merit) groups.
+As Model 3 made more accurate predictions than Models 0--2, we concluded that, as hypothesized, participants’ categorizations differed across both the targets’ and the participants’ group memberships.
+
+\begin{table}
+\caption{Comparison of logistic regression models estimating group and individual differences in whom participants categorize as “us” and “not us”}
+\centering
+\figureversion{lining, tabular}
+\small
+\begin{tabularx}{\linewidth}{rXrrrrr} \toprule
+\textbf{(A)} & \textit{\textbf{Group differences}} & \multicolumn{1}{l}{} & \multicolumn{4}{c}{$\Delta\textit{ELPD}/\textit{SE}$}                                                                                    \\ \cmidrule{4-7}
+\#           & Description                         & \textit{w}           & M0                          & M1                           & M2                           & M3                           \\ \midrule
+M0           & Varying intercept (Participants)    & .00                  & {\color[HTML]{E0E0E0} 0.0}  & {\color[HTML]{B2182B} -25.9} & {\color[HTML]{B2182B} -27.0} & {\color[HTML]{B2182B} -27.2} \\
+M1           & M0 + Varying intercept (Categories) & .00                  & {\color[HTML]{2166AC} 25.9} & {\color[HTML]{E0E0E0} 0.0}   & {\color[HTML]{B2182B} -6.8}  & {\color[HTML]{B2182B} -7.1}  \\
+M2           & M1 + Varying effect (SC/ST)         & .02                  & {\color[HTML]{2166AC} 27.0} & {\color[HTML]{2166AC} 6.8}   & {\color[HTML]{E0E0E0} 0.0}   & {\color[HTML]{F4A582} -2.3}  \\
+M3           & M2 + Varying effect (OBC)           & .98                  & {\color[HTML]{2166AC} 27.2} & {\color[HTML]{2166AC} 7.1}   & {\color[HTML]{92C5DE} 2.3}   & {\color[HTML]{E0E0E0} 0.0}   \\ \bottomrule \addlinespace
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{rXrrrrrr} \toprule
+\textbf{(B)} & \textit{\textbf{Individual differences}} & \multicolumn{1}{l}{} & \multicolumn{5}{c}{$\Delta\textit{ELPD}/\textit{SE}$}                                                                                    \\ \cmidrule{4-8}
+\#           & Description                         & \textit{w}           & M3                          & M4                          & M5                          & M6                          & M7                         \\ \midrule
+M3                               & Group differences (SC/ST, OBC)           & .00                  & {\color[HTML]{E0E0E0} 0.0}  & {\color[HTML]{D6604D} -3.2} & {\color[HTML]{B2182B} -3.5} & {\color[HTML]{B2182B} -3.3} & {\color[HTML]{E0E0E0} 1.4} \\
+M4                               & M3 + Fixed effects (QC + PC + NC + OF)   & .08                  & {\color[HTML]{4393C3} 3.2}  & {\color[HTML]{E0E0E0} 0.0}  & {\color[HTML]{B2182B} -3.8} & {\color[HTML]{E0E0E0} -0.8} & {\color[HTML]{2166AC} 3.5} \\
+M5                               & M4 + Fixed effects (NC + OF)             & .59                  & {\color[HTML]{2166AC} 3.5}  & {\color[HTML]{2166AC} 3.8}  & {\color[HTML]{E0E0E0} 0.0}  & {\color[HTML]{E0E0E0} 0.5}  & {\color[HTML]{2166AC} 3.8} \\
+M6                               & M5 + Varying effects (NC + OF)           & .33                  & {\color[HTML]{2166AC} 3.3}  & {\color[HTML]{E0E0E0} 0.8}  & {\color[HTML]{E0E0E0} -0.5} & {\color[HTML]{E0E0E0} 0.0}  & {\color[HTML]{2166AC} 3.5} \\
+M7                               & M3 + Fixed effects (SDO-D + SDO-E)       & .00                  & {\color[HTML]{E0E0E0} -1.4} & {\color[HTML]{B2182B} -3.5} & {\color[HTML]{B2182B} -3.8} & {\color[HTML]{B2182B} -3.5} & {\color[HTML]{E0E0E0} 0.0} \\ \bottomrule \addlinespace
+\end{tabularx}
+\label{tab:t2}
+\caption*{\textit{Note.} $w$ is the weight of each model based on its relative out-of-sample prediction accuracy.
+$\Delta\textit{ELPD}/\textit{SE}$ is the difference in out-of-sample prediction accuracy between each pair of models, divided by its standard error.
+For a conventional interpretation, consider the critical values to be $|\Delta\textit{ELPD}/\textit{SE}| > 1.96$ for $p < .05$, 2.58 for $p < .01$, and 3.29 for $p < .001$ in a two-sided null-hypothesis significance test.
+QC = quantity of contact, PC = positive contact, NC = negative contact, OF = outgroup friendship, SDO-D = Dominance, SDO-E = Egalitarianism}
+\end{table}
+
+Second, we inspected estimated probabilities from Model 3 to examine whether group differences were in the hypothesized direction.
+Specifically, we examined whether, as hypothesized, participants from all backgrounds tended to exclude targets from religious and national outgroups---and whether participants from advantaged castes tended to exclude targets from disadvantaged castes, and vice versa.
+
+As Figure~\ref{fig:f3} shows, we found that participants from all backgrounds tended to exclude targets from national and religious outgroups.
+As predicted, few participants categorized Bangladeshi Muslims, who are both a national and a religious outgroup, as “us” ($\Pr = .17, [.14, .21]$).
+Participants were somewhat more likely to categorize Sri Lankan and Nepali Hindus, who are a national but not a religious outgroup for most participants, as “us” ($\Pr = .46, [.40, .52]$)---although GM, OBC and SC/ST participants were still, respectively, $1.90, [1.71, 2.15]$; $1.98, [1.77, 2.25]$, and $1.90, [1.70, 2.16]$ times more likely to categorize Indian Hindus, who are both a national and a religious ingroup, as “us”.
+Compared to Indian Hindu targets, GM ($\Pr = .84, [.80, .87]$), OBC ($\Pr = .84, [.80, .87]$), and SC/ST ($\Pr = .47, [.38, .57]$) participants were less likely to include Indian Muslim targets, who are a religious but not a national outgroup, in their ingroup.
+As hypothesized, we thus found strong evidence that participants from all caste groups espoused social identities that excluded national and religious outgroups.
+
+\begin{figure}
+\caption{Estimated probability of participants categorizing a target as “us” versus “not us” by targets’ nationality, religion, and caste (vertical) and participants’ caste membership (horizontal)}
+\centering
+\includegraphics[scale=1]{../figures/figure-3}
+\caption*{\textit{Note.} Dots (•) indicate the most plausible estimate for a given target’s probability of being included in participants’ ingroup, while the shaded ribbons encompass the 67\% (darkest shade), 89\%, and 97\% (lightest shade) most plausible estimates of that probability.
+Pluses (+) indicate the observed proportion of participants who included a given target in their ingroup.
+Comparing predicted and observed proportions shows that the model represents the data reasonably well.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe}
+\label{fig:f3}
+\end{figure}
+
+As Figure~\ref{fig:f3} shows, we also found that how likely participants were to include Indian, Hindu targets in their ingroup varied as a function of both their own and the targets’ group membership.
+As predicted, GM participants (the most advantaged group) included Hindu, GM targets in their ingroup much more often than they included Hindu, SC/ST targets (the most disadvantaged group): $\Pr = .94, [.92, .97]$ versus $\Pr  = .80, [.73, .85]$, $\Delta\Pr = .14, [.09, .21]$.
+Likewise, SC/ST participants included Hindu, GM targets much less often than they included Hindu, SC/ST targets: $\Pr = .88, [.82, .92]$ versus $\Pr = .97, [.95, .98]$, $\Delta\Pr = -.09, [-.05, -.14]$.
+Both GM and SC/ST participants included targets from their own caste group more often than Hindu, OBC targets (the intermediate group): $\Delta\Pr = .04, [.08, >.00]$ and $\Delta\Pr = .17, [.24, .11]$, respectively.
+As hypothesized, we thus found strong evidence that participants from advantaged caste groups espoused social identities that excluded disadvantaged caste groups and vice versa.
+
+Although we did not make clear predictions, we examined whether participants from the intermediate (OBC) group would espouse social identities that included targets from the advantaged (GM) group or the disadvantaged (SC/ST) group.
+Other than SC/ST participants, OBC participants included Hindu, GM targets in their ingroup as often as targets from their own caste group:  $\Pr = .94, [.92, .96]$ versus $\Pr = .95, [.93, .97]$, $\Delta\Pr = -.01, [-.04, .02]$.
+Like GM participants, OBC participants included targets from their own caste group more often than they included SC/ST targets:  $\Pr = .95, [.93, .97]$ versus $\Pr = .87, [.82, .90]$, $\Delta\Pr = .08, [.05, .13]$.
+This shows that participants from the intermediate group espoused social identities that included the most advantaged group, but not the most disadvantaged group.
+
+\subsection{Individual differences}
+
+Models 0--3 showed that group memberships shaped whom participants considered “us” and “not us”, though none of these associations were without exception.
+Models 4--7 examined to what extent individual differences in past experiences and ideological orientations explain why some participants excluded targets from caste and religious outgroups---and why others did not.
+
+First, we compared Models 4--6 which tested whether intergroup contact was associated with how participants categorized Indians from caste and religious outgroups.
+Model 4 extended Model 3 by including contact quantity, positive contact, negative contact, and outgroup friendship as predictors of participants’ categorizations.
+As Table~\ref{tab:t2} shows, Model 4 made more accurate predictions than Model 3.
+Negative contact ($e^\beta = 0.81, [0.72, 0.91]$) and outgroup friendship ($e^\beta = 1.48, [1.28, 1.72]$) were associated with participants’ categorizations, but neither positive contact ($e^\beta = 1.01, [0.87, 1.16]$) nor contact quantity ($e^\beta = 0.99, [0.86, 1.14]$) were.\footnote{An odds ratio of $e^\beta = 1$ means that a predictor does not affect the odds of the relevant outcome; odds ratios of $e^\beta > 1$ and $e^\beta < 1$ mean, respectively, that a predictor makes the relevant outcome more and less likely.} Model 5 included only negative contact and outgroup friendship, and made more accurate predictions than Models 3 and 4.
+Model 6 extended Model 5 by estimating the relationships between contact and categorizations as varying across the four combinations of target caste and religion.
+Comparing the models’ Pseudo-BMA weights, we found that Models 5 ($w = .59$) and 6 ($w = .33$) both contributed to predicting participants’ categorizations.
+As Model 6, however, made somewhat less accurate predictions ($\Delta\textit{ELPD}/\textit{SE} = -0.5$), we selected the more parsimonious Model 5.
+We thus concluded that outgroup friendship and negative contact---but not contact quantity and positive contact---were associated with whom participants considered “us” and “not us”.
+
+Second, we inspected estimates from Model 5 to examine whether the estimated coefficients were in the hypothesized direction.
+Figure~\ref{fig:f4} shows the estimated probabilities of participants categorizing targets as “us” as a function of their contact experiences.
+Across targets and participants, the odds of categorizing an outgroup target as “us” were $e^\beta = 1.48, [1.32, 1.68]$ times higher for each additional standard deviation of outgroup friendship.
+These odds were $e^\beta = 0.81, [0.72, 0.90]$ times lower for each standard deviation of negative contact.
+This means, for example, that GM participants who reported “never” having any negative contact with Muslims were more likely to categorize Indian Muslims as “us” than GM participants who reported “sometimes” having negative contact, $\Delta\Pr = .05, [.09, .03]$.
+GM participants who reported no friendships with Muslims were a lot less likely to include Indian Muslims in their ingroup than GM participants who had 2--5 Muslim friends with whom they “sometimes” spent time, $\Delta\Pr = .18, [.12, .24]$.
+
+\begin{figure}
+\caption{Estimated probability of participants categorizing a target as “us” versus “not us” as a function of the targets’ group memberships (horizontal), the participants’ group memberships (colour), and the reported amount of negative contact and outgroup friendship with the relevant groups}
+\centering
+\includegraphics[scale=1]{../figures/figure-4}
+\caption*{\textit{Note.} GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe}
+\label{fig:f4}
+\end{figure}
+
+Model 7 extended Model 3 by exploring whether social dominance orientation was associated with participants’ categorizations of targets from lower-status outgroups.
+Model 7 found little evidence for associations between participants’ categorizations and their SDO-Dominance scores ($e^\beta = 0.87, [0.69, 1.09]$) or SDO-Egalitarianism scores ($e^\beta = 0.99, [0.79, 1.24]$).
+Together, these findings show that group and individual differences explained whom participants included in their ingroup.
+As expected, past experiences with outgroup members explained why some participants included targets of (objective) caste or religions outgroups in their (subjective) ingroup, when others did not.
+In contrast, ideological orientations did not motivate participants to exclude lower-status groups.
+
+\subsection{Consequences}
+
+After examining potential antecedents, we turned to potential consequences of inclusive social identities.
+We analysed how participants’ categorizations related to their intergroup attitudes, their support for social change, and their perceptions of intergroup threat.
+
+\subsubsection{Intergroup attitudes}
+
+Across eight models, we examined how participants’ target-wise social distance and feeling thermometer ratings varied as a function of the targets’ and participants’ group memberships and of participants’ categorization.
+
+Models 0--3 estimated ratings (on either outcome) as varying across participants but fixed across targets (M0), as varying across target categories and participants (M1), and tested whether SC/ST participants’ responses differed from GM and OBC participants’ (M2), and whether OBC participants’ responses differed from GM participants’ (M3).
+As Table~\ref{tab:t3} shows, Models 1--3 improved upon the predictions of simpler models, showing that participants’ ratings depended on the targets’ and the participants’ group memberships.
+
+\begin{table}
+\caption{Comparison of multivariate linear regression models estimating participants’ social distance (SD) and feeling thermometer (FT) ratings as a function of group differences and target categorizations}
+\centering
+\figureversion{lining, tabular}
+\small
+\begin{tabularx}{\linewidth}{rXr@{~}rrr@{~}r@{~}r@{~}r} \toprule
+\multicolumn{1}{c}{\textbf{(A)}} & \textit{\textbf{Group differences}} & \multicolumn{2}{c}{$R^2$} & \multicolumn{1}{l}{} & \multicolumn{4}{c}{$\Delta\textit{ELPD}/\textit{SE}$}                                                                                    \\ \cmidrule{6-9}
+\#                               & Description                         & SD             & FT             & \textit{w}           & M0                          & M1                           & M2                           & M3                           \\ \midrule
+M0                               & Varying intercept (Participants)    & .26            & .28            & .00                  & {\color[HTML]{E0E0E0} 0.0}  & {\color[HTML]{B2182B} -22.4} & {\color[HTML]{B2182B} -23.3} & {\color[HTML]{B2182B} -23.5} \\
+M1                               & M0 + Varying intercept (Categories  & .39            & .44            & .00                  & {\color[HTML]{2166AC} 22.4} & {\color[HTML]{E0E0E0} 0.0}   & {\color[HTML]{B2182B} -5.7}  & {\color[HTML]{B2182B} -6.4}  \\
+M2                               & M1 + Varying effect (SC/ST)         & .39            & .44            & .00                  & {\color[HTML]{2166AC} 23.3} & {\color[HTML]{2166AC} 5.7}   & {\color[HTML]{E0E0E0} 0.0}   & {\color[HTML]{D6604D} -3.1}  \\
+M3                               & M2 + Varying effect (OBC)           & .40            & .45            & \textgreater .99     & {\color[HTML]{2166AC} 23.5} & {\color[HTML]{2166AC} 6.4}   & {\color[HTML]{4393C3} 3.1}   & {\color[HTML]{E0E0E0} 0.0}   \\ \bottomrule \addlinespace \toprule
+\multicolumn{1}{c}{\textbf{(B)}} & \textit{\textbf{Consequences}}      & \multicolumn{2}{c}{$R^2$} & \multicolumn{1}{l}{} & \multicolumn{4}{c}{$\Delta\textit{ELPD}/\textit{SE}$}                                                                                    \\ \cmidrule{6-9}
+\#                               & Description                         & SD             & FT             & \textit{w}           & M3                          & M4                           & M5                           & M6                           \\ \midrule
+M3                               & Group differences (SC/ST, OBC)      & .40            & .45            & .00                  & {\color[HTML]{E0E0E0} 0.0}  & {\color[HTML]{B2182B} -9.3}  & {\color[HTML]{B2182B} -9.5}  & {\color[HTML]{B2182B} -9.1}  \\
+M4                               & M3 + Fixed effect (Categorization)  & .43            & .47            & .01                  & {\color[HTML]{2166AC} 9.3}  & {\color[HTML]{E0E0E0} 0.0}   & {\color[HTML]{D6604D} -2.6}  & {\color[HTML]{E0E0E0} -1.5}  \\
+M5                               & M4 + Varying effect (Categories)    & .43            & .48            & .88                  & {\color[HTML]{2166AC} 9.5}  & {\color[HTML]{4393C3} 2.6}   & {\color[HTML]{E0E0E0} 0.0}   & {\color[HTML]{E0E0E0} 1.2}   \\
+M6                               & M5 + Interaction (SC/ST, OBC)       & .43            & .48            & .11                  & {\color[HTML]{2166AC} 9.1}  & {\color[HTML]{E0E0E0} 1.5}   & {\color[HTML]{E0E0E0} -1.2}  & {\color[HTML]{E0E0E0} 0.0}  \\ \bottomrule \addlinespace
+\end{tabularx}
+\label{tab:t3}
+\caption*{\textit{Note.} $w$ is the weight of each model based on its relative out-of-sample prediction accuracy.
+$\Delta\textit{ELPD}/\textit{SE}$ is the difference in out-of-sample prediction accuracy between each pair of models, divided by its standard error.
+For a conventional interpretation, consider the critical values to be $|\Delta\textit{ELPD}/\textit{SE}| > 1.96$ for $p < .05$, 2.58 for $p < .01$, and 3.29 for $p < .001$ in a two-sided null-hypothesis significance test.}
+\end{table}
+
+Models 4--6 tested whether participants who categorized a target as “us” rated that target more favourably than participants who categorized the same target as “not us”.
+Models estimated this difference as constant across target categories (M4), as varying across target categories (M5), and tested whether this difference depended on participants’ caste memberships (M6).
+Models 4 and 5, but not Model 6, made better predictions than less complex models, showing that how favourably participants felt toward a target depended on whether they had categorized that target as “us” or “not us”, and that the size of this difference depended on the targets’---but not the participants’---group memberships.
+
+Figure~\ref{fig:f5} shows the estimated social distance and feeling thermometer ratings as a function of target categorizations and participants’ group memberships.
+For all categories, participants felt more comfortable sharing a room with targets whom they categorized as “us” than with targets they categorized as “not us”.
+This difference was smallest for Indian, Hindu, GM targets ($\beta = 0.69, [0.33, 1.03]$; Cohen’s $d = 0.30, [0.14, 0.44]$) and greatest for foreign, Hindu targets ($\beta = 1.39, [1.14, 1.64]$; Cohen’s $d = 0.60, [0.49, 0.71]$).
+We found a similar pattern for feeling thermometer ratings.
+The difference was smallest for Indian, Hindu, OBC targets ($\beta = 8.3, [3.9, 12.7]$, Cohen’s $d = 0.25, [0.12, 0.39]$) and greatest for foreign, Hindu targets ($\beta = 21.1, [17.9, 24.4]$, Cohen’s $d = 0.64, [0.54, 0.74]$).
+Feeling thermometer and social distance ratings were highly correlated ($r = .58, [.56, .60]$).
+Categorizing a target as “us” was thus associated with more warmth and less social distance toward that target.
+
+\begin{figure}
+\caption{Posterior probabilities of social distance (\textbf{A}) and feeling thermometer (\textbf{B}) ratings as a function of target categorizations}
+\centering
+\includegraphics[scale=1]{../figures/figure-5}
+\caption*{\textit{Note.} Points and diamonds mark the estimated mean ratings for targets categorized as “us” and “not us”, respectively.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe}
+\label{fig:f5}
+\end{figure}
+
+\subsubsection{Support for social change}
+
+Across four models, we examined how support for reservation policies benefiting SC/ST, OBC, and Muslim applicants varied as a function of the participants’ group memberships, their contact experiences, and their target categorizations.
+Model 0 estimated distinct means for the three target categories (SC/ST, OBC, Muslims).
+Model 1 extended Model 0 by estimating distinct means for GM, OBC, and SC/ST participants.
+As Table~\ref{tab:t4} shows, Model 1 made more accurate predictions than Model 0, showing that participants’ group memberships shaped their policy support ratings.
+
+\begin{table}
+\caption{Comparison of multivariate linear regression models estimating participants’ policy support and perceived (dis-)advantage ratings as a function of group differences, intergroup contact, and target categorizations}
+\centering
+\figureversion{lining, tabular}
+\small
+\begin{tabularx}{\linewidth}{rXrrrrrr} \toprule
+\textbf{(A)} & \textit{\textbf{Policy support}}            & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{4}{c}{$\Delta\textit{ELPD}/\textit{SE}$}                                                                                \\ \cmidrule{5-8}
+\#           & Description                                 & $R^2$          & \textit{w}           & M0                         & M1                          & M2                          & M3                          \\ \midrule
+M0           & Group differences (Categories)              & .00                  & .00                  & {\color[HTML]{E0E0E0} 0.0} & {\color[HTML]{B2182B} -6.8} & {\color[HTML]{B2182B} -6.2} & {\color[HTML]{B2182B} -6.7} \\
+M1           & M0 + Fixed effects (SC/ST + OBC)            & .22                  & .60                  & {\color[HTML]{2166AC} 6.8} & {\color[HTML]{E0E0E0} 0.0}  & {\color[HTML]{F4A582} 2.4}  & {\color[HTML]{E0E0E0} 0.3}  \\
+M2           & M1 + Fixed effects (NC + OF)                & .24                  & .01                  & {\color[HTML]{2166AC} 6.2} & {\color[HTML]{92C5DE} -2.4} & {\color[HTML]{E0E0E0} 0.0}  & {\color[HTML]{FDDBC7} -1.7} \\
+M3           & M1 + Fixed effects (Categorization)         & .23                  & .39                  & {\color[HTML]{2166AC} 6.7} & {\color[HTML]{E0E0E0} -0.3} & {\color[HTML]{D1E5F0} 1.7}  & {\color[HTML]{E0E0E0} 0.0}  \\ \bottomrule \addlinespace \toprule
+\textbf{(B)} & \textit{\textbf{Perceived (dis-)advantage}} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{4}{c}{$\Delta\textit{ELPD}/\textit{SE}$}                                                                                \\ \cmidrule{5-8}
+\#           & Description                                 & $R^2$ & \textit{w}           & M0                         & M1                          & M2                          & M3                          \\ \midrule
+M0           & Group differences (Categories)              & .00                  & .04                  & {\color[HTML]{E0E0E0} 0.0} & {\color[HTML]{FDDBC7} -1.8} & {\color[HTML]{E0E0E0} -0.3} & {\color[HTML]{E0E0E0} -1.2} \\
+M1           & M0 + Fixed effects (SC/ST + OBC)            & .04                  & .67                  & {\color[HTML]{D1E5F0} 1.8} & {\color[HTML]{E0E0E0} 0.0}  & {\color[HTML]{D1E5F0} 1.7}  & {\color[HTML]{E0E0E0} 0.7}  \\
+M2           & M1 + Fixed effects (NC + OF)                & .06                  & .04                  & {\color[HTML]{E0E0E0} 0.3} & {\color[HTML]{FDDBC7} -1.7} & {\color[HTML]{E0E0E0} 0.0}  & {\color[HTML]{E0E0E0} -1.1} \\
+M3           & M1 + Fixed effects (Categorization)         & .05                  & .25                  & {\color[HTML]{E0E0E0} 1.2} & {\color[HTML]{E0E0E0} -0.7} & {\color[HTML]{E0E0E0} 1.1}  & {\color[HTML]{E0E0E0} 0.0} \\ \bottomrule \addlinespace
+\end{tabularx}
+\label{tab:t4}
+\caption*{\textit{Note.} $R^2$ is the mean $R^2$ across categories.
+$w$ is the weight of each model based on its relative out-of-sample prediction accuracy.
+$\Delta\textit{ELPD}/\textit{SE}$ is the difference in out-of-sample prediction accuracy between each pair of models, divided by its standard error.
+For a conventional interpretation, consider the critical values to be $|\Delta\textit{ELPD}/\textit{SE}| > 1.96$ for $p < .05$, 2.58 for $p < .01$, and 3.29 for $p < .001$ in a two-sided null-hypothesis significance test.}
+\end{table}
+
+Model 2 extended Model 1 by including outgroup friendship and negative contact as predictor variables: Model 2 estimated to what extent contact with the most advantaged (GM) caste group was associated with support for policies benefiting their own group among participants from the most disadvantaged (SC/ST) and intermediate (OBC) caste groups.
+Model 2 also estimated to what extent contact with SC/ST, OBC, and Muslim people was associated with support for policies benefitting these groups among participants not from these groups.
+As Model 2 made less accurate predictions than Model 3, we found no evidence that intergroup contact decreases policy support among the disadvantaged or increases policy support among the advantaged.
+
+Model 3 extended Model 1 by including participants’ aggregated target categorizations as predictor variables: Model 3 tested whether the proportion of GM targets that SC/ST and OBC participants had considered “us” was associated with their support for policies benefiting their own group.
+Model 3 also tested whether the proportions of SC/ST, OBC and Muslim targets that participants had considered “us” was associated with support for policies benefitting these groups among participants not from these groups.
+Models 1 ($w = .60$) and 3 ($w = .39$) both contributed to predicting participants’ policy support ratings.
+As Model 3, however, made somewhat less accurate predictions ($\Delta\textit{ELPD}/\textit{SE} = -0.4$), we selected the more parsimonious Model 1.
+We thus concluded that participants’ policy support ratings depended on their own group memberships, but not on their contact experiences and target categorizations.
+
+\begin{figure}
+\caption{Posterior probabilities of policy support ratings for different target groups (right) by participants’ caste ingroup (left)}
+\centering
+\includegraphics[scale=1]{../figures/figure-6}
+\caption*{\textit{Note.} Diamonds are the point estimates of each mean rating while intervals encompass the 97\% most plausible estimates.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.}
+\label{fig:f6}
+\end{figure}
+
+\begin{figure}
+\caption{Posterior probabilities of perceived (dis-)advantage ratings for different target groups (right) by participants’ caste ingroup (left)}
+\centering
+\includegraphics[scale=1]{../figures/figure-7}
+\caption*{\textit{Note.} Diamonds are the point estimates of each mean rating while intervals encompass the 97\% most plausible estimates.
+GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.}
+\label{fig:f7}
+\end{figure}
+
+Figure 6 shows the estimated group differences in policy support ratings.
+We found that policy support was strongly aligned with participants’ caste interests.
+SC/ST participants supported reservations for both SC/ST and OBC students, while OBC participants only supported reservations for their own group.
+GM participants, for the most part, opposed reservation policies.
+We estimated a similar set of four models with participants’ perceived (dis-)advantage ratings as outcome variables.
+As Table~\ref{tab:t4} shows, we again found Model 1 to make the most accurate out-of-sample predictions.
+Figure  7 shows the estimated group differences in perceived (dis-)advantage ratings.
+We found that, contradicting prevailing social inequalities, GM and OBC participants rated their own groups’ lives as substantially harder than SC/ST members’ lives.
+Contrary to our predictions, we did not find more inclusive identities or intergroup contact to be associated with perceived (dis-)advantage or policy support ratings.
+
+Intergroup threat
+We also explored to what extent participants’ perceptions of realistic and symbolic threat depended on how inclusive their identity construals were.
+Results from a series of multilevel models showed that participants reported more realistic ($M = 3.62, [3.49, 3.75]$) than symbolic ($M = 3.21, [3.09, 3.33]$) threat from (same-religion) Dalits, but more symbolic ($M = 3.47, [3.34, 3.61]$) than realistic ($M = 3.23, [3.06, 3.38]$) threat from (different-religion) Muslims.
+Contrary to predictions, we did not find that participants felt less threatened by Muslims and Dalits if they categorized more targets from these outgroups as “us” (for details, see Appendix E).
+
+Overall, we thus found that when participants included a person in their ingroup, they had, on average, more favourable attitudes to and desired less social distance from that person.
+Participants’ categorizations, however, were unrelated to perceptions of intergroup threat and relative (dis-)advantage and to support for affirmative action.
+
+\section{Discussion}
+
+We examined how people construct their social identities from multiple social categories and how more inclusive identities relate to intergroup contact, outgroup attitudes, and support for social change.
+As hypothesized, we found that cross-group friendship was associated with more inclusive identities which, in turn, were associated with more favourable outgroup attitudes.
+Negative contact was associated with less inclusive identities.
+Contrary to past research, neither intergroup contact nor more inclusive identities were associated with perceived (dis-)advantages or support for affirmative action.
+Below, we discuss implications, strengths, and limitations of this research.
+
+\subsection{Implications}
+
+Our research has implications for understanding intergroup relations in unequal societies.
+Among advantaged groups, our research documented patterns of inclusion/exclusion that map onto persistent social divides.
+Participants from dominant caste groups tended to exclude subordinate caste groups from the common ingroup; participants from the dominant Hindu religion tended to exclude Indian Muslims.
+Among disadvantaged groups, we found more complex patterns.
+Participants from intermediate caste groups (OBC, Other Backward Classes) faced the choice of aligning themselves with dominant caste groups (GM, General Merit) or forming a coalition with subordinate caste groups (SC/ST, Scheduled Caste/Scheduled Tribe).
+OBC participants tended to include dominant GM targets and exclude subordinate SC/ST targets, thus choosing derogation over coalition \parencite{craig_coalition_2012}.
+Similarly, SC/ST participants rejected a solidarity-based social identity that includes Indian Muslims.
+
+Our findings suggest that cross-group friendship can help to overcome these divisions by fostering social identities that include Indians of all castes and religions.
+As more inclusive identities were related to less social distance and more warmth toward caste and religious minorities, our research suggests that positive contact could help reduce interpersonal discrimination and violence against these groups.
+In line with recent research \parencite{hayward_toward_2017}, we found that negative contact could exacerbate social divisions by fostering less inclusive identities.
+More broadly, our research speaks to \emph{how} contact reduces prejudice \parencite{pettigrew_how_2008}.
+Our findings support arguments \parencite{gaertner_reducing_2000, pettigrew_intergroup_1998} that contact can reduce prejudice, in part, by changing how we understand our social identities.
+
+Our research also examined support for social change.
+Contrary to past research, neither positive nor negative contact \parencite{hayward_how_2018, reimer_intergroup_2017} were associated with support for social change---or perceptions of relative advantage and disadvantage---in advantaged \parencite{selvanathan_whites_2018, dixon_intergroup_2007} and disadvantaged \parencite{dixon_beyond_2012} groups.
+Similarly, more inclusive identities were not associated with opposition to affirmative action among the disadvantaged \parencite{dixon_attitudes_2012}.
+Features of the participants’ situation might explain this discrepancy.
+As university students, participants have personally experienced the impact of reservation policies.
+For SC/ST and OBC students, reservation policies facilitated admission to state-funded universities.
+This experience might explain why these students strongly support reservation (at least for their own group).
+For GM students, reservation policies thwarted admission to state-funded universities.
+This experience might explain why, in contrast to societal realities, GM students saw themselves at a disadvantage relative to other caste groups \parencite[see][]{norton_whites_2011}.
+
+Our research has practical implications for intergroup relations in today’s India.
+On the one hand, our findings help explain recent developments in Hindu---Muslim relations.
+Since we conducted this study, the Hindu-nationalist BJP government was re-elected and enacted the Citizenship Amendment Act which excluded Muslims from a newly-opened path to Indian citizenship \parencite{noauthor_citizenship_2019}.
+Many Indians, including Hindus, protested the bill and for a more inclusive nationalism.
+These protests, in turn, were met with violent backlash, fomented by BJP politicians, culminating in an anti-Muslim pogrom in Delhi \parencite{kamdar_what_2020}.
+In line with our findings, these developments highlight the deleterious consequences of exclusive social identities.
+On the other hand, our findings point to cross-group friendship as a means to foster inclusive social identities.
+Reservation policies, which reserve seats for caste and (in some states) religious minorities, make universities promising avenues for intergroup contact.
+Just as our findings revealed strong opposition to reservation policies by advantaged caste groups, our findings thus also provide evidence of the importance of reservation policies for facilitating intergroup contact.\footnote{This is not to suggest that these instrumental benefits matter more than their role in addressing past and current injustices.}
+
+\subsection{Strengths and limitations}
+
+Our findings show that the triple crossed-categorization task \parencite{van_dommelen_construing_2015} is an intuitive and informative method for studying social identification across multiple categories.
+We adapted the task to answer new questions about social identification.
+First, we recruited respondents from multiple groups, allowing us to study both individual and group differences \parencite[see also][]{brankovic_social_2016}.
+Second, we estimated responses as varying across targets and participants using multilevel models.
+This allowed more fine-grained analyses than the quantitative and qualitative summaries provided by van Dommelen and colleagues, and may explain why we found more consistent effects of intergroup contact.
+Together, these changes open the task to a broader range of research questions.
+
+Our research also improves upon other approaches to studying identification across multiple social categories.
+For example, we could have tested our hypotheses by examining whether intergroup contact leads participants to identify with a more inclusive common ingroup (Indians) instead of their less inclusive subordinate ingroups (Hindus).
+A problem with this approach is that people tend to perceive the common ingroup as more similar to their own narrow ingroup than to subordinate outgroups \parencite{wenzel_ingroup_2003}, thus excluding outgroup members from the common ingroup.
+Instead, we allowed participants to decide where to draw the line between ingroup and outgroup and to thus determine the content of their subjective ingroup.
+Another strength of our research is that we studied intergroup relations in a context underrepresented in psychological research.
+Our research is one of few studies examining the effects of intergroup contact on Hindu–Muslim relations in South Asia \parencite[for other examples, see][]{islam_dimensions_1993, tausch_relationships_2009} and is, to our knowledge, the first study examining the effects of intergroup contact on caste relations.
+
+Despite these strengths, our research is qualified by some methodological limitations.
+We presented all participants with the same combination of target groups.
+This within-subjects design cannot determine whether the observed construals generalize beyond the specific combination of stimuli used.
+For example, participants might have relied on the specific combination of stimuli to rank target groups and to decide where to draw the line between “us” and “not us”---suggesting that we would find smaller group differences in a between-subjects design.
+Another limitation is that the within-subjects design limited the number of categories we could consider without overburdening participants.
+Class, rather than caste, could explain why some participants excluded targets from disadvantaged outgroups.
+Gender could have intersectional effects on whom participants consider “us” and “not us”---for example, by activating different stereotypes about Muslim men and Muslim women.
+Future research should combine the advantages of within- and between-subjects designs by using a planned missingness design in which each participant views a sample of stimuli from a larger set that includes more combinations of categories than is feasible in a within-subjects design.
+
+Another limitation is that we measured categorization and attitudes for the same targets.
+This design cannot rule out that these variables measure the same construct, rather than represent a genuine association across constructs.
+One reason to think so is that intergroup threat, a more distal measure, did not correlate with participants’ categorizations.\footnote{An explanation might be that threat perceptions stem from economic anxieties (e.g., fearing affirmative action as a threat to one’s career) and ideological beliefs (e.g., Hindutva), rather than identity processes.} A final limitation is we did not manipulate intergroup contact.
+This design cannot rule out confounding explanations of the observed relationship between contact and identification.
+Experimental studies tend to manipulate short-term ‘intergroup interactions’ rather than long-term ‘intergroup contact’ (MacInnis \& Page-Gould, \cite*{macinnis_how_2015}; for rare exceptions, see Laar et al., \cite*{laar_effect_2005}, and Shook \& Fazio, \cite*{shook_interracial_2008}).
+Our findings suggest, however, that cross-group friendship, not superficial interaction, is required for people to change their social identities.
+Future research should address these limitations by assessing intergroup bias with proximal and distal measures and by testing the hypothesized relationships over time.
+
+\section{Conclusion}
+
+To conclude, in a unique study of caste, religion, and nationality in South India, we found correlational evidence that intergroup contact can change not only how we see others, but also how we see ourselves---that is, that intergroup contact can foster more inclusive social identities and thus improve intergroup relations in unequal societies.
+Fostering more inclusive identities, however, does not seem to overcome entrenched opposition to (or undermine support for) affirmative action.
+
+\newpage
 

### 2020-08-31 scripts/results_consequences.R

@@ -2,6 +2,9 @@ rm(list = ls())
 
 # Notes -------------------------------------------------------------------
 
+  #########################################################################
+  # Adjust n_cores to the number of CPU cores you want to use.            #
+  #########################################################################
 
 # Library -----------------------------------------------------------------
   

### 2020-08-31 scripts/results_policy_support.R

@@ -2,6 +2,9 @@ rm(list = ls())
 
 # Notes -------------------------------------------------------------------
 
+  #########################################################################
+  # Adjust n_cores to the number of CPU cores you want to use.            #
+  #########################################################################
 
 # Library -----------------------------------------------------------------
 

### 2020-08-31 manuscript/manuscript.tex
correct typo

@@
 
-Intergroup threat
+\subsubsection{Intergroup threat}
+
 We also explored to what extent participants’ perceptions of realistic and symbolic threat depended on how inclusive their identity construals were.
